### 2021-04-21 plan.tex
Added plan draft and MAPF paper summary

\documentclass[a4paper,10pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\usepackage[backend=bibtex]{biblatex}
\addbibresource{sources.bib}
\usepackage{babel}

\title{Research Plan for MAPF with matching using ICTS (draft)}
\author{Thom van der Woude}
\date{\today}

\begin{document}
\maketitle

\section*{Background of the research}
The Dutch Railways (NS) company needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day. The problem of scheduling the trains to achieve this is the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020} and it is a typical NP-hard problem. To gain more insight into the characteristics of this many-sided problem and in particular the feasibility of its instances, a relaxation is considered: the multi-agent path finding problem extended with a matching sub-problem or matching multi-agent pathfinding (hereafter MMAPF). 
\paragraph{Multi-agent pathfinding} MAPF is a well-studied problem, a general overview is given in \cite{stern2019}. Somewhat informally, it is the problem of routing multiple agents on a graph (often a 4-connected grid) to multiple distinct destinations without any conflicts, with definitions of what constitutes a conflict varying; in this project, conflict is taken to mean 'occupy the same node' or 'traverse the same edge in opposite directions at the same time-step'. Typically one of two things is minimized: the sum of individual costs (SIC), or the length of the longest path (also known as \textit{makespan}). Algorithms for MAPF are often designed to find optimal solutions so that for instance the SIC is minimal.

\paragraph{Matching Multi-agent pathfinding as TUSS relaxation}
For a problem to be a relaxation of TUSS, it has to be at most as difficult as TUSS for each instance assuming some suitable mapping from the original problem to the relaxation. In one respect TUSS is somewhat easier to solve than classical MAPF: trains are partitioned into types (equivalence classes, often denoted by colours) and destinations are labelled as destinations for trains of one specific type. This means that as far as this matching is concerned, for any valid matching there can be many equivalent permutations, so that in different optimal solutions a single train might have different destinations. As a consequence, this matching has to be modelled in the relaxed problem, resulting in MMAPF. Contrast this variation with both normal MAPF where each agent only has one target and anonymous MAPF where agents can be assigned to any target. See \cite{ma2016} for a discussion of MAPF with matching.

\paragraph{Solving MAPF with matching}
There exist many different algorithms for solving the MAPF problem. 
Some current examples include conflict-based search\cite{sharon2015}, branch-and-cut-and-price\cite{lam2019}, A* with Independence detection and Operator Decomposition\cite{standley2010}, M*\cite{wagner2011} and Increasing Cost Tree Search\cite{sharon2011}. 
None of these are designed to work with matching out-of-the-box, so a naive way to incorperate matching into MAPF would be to generate legal matchings in preprocessing and enumerate these until one is found for which MAPF finds a solution. 
However, the challenge of this research project is to find ways using heuristics, preprocessing or other methods to generate good matchings that result in feasible MAPF problems and ideally efficient MAPF solutions. 
Similar to a previous iteration of this research project, we each chose an algorithm to work with as a start of our respective subprojects: I will be working on incorperating matching into Increasing Cost Tree Search MAPF-solving.

\paragraph{TUSS to MAPF with matching}
Finding a suitable mapping between TUSS and MMAPF instances is an unsolved problem: intuitively it is desirable to preserve feasibility so that there can never be a feasible TUSS instance mapped to an infeasible MMAPF instance, but perhaps it should be acceptable for the mapping to turn infeasible TUSS instances into feasible MMAPF instances, as the latter problem is a relaxation of the former. In any case, a good mapping that preserves key instance properties is important for MMAPF to be practically useful as a relaxation of TUSS so should time allow this would be interesting to consider.

\section*{Research Question}
The key research question that I aim to answer in this subproject is this: How can the Increasing Cost Tree Search method be used or adapted to efficiently find solutions to Multi-agent path-finding with matching? Relevant subquestions are as follows, where matching is to be understood as a single legal matching of trains to targets (departures) of their respective types:\footnote{These subquestions were taken from the initial project proposal at \url{https://projectforum.tudelft.nl/course_editions/39/projects/977}}
\begin{enumerate}
	\item Can we use a heuristic or preprocessing step to calculate a matching? And can we do so such that the resulting instance with the fixed matching is feasible?
	\item Can we use instance features to (help) determine an efficient matching?
	\item How can we improve upon a matching once one has been found?
\end{enumerate}

\section*{Method}
As a first step, an existing implementation of Increasing Cost Tree Search has to be found or a new one has to be implemented following the paper if no algorithm is publicly available. Next, the generation of agent-target matchings is to be implemented, which are translated into MAPF instances to be solved using ICTS. It might be possible to collaborate within the peer group here as we all have to do this step. Once this task has been completed, the project takes a more theoretical turn and I intend to study literature specific to MAPF with colours/teams or similar problems with the additional matching constraint in order to work towards answering the subquestions. Here also I hope to collaborate with my peer group and exchange ideas, perhaps about how properties of instances might be exploited in finding matchings or similar concepts.

\section*{Planning of the (first week of the) research project} 
For now I assume that reading a paper, looking into relevant citations and making a summary for comprehension takes around 3-4 hours which is also reflected in my planning. Also note that I take the tasks this first week to be seperate from those to be described by the end of this week in Method.
\begin{enumerate}
	\item[19-4 ] 
	\begin{enumerate}
		\item[10:45] Start of research project
		\item[12:45] Meeting with peer group
		\item[13:45] Assignment of subproject (ICTS)
		\item[15:45] Planning of first week (deadline at 19-4 23:59).
	\end{enumerate}
	\item[20-4] 
	\begin{enumerate}
	\item[9:00] Revise information literacy, find relevant conferences/journals for this research project
	\item[10:00] Read and summarize \cite{stern2019}
	\item[15:00] Read and summarize \cite{mulderij2020}
	\end{enumerate}
	\item[21-4]
		\begin{enumerate}
		\item[9:00] Read and summarize \cite{sharon2011}, the original ICTS paper.
		\item[13:00] Read and summarize \cite{standley2010}
		\item[15:00] Look into other important citations in \cite{sharon2011}
	\end{enumerate}
	\item[22-4] \begin{enumerate}
		\item[9:00] Look into possible existing ICTS implementations that can be used (important for planning).
		\item[10:00] Survey MAPF literature in a breadth-first way in order to flesh out background of research. Also think about research question formulation and corresponding methods.
		\item[13:00] Meet with group and supervisor on Teams.
		\item[14:00] Continue planning the research.
	\end{enumerate}
	\item[23-4]\begin{enumerate}
		\item[9:00]  Finish research plan (official deadline is at 25-4 23:59 but target deadline at 23-4 23:59). If there is time remaining, start familiarizing with the MAPF web API that our peer group 'inherited' from the previous instance of this project, and start implementing ICTS if no suitable existing implementation was found the previous day. (note: this is just one block as I am not sure how long this will take given that planning is rather hard)
	\end{enumerate}
\end{enumerate}
\printbibliography

\end{document}

### 2021-04-21 tuss.tex
Added rough summary of TUSS paper

\documentclass[a4paper,10pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{marginnote}
\include{prelude}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\usepackage[backend=bibtex]{biblatex}
\addbibresource{sources.bib}
\usepackage{babel}

\title{Reviewed: Train Unit Shunting and Servicing: a Real-Life Application of Multi-Agent Path Finding}
\author{Thom van der Woude}
\date{\today}

\begin{document}
	\maketitle
	\paragraph{First run-through}
	Only heuristics can solve instances of the full TUSS problem currently, and little is known about the properties of the found solutions. Bounds for quality of heuristic solutions to TUSS instances are needed: only then can you really know what still can be achieved with current shunting yard capacity and an increasing number of trains, and can you say whether new investment is needed. This is why analysis of a relaxation is proposed as a way to establish bounds.

	MAPF: abstract collision-free routing for robots/automated vehicles through environments.

	Train Unit Shunting Problem (TUSP): the problem of parking and matching arriving train units to departures. Does not consider servicing at the yard! Maintainance/servicing tasks added as extensions, eventually resulting in the full Train Unit Shunting and Servicing problem: \cite{Artigues2014} first introduced full problem statement. Also showed only heuristic solutions are currently possible for practical instances. It envelopes everything that happens to a train outside of brining people from A to B. So the shunting of trains integrated with the scheduling of various servicing activities.
	"The  main  objective  of  this  work  is  therefore  to  identify  whether  MAPF models (and algorithms) can be used or extended to provide a relaxation of the TUSS problem. The contributions of this paper include an introduction of TUSS from the viewpoint of MAPF, and an analysis of similarities and differences to arrive at a relaxation of TUSS based on MAPF"

	Railway network: nodes/hubs are major cities. Hubs have both a station (for transport) and some yards (for shunting/servicing). Transport time-tables dictate the required output of the yards, as tuples of departure times and traintypes, but also when trains of certain types become available for further transport or service after reaching their destination. There is also a maintenance program dictating what tasks are to be done for specific train-types, dpeending on the state of the vehicle.

	"Informally speaking, the objective of the Train  Unit  Shunting  and  Service Problem is  to  find  a  feasible  schedule  for  all  activities  required  to  take  train units from a station platform to a yard, find conflict-free routes to tracks that are needed for the trains to get serviced and parked, and deliver the trains to the  transportation  process  as  specified,  while  respecting  all  kinds  of  resource constraints."

	Sub-problems: matching problem between trains to be delivered to transport system and those arriving/present in yard. There is also the resource-constrained scheduling of allocating service resources to trains that have to be serviced. Should consider conditional tasks. There is also the staff scheduling and rostering problem: staff can only drive trains for so long per day and so on. Then the parking problem: where to put the trains (that are perhaps waiting to be serviced)? This is like bin-packing. Then there is the coupling and decoupling problem to account for incombing and outbound train configurations, and the routing problem of driving trains from and to the yard without conflicts with transport/cargo trains and also visiting appropriate servicing/parking tracks.

	Take-away: there is a lot of complexity, a lot of things that ideally should be planned at once. Current approach: plan sequentially: first solve matching for decoupled train units, schedule maintenance tasks and so on.

	Bounds for hub capacity: depend on planning approach, 'dynamic' planning is used these days using up-to-date train-data. Current relaxed problem: models all subproblems except routing. Relaxed problem should be complete: no feasible solution to original problem should be infeasible when relaxed (so discarded)

	Related work: \cite{Freling2002} first mathematically modelled TUSP with track assignment and matching considered seperately. From there many model improvements to eventually TUSS. Only heuristic solutions, things like annealing and machine learning/local search really seem to work.

	A complete solver is needed to show feasibility or infeasibility of instances.

	MAPF has already been solved at scale (see CBS, BCP), TUSS has not. Collision between agents? Branch and consider subproblems recursively.

	Novelty of paper: relaxations of TUSS for working towards solving TUSS at scale.
	\paragraph{MAPF definition that is extended}
	MAPF statement: different from that other one with actions as functions. Uses a space-time graph (time-extended graph). Given connected undirected graph $G = (L,E)$ with
	 locations $l \in L$, let $V = L \times \mathbb{Z}_+$ and let each $v = (l,t) \in V$ represent a combination of a location $l$ and time $t$. Now define the time-extended edge set $\hat E \subset V \times V$ with $e = (v_1,v_2) = ((l_1,t_1),(l_2,t_2))\in \hat E$ if and only if $t_2  = t_1 + 1$ and $(l_1,l_2)\in E$ or $l_1 = l_2$. Its reverse is defined as $e' = ((l_1,t_2),(l_2,t_1)) \in \hat E$ In words, this means that $\hat E$ represents points in space that can be reached at the next time-step if a certain action is chosen at the present time-step. Let $c(e) = 1$ denote the cost for each $e\in \hat E$. Let $a \in A$ be an agent with start and goal locations $s_a,g_a\in L$. A path $\pi$ of length $k\in\mathbb{Z}_+$ is a vector of locations $(l_0,l_1,\ldots,l_{k-1})$ where $l_0 = s_a, l_{k-1} = g_a$ and $((l_t,t),(l_{t+1},t+1))\in E_t$ for all $t\in\{0,1,\ldots,k-2\}$. For $t>k$ the agent is assumed to remain at $g_a$.

	 What defines a solution then? A set of paths so that each vertex $v = (l,t)\in V$ is visited at most once and each edge $e$ and its reverse $e'$ are also visited in total at most once. Compare this to the more tedious formulation where feasible solutions had a quite complicated definition.

	 Minimization: is there a set of paths $p_a$ with $a\in A$ such that the total cost of all edges in all paths $\sum_{a\in A} c(\pi_a) \leq k$ for some bound $k$? This is a PSPACE-complete decision problem.

	 Note: matching is needed for MAPF to possibly be a relaxation of TUSS.

	 Idea for instance translation: trains as agents, shunting yard as graph with tracks being represented by  a number of nodes (optimistic about the number of trains that could fit on it by dividing length by shortest train, rounding up). The goal is to now find paths to these tracks on which certain services can be performed so that trains collide neither on tracks or abstractly in resource allocation.

	 \paragraph{Extensions}
	 Approach: starting with MAPF with matching, define series of progressively more detailed relaxations of TUSS.

	 Second extension: direction of movement of trains is factored in. Third: set of service tasks is included for each agent. Fourth, some additional possible extensions in brief.

	 Matching: a bit like multi-commodity flow problem. Compositions of train units are set to leave the yard for transport, but unit identity is irrelevant, only type is considered. In reality these are coupled but this is first left out: it also only relaxes the problem further formally. Key assumption: as many train units of each type arrive as depart for the total problem instance. However, each agent $a$ is assigned an expected arrival time $t$ so that it's start node is $(l,t)\in V$ (not in $L$!), and also get assigned a type $o\in O$. Similarly, goal nodes get a $t$ so that they are also in $V$ and are marked with a certain train type that is to leave at that place and time. So $g = \{g_1 = (l_1,t_1,o_i),\ldots, g_n\}$.

	 In practice you could have $t=0$ for all 'arrivals'/start nodes and fix departure times with the problem still being a relaxation.

	 Direction of movement extension would have it cost $c_{rev}$ to reverse direction at a node. This is done by turning each node $v$ into a $v_l,v_r$ pair indicating leftward or rightward movement and an edge with cost $c_{rev}$ between them (and the implicit constraint that there can be at most one agent in total in $v_l,v_r$). This turns the problem into a variation of weighted MAPF.

	 Including service tasks is important for the relaxation to really be relevant to TUSS and not just something like TUSP. Service tasks can be modelled as waypoints that agents should pass on their path. This means that on the per-agent level, you should do something not unlike TSP. Such a formulation ensures that order that the tasks are performed in is not considered, only completion of all tasks is and that agents can move over 'task'-nodes like any other location on the graph, possibly temporarely blocking other agents that need to be serviced there and so on.

	 Other extensions:
	 Some locations cannot be used for parking (track changes/platforms): waiting is limited to few time-steps. Removing all wait edges there may not yield a relaxation always.

	 The relation between train units, their servicing and trains as sequences of units is still an open question in modelling TUSS relaxations.

	 How to model tracks more realistically? Pair train types with lengths and add constraints so that the trains on the nodes making up a track do not exceed the total length of the modelled track.

	 Planning of personnel is important: drivers, maintenance crews, cleaners. Each have their expertise, are time-limited, and also have to physically make their way from one service track or train to the next. You could argue that when you want to learn the raw top capacity of an expensive shunting yard, you should not think about this too much.

	 Next: you could star tlooking at motion-planning-like things: trains have variable speed, changing momentum takes time, and because of this and other safety requirements there are limits on speed and the minimum time between two trains crossing the same track change and similar locations. Formulating this as strictly a relaxation is difficult (you can easily be too strict).

	 \paragraph{Conclusion}
	 There are many practical details in TUSS: many subproblems to consider and factor in. To work towards upper-bound analysis, the MAPF with matching relaxation is considered and a naïve method of converting between TUSS and relaxed MAPF with matching instances is given. The space-time-graph formulation is interesting as it enables simple modelling of arrival and departure times of different units. Direction and cost of reversal can easily be modelled, although it does require considering the properties of weighted MAPF. Task waypoints can model servicing/maintenance work that has to be done.

	 Something totally different: consider restrictions rather than relaxations to limit the search for solutions.

	 Lastly: there is more to TUSS and therefore relaxations than feasibility: cost in terms of personnel and so on is also relevant and should ideally be minimized. Practically, this could be done by minimizing simultaneous actions in solutions. At this point there simply isn't much 'choice' in picking solutions however: you just have to hope that what the heuristic search outputs is good.
	\printbibliography

\end{document}

### 2021-04-25 plan.tex
Finished basic research plan

@@
 \geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
-\usepackage[backend=bibtex]{biblatex}
+\usepackage[backend=biber,style=ieee]{biblatex}
 \addbibresource{sources.bib}
@@
 
-\title{Research Plan for MAPF with matching using ICTS (draft)}
+\title{Research Plan for MAPF with matching using ICTS}
 \author{Thom van der Woude}
@@
 	\section*{Background of the research}
-The Dutch Railways (NS) company needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day.
-The problem of scheduling the trains to achieve this is the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020} and it is a typical NP-hard problem.
-To gain more insight into the characteristics of this many-sided problem and in particular the feasibility of its instances, a relaxation is considered: the multi-agent path finding problem extended with a matching sub-problem or matching multi-agent pathfinding (hereafter MMAPF).
-\paragraph{Multi-agent pathfinding} MAPF is a well-studied problem, a general overview is given in \cite{stern2019}.
-Somewhat informally, it is the problem of routing multiple agents on a graph (often a 4-connected grid) to multiple distinct destinations without any conflicts, with definitions of what constitutes a conflict varying; in this project, conflict is taken to mean 'occupy the same node' or 'traverse the same edge in opposite directions at the same time-step'.
+	The Dutch Railways (NS) company\footnote{\url{https://www.ns.nl/}} needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day.
+The problem of scheduling the trains to achieve this is called the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}.
+It is an NP-hard problem with many different subproblems such as the scheduling of personnel, the coupling and decoupling of train units entering and leaving the yard, etc.
+The company is interested in learning tighter upper-bounds for the capacity of their shunting yards but a problem is that in practical scenarios, only heuristics can solve TUSS instances (as was shown by Geiger et al.
+\cite{geiger2018}), leaving the company in the dark about what optimal solutions would look like and what could still be achieved using existing shunting infrastructure.
+To gain more insight into the capacity of shunting yards and the feasibility of problem instances, a relaxation of TUSS is considered: the multi-agent pathfinding problem extended with a matching subproblem (hereafter MAPFM).
+The idea of this research project is to develop and compare different algorithms for solving the MAPFM problem so that assuming a suitable translation from a TUSS instance to a MAPFM instance, such algorithms could be used to learn about the TUSS instance by solving or attempting to solve the corresponding MAPFM instance.
+	\subsection*{Multi-agent pathfinding} MAPF is a well-studied problem, a general overview is given in \cite{stern2019}.
+Somewhat informally, it is the problem of routing multiple agents on a graph (often a 4-connected grid) to multiple distinct destinations without any conflicts, with definitions of what constitutes a conflict varying; in this project, conflict is taken to mean 'occupy the same node' (vertex conflict) or 'traverse the same edge in opposite directions at the same time-step' (edge conflict).
 Typically one of two things is minimized: the sum of individual costs (SIC), or the length of the longest path (also known as \textit{makespan}).
-Algorithms for MAPF are often designed to find optimal solutions so that for instance the SIC is minimal.
+In the context of this project, the goal is to find an optimal solution to MAPF instances if one exists, where the optimal solution is the solution with the lowest SIC.
+The graph is assumed to be a 4-connected grid.
 
-\paragraph{Matching Multi-agent pathfinding as TUSS relaxation}
+	\subsection*{Matching Multi-agent pathfinding as TUSS relaxation}
 	For a problem to be a relaxation of TUSS, it has to be at most as difficult as TUSS for each instance assuming some suitable mapping from the original problem to the relaxation.
-In one respect TUSS is somewhat easier to solve than classical MAPF: trains are partitioned into types (equivalence classes, often denoted by colours) and destinations are labelled as destinations for trains of one specific type.
-This means that as far as this matching is concerned, for any valid matching there can be many equivalent permutations, so that in different optimal solutions a single train might have different destinations.
-As a consequence, this matching has to be modelled in the relaxed problem, resulting in MMAPF.
-Contrast this variation with both normal MAPF where each agent only has one target and anonymous MAPF where agents can be assigned to any target.
-See \cite{ma2016} for a discussion of MAPF with matching.
+In one respect TUSS is somewhat easier to solve than classical MAPF: trains are partitioned into types and destinations are labelled as destinations for trains of one specific type.
+This means that as far as this matching is concerned, for any valid matching there can be many equivalent permutations so that in different optimal solutions a single train might have different destinations.
+As a consequence, this matching has to be modelled in the relaxed problem, resulting in MAPFM.
+MAPFM is a generalization of both classical and anonymous MAPF, a variation where agents can be assigned to any target: the classical version corresponds to MAPFM with $k$ singleton types (classes) for $k$ agents and the anonymous variant is MAPFM with just $1$ type for $k$ agents\cite{ma2016}.
 
-\paragraph{Solving MAPF with matching}
-There exist many different algorithms for solving the MAPF problem. 
-Some current examples include conflict-based search\cite{sharon2015}, branch-and-cut-and-price\cite{lam2019}, A* with Independence detection and Operator Decomposition\cite{standley2010}, M*\cite{wagner2011} and Increasing Cost Tree Search\cite{sharon2011}.
-None of these are designed to work with matching out-of-the-box, so a naive way to incorperate matching into MAPF would be to generate legal matchings in preprocessing and enumerate these until one is found for which MAPF finds a solution.
-However, the challenge of this research project is to find ways using heuristics, preprocessing or other methods to generate good matchings that result in feasible MAPF problems and ideally efficient MAPF solutions.
-Similar to a previous iteration of this research project, we each chose an algorithm to work with as a start of our respective subprojects: I will be working on incorperating matching into Increasing Cost Tree Search MAPF-solving.
-
-\paragraph{TUSS to MAPF with matching}
-Finding a suitable mapping between TUSS and MMAPF instances is an unsolved problem: intuitively it is desirable to preserve feasibility so that there can never be a feasible TUSS instance mapped to an infeasible MMAPF instance, but perhaps it should be acceptable for the mapping to turn infeasible TUSS instances into feasible MMAPF instances, as the latter problem is a relaxation of the former.
-In any case, a good mapping that preserves key instance properties is important for MMAPF to be practically useful as a relaxation of TUSS so should time allow this would be interesting to consider.
+	\subsection*{Solving MAPF with matching}
+	There exist many different algorithms for solving the MAPF problem: some examples include conflict-based search\cite{sharon2015}, branch-and-cut-and-price\cite{lam2019}, A* with Independence detection and Operator Decomposition\cite{standley2010}, M*\cite{wagner2011} and Increasing Cost Tree Search\cite{sharon2011}.
+Comparatively, little research has been done on MAPF with matching however and the Conflict-Based Min-Cost-Flow algorithm by Ma and Koenig \cite{ma2016} appears to be one of the few existing approaches to solving this more general problem along with the somewhat similar one described in \cite{henkel2019}.
+Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
+All-in-all, it is an interesting method that by the reported experimental results seems to be a practical solver even for certain instances with a few hundred agents, which is also why a member of the peer group will be taking this approach as a starting point.
+This subproject, however, will instead take the Increasing Cost Tree Search method as the starting point for developing a novel algorithm for MAPFM, the performance of which can then be compared to other solvers based on different MAPF algorithms.
 
 	\section*{Research Question}
-The key research question that I aim to answer in this subproject is this: How can the Increasing Cost Tree Search method be used or adapted to efficiently find solutions to Multi-agent path-finding with matching?
-Relevant subquestions are as follows, where matching is to be understood as a single legal matching of trains to targets (departures) of their respective types:\footnote{These subquestions were taken from the initial project proposal at \url{https://projectforum.tudelft.nl/course_editions/39/projects/977}}
+	The key research question that I aim to answer in this subproject is this:\begin{center}
+		Can an efficient algorithm be derived for optimally solving MAPFM based on the Increasing Cost Tree Search algorithm for MAPF? 
+	\end{center} 
+	To define what is meant by efficient, consider a naïve ICTS-based MAPFM solver and let $n_1,\ldots,n_l$ denote the number of agents (and therefore targets) of each of the $l$ types.
+There are $N = \prod_{i = 1}^l n_i!$ legal matchings that can all be translated into MAPF instances which can be solved by regular ICTS or perhaps a variation with pruning and/or independence detection.
+Let the chosen ICTS variant be $O(X)$ (for the analysis of ICTS and its variants, see \cite{sharon2011}).
+To find the matching with the lowest sum of individual costs, in the worst-case, all matchings would have to be considered, so that this approach is $O(N\times X)$.
+
+	Formally then, an efficient algorithm for optimally solving MAPFM is asymptotically better than the above assuming regular ICTS.
+Ideally, it should also perform better (empirically) than the approach described in \cite{ma2016} and algorithms derived in parallel subprojects within the peer group on certain classes of MAPFM instances, similarly to how ICTS outperforms alternative algorithms like A* + OD on specific instances \cite{sharon2011}.
+Although this is a bit harder to formalize, comparing the algorithm to alternative algorithms is therefore also an important part of determining its significance.
+	\subsection*{Sub-questions}
+	As part of answering this research question, there will be an effort to develop candidate ICTS-based algorithms for MAPFM which appear to have desirable properties, and assuming at least one such candidate is found, for each the following sub-questions will be answered
 	\begin{enumerate}
-	\item Can we use a heuristic or preprocessing step to calculate a matching? And can we do so such that the resulting instance with the fixed matching is feasible?
-	\item Can we use instance features to (help) determine an efficient matching?
-	\item How can we improve upon a matching once one has been found?
+		\item What is the time complexity of the algorithm and can it be shown to be asymptotically better than the naïve approach?
+		\item Is the algorithm optimal?
+		\item What is the experimental run-time performance of the algorithm in different scenarios?
+		\begin{enumerate}
+			\item How does it compare to the naïve approach?
+			\item How does it compare to CBM, the algorithm by Ma and Koenig \cite{ma2016}?\footnote{Planning-wise, it is assumed that there will be an implementation of this available within the peer group as there will be someone taking this algorithm as a starting point}
+			\item How does it compare to the other algorithms developed within the peer group?
 		\end{enumerate}
+		\item Is the algorithm complete or can it be made complete by incorporating a polynomial-time feasibility check\footnote{The latter is the case for ICTS so it would be interesting to see what this means for a proposed ICTS-based algorithm} such as that described in \cite{yu2015}?
+	\end{enumerate}
+	If sub-questions 1 and 2 are answered in the affirmative for any candidate algorithm, then yes, an efficient and optimal algorithm based on ICTS could be derived so the next question is how it compares to the alternatives.
+Comparison with alternative algorithms is done in the first place by comparing both benchmark performance and computational complexity and in the second place by considering the completeness of the algorithm.
+Completeness is relevant because in ICTS and CBS this is something that is not always guaranteed \cite{sharon2015} and it might be important if MAPFM as TUSS relaxation is to be used for checking the feasibility of relaxed TUSS instances \cite{mulderij2020}.
+The completeness subquestion does have relatively low priority and is something to work on if there is time left.
+	\subsection*{Candidate algorithm}
+	\label{candidate}
+	In preparing for the meeting in the first week with the peer group and supervisor, a simple variation of ICTS came to mind: Consider $k$ agents $a_1,a_2,\ldots,a_k$ and goals $g_1,g_2,\ldots,g_k$.
+Let $t_{g_i}$ denote the type of goal $g_i$ and let $t_{a_i}$ denote the type of agent $a_i$.
+With $opt(i,j)$ being the cost shortest path from the starting position of agent $a_i$ to target $g_j$, let $C_i$ in $(C_1,C_2,\ldots,C_k)$  be defined as the minimal $opt(i,j)$ with $j$ such that $t_{a_i} = t_{g_j}$.
+Let this $(C_1,C_2,\ldots,C_k)$ be the root node of the Increasing Cost Tree.
+Now modify the generation of the MDDs for each $a_i$ in the low-level search to include any $g_j$ such that $t_{a_i} = t_{g_j}$ as goal node, otherwise keeping the low-level search the same.
 
+	The hypothesis is that this modification of ICTS is optimal and could be asymptotically better than the naïve approach with some refinements.
+It is not difficult to find pathological cases for the definition above without any enhancements.
+Consider the case wherein agents $a_x,a_y$ have the same type with there being goals $g_a,g_b$ of the corresponding type such that $opt(x,a) = 1,opt(y,a) = 1$ and $opt(x,b) = 10000,opt(y,b) = 10000$; due to the BFS expansion of the ICT tree, this instance would require the construction of an ICT that cannot possibly fit in memory.
+Possibly, exploiting properties of legal agent-goal matchings could help for such cases, as intuitively for any solution, either $a_x$ or $a_y$ will have to take at least $10000$ steps to get to the assigned goal.
+
+	The plan is to use this ICTS variation as starting point in the search for ICTS-based MAPFM algorithms, as the first possible candidate to consider, analyse, extend and so on.
 	\section*{Method}
-As a first step, an existing implementation of Increasing Cost Tree Search has to be found or a new one has to be implemented following the paper if no algorithm is publicly available.
-Next, the generation of agent-target matchings is to be implemented, which are translated into MAPF instances to be solved using ICTS.
-It might be possible to collaborate within the peer group here as we all have to do this step.
-Once this task has been completed, the project takes a more theoretical turn and I intend to study literature specific to MAPF with colours/teams or similar problems with the additional matching constraint in order to work towards answering the subquestions.
-Here also I hope to collaborate with my peer group and exchange ideas, perhaps about how properties of instances might be exploited in finding matchings or similar concepts.
+	The following gives an outline of the steps that will be taken to answer the research question and corresponding sub-questions above.
+This does not include some of the mandatory activities related to the Academic Communication Skills, Information Literacy and Responsible Research modules but these are incorporated into the planning in the next section.
+	\begin{enumerate}
+		\item \textbf{Implement the ICTS algorithm in Python} \footnote{\url{https://github.com/vikikkdi/icts} and \url{https://github.com/AdamBignell/ICTS-vs-EPEA} have come to my attention as a possible existing implementations of ICTS.
+I still aim to go through the motions of implementing ICTS myself with these as a reference to gain the understanding that is needed to be able to extend it confidently.} --- \textit{3 -- 5 days}
+		\begin{enumerate}
+			\item Implement the low-level search and the MDD datastructure with joins, unfolds and search. --- \textit{1 -- 2 days}
+			\item Implement the high-level ICT search and test the resulting base algorithm.--- \textit{1 day}
+			\item Implement pruning techniques (simple and advanced pruning for both pairs and triples following \cite{sharon2011}). --- \textit{1 day}
+			\item Optional: integrate algorithm into independence detection framework. --- \textit{1 day}
+		\end{enumerate} 
+		\item \textbf{Implement naïve MAPFM algorithm}: Enumerating all possible matchings and solve these --- \textit{Half a day}
+		\item \textbf{Research MAPF with matching}: read \cite{ma2016},\cite{henkel2019} and related work. --- \textit{3 -- 4 days}
+		\item \textbf{Create ICTS-based MAPFM algorithms}: start with the candidate described above and experiment with different ideas such as max-flows, the meta-agent framework, pruning, use of heuristics\ldots.
+Each idea that is tried out is to be documented.
+--- \textit{5 -- 7 days}
+		\item \textbf{Evaluate algorithms}: for each  --- \textit{3 -- 5 days}
+		\begin{enumerate}
+			\item Analyse time complexity, determine if the algorithm is an improvement over naïve approach
+			\item Show optimality or give a counterexample
+			\item Benchmark and compare to other algorithms using website\footnote{\url{https://dev.mapf.nl/}} that was set up for this purpose.
+Perhaps also run local benchmarks using experimental setup similar to that described in \cite{stern2019}.
+Record results for later use in paper.
+--- \textit{1 -- 2 days}
+			\item Optional: Consider completeness of algorithm
+		\end{enumerate} 
+		If I came up with multiple algorithms before, I aim to also select one to proceed with at this point unless there is a good argument for choosing two (e.g.
+neither being strictly better than the other)
+		\item \textbf{Process experimental data and analyze results}: the performance of the algorithm(s) should be characterized as a function of various parameters like agent-vertex density, number of teams, size of largest team and number of agents and in this way compared to alternative algorithms.
+Data should also be translated into tables, graphs, diagrams etc.
+that can later be used in the poster and paper.
+--- \textit{4 -- 6 days}
+		\item \textbf{Try to improve on found algorithm}: if there is time left, it would be good to spend more time looking for ways to improve on the performance of the found ICTS-based solution, again recording experimental data and considering its complexity.
+		%\item If there is time: study work on feasibility-checking \cite{yu2015} and see if concepts can be used to optimize search for good matchings and ensuring algorithm completeness.--- \textit{3+ days}
+		\item \textbf{Write the draft of the paper} --- \textit{6 -- 8 days}
+		\item \textbf{Finish final paper} --- \textit{2 -- 4 days}
+		\item \textbf{Compile results into poster} --- \textit{3 days}
 
-\section*{Planning of the (first week of the) research project} 
-For now I assume that reading a paper, looking into relevant citations and making a summary for comprehension takes around 3-4 hours which is also reflected in my planning.
-Also note that I take the tasks this first week to be seperate from those to be described by the end of this week in Method.
+	\end{enumerate}
+	\section*{Planning} 
+	\paragraph{Week 1}
+	\textbf{This week: draft research plan (19-4 23:59) and final research plan (25-4 23:59)}\footnote{This was the planning of the week leading up to the deadline of the research plan.
+It is included for completeness.}
 	\begin{enumerate}
@@
 		\item[23-4]\begin{enumerate}
-		\item[9:00]  Finish research plan (official deadline is at 25-4 23:59 but target deadline at 23-4 23:59).
+			\item[9:00]  Finish research plan.
 If there is time remaining, start familiarizing with the MAPF web API that our peer group 'inherited' from the previous instance of this project, and start implementing ICTS if no suitable existing implementation was found the previous day.
-(note: this is just one block as I am not sure how long this will take given that planning is rather hard)
 		\end{enumerate}
+	\end{enumerate}
+	\paragraph{Week 2} \textbf{This week: Research plan presentation (29-4 13:00), slides should be uploaded (deadline 2-5 23:59), Responsible Research readings.}
+	\begin{enumerate}
+		\item[26-4 ] Implement MDD datastructure with all operations and $k$-agent search.
+		\item[27-4 ] Finish MDD, test it and start working on high-level ICT search
+		\item[28-4 ] Finish implementing high-level ICT search, test it, and prepare research plan presentation.
+		\item[29-4 ] Read Responsible Research material (see Brightspace). Prepare presentation and present research plan to project group at 13:00. Process feedback on research plan.
+		\item[30-4 ] Implement simple and enhanced pruning for both pairs and triples. Test it and try out full ICTS algorithm with and without pruning using \url{www.mapf.nl} problem sets.
+	\end{enumerate}
+	\paragraph{Week 3} \textbf{This week: First ACS session (7-5 8:45-10:45)}
+	\begin{enumerate}
+		\item[3-5 ] Implement naïve MAPFM algorithm using ICTS and experiment a bit with MAPF Python API that was inherited from the previous instance of this research project (and further developed by Jonathan).
+Read \cite{ma2016}
+		\item[4-5 ] Read \cite{henkel2019}
+		\item[5-5 ] (Liberation day)
+		\item[6-5 ] Look into papers cited in \cite{ma2016}, \cite{henkel2019}. Meeting with peer group and supervisor at 13:00, discuss ideas for algorithmic extensions for matching.
+		\item[7-5 ] Scientific writing session at 8:45. Implement ICTS variation for MAPFM outlined above, run some first benchmarks.
+	\end{enumerate}
+	\paragraph{Week 4} \textbf{This week: Responsible Research session for discussing literature (10-5)}
+	\begin{enumerate}
+		\item[10-5 ] Attend responsible research session. Continue Friday's work.
+		\item[11-5 ] Create ICTS-based MAPFM algorithms
+		\item[12-5 ] Create ICTS-based MAPFM algorithms
+		\item[13-5 ] (Ascension Day)
+		\item[14-5 ] Create ICTS-based MAPFM algorithms
+	\end{enumerate}
+	\paragraph{Week 5} \textbf{This week: second ACS session (17-5 15:45-17:45) and midterm presentation (19-5). Midterm poster deadline at (19-5 23:59)}
+	\begin{enumerate}
+		\item[17-5 ] Second scientific writing session. Start evaluation of algorithm(s) derived in previous week
+		\item[18-5 ] Prepare midterm presentation.
+		\item[19-5 ] Midterm presentation. Process feedback and continue evaluation of algorithm(s)
+		\item[20-5 ] Evaluate algorithms. Meet with peer group and supervisor, perhaps discuss how midterm feedback is being implemented.
+		\item[21-5 ] Evaluate algorithms
+	\end{enumerate}
+	\paragraph{Week 6} \textbf{This week: third ACS session (28-5 8:45-10:45)}
+	\begin{enumerate}
+		\item[24-5 ] (Whit monday)
+		\item[25-5 ] Aim to finish up evaluation of algorithms, in particular comparison with algorithms derived within peer group.
+		\item[26-5 ] Start processing of experimental data and analysis of results
+		\item[27-5 ] Meeting with peer-group and continue processing and analysis
+		\item[28-5 ] Scientific writing session at 8:45. Try to schedule Responsible Research coaching for this day if necessary (i.e. mandatory). Process experimental data and analyze results
+	\end{enumerate}
+	\paragraph{Week 7} \textbf{This week: ACS coaching (4-6)}
+	\begin{enumerate}
+		\item[31-5 ] Buffer: These three days, I will either catch up if I am behind, do some algorithmic optimizations or start writing the paper draft early.
+		\item[1-6 ] Buffer
+		\item[2-6 ] Buffer
+		\item[3-6 ] Meeting with peer-group and supervisor. Work on paper draft
+		\item[4-6 ] ACS coaching (register for this). Work on paper draft 
+	\end{enumerate}
+	\paragraph{Week 8} \textbf{This week: Submit paper draft v1 (7-6 23:59), peer review before meeting (10-6 13:00) }
+	\begin{enumerate}
+		\item[7-6 ] Finish and submit draft v1
+		\item[8-6 ] Do peer review
+		\item[9-6 ] Do peer review
+		\item[10-6 ] Finish peer review prior to meeting with peer-group and supervisor. Process peer review feedback
+		\item[11-6 ] Work on paper draft
+	\end{enumerate}
+	\paragraph{Week 9} \textbf{This week: Submit paper draft v2 (16-6 23:59)}
+	\begin{enumerate}
+		\item[14-6 ] Work on paper draft
+		\item[15-6 ] Work on paper draft
+		\item[16-6 ] Submit paper draft v2.
+		\item[17-6 ] Meeting with peer-group and supervisor. Write paper
+		\item[18-6 ] Write paper
+	\end{enumerate}
+	\paragraph{Week 10} \textbf{This week: Submit final paper (27-6 23:59)}
+	\begin{enumerate}
+		\item[21-6 ] Finish paper
+		\item[22-6 ] Finish paper
+		\item[23-6 ] Start work on poster.
+		\item[24-6 ] Meeting with peer-group and supervisor.
+		\item[25-6 ] Finish and submit final version of paper
+	\end{enumerate}
+	\paragraph{Week 11} \textbf{This week: Submit poster (29-6 23:59) and final presentation (1-7 or 2-7)}
+	\begin{enumerate}
+		\item[28-6 ] Work on poster
+		\item[29-6 ] Submit poster and prepare presentation
+		\item[30-6 ] Practice presentation
+		\item[1-7 ] Present work
+		\item[2-7 ] Present work
 	\end{enumerate}

### 2021-04-26 docs/icts.tex
Added docs folder and MAPF solving setup

\documentclass[a4paper,10pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{marginnote}
\include{prelude}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\usepackage[backend=biber]{biblatex}
\addbibresource{sources.bib}
\usepackage{babel}

\title{Reviewed: The Increasing Cost Tree Search for Optimal Multi-agent Pathfinding}
\author{Thom van der Woude}
\date{\today}

\begin{document}
	\maketitle
	\paragraph{Overview}\marginnote{51 pages to go!}
	Typical optimal MAPF approach uses A* as single-agent search subroutine in finding per-agent paths. ICTS is a novel two-level method: top-level is an abstract increasing cost tree where each leaf represents a node where one agent gets a higher cost for its path (not a budget, exact cost!). The root node has a cost vector with the cost of the single-agent shortest path for each agent to target. What is the second-level processing of each node? It considers all combinations of all paths with the exact given cost per agent and sees if any has a non-conflicting solution. A smart datastructure is used to be able to enumerate all paths for a given agent.
	\paragraph{Solving MAPF: A* as a classical coupled approach}
    A* is a building block of MAPF algorithms: single-agent pathfinding can be done using A* and a proper heuristic $h(n)$ (remembering that $f(n) = g(n) + h(n)$), but multi-agent pathfinding can be reformulated as a 'single-agent' problem too: consider the state of this superagent to be the vector of all agent locations, and you can simply use A*. Specifically, each agent has at most $b$ + 1 actions where $b$ is the max degree of any location vertex and the $+1$ represents a wait action; for $k$ agents each $k$-agent state on the graph therefore has $O(b^k) \equiv O(e^k)$ children. It is clear that perhaps by using a good heuristic and given a lot of time and compute, A* can be used to solve MAPF. This is a traditional example of a coupled approach to MAPF, where the actions of all are coupled into one path-finding 'agent'. Decoupled approaches also exist but usually do not guarantee global optimality.

    When are coupled, decoupled approaches used? First for optimal solutions with lower $k$, second with suboptimal solutions with high $k$.

    Where is ICTS coming from? Complete MAPF solutions consist of individual paths of different agents. Let the increasing cost tree (ICT) consist of nodes represented by $k$-vectors $(C_1,C_2,\ldots,C_k)$ that represent all possible solutions in which the cost of each $\pi_i$ for agent $i$ is exactly $C_i$. The children of each node are all $k$-vectors generated by incrementing one of the costs. So an ICT node (with $k = 3$) $(4,3,5)$ may have three parents $(3,3,5),(4,2,5),(4,3,4)$ in a given instance (this is accounted for in implementation). Traversal is breadth-first.

    The low-level routine searches the space of possible solutions with the costs as given by the node, which is done using multi-value decision diagrams which store all possible paths for a given cost and a given agent. All possible combinations of single-agent paths are considered to see if any non-conflicting combination exists.

    What is lost? Information from an admissible heuristic as in A*. There are pruning techniques however for recognizing nodes with no valid solution (look at pairs/triples(/quadruples/quintuples/...) of agents, see if there is any non-conflicting solution).

    There is both a theoretical and experimental comparison of ICTS and A*, with a naturel ICTS variant and a triple-pruning variant.
    \paragraph{n'th statement of MAPF and assumptions}
    $k$ agents $a_1,a_2,\ldots,a_k$. A graph $G = (V,E)$ with $|V| = N$. A $start_i,goal_i\in V$ for each agent $a_i$. $b_{base}$ is the (maximal) branching factor of a single-agent, so $b_{base} = 4+1$ in a 4-connected grid. Each action is assumed to have unit cost. Agents wait at goals (so they stay there and occupy it) but this costs nothing. Constraints: states can be occupied by at most one. Swapping is also illegal, but following is allowed. Sum of costs is minimized in this paper. A centralized computing/solving approach is assumed in this paper as opposed to distributed settings.
    \paragraph{On decoupled approaches}
	Decoupled means that paths are planned for agents seperately, which has consequences for optimality and completeness: they cannot be guaranteed. Much research has been done here: a main result is the Hierarchical cooperative A* algorithm where agents are planned one at a time and each time a path is translated to a sequence of nodes that are reserved at certain timesteps\cite{silver2005}. This can be done using a basic reservation-table that becomes increasingly full as more agents are planned. HCA* is not guaranteed to be complete (deadlocks might occur!) and found solutions are often suboptimal. It uses the admissible heuristic for each agent that is the path cost when all other agents and reservations are ignored. Other interesting idea (used for traffic modelling): flow restrictions that force agents to move in certain directions, exactly like traffic laws! Each position could be assigned one or maybe two directions.\marginnote{Really wonderful concept: think about what makes humans in cars avoid collisions, its the law!}. There are also polynomial-time decoupled algorithms based on the idea of 'macros' (pairwise swaps of agents for instance).

	The key take-away is that decoupled algorithms are at best complete for special types of graphs but noncomplete and almost without exception suboptimal in the general case.
	\paragraph{Coupled approaches}
	Coupled approaches take the $k$ agents to be an agent together that can be in a state that corresponds to any legal way to place $k$ agents into the $N$ vertices, with start and goal states being the entire lists given as part of the instance. 'Operators' between states are all the non-conflicting actions agents can have.
	\paragraph{Coupled approach: A*}
	With $b_{base}$ as per-agent branching factor, let $b_{potential} = b_{base}^k$ represent the worst-case potential branching factor. Let $b_{legal}$ represent the non-conflicting (and non-blocked) actions that can be taken. It turns out that in the general case, identifiying $b_{legal}$ neighbours from the $b_{potential}$ potential neighbours of a given $k$-agent state is a CSP problem with conflict-rules and map geometry as constraints (map geometry can be factored out of course by only considering non-blocked moves)

	With this formulation out of the way, what about heuristics (you know, what makes A* a lot nicer than UCS)? Single-agent search has many sophisticated heuristic search techniques, but state-of-the-art MAPF heuristic approaches are relatively simple. A cheap idea is summing the manhattan distance of agents to goals on grids (or air-line distance/'as the crow flies' for general graphs). Sum of individual costs assuming individual optimal paths is also possible but more expensive. Pre-calculation of all-pairs shortest path or just shortest paths from all vertices to all targets can really save work later on. Curiously, this is negligible compared to the work done for solving MAPF itself.

	Subgraph decmoposition can be used to abstract a map into linked structures with certain topologies like cliques, halls, rings and so on. This does not work for the general case, as in large open spaces.

	\paragraph{Standley's Operator decomposition for A*}
	As was mentioned before, 'operator's in this coupled scheme are the full transitions between (legal) vectors of agents. Operator decomposition\cite{standley2010} decomposes state transistions into a sequence of intermediate states where the operator is applied to an increasing number of agents (one at a time) until it is applied to all $k$ agents. The idea is to prune misleading directions that agents can go without generating all possible moves of the other agents together with such misleading directions. Graphically, if there are two agents where the first has 3 moves, the second 4, it is the difference between first considering all 3 children where you move the first agent (and stop there if the outcome is very bad after just moving this first agent) and then for each of these 3, proceed to consider all 4 children where the second agent moves versus directly considering the 12 potential children of the root.

	The idea here, is that usually the heuristic in A* is not only admissible but also consistent so that the estimated final cost to the goal of a partial solution $f(n)$ is monotonically non-decreasing. This means that you can get formal about the 'badness' of certain intermediate states: if their $f$ values are greater than $f_{parent}$, you can prune them because the $f$ of the select child will have $f\leq f_{parent}$ for any solution.
	\paragraph{Standley's Independence Detection for coupled MAPF generally}
	Independence detection is a top-level approach that calls your MAPF solver as subroutine. It starts by assuming that all agents are independent and plans a path for each singleton group. Then it enters a loop until no conflicts occur, that simulates execution of all paths until a conflict occurs at which point there is an optional 'band-aid' fix moment after which it will merge the conflicting groups into one and plan paths for the agents within this dependent group (that is still assumed to be independent of any other group).

	The worst-case of an IDified MAPF algorithm is still $O(b^k)$, but sometimes the size of the largest subproblem that has to be solved $k'$ may be smaller than $k$ so that $O(b^{k'})$ comes to dominate the complexity,meaning that you get a speedup of a factor $b^{k - k'}$ which for high $b$ and high $k$ can be a lot!

	This can be improved upon still using conflict avoidance (assuming A* subroutine): when solving a merged group with A*, "A* search breaks ties in favor of states that will create the least amount of conflicts with existing planned paths of other agents (agents that are not part of the merged group)". How? Maintain a table of all paths currently planned (that still have to be fully checked), and consider in particular those corresponding to agents outside the currently recomputing group: now break ties by picking the states that will conflict the lowest number of other paths. The advantage is that the independence between groups that are formed is optimized to ensure that often $k'<k$.

	ID is general and can be applied to any optimal MAPF solver: implementing conflict avoidance will differ per algorithm, in ICTS perhaps in the enumeration of possible path combinations you could for each agent rank the possible paths by increasing number of conflicts with agents outside of the group being merged/computed.
	\section{ICTS formalization of MAPF}
	ICTS divides MAPF into two:
	\begin{itemize}
		\item What is the cost of the path of each agent in an optimal solution?
		\item How to find a non-conflicting set of paths given individual costs?
	\end{itemize}
	This gives rise to two levels of search:
	\begin{itemize}
		\item Top-level: Search for a minimal cost combination of individual agent costs
		\item Bottom-level: Search for a valid solution given a set of cost constraints, acting as a goal-test for the top-level search.
	\end{itemize}
	\paragraph{Top-level}
	Nodes as $k$-vectors $(C_1,C_2,\ldots,C_k)$. Each node $s$ represents all possible (candidate) solutions in which the cost of each $a_i$ is $C_i$ as given by the vector, the sum being the cost of (solution) $s$. The root of the tree is given by the shortest-path costs for agents ignoring others. Successors are defined by incrementing individual agents and pruning duplicates. BFS of this structure guarantees optimality. $\Delta$ denotes the difference between the optimal cost of the complete solution and the cost of the root, so the sum of individual shortest paths. The number of ICT nodes is $O(k^\Delta)$.

	What about this $\Delta$ versus $k$? It is often much lower in more open settings but much higher in tight corridors with many conflicts.
	\paragraph{Bottom-level}
	A simple bottom-level check is for each agent $a_i$ to enumerate all paths of length $C_i$ and then take the cross product of all such path 'lists'. But this will be a huge cross-product!

	Multi-value decision diagrams give a more compact representation of all paths and also enable cheaper combination. MDDs are DAGs not unlike binary decisino diagrams but with more options. Let $MDD^c_i$ store all paths of length $c$ for $a_i$. Any $MDD^c_i$ has exactly $c$ levels (with $c\geq opt_i$) and therefore consists of $O(|V| \cdot c)$ nodes. To build an MDD, perform BFS from the start location of $a_i$ down to depth $c$ and store the resulting partial DAG starting at $start(i)$ and ending at $goal(i)$ at depth $c$. You can also reuse $MDD^c_i$ in building $MDD^{c+1}_i$. Let $MDD^c_i(x,t)$ denote a node with location $x$ at time $t$ in this diagram. 	
	\paragraph{Goal test}
	To start looking for solutions, nondeterministically (MDD must be a monadic type) combine MDDs so nodes are generated so that each possible 'choice'/action is taken by each agent at each level with conflicts being filtered out. Somewhat formally, starting at $MDD_{ij}([x_i,x_j],t)$: let $\bar x_i,\bar x_j$ be children of these roots and let $MDD_{ij}([\bar x_i,\bar x_j],t+1)$ be a child of this root if the children do not conflict. They conflict if $\bar x_i = \bar x_j$ or $\bar x_j = x_i, \bar x_i = x_j$.

	You could build and store $MDD_{ij}$ in memory. The sink node of a MDD is a node at which all agents arrive at their goal, found at level $c$. Intuitively you want to find a path without conflicts through the MDD to this sink. Practical MDD merging is about checking if you can get to a sink-node which indicates that there is a way to choose paths so that there is no conflicts, avoiding the full construction but instead using the formal definition of the children of a certain node (non-conflicting combinations of the children of all agents from which (sub)MDDs are 'merged') in something like a depth-first search.

	For $k > 2$ agents, the constructive definition in any case is boring and inductive/recursive. The definitional one is also not too bad: a node $n = MDD_{[k]}(x[k],t)$ in a $k$-agent MDD has $k$ locations of $k$ agents at time $t$ in the vector $x_[k]$. It is the unification  of $k$ single-agent MDD nodes of level $t$ that do not conflict. The size of $MDD_{[k]}$ is $O(c \times |V| ^k)$ so exponential in $k$. This is why in practice you only want to build the actual MDDs for individual agents and use the above definition for nodes in the $k$-agent MDD in a search. Note: worst-case is that there is no way to a node at level $c$ which in practice means that a large chunk of the exponential tree will have to be visited. If conflicts occur early this might make up for this.

	How to search? Just be systematic and exhaustive. DFS is nice because it is usually 'the fastest way down' and the goal is to get to the node with depth $c$.

	Consider the use of ID. If it is not used, you could just do DFS (formally best-first search expanding the highest $g(n)$ node $n$) with maybe a transposition table to avoid visiting nodes twice. If ID is used, maintain a conflict avoidance table with the possibly conflicting (space,time) nodes of other groups as before and do best-first search preferring nodes with the fewest conflicts with other groups (maybe as tie-breaker in a similar BFS formulation)?

	\paragraph{Analysis: ICTS versus A* with OD using SIC heuristic}
	A* expands all nodes with f < C* and some of the nodes with f = C*. The worst-case is expanding all $n$ with $f(n) \leq C*$ assuming in this case the SIC heuristic. Denote the number of such nodes with $X$. A* with a consistent heuristic (like SIC) by \cite{dechter1985} is optimally effective/efficient meaning that it expands the minimal number of nodes to get get an admissible solution. \marginnote{In Dechter's paper, tie-breaking also plays a role in the result statement}. So any admissible MAPF algorithm is at least $O(X)$. It turns out that A* (with OD) does much worse than this in practice.

	Understanding ICTS complexity has two parts: first the complexity of individual per-node bottom-level searches, next how these are composed as part of top-level traversal of the ICT. $O(k^\Delta)$ ICT nodes are visited in the top-level. Such a visit involves constructing $k$ single-agent MDDs with costs depending on the ICT node and next searching the k-agent MDD search space. The first part is crudely $O(k\cdot c_{max} \cdot |V|)$ where $c_{max}$ is the maximal cost of any agent in the node, so it can be omitted as the complexity of searching the MDD search space is higher and bounded by $X$:

	Firstly, for any node $m$ visited in this $k$-agent search space for node $(C_1,\ldots,C_k)$, $f(m) \leq \sum_{i=1}^k C_i$ with SIC being the heuristic in $f$. Outline of the proof: $m$ is a possible configuration of agents at a time-step, consisting of $loc_i(m)$ for each agent $a_i$. Let $g_i(m)$ denote the cost of $a_i$ arriving there, $h_i(m)$ the (admissible) estiamte of the distance from $loc_i(m)$ to $goal_i$ and $f_i(m) = g_i(m) + h_i(m)$. Clearly
	\[f(m) = g(m) + h(m) = \sum_{i=1}^k g_i(m) + \sum_{i=1}^k h_i(m) = \sum_{i=1}^kf_i(m)\]
	Following the MDD construction, each $MDD_i$ contains nodes on a path of cost $C_i$ from $start_i$ to $goal_i$ so $f_i(m) \leq C_i$ (as $f_f(m)$ uses admissible heuristic $h_i(m)$). This then means that always $f(m) \leq \sum_{i=1}^kC_i$

	Now by definition of the ICT traversal, at any point $\sum_{i = 1}^k C_i \leq C*$. So together, for any node $m$ visited in low-level search,  $f(m) \leq C*$. So at most $X$ states are visited in a low-level search and the transposition table makes sure that states are visited at most once.

	Note: $n$ with $f(n) > C*$ are never considered, not even to reject them!
	\paragraph{A* analysis}
	A* expands only X nodes but generates many more as all $b_{legal} = O(b_{base}^k)$ children are generated in expansion so that A* generates $O(X \times b_{legal}$ nodes in fact. Because 'visiting' in A* is constant, you might as well say that as far as complexity is concerned $O(X \times b_{legal}$ nodes are visited. OD changes the branching factor from $b_{legal}$ to $b_{base}$ but increases the depth of the goal node by a factor $k$. Some analysis suggests therefore $\Omega(X \times b_{base})$ as a lower bound for complexity. Worst-case? Consider agent $a_i$ at $loc$ with $h_{SIC}$ being the heuristic and $b_{SIC}$ the number of neighbours with $h_{SIC} = h_{SIC}(loc) - 1$ (at most two in diagonal case on 4-grid). In A* OD, at worst $b_{SIC}$ out of $b_{base}$ will be expanded as they have the same $f$ as the parent. So $O(b_{SIC}^k)$ intermediate nodes will be expanded under a given full node and each of these will also generate $b_{base}-b_{SIC}$ children that are not expanded. So the number of generated nodes is $O(b_{SIC}^k(b_{base}-b_{SIC})) \equiv O(b_{SIC}^k)$. The result is as expected: still an exponential number of nodes is generated but the base of the exponential is rather different, which is rather important in practical complexity. Now this $O(b_{SIC}^k)$ thing is only a single node generating children, so in the end the complexity is $O(X\times b_{SIC}^k)$ because you do it for every node you minimally have to expand for optimality.

	On a 4-grid: the factor changes from $5^k$ to $2^k$.

	\paragraph{Analysis summarized}
	Remembering that $b_{base} = 5$, $b_{SIC} = 2$ (both worst-case values),
	Basic A* is $O(X\times b^k_{base}$, A* with OD is $O(X\times b_{IC}^k\cdot b_{base})$ and ICTS is $O(X\times k^\Delta)$. So what is interesting in benchmarks and practical scenarios is knowing when $\Delta$ be large or small. There is no easy answer here, but it will usually be high in dense, high $k$ scenarios and low in more open low $k$ scenarios.

	\paragraph{Experimental results}
	Let $k'$ denote the effective number of agents, the size of the largest subproblem solved by embedding algorithms in the ID framework.

	Type 1: both using ID. Uniformly random locations, $k$ agents, average $k'$ is reported.

	Type 2: Not using ID, so always $k' = k$, fixed number of agents with no ID tricks. ID is used to 'fill buckets' with problem instances of these fixed number of agents however by randomly simulating IDified MAPF until each $k$ value has enough samples. Because they are generated by ID, there is at least one agent always that conflicts with others so that they really are a dependent (coupled) group of agents.

	Nodes reported for A* are just full nodes and in OD also intermediate nodes. In ICTS, it is the sum of $k$-agent MDD nodes visited in the low-level searches.

	experimental result: $\Delta$ gets high for many conflicts. The relation between $k$ and the number of conflicts is complicated: the density $k/N$ with $|V| = N$ being the number of nodes is relevant but does not tell all, map topology is important to.

	The 50ms for A*, 37 seconds for ICTS example is curious: it is a pathology caused by topology not by something crude like density.

	ICTS with makespan: linearly increasing ICT, integer division enumeration at each node.
	\paragraph{Pruning for ICTS}
	Only the last node is a goal node for which the goal test will return true. Before fully doing low-level search, can we perhaps try to prune a node? You could pairwise search each $MDD_{ij}$ with DFS for a solution for every possible pair. If there is none for any pair, you know you can prune. This approach is called simple pairwise pruning. It results in $k \choose 2$ runs of 2-agent-MDD search.

	Enhanced pairwise pruning: in enhanced pairwise pruning, you do breadth-first search in the pairwise pruning and modify the MDDs of agents as you go: specifically, you remove any conflicting nodes, nodes that cannot be added when combining the two. This is called unfolding in the paper. The result of this is that more often there will be a possibility to prune (called cascading effect) and once you get to bottom-level search if no pruning is done, the work is much lighter.

	This cascading effect is curious in that if you would start looping over all pairs from the beginning, you may still prune the node. This is essentially the repeated enhanced pruning technique, which will either result in a prune or stop iterating when agent MDDs stop changing. This is like arc-consistency in CSP.

	SPP versus (iterated) EPP: EEP's BFS can be much slower than SPP's DFS, but EEP may result in more prunes and less work if pruning doesn't work (so time is not just wasted if in the end there is no prune). In terms of complexity, even in DFS the worst case is that all $|V|^2\times d$ nodes of the two-agent MDD of depth $d$ are visited which is done for all $k \choose 2$ pairs so both SPP and EPP are $O(|V|^2\times k^2)$

	All the above can be applied to $m$-agents. $m=3$ is often a good value. Emperically, repeated enhanced variants seem just not worth it. The difference between enhanced and simple is already very large.

	Conclusion from emperical comparison: enhanced pruning becomes important on dense, complicated graphs with many agents. More generally, you need to prune like crazy if there's a lot of agents on a small map.

	Another conclusion: ICTS with ID and 3 enhanced pruning is a powerful combination, it can solve problems fast!

	Immediate expand enhancement for A*: if child node has exact same $f$ value, immediately expand the thing.

	\paragraph{Discussion and future work}
	ICTS was presented, compared to state-of-the-art A* approach with OD, ID, immediate expand and so on. A* degrades as k increases, ICTS performance degrades as $\Delta$ increases (function of both $k$ and map size).

	Generally: if $\Delta$ is expected to be high due to dense map, high $k$, go for more sophisticated pruning.

	Future work directions: low-level search as just a constraint satisfaction problem: use of general CSP methods, more advanced pruning. Development of current arc-consistency and path-consistency ideas encoded in algorithm.

	Understanding problem (instance) parameters and relation to ICTS (and pruning) performance.

	ICTS for weighted graphs, agents with abstract goal instead of specific goal (group of agents should leave certain area... why does this sound military somehow?)
	\printbibliography

\end{document}

### 2021-04-26 docs/intro.tex
Added docs folder and MAPF solving setup

\documentclass[11pt]{report}
\title{Notes for intro}
\author{Thom van der Woude}
\date{\today}
\begin{document}
 \maketitle
 \section{Introduction}
 This course is something new. What is research? A research cycle: read-write-rinse-repeat.
 \paragraph{On research}
 'The systematic investigation into and study of materials and sources in order to establish facts and reach new conclusions.'

 You investigate a question, you establish a fact (maybe reproduce facts), reach conclusions.

 Failure is part of research.

 Ask good questions, many of them. Find answers to these. Communicate the answers you found.

 You don't have to do the module if you have already done it. But it is good to do anyway.

 \paragraph{Research skills}
 You need to know how to find information but also how to review/think about literature and work of peers. Also responsibly developing/investigating and communicating your entire proces and your results.

 Deliverables are always individual.

 Wat is het? Wat zijn bestaande variaties? Implementatie bouwen. Dan kijken naar matching.

\section{Information literacy}

\paragraph{Analysing}
Efficient searching for scientific information starts with analysing. You analyse your assignment and the background information that you have in order to formulate a general research topic. You split your research topic into sub-questions, which you then use to create a search plan.

With a good search plan, you know what you are looking for and you can be reasonably sure that you won't miss any important information. It ensures that your search results are relevant and complete.

Mind maps for overview?

\paragraph{Searching and evaluating}
After formulating your search query, you still need to determine what kind of information you're actually looking for, which information source you should use and how to search in this information source.

Evaluate your search by looking at the number and relevance of the results and you check the scientific nature of the results. Modify your search query if necessary.
\paragraph{Processing}
In order to use the publications you found, you first need to save them. Think about what your goal is when you save them:

to read them yourself
to share them with others
to generate a literature list
or a combination of the above

\end{document}

### 2021-04-26 docs/mapf.tex
Added docs folder and MAPF solving setup

\documentclass[a4paper,10pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{marginnote}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\usepackage[backend=bibtex]{biblatex}
\addbibresource{sources.bib}
\usepackage{babel}

\title{Reviewed: Multi-Agent Pathfinding: Definitions, Variants, and Benchmarks}
\author{Thom van der Woude}
\date{\today}

\begin{document}
	\maketitle
	\paragraph{First run-through}
	This paper is about unifying terminology and methodology (by providing common benchmarks and evaluation methods) of MAPF research to find a common language to express results in. First classical MAPF is formally described, different types of conflicts are discussed and also what agents do when they reach the target (Disappear or either stay put or move out of the way if this is needed). Makespan and sum of cost are mentioned as the two typical objective functions.

	Then variants past classical MAPF are discussed: first, MAPF on weighted graphs; second, additional feasibility rules that assert robustness of solutions to short delays or more complex rules that restrict possible actions of agents by requiring them to maintain 'formation', keep a communication link up or something similar (quite relevant in real-world settings).

	MAPF is quite abstract: many practical applications need MAPF plans to be translated to motion plannings for physical agents with more properties to consider.

	There are also anonymous, colored and online MAPF. Online MAPF has two variants: a warehouse model where agents are retasked after reaching target and a road intersection model where agents with set targets may appear.

	Benchmarks: there are the Dragon Age Origins maps, open nxn grids, nxn grids with some random obstacles nad warehouse grids. Source and target assignment is done randomly, using clustered sources and targets (more difficult instances) or picking from pools of designated sources and targets.

	Two real benchmarks: Grid-based MAPF (introduced in this paper!) using movingAI maps like DAO.
	Asprilo for simulating an automated warehouse.
	\section{Summary}
	MAPF: planning paths for multiple agents without them colliding as they concurrently move towards their goals. Applications range from automated warehouses and automotives to robotics and videogames. This paper will both present a unified terminology, go over the classical MAPF and classify different types of extensions and variations and introduce a new grid-based benchmark for emperical comparison of algorithms based on the movingAI maps. "This paper aims to address this growing challenge by introducing a unified terminology to describe MAPF problems, and by establishing common benchmarks and evaluation measures for evaluating MAPF algorithms." References to state-of-the-art surveys: \cite{Felner2017,ma2016}
	\paragraph{A statement of classical MAPF}
	The MAPF problem input assuming $k$ agents is $\langle G, s, t\rangle$ with an undirected graph $G = (V,E)$ and $s,t$ such that $s: [1,\ldots,k] \to V$ maps agents to source vertices, $t: [1,\ldots,k] \to V$ maps agents to target vertices. Time is discretized and agent speed is uniform: at each step, each agent can perform a single action $a : V \to V$ (actions are functions from vertices to vertices) so $a(v) = v'$ will be the vertex in the next time-step if $a$ is chosen. By assuming each $v\in V$ to have a self-loop, for any $a(v) = v'$, $(v,v') \in E$. If $v' = v$, this corresponds to waiting for a single step.

	Given agent $i$ and sequence of actions (path) $\pi = (a_1,\ldots,a_n)$, let $\pi_i[x]$ denote the location of $i$ after executing the first $x$ actions in $\pi$ so that $\pi_i[x] = a_x(a_{x-1}(\cdots(a_1(s(i)))\cdots))$. If $\pi_i[|\pi|] = t(i)$, $\pi$ is a single-agent plan. $k$ single-agent plans for different agents define a solution to the MAPF problem.

	\paragraph{Conflicts and at-target behaviour}
	Conflicts relevant to the project are
	\begin{enumerate}
		\item Vertex conflict: $\pi_i,\pi_j$ conflict if for some time-step $x$, $\pi_i[x] = \pi_j[x]$.
		\item Edge conflict: $\pi_i,\pi_j$ conflict if for some time-step $x$, $\pi_i[x] = \pi_j[x]$ and $\pi_i[x+1] = \pi_j[x+1]$
		\item Swapping conflict: $\pi_i,\pi_j$ conflict if for some time-step $x$, $\pi_i[x] = \pi_j[x+1]$ and $\pi_i[x+1] = \pi_j[x]$
	\end{enumerate}
	Following and cycling conflicts are also described but are not so relevant.

	Upon reaching target, an agent $i$ can either stay there so that for $t\geq |\pi_i|$, $\pi_i[t] = \pi_i[|\pi_i|]$ (with all the usual (vertex) conflicts) or disappear 'into' the target, meaning that it will never conflict with another agent $j$.
	\paragraph{Objective functions}
	Given solution $\pi = \{\pi_1,\cdots,\pi_k\}$ , there are two common objective functions:
	\begin{itemize}
	\item Makespan, or the total number of steps for all agents to reach their target, defined as $\max_{1\leq i \leq k} |\pi_i]$
	\item Sum of costs, defined as $\sum_{1\leq i \leq k} |\pi_i|$ (sometimes called flowtime)
	\end{itemize}
	\marginnote{The paper refers to search-based and compilation-based methods}
	\paragraph{Past classical MAPF}
	MAPF on weighted graphs models variable action-times. Weighted graphs have been studied are $2^k$-neighbour grids and graphs representing points in euclidean space (as in roadmaps).

	There are also alternative feasibility rules, besides the basic no-conflicts rule: you could want a k-robust MAPF plan where each agent can be delayed $0-k$ timesteps without there being any conflicts. Similarly, you might impose rules that restrict agent actions to make sure they keep formation, and let maintaining formation be an additional feasibility rule.

	Another line of variations involve bridging the gap between the abstract MAPF and concrete motion planning problem that has to program actual agents with limited degrees of freedom to move through a space. This requires considering the 'configuration' an agent is in: the location, orientation, velocity and so on. Depending on what aspect of the physical agent is important, you could either focus on the volume they occupy by perhaps marking more surrounding vertices as occupied, or consider kinematic constraints in action selection, resulting in a directed graph.
	\paragraph{Anonymous, colored and online MAPF}
	Lastly, you can consider the relation between tasks and agents. In classical MAPF, each agent has a single target. Alternatively, you could do anonymous MAPF where exactly one agent needs to get to each target but it doesn't matter which agent goes to which target. Generalizing this idea, you could divide agents into groups (color the agents), similarly group targets and plan so that agents within groups are matched to targets that belong to that group. In online MAPF, agents still at any point in time have a single target, but you want to solve MAPF-like problems in sequence on the same graph. There are two main online models: in a warehouse model, you reassign agents that have got to their target; in a road intersection model, you have new agents appear with each one task.  
	\section{Benchmarks}
	To evaluate MAPF algorithms, you can consider different types of graphs:
	\begin{enumerate}
		\item Open NxN grids
		\item Unstructuerd NxN grids with random obstacles
		\item Structured maps like Dragon Age Origins maps
		\item Warehouse grids or grids modelling other relevant real-world applications
	\end{enumerate}
	You also need to assign sources and targets systematically:
		\begin{enumerate}
			\item Random. You generate random vertex pairs with paths between them
			\item Clustured. You can generate one random pair and cluster source and target around this pair for a more complex problem (more conflicts probably)
			\item Designated. You can handcraft source and target vertices, perhaps to model something like warehouse protocols.
	\end{enumerate}
	\paragraph{Grid-based MAPF benchmark and Asprilo}
	Uses a wide variety of graphs from the MovingAI pathfinding repository. Each map has 25 scenarios with source and target vertex lists. As a robust benchmark method, you could set a time-out of say 30 seconds assuming a set hardware-software setup. Then try to solve each scenario (different s,t lists) with as many agents as possible in increasing order until a time-out occurs, and consider the resulting statistic (worst and best scenario, agents in average scenario and so on). Modulo hardwarde-software implementation considerations, this gives a robust emperic way of comparing algorithms.

	Asprilo has a M domain which corresponds to MAPF in an automated warehouse setting.

	\paragraph{Conclusion}
	The authors hope that this unification of MAPF terminology and emperical evaluation will be useful to the MAPF community.
	\printbibliography

\end{document}

### 2021-04-26 docs/plan.tex
Added docs folder and MAPF solving setup

--- 2021-04-25 plan.tex
@@
 
-\title{Research Plan for MAPF with matching using ICTS}
+\title{Research Plan for Multi-Agent Path Finding with matching using Increasing Cost Tree Search}
 \author{Thom van der Woude}
+\newcommand{\namelistlabel}[1]{\mbox{#1}\hfil}
+\newenvironment{namelist}[1]{%1
+	\begin{list}{}
+		{
+			\let\makelabel\namelistlabel
+			\settowidth{\labelwidth}{#1}
+			\setlength{\leftmargin}{1.1\labelwidth}
+		}
+	}{
+\end{list}}
 \date{\today}
@@
 	\maketitle
+	\begin{namelist}{xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx}
+		\item[{\bf Title:}]
+		Multi-Agent Path Finding with matching using Increasing Cost Tree Search
+		\item[{\bf Author:}]
+		Thom van der Woude
+		\item[{\bf Responsible Professor:}]
+		Mathijs de Weerdt
+		\item[{\bf Other Supervisor:}]
+		Jesse Mulderij
+		\item[{\bf Peer group members:}]
+		Robbin Baauw, Jonathan Dönszelmann, Ivar de Bruin, Jaap de Jong
+	\end{namelist}
 
@@
 The idea of this research project is to develop and compare different algorithms for solving the MAPFM problem so that assuming a suitable translation from a TUSS instance to a MAPFM instance, such algorithms could be used to learn about the TUSS instance by solving or attempting to solve the corresponding MAPFM instance.
-	\subsection*{Multi-agent pathfinding} MAPF is a well-studied problem, a general overview is given in \cite{stern2019}.
-Somewhat informally, it is the problem of routing multiple agents on a graph (often a 4-connected grid) to multiple distinct destinations without any conflicts, with definitions of what constitutes a conflict varying; in this project, conflict is taken to mean 'occupy the same node' (vertex conflict) or 'traverse the same edge in opposite directions at the same time-step' (edge conflict).
-Typically one of two things is minimized: the sum of individual costs (SIC), or the length of the longest path (also known as \textit{makespan}).
+	\subsection*{Multi-agent pathfinding} MAPF is a well-studied problem.
+A general overview is given in \cite{stern2019}.
+Somewhat informally, MAPF is the problem of routing multiple agents on a graph (often a 4-connected grid) to multiple distinct destinations without any conflicts, with definitions of what constitutes a conflict varying.
+In this project, conflict means 'occupy the same node' (vertex conflict) or 'traverse the same edge in opposite directions at the same time-step' (edge conflict).
+Typically one of two things is minimized: the sum of individual costs (SIC) or the length of the longest path (also known as \textit{makespan}).
 In the context of this project, the goal is to find an optimal solution to MAPF instances if one exists, where the optimal solution is the solution with the lowest SIC.
@@
 	\subsection*{Matching Multi-agent pathfinding as TUSS relaxation}
-	For a problem to be a relaxation of TUSS, it has to be at most as difficult as TUSS for each instance assuming some suitable mapping from the original problem to the relaxation.
-In one respect TUSS is somewhat easier to solve than classical MAPF: trains are partitioned into types and destinations are labelled as destinations for trains of one specific type.
-This means that as far as this matching is concerned, for any valid matching there can be many equivalent permutations so that in different optimal solutions a single train might have different destinations.
+	For a problem to be a relaxation of TUSS, it has to be at most as difficult as TUSS for each instance, assuming some suitable mapping from the original problem to the relaxation.
+In one respect, TUSS is somewhat easier to solve than classical MAPF: trains are partitioned into types and destinations are labelled as destinations for trains of one specific type.
+This means that as far as this matching is concerned, for any valid matching, there can be many equivalent permutations so that in different optimal solutions, a single train might have different destinations.
 As a consequence, this matching has to be modelled in the relaxed problem, resulting in MAPFM.
-MAPFM is a generalization of both classical and anonymous MAPF, a variation where agents can be assigned to any target: the classical version corresponds to MAPFM with $k$ singleton types (classes) for $k$ agents and the anonymous variant is MAPFM with just $1$ type for $k$ agents\cite{ma2016}.
+MAPFM generalizes both classical and anonymous MAPF, a variation where agents can be assigned to any target: the classical version corresponds to MAPFM with $k$ singleton types (classes) for $k$ agents, and the anonymous variant is MAPFM with just $1$ type for $k$ agents\cite{ma2016}.
 
@@
 	There exist many different algorithms for solving the MAPF problem: some examples include conflict-based search\cite{sharon2015}, branch-and-cut-and-price\cite{lam2019}, A* with Independence detection and Operator Decomposition\cite{standley2010}, M*\cite{wagner2011} and Increasing Cost Tree Search\cite{sharon2011}.
-Comparatively, little research has been done on MAPF with matching however and the Conflict-Based Min-Cost-Flow algorithm by Ma and Koenig \cite{ma2016} appears to be one of the few existing approaches to solving this more general problem along with the somewhat similar one described in \cite{henkel2019}.
+Comparatively, little research has been done on MAPF with matching however, and the Conflict-Based Min-Cost-Flow algorithm by Ma and Koenig \cite{ma2016} appears to be one of the few existing approaches to solving this more general problem along with the somewhat similar one described in \cite{henkel2019}.
 Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
@@
 	To define what is meant by efficient, consider a naïve ICTS-based MAPFM solver and let $n_1,\ldots,n_l$ denote the number of agents (and therefore targets) of each of the $l$ types.
-There are $N = \prod_{i = 1}^l n_i!$ legal matchings that can all be translated into MAPF instances which can be solved by regular ICTS or perhaps a variation with pruning and/or independence detection.
+There are $N = \prod_{i = 1}^l n_i!$ legal matchings that can all be translated into MAPF instances which can be solved by regular ICTS or perhaps a variation with pruning or independence detection.
 Let the chosen ICTS variant be $O(X)$ (for the analysis of ICTS and its variants, see \cite{sharon2011}).
-To find the matching with the lowest sum of individual costs, in the worst-case, all matchings would have to be considered, so that this approach is $O(N\times X)$.
+Finding the minimal sum of individual costs matching requires considering all matching.
+Therefore this approach is $O(N\times X)$.
 
@@
 Ideally, it should also perform better (empirically) than the approach described in \cite{ma2016} and algorithms derived in parallel subprojects within the peer group on certain classes of MAPFM instances, similarly to how ICTS outperforms alternative algorithms like A* + OD on specific instances \cite{sharon2011}.
-Although this is a bit harder to formalize, comparing the algorithm to alternative algorithms is therefore also an important part of determining its significance.
+Although this is a bit harder to formalize, comparing the algorithm to alternative algorithms is therefore also an important part of determining its significance as a result of the research project.
 	\subsection*{Sub-questions}
-	As part of answering this research question, there will be an effort to develop candidate ICTS-based algorithms for MAPFM which appear to have desirable properties, and assuming at least one such candidate is found, for each the following sub-questions will be answered
+	As part of answering this research question, there will be an effort to develop candidate ICTS-based algorithms for MAPFM which appear to have desirable properties, and assuming at least one such candidate is found, for each, the following sub-questions will be answered
 	\begin{enumerate}
-		\item What is the time complexity of the algorithm and can it be shown to be asymptotically better than the naïve approach?
+		\item What is the time complexity of the algorithm, and can it be shown to be asymptotically better than the naïve approach?
 		\item Is the algorithm optimal?
@@
 		\end{enumerate}
-		\item Is the algorithm complete or can it be made complete by incorporating a polynomial-time feasibility check\footnote{The latter is the case for ICTS so it would be interesting to see what this means for a proposed ICTS-based algorithm} such as that described in \cite{yu2015}?
+		\item Is the algorithm complete, or can it be made complete by incorporating a polynomial-time feasibility check\footnote{The latter is the case for ICTS, so it would be interesting to see what this means for a proposed ICTS-based algorithm} such as that described in \cite{yu2015}?
 	\end{enumerate}
@@
 	The following gives an outline of the steps that will be taken to answer the research question and corresponding sub-questions above.
-This does not include some of the mandatory activities related to the Academic Communication Skills, Information Literacy and Responsible Research modules but these are incorporated into the planning in the next section.
+This does not include some of the mandatory activities related to the Academic Communication Skills, Information Literacy and Responsible Research modules.
+These are part of the planning in the next section, however.
 	\begin{enumerate}
@@
 	\end{enumerate}
-	\paragraph{Week 2} \textbf{This week: Research plan presentation (29-4 13:00), slides should be uploaded (deadline 2-5 23:59), Responsible Research readings.}
+	\paragraph{Week 2} \textbf{This week: research plan presentation (29-4 13:00), slides should be uploaded (deadline 2-5 23:59), Responsible Research readings.}
 	\begin{enumerate}
@@
 	\end{enumerate}
-	\paragraph{Week 3} \textbf{This week: First ACS session (7-5 8:45-10:45)}
+	\paragraph{Week 3} \textbf{This week: first ACS session (7-5 8:45-10:45)}
 	\begin{enumerate}
@@
 	\end{enumerate}
-	\paragraph{Week 7} \textbf{This week: ACS coaching (4-6)}
+	\paragraph{Week 7} \textbf{This week: Scientific writing at 8:45-10:45 and ACS coaching (4-6)}
 	\begin{enumerate}
@@
 	\end{enumerate}
-	\paragraph{Week 8} \textbf{This week: Submit paper draft v1 (7-6 23:59), peer review before meeting (10-6 13:00) }
+	\paragraph{Week 8} \textbf{This week: submit paper draft v1 (7-6 23:59), peer review before meeting (10-6 13:00) }
 	\begin{enumerate}
@@
 	\end{enumerate}
-	\paragraph{Week 9} \textbf{This week: Submit paper draft v2 (16-6 23:59)}
+	\paragraph{Week 9} \textbf{This week: feedback from supervisor, submit paper draft v2 (16-6 23:59)}
 	\begin{enumerate}
@@
 		\item[16-6 ] Submit paper draft v2.
-		\item[17-6 ] Meeting with peer-group and supervisor. Write paper
-		\item[18-6 ] Write paper
+		\item[17-6 ] Meeting with peer-group and supervisor. Write paper.
+		\item[18-6 ] Write paper. Process feedback from supervisor.
 	\end{enumerate}
-	\paragraph{Week 10} \textbf{This week: Submit final paper (27-6 23:59)}
+	\paragraph{Week 10} \textbf{This week: feedback from responsible professor, submit final paper (27-6 23:59)}
 	\begin{enumerate}
 		\item[21-6 ] Finish paper
-		\item[22-6 ] Finish paper
+		\item[22-6 ] Finish paper. Process feedback.
 		\item[23-6 ] Start work on poster.
@@
 	\end{enumerate}
-	\paragraph{Week 11} \textbf{This week: Submit poster (29-6 23:59) and final presentation (1-7 or 2-7)}
+	\paragraph{Week 11} \textbf{This week: submit poster (29-6 23:59) and final presentation (1-7 or 2-7)}
 	\begin{enumerate}

### 2021-04-26 main.py

@@ -1,0 +1,141 @@
+import heapq
+from typing import List, Optional, Tuple
+from mapfmclient import MapfBenchmarker, Problem, Solution, MarkedLocation
+
+
+class Location:
+    def __init__(self, x: int, y: int):
+        self.x: int = x
+        self.y: int = y
+
+    def __eq__(self, other) -> bool:
+        return self.x == other.x and self.y == other.y
+
+    def __hash__(self):
+        return hash((self.x,self.y))
+
+    @classmethod
+    def from_dict(cls, dct) -> "Location":
+        return cls(dct["x"], dct["y"])
+
+
+class Node:
+    def __init__(self, parent, loc: Location, cost: int, heuristic: int):
+        self.parent: Optional[Node] = parent
+        self.loc: Location = loc
+        self.cost: int = cost
+        self.heuristic: int = heuristic
+
+    def __key(self):
+        return (self.attr_a, self.attr_b, self.attr_c)
+
+    def __hash__(self):
+        return hash(self.loc)
+
+    def is_root(self):
+        return self.parent is None
+
+    def is_goal(self, goal: Location) -> bool:
+        return self.loc == goal
+
+    def get_directions(self):
+        if self.is_root():
+            return [self.loc]
+        else:
+            par_dirs = self.parent.get_directions()
+            par_dirs.append(self.loc)
+            return par_dirs
+
+    def __eq__(self, other) -> bool:
+        return self.cost + self.heuristic == other.cost + other.heuristic
+
+    def __ne__(self, other) -> bool:
+        return self.cost + self.heuristic != other.cost + other.heuristic
+
+    def __ge__(self, other) -> bool:
+        return self.cost + self.heuristic >= other.cost + other.heuristic
+
+    def __lt__(self, other) -> bool:
+        return self.cost + self.heuristic < other.cost + other.heuristic
+
+    def __gt__(self, other) -> bool:
+        return self.cost + self.heuristic > other.cost + other.heuristic
+
+    def __le__(self, other) -> bool:
+        return self.cost + self.heuristic <= other.cost + other.heuristic
+
+
+class Maze:
+    def __init__(self, grid: List[List[int]], width: int, height: int):
+        self.grid = grid
+        self.width = width
+        self.height = height
+
[…]

### 2021-04-26 main.py
Added some type hints

@@ -1,5 +1,5 @@
 import heapq
-from typing import List, Optional, Tuple
+from typing import List, Optional, Tuple, Set
 from mapfmclient import MapfBenchmarker, Problem, Solution, MarkedLocation
 
 
@@ -73,8 +73,8 @@ class Maze:
 
     def get_valid_children(self, loc: Location) -> List[Location]:
         x, y = loc.x, loc.y
-        all_children = [(x + 1, y), (x - 1, y), (x, y + 1), (x, y - 1), (x, y)]
-        good_children = []
+        all_children: List[Tuple[int,int]] = [(x + 1, y), (x - 1, y), (x, y + 1), (x, y - 1), (x, y)]
+        good_children: List[Tuple[int,int]] = []
         for c in all_children:
             if c[0] >= 0 and c[0] < self.height and c[1] >= 0 and c[1] < self.width:
                 if not self.grid[c[1]][c[0]]:
@@ -89,7 +89,7 @@ def heuristic(node: Location, goal: Location) -> int:
 def astar(maze: Maze, start: Location, goal: Location) -> List[Tuple[int,int]]:
     ls: List[Node] = [Node(None, start, 0, heuristic(start, goal))]
     heapq.heapify(ls)
-    seen = set()
+    seen: Set[Location] = set()
     while ls:
         n: Node = heapq.heappop(ls)
         if (n.loc) not in seen:
@@ -102,23 +102,17 @@ def astar(maze: Maze, start: Location, goal: Location) -> List[Tuple[int,int]]:
 
 
 def solve(problem: Problem) -> Solution:
-    maze = Maze(problem.grid, problem.width, problem.height)
-    paths = []
+    maze: Maze = Maze(problem.grid, problem.width, problem.height)
+    paths: List[List[Tuple[int,int]]] = []
 
     assert len(problem.starts) == 1
     assert len(problem.goals) == 1
 
-    start = problem.starts[0]
-    goal = problem.goals[0]
-    path = astar(maze,Location(start.x,start.y),Location(goal.x,goal.y))
+    start: MarkedLocation = problem.starts[0]
+    goal: MarkedLocation = problem.goals[0]
+    path: List[Tuple[int,int]] = astar(maze,Location(start.x,start.y),Location(goal.x,goal.y))
     print("Length of found solution: {}".format(len(path)))
     paths.append(path)
-    """
-    Now paths looks like:
-
-    paths = list[Path]
-    Path = List[(x, y)]
[…]

### 2021-04-26 main.py
Implemented basic depth-limited BFS DAG construction

@@ -1,5 +1,6 @@
 import heapq
-from typing import List, Optional, Tuple, Set
+from collections import deque, defaultdict
+from typing import List, Optional, Tuple, Set, DefaultDict
 from mapfmclient import MapfBenchmarker, Problem, Solution, MarkedLocation
 
 
@@ -12,7 +13,7 @@ class Location:
         return self.x == other.x and self.y == other.y
 
     def __hash__(self):
-        return hash((self.x,self.y))
+        return hash((self.x, self.y))
 
     @classmethod
     def from_dict(cls, dct) -> "Location":
@@ -25,9 +26,6 @@ class Node:
         self.loc: Location = loc
         self.cost: int = cost
         self.heuristic: int = heuristic
-
-    def __key(self):
-        return (self.attr_a, self.attr_b, self.attr_c)
 
     def __hash__(self):
         return hash(self.loc)
@@ -73,10 +71,10 @@ class Maze:
 
     def get_valid_children(self, loc: Location) -> List[Location]:
         x, y = loc.x, loc.y
-        all_children: List[Tuple[int,int]] = [(x + 1, y), (x - 1, y), (x, y + 1), (x, y - 1), (x, y)]
-        good_children: List[Tuple[int,int]] = []
+        all_children: List[Tuple[int, int]] = [(x + 1, y), (x - 1, y), (x, y + 1), (x, y - 1), (x, y)]
+        good_children: List[Tuple[int, int]] = []
         for c in all_children:
-            if c[0] >= 0 and c[0] < self.height and c[1] >= 0 and c[1] < self.width:
+            if 0 <= c[0] < self.height and 0 <= c[1] < self.width:
                 if not self.grid[c[1]][c[0]]:
                     good_children.append(c)
         return list(map(lambda x: Location(x[0], x[1]), good_children))
@@ -86,7 +84,38 @@ def heuristic(node: Location, goal: Location) -> int:
     return abs(goal.x - node.x) + abs(goal.y - node.y)
 
 
-def astar(maze: Maze, start: Location, goal: Location) -> List[Tuple[int,int]]:
+class MDD:
+    def __init__(self, maze: Maze, agent: int, start: Location, goal: Location, depth: int):
+        self.agent: int = agent
+        self.start: Location = start
+        self.goal: Location = goal
+        self.depth: int = depth
+        tree = construct_bfs_tree(maze,start,depth)
+
+
[…]

### 2021-04-30 main.py
Added advanced pruning, speeded up hashing

@@ -1,15 +1,20 @@
 import heapq
 import itertools
 from itertools import combinations
-from copy import copy
+from copy import copy, deepcopy
 import sys
 
-from matplotlib import pyplot as plt
+# from matplotlib import pyplot as plt
 from pprint import pprint
 from collections import deque, defaultdict
 from typing import List, Optional, Tuple, Set, DefaultDict, Any, Union, Deque
+
+import requests
 from mapfmclient import MapfBenchmarker, Problem, Solution, MarkedLocation
-from graphviz import Digraph
+# from graphviz import Digraph
+
+row_factor = 1000
+depth_factor = 1000000
 
 
 class Location:
@@ -21,7 +26,7 @@ class Location:
         return self.x == other.x and self.y == other.y
 
     def __hash__(self):
-        return hash((self.x, self.y))
+        return self.x + self.y * row_factor
 
     def __str__(self):
         return '(' + str(self.x) + ',' + str(self.y) + ')'
@@ -142,20 +147,20 @@ class MDD:
             self.populate_levels(self.mdd)
 
     # Constructs a graph of the MDD.
-    def show(self):
-        items = list(sorted(self.mdd.items(), key=lambda x: x[0][1]))
-        g = Digraph()
-        added = set()
-        plt.tight_layout()
-        for ((loc, d), v) in items:
-            node_str = str(loc) + ',' + str(d)
-            g.node(node_str)
-            for (c_loc, c_depth) in v:
-                child_str = str(c_loc) + ',' + str(c_depth)
-                if not child_str in added:
-                    added.add(child_str)
-                g.edge(node_str, child_str)
-        return g
+    # def show(self):
+    #     items = list(sorted(self.mdd.items(), key=lambda x: x[0][1]))
+    #     g = Digraph()
+    #     added = set()
+    #     plt.tight_layout()
+    #     for ((loc, d), v) in items:
+    #         node_str = str(loc) + ',' + str(d)
+    #         g.node(node_str)
+    #         for (c_loc, c_depth) in v:
+    #             child_str = str(c_loc) + ',' + str(c_depth)
+    #             if not child_str in added:
+    #                 added.add(child_str)
+    #             g.edge(node_str, child_str)
+    #     return g
 
     def populate_levels(self, mdd: MDDGraph):
[…]

### 2021-04-30 main.py
Switched to a compact (integer) location representation

@@ -13,33 +13,26 @@ import requests
 from mapfmclient import MapfBenchmarker, Problem, Solution, MarkedLocation
 # from graphviz import Digraph
 
-row_factor = 1000
+row_factor = 2048
 depth_factor = 1000000
 
+CompactLocation = int
+# type alias for graph structure of MDD
+MDDGraph = Optional[DefaultDict[Tuple[CompactLocation, int], Set[Tuple[CompactLocation, int]]]]
 
-class Location:
-    def __init__(self, x: int, y: int):
-        self.x: int = x
-        self.y: int = y
+JointSolution = List[Tuple[Tuple[CompactLocation, ...], int]]
 
-    def __eq__(self, other) -> bool:
-        return self.x == other.x and self.y == other.y
 
-    def __hash__(self):
-        return self.x + self.y * row_factor
+def compact_location(x,y):
+    return x + y * row_factor
 
-    def __str__(self):
-        return '(' + str(self.x) + ',' + str(self.y) + ')'
-
-    @classmethod
-    def from_dict(cls, dct) -> "Location":
-        return cls(dct["x"], dct["y"])
-
+def expand_location(c: CompactLocation):
+    return (c % row_factor, c // row_factor)
 
 class Node:
-    def __init__(self, parent, loc: Location, cost: int, heuristic: int):
+    def __init__(self, parent, loc: CompactLocation, cost: int, heuristic: int):
         self.parent: Optional[Node] = parent
-        self.loc: Location = loc
+        self.loc: CompactLocation = loc
         self.cost: int = cost
         self.heuristic: int = heuristic
 
@@ -49,7 +42,7 @@ class Node:
     def is_root(self):
         return self.parent is None
 
-    def is_goal(self, goal: Location) -> bool:
+    def is_goal(self, goal: CompactLocation) -> bool:
         return self.loc == goal
 
     def get_directions(self):
@@ -85,51 +78,48 @@ class Maze:
         self.width = width
         self.height = height
 
-    def get_valid_children(self, loc: Location) -> List[Location]:
-        x, y = loc.x, loc.y
+    def get_valid_children(self, loc: CompactLocation) -> List[CompactLocation]:
+        x, y = expand_location(loc)
         all_children: List[Tuple[int, int]] = [(x + 1, y), (x - 1, y), (x, y + 1), (x, y - 1), (x, y)]
[…]

### 2021-04-30 main.py
Cleaned up a bit, corrected recursive passing of enhanced pruning parameter

@@ -7,10 +7,11 @@ import sys
 # from matplotlib import pyplot as plt
 from pprint import pprint
 from collections import deque, defaultdict
-from typing import List, Optional, Tuple, Set, DefaultDict, Any, Union, Deque
+from typing import List, Optional, Tuple, Set, DefaultDict, Any, Union, Deque, Iterable
 
 import requests
 from mapfmclient import MapfBenchmarker, Problem, Solution, MarkedLocation
+
 # from graphviz import Digraph
 
 row_factor = 2048
@@ -23,11 +24,13 @@ MDDGraph = Optional[DefaultDict[Tuple[CompactLocation, int], Set[Tuple[CompactLo
 JointSolution = List[Tuple[Tuple[CompactLocation, ...], int]]
 
 
-def compact_location(x,y):
+def compact_location(x, y):
     return x + y * row_factor
+
 
 def expand_location(c: CompactLocation):
     return (c % row_factor, c // row_factor)
+
 
 class Node:
     def __init__(self, parent, loc: CompactLocation, cost: int, heuristic: int):
@@ -85,7 +88,7 @@ class Maze:
         for c in all_children:
             if 0 <= c[0] < self.width and 0 <= c[1] < self.height:
                 if not self.grid[c[1]][c[0]]:
-                    good_children.append(compact_location(c[0],c[1]))
+                    good_children.append(compact_location(c[0], c[1]))
         return good_children
 
 
@@ -110,9 +113,9 @@ def astar(maze: Maze, start: CompactLocation, goal: CompactLocation) -> List[Tup
     return []
 
 
-
 class MDD:
-    def __init__(self, maze: Maze, agent: int, start: CompactLocation, goal: CompactLocation, depth: int, last_mdd=None):
+    def __init__(self, maze: Maze, agent: int, start: CompactLocation, goal: CompactLocation, depth: int,
+                 last_mdd=None):
         self.agent: int = agent
         self.start: CompactLocation = start
         self.goal: CompactLocation = goal
@@ -165,11 +168,11 @@ class MDD:
             return {self.goal}
         return self.level[i]
 
-    def get_children_at_node(self, node: CompactLocation, curr_depth: int) -> List[CompactLocation]:
+    def get_children_at_node(self, node: CompactLocation, curr_depth: int) -> Iterable[CompactLocation]:
         if self.goal == node and curr_depth >= self.depth:
             return [self.goal]
         else:
[…]

### 2021-04-30 main.py
Added accumulator to enhanced pruning

@@ -282,7 +282,7 @@ def prune_joint_children(joint_child_nodes, curr_nodes: List[CompactLocation]):
             lambda node: all_different(node) and not has_edge_collisions(curr_nodes, node), joint_child_nodes)
 
 
-def get_valid_children(mdds: List[MDD], curr_nodes: List[CompactLocation], curr_depth: int, unfold_mdds: bool = False):
+def get_valid_children(mdds: List[MDD], curr_nodes: List[CompactLocation], curr_depth: int, unfold_mdds: bool = False, accumulator: List = []):
     per_mdd_children = get_children_for_mdds(mdds, curr_nodes, curr_depth)
     all_joint_child_nodes = itertools.product(*per_mdd_children)
     pruned = prune_joint_children(all_joint_child_nodes, curr_nodes)
@@ -298,6 +298,7 @@ def get_valid_children(mdds: List[MDD], curr_nodes: List[CompactLocation], curr_
                 if not occurs:
                     if curr_depth < mdds[i].depth:
                         mdds[i].mdd[(node, curr_depth)].remove((child, curr_depth + 1))
+                        accumulator.append((i,(node, curr_depth),(child, curr_depth + 1)))
 
     return pruned
 
@@ -312,7 +313,7 @@ def get_valid_children(mdds: List[MDD], curr_nodes: List[CompactLocation], curr_
 #         return list(map(lambda p: p[0], self.mdd[(node, curr_depth)]))
 
 
-def seek_solution_in_joint_mdd(mdds: List[MDD], constructive: bool, unfold: bool = False) -> Union[bool, JointSolution]:
+def seek_solution_in_joint_mdd(mdds: List[MDD], constructive: bool, unfold: bool = False, accumulator: List = []) -> Union[bool, JointSolution]:
     for mdd in mdds:
         if not mdd.mdd:
             if constructive:
@@ -326,12 +327,12 @@ def seek_solution_in_joint_mdd(mdds: List[MDD], constructive: bool, unfold: bool
         solution, _ = joint_mdd_dfs_constructive(mdds, None, (roots, 0), max(depths), visited)
         return solution
     else:
-        found_path, visited = joint_mdd_dfs(mdds, (roots, 0), max(depths), visited, unfold)
+        found_path, visited = joint_mdd_dfs(mdds, (roots, 0), max(depths), visited, unfold, accumulator)
         return found_path
 
 
 def joint_mdd_dfs(mdds: List[MDD], curr: Tuple[Any, int], max_depth: int,
[…]

### 2021-05-06 src/mapfm/solve.py
Added handling of unsolvable matchings, worked on paper introduction

@@ -76,11 +76,12 @@ class Solver:
         min_sol = None
         for matching in matchings:
             sol = self.solve_matching(matching)
-            sic = sol.sic
-            if not min_sic or min_sic > sic:
-                min_sic = sic
-                min_sol = sol.solution
-                self.update_budget(min_sic)
+            if sol:
+                sic = sol.sic
+                if not min_sic or min_sic > sic:
+                    min_sic = sic
+                    min_sol = sol.solution
+                    self.update_budget(min_sic)
         subsols = list(zip(*min_sol))
         for subsol in subsols:
             paths.append(list(map(lambda loc: expand_location(loc), subsol)))
@@ -170,6 +171,8 @@ class Solver:
                     matching,
                     context
                 )
+                if not group_sol:
+                    return None
                 group_sic[merged_group] = group_sol.sic
                 group_agent_paths = list(zip(*group_sol.solution))
 

### 2021-05-21 src/map/map_parser.py
Generated some results and diagrams

@@ -45,9 +45,3 @@ class MapParser:
     def parse_batch(self, folder):
         paths = os.listdir(os.path.join(self.map_root, folder))
         return [self.parse_map(str(os.path.join(folder, path))) for path in paths]
-
-
-if __name__ == "__main__":
-    parser = MapParser("../maps")
-    problems = parser.parse_batch("test2")
-    print(problems)

### 2021-05-21 src/mapfm/ict_search.py

@@ -43,7 +43,7 @@ class ICTSearcher(object):
         self.open_spaces = find_number_of_open_spaces(maze)
         self.lower_sic_bound = 0
         self.budget = budget
-        self.debug = False
+        self.debug = True
 
     def calculate_upper_bound_cost(self, k: int):
         return (k ** 2) * self.open_spaces

### 2021-05-21 src/mapfm/mdd.py

@@ -1,8 +1,8 @@
 from collections import defaultdict, deque
 from typing import Optional, DefaultDict, Tuple, Set, Iterable, Deque
 
-# from graphviz import Digraph
-# from matplotlib import pyplot as plt
+from graphviz import Digraph
+from matplotlib import pyplot as plt
 
 from mapfm.compact_location import CompactLocation, expand_location
 from mapfm.maze import Maze
@@ -68,22 +68,23 @@ class MDD(object):
         else:
             return map(lambda p: p[0], self.mdd[(node, curr_depth)])
 
-    # def show(self):
-    #     items = list(sorted(self.mdd.items(), key=lambda x: x[0][2]))
-    #     g = Digraph(format="png")
-    #     added = set()
-    #     plt.tight_layout()
-    #     for ((loc, d), v) in items:
-    #         exp_loc = expand_location(loc)
-    #         node_str = str(exp_loc) + "," + str(d)
-    #         g.node(node_str)
-    #         for (c_loc, c_depth) in v:
-    #             exp_c_loc = expand_location(c_loc)
-    #             child_str = str(exp_c_loc) + "," + str(c_depth)
-    #             if not child_str in added:
-    #                 added.add(child_str)
-    #             g.edge(node_str, child_str)
-    #     return g
+    def show(self):
+        print(list(self.mdd.items())[0])
+        items = list(sorted(self.mdd.items(), key=lambda x: x[0][1]))
+        g = Digraph(format="png")
+        added = set()
+        plt.tight_layout()
+        for ((loc, d), v) in items:
+            exp_loc = expand_location(loc)
+            node_str = str(exp_loc) + "," + str(d)
+            g.node(node_str)
+            for (c_loc, c_depth) in v:
+                exp_c_loc = expand_location(c_loc)
+                child_str = str(exp_c_loc) + "," + str(c_depth)
+                if not child_str in added:
+                    added.add(child_str)
+                g.edge(node_str, child_str)
+        return g
 
 
 """

### 2021-05-21 src/mapfm/solve.py

@@ -17,14 +17,14 @@ def solve_api(problem: Problem) -> Solution:
     return solve(problem)[0]
 
 def solve_api_enum(problem: Problem) -> Solution:
-    return solve_enum(problem)[0]
+    return solve_enum_sorted(problem)[0]
 
 def solve(problem: Problem) -> Solution:
-    solver = Solver(problem, 3, prune = True, enhanced = True, id = True, conflict_avoidance = True, enumerative = False)
+    solver = Solver(problem, 3, prune = True, enhanced = True, id = False, conflict_avoidance = True, enumerative = False)
     return solver.solve()
 
 def solve_enum_sorted(problem: Problem) -> Solution:
-    solver = Solver(problem, 3, prune = True, enhanced = True, id = True, conflict_avoidance = True, enumerative = True, sorted = True)
+    solver = Solver(problem, 3, prune = True, enhanced = True, id = False, conflict_avoidance = True, enumerative = True, sorted = True)
     return solver.solve()
 
 def solve_enum(problem: Problem) -> Solution:

### 2021-05-21 src/bench.py
Cleaned up repo

@@ -99,7 +99,7 @@ def gen_problem_random(width,height,density,t,k_team):
     return Problem(grid, width, height, starts, goals)
 
 
-# computes success rate and mean solution time
+# computes success rate and avg + std run-time
 def process_results(solutions):
     return np.array([int(bool(x[1]) and bool(x[1][0])) for x in solutions]).mean(),np.array([x[2] for x in solutions]).mean(),np.array([x[2] for x in solutions]).std()
 
@@ -130,34 +130,6 @@ def test_queue(solver,map_parser, timeout, queue: BenchmarkQueue, output):
 
 if __name__ == "__main__":
     map_root = "../maps"
-    # for agent in range(1,11):
-    #     for team in [1,3]:
-    #         queue.add("Open-20x20-A{}_T{}".format(agent,team))
     map_parser = MapParser(map_root)
-    # os.system("cp /dev/null enum_sorted_results.txt; cp full_queue.txt queue.txt")
-    # test_queue(solve_enum_sorted,map_parser,30000, BenchmarkQueue("queue.txt"), "enum_sorted_results.txt")
-    # os.system("cp /dev/null enum_results.txt; cp full_queue.txt queue.txt")
-    # test_queue(solve_enum,map_parser,30000, BenchmarkQueue("queue.txt"), "enum_results.txt")
     os.system("cp /dev/null results.txt; cp full_queue.txt queue.txt")
     test_queue(solve,map_parser,30000, BenchmarkQueue("queue.txt"), "results.txt")
-    # # solve_debug(5)
-    # results_summary = []
-    # raw_sols = defaultdict(list)
-    # for team_size in [1, 2, 3, 4, 6, 12]:
-    #     enum_sols = solve_setting(solve_enum, 12//team_size, team_size, 300000, 16)
-    #     raw_sols[team_size].append(enum_sols)
-    #     enum_success, enum_mean_time = process_results(enum_sols)
-    #     print(enum_success, enum_mean_time)
-    #     results_summary.append((enum_success, enum_mean_time))
-    # # print(results_summary)
-    # # results_summary = np.array(results_summary)
-    # print(raw_sols)
-    # filename = 'raw_results.txt'
-    # outfile = open(filename, 'wb')
-    # pickle.dump(raw_sols, outfile)
-    # outfile.close()
-    # # infile = open(filename, 'rb')
-    # # loaded_raw_sols = pickle.load(infile)
-    # # print(loaded_raw_sols)
[…]

### 2021-05-21 src/mapfm/compact_location.py

@@ -1,4 +1,4 @@
-ROW_FACTOR = 2048
+ROW_FACTOR = 4096
 
 CompactLocation = int
 

### 2021-05-21 src/mapfm/ict_search.py

@@ -43,7 +43,7 @@ class ICTSearcher(object):
         self.open_spaces = find_number_of_open_spaces(maze)
         self.lower_sic_bound = 0
         self.budget = budget
-        self.debug = True
+        self.debug = False
 
     def calculate_upper_bound_cost(self, k: int):
         return (k ** 2) * self.open_spaces

### 2021-05-21 docs/paper-introduction.tex
Removed some dead/duplicate code

\documentclass[a4paper,10pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{sources.bib}
\usepackage{babel}

\title{Multi-Agent Path Finding with matching using Increasing Cost Tree Search}
\author{Thom van der Woude}
\newcommand{\namelistlabel}[1]{\mbox{#1}\hfil}
\newenvironment{namelist}[1]{%1
	\begin{list}{}
		{
			\let\makelabel\namelistlabel
			\settowidth{\labelwidth}{#1}
			\setlength{\leftmargin}{1.1\labelwidth}
		}
	}{
\end{list}}
\date{\today}

\begin{document}
	\maketitle
	\begin{namelist}{xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx}
		\item[{\bf Title:}]
		Multi-Agent Path Finding with matching using Increasing Cost Tree Search
		\item[{\bf Author:}]
		Thom van der Woude
		\item[{\bf Responsible Professor:}]
		Mathijs de Weerdt
		\item[{\bf Other Supervisor:}]
		Jesse Mulderij
		\item[{\bf Peer group members:}]
		Robbin Baauw, Jonathan Dönszelmann, Ivar de Bruin, Jaap de Jong
	\end{namelist}

	\section*{Introduction}
	The Dutch Railways (NS) company\footnote{\url{https://www.ns.nl/}} needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day. The problem of scheduling the trains to achieve this is called the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}. It is an NP-hard problem with many different subproblems in addition to the basic routing, such as the scheduling of personnel and coupling and decoupling of train units entering and leaving the yard. The company is interested in learning tighter upper-bounds for the capacity of their shunting yards but a problem is that in practical scenarios, only heuristics can solve TUSS instances (as was shown by Geiger et al. \cite{geiger2018}), which gives little information about what optimal solutions would look like and what could still be achieved using existing shunting infrastructure. To gain more insight into the capacity of shunting yards and the feasibility of problem instances, relaxations of TUSS can be useful. In \cite{mulderij2020}, the the multi-agent pathfinding (MAPF) problem extended \cite{stern2019} with a matching subproblem (hereafter MAPFM) is given as such a relaxation. Comparatively little research has been done on MAPFM, and the Conflict-Based Min-Cost-Flow algorithm by Ma and Koenig \cite{ma2016} is one of the few existing approaches to solving this more general problem along with the somewhat similar one described in \cite{henkel2019}. Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search. This work introduces a novel algorithm for solving MAPFM based on the Increasing Cost Tree Search (ICTS) algorithm for MAPF \cite{sharon2011}. ICTS, in short, is a two-level approach to MAPF with a top-level breadth-first traversal of an Increasing Cost Tree (ICT) representing combinations of per-agent path-lengths, and a bottom-level evaluation of ICT nodes using multi-value decision diagrams (MDDS) that represent for each agents all possible paths to the goal of a set length.

	Pathfinding is a problem with many applications ranging from navigation and network routing to solving puzzles like Sokoban \cite{junghanns1999}. When paths for different agents can conflict, they need to be planned together to find a non-conflicting combination, giving rise to the multi-agent pathfinding problem \cite{stern2019}. There exist two main classes of agent-goal assignments for MAPF in the literature: anonymous MAPF \cite{yu2013} wherein agents can be matched to any goal and non-anonymous or regular MAPF where each agent has a single matching goal. A further generalization of this is the target assignment and path finding (TAPF) problem described in \cite{ma2016}, wherein both agents and goals are partitioned into same-sized teams and agents can be matched to any goal of their team. TAPF is a relaxation of the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}, the problem of scheduling the cleaning and servicing of trains during the night in shunting yards. Specifically, in TUSS, each train unit has a type and a goal,

	\newpage
	\printbibliography
\end{document}

### 2021-05-21 docs/paper.tex
Removed some dead/duplicate code

\documentclass[english]{article}
\usepackage{geometry}
\usepackage{inputenc}
\geometry{verbose,tmargin=3.5cm,bmargin=4cm,lmargin=3.8cm,rmargin=3.8cm}
\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{sources.bib}
\makeatletter
\usepackage{url}
\makeatother
\usepackage{babel}

\begin{document}

\title{Multi-Agent Path Finding with matching using Increasing Cost Tree Search}

\author{Thom van der Woude}
\date{\today}

\maketitle

\section{Introduction}The Dutch Railways (NS) company\footnote{\url{https://www.ns.nl/}} needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day. The problem of scheduling the trains to achieve this is called the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}. It is an NP-hard problem with many different subproblems in addition to the basic routing, such as the scheduling of personnel and coupling and decoupling of train units entering and leaving the yard. The company is interested in learning tighter upper-bounds for the capacity of their shunting yards but a problem is that in practical scenarios, only heuristics can solve TUSS instances (as was shown by Geiger et al. \cite{geiger2018}), which gives little information about what optimal solutions would look like and what could still be achieved using existing shunting infrastructure. To gain more insight into the capacity of shunting yards and the feasibility of problem instances, Mulderij et al. \cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation that can be used to compute upper-bounds for TUSS instances by solving the corresponding MAPFM instances optimally.

Comparatively, little research has been done on MAPFM, and the Conflict-Based Min-Cost-Flow algorithm by Ma and Koenig \cite{ma2016} is one of the few existing approaches to optimally solve this more general problem along with the somewhat similar one described in \cite{henkel2019}. Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search. This begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?

This work is the outcome of a search for an efficient algorithm for optimally solving MAPFM derived from ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}. ICTS, in short, is a two-level approach to MAPF with a top-level breadth-first traversal of an Increasing Cost Tree (ICT) representing combinations of per-agent path-lengths, and a bottom-level evaluation of ICT nodes using multi-value decision diagrams (MDDS) that represent per agent all possible paths to the goal of a set length. In the context of a research project in which multiple such MAPF algorithms were taken as starting points for MAPFM algorithms within a peer group, the novel ICTS-based algorithm is compared to these algorithms on a set of standard benchmarks described in \cite{stern2019}, in addition to being analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}. Lastly, completeness of the algorithm is considered as this is an important property in the context of MAPFM as a TUSS relaxation. Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.
\printbibliography

\end{document}

### 2021-05-21 docs/tapf.tex
Removed some dead/duplicate code

--- 2021-04-21 tuss.tex
@@
 	\paragraph{First run-through}
-	Only heuristics can solve instances of the full TUSS problem currently, and little is known about the properties of the found solutions.
-Bounds for quality of heuristic solutions to TUSS instances are needed: only then can you really know what still can be achieved with current shunting yard capacity and an increasing number of trains, and can you say whether new investment is needed.
-This is why analysis of a relaxation is proposed as a way to establish bounds.
-
-	MAPF: abstract collision-free routing for robots/automated vehicles through environments.
-
-	Train Unit Shunting Problem (TUSP): the problem of parking and matching arriving train units to departures.
-Does not consider servicing at the yard!
-Maintainance/servicing tasks added as extensions, eventually resulting in the full Train Unit Shunting and Servicing problem: \cite{Artigues2014} first introduced full problem statement.
-Also showed only heuristic solutions are currently possible for practical instances.
-It envelopes everything that happens to a train outside of brining people from A to B.
-So the shunting of trains integrated with the scheduling of various servicing activities.
-	"The  main  objective  of  this  work  is  therefore  to  identify  whether  MAPF models (and algorithms) can be used or extended to provide a relaxation of the TUSS problem.
-The contributions of this paper include an introduction of TUSS from the viewpoint of MAPF, and an analysis of similarities and differences to arrive at a relaxation of TUSS based on MAPF"
-
-	Railway network: nodes/hubs are major cities.
-Hubs have both a station (for transport) and some yards (for shunting/servicing).
-Transport time-tables dictate the required output of the yards, as tuples of departure times and traintypes, but also when trains of certain types become available for further transport or service after reaching their destination.
-There is also a maintenance program dictating what tasks are to be done for specific train-types, dpeending on the state of the vehicle.
-
-	"Informally speaking, the objective of the Train  Unit  Shunting  and  Service Problem is  to  find  a  feasible  schedule  for  all  activities  required  to  take  train units from a station platform to a yard, find conflict-free routes to tracks that are needed for the trains to get serviced and parked, and deliver the trains to the  transportation  process  as  specified,  while  respecting  all  kinds  of  resource constraints."
-
-	Sub-problems: matching problem between trains to be delivered to transport system and those arriving/present in yard.
-There is also the resource-constrained scheduling of allocating service resources to trains that have to be serviced.
-Should consider conditional tasks.
-There is also the staff scheduling and rostering problem: staff can only drive trains for so long per day and so on.
-Then the parking problem: where to put the trains (that are perhaps waiting to be serviced)?
-This is like bin-packing.
-Then there is the coupling and decoupling problem to account for incombing and outbound train configurations, and the routing problem of driving trains from and to the yard without conflicts with transport/cargo trains and also visiting appropriate servicing/parking tracks.
-
-	Take-away: there is a lot of complexity, a lot of things that ideally should be planned at once.
-Current approach: plan sequentially: first solve matching for decoupled train units, schedule maintenance tasks and so on.
-
-	Bounds for hub capacity: depend on planning approach, 'dynamic' planning is used these days using up-to-date train-data.
-Current relaxed problem: models all subproblems except routing.
-Relaxed problem should be complete: no feasible solution to original problem should be infeasible when relaxed (so discarded)
-
-	Related work: \cite{Freling2002} first mathematically modelled TUSP with track assignment and matching considered seperately.
-From there many model improvements to eventually TUSS.
-Only heuristic solutions, things like annealing and machine learning/local search really seem to work.
-
-	A complete solver is needed to show feasibility or infeasibility of instances.
-
-	MAPF has already been solved at scale (see CBS, BCP), TUSS has not. Collision between agents? Branch and consider subproblems recursively.
-
-	Novelty of paper: relaxations of TUSS for working towards solving TUSS at scale.
-	\paragraph{MAPF definition that is extended}
-	MAPF statement: different from that other one with actions as functions. Uses a space-time graph (time-extended graph). Given connected undirected graph $G = (L,E)$ with
-	 locations $l \in L$, let $V = L \times \mathbb{Z}_+$ and let each $v = (l,t) \in V$ represent a combination of a location $l$ and time $t$.
-Now define the time-extended edge set $\hat E \subset V \times V$ with $e = (v_1,v_2) = ((l_1,t_1),(l_2,t_2))\in \hat E$ if and only if $t_2  = t_1 + 1$ and $(l_1,l_2)\in E$ or $l_1 = l_2$.
-Its reverse is defined as $e' = ((l_1,t_2),(l_2,t_1)) \in \hat E$ In words, this means that $\hat E$ represents points in space that can be reached at the next time-step if a certain action is chosen at the present time-step.
-Let $c(e) = 1$ denote the cost for each $e\in \hat E$.
-Let $a \in A$ be an agent with start and goal locations $s_a,g_a\in L$.
-A path $\pi$ of length $k\in\mathbb{Z}_+$ is a vector of locations $(l_0,l_1,\ldots,l_{k-1})$ where $l_0 = s_a, l_{k-1} = g_a$ and $((l_t,t),(l_{t+1},t+1))\in E_t$ for all $t\in\{0,1,\ldots,k-2\}$.
-For $t>k$ the agent is assumed to remain at $g_a$.
-
-	 What defines a solution then?
-A set of paths so that each vertex $v = (l,t)\in V$ is visited at most once and each edge $e$ and its reverse $e'$ are also visited in total at most once.
-Compare this to the more tedious formulation where feasible solutions had a quite complicated definition.
-
-	 Minimization: is there a set of paths $p_a$ with $a\in A$ such that the total cost of all edges in all paths $\sum_{a\in A} c(\pi_a) \leq k$ for some bound $k$?
-This is a PSPACE-complete decision problem.
-
-	 Note: matching is needed for MAPF to possibly be a relaxation of TUSS.
-
-	 Idea for instance translation: trains as agents, shunting yard as graph with tracks being represented by  a number of nodes (optimistic about the number of trains that could fit on it by dividing length by shortest train, rounding up).
-The goal is to now find paths to these tracks on which certain services can be performed so that trains collide neither on tracks or abstractly in resource allocation.
-
-	 \paragraph{Extensions}
-	 Approach: starting with MAPF with matching, define series of progressively more detailed relaxations of TUSS.
-
-	 Second extension: direction of movement of trains is factored in. Third: set of service tasks is included for each agent. Fourth, some additional possible extensions in brief.
-
-	 Matching: a bit like multi-commodity flow problem.
-Compositions of train units are set to leave the yard for transport, but unit identity is irrelevant, only type is considered.
-In reality these are coupled but this is first left out: it also only relaxes the problem further formally.
-Key assumption: as many train units of each type arrive as depart for the total problem instance.
-However, each agent $a$ is assigned an expected arrival time $t$ so that it's start node is $(l,t)\in V$ (not in $L$!), and also get assigned a type $o\in O$.
-Similarly, goal nodes get a $t$ so that they are also in $V$ and are marked with a certain train type that is to leave at that place and time.
-So $g = \{g_1 = (l_1,t_1,o_i),\ldots, g_n\}$.
-
-	 In practice you could have $t=0$ for all 'arrivals'/start nodes and fix departure times with the problem still being a relaxation.
-
-	 Direction of movement extension would have it cost $c_{rev}$ to reverse direction at a node.
-This is done by turning each node $v$ into a $v_l,v_r$ pair indicating leftward or rightward movement and an edge with cost $c_{rev}$ between them (and the implicit constraint that there can be at most one agent in total in $v_l,v_r$).
-This turns the problem into a variation of weighted MAPF.
-
-	 Including service tasks is important for the relaxation to really be relevant to TUSS and not just something like TUSP.
-Service tasks can be modelled as waypoints that agents should pass on their path.
-This means that on the per-agent level, you should do something not unlike TSP.
-Such a formulation ensures that order that the tasks are performed in is not considered, only completion of all tasks is and that agents can move over 'task'-nodes like any other location on the graph, possibly temporarely blocking other agents that need to be serviced there and so on.
-
-	 Other extensions:
-	 Some locations cannot be used for parking (track changes/platforms): waiting is limited to few time-steps. Removing all wait edges there may not yield a relaxation always.
-
-	 The relation between train units, their servicing and trains as sequences of units is still an open question in modelling TUSS relaxations.
-
-	 How to model tracks more realistically? Pair train types with lengths and add constraints so that the trains on the nodes making up a track do not exceed the total length of the modelled track.
-
-	 Planning of personnel is important: drivers, maintenance crews, cleaners.
-Each have their expertise, are time-limited, and also have to physically make their way from one service track or train to the next.
-You could argue that when you want to learn the raw top capacity of an expensive shunting yard, you should not think about this too much.
-
-	 Next: you could star tlooking at motion-planning-like things: trains have variable speed, changing momentum takes time, and because of this and other safety requirements there are limits on speed and the minimum time between two trains crossing the same track change and similar locations.
-Formulating this as strictly a relaxation is difficult (you can easily be too strict).
-
-	 \paragraph{Conclusion}
-	 There are many practical details in TUSS: many subproblems to consider and factor in.
-To work towards upper-bound analysis, the MAPF with matching relaxation is considered and a naïve method of converting between TUSS and relaxed MAPF with matching instances is given.
-The space-time-graph formulation is interesting as it enables simple modelling of arrival and departure times of different units.
-Direction and cost of reversal can easily be modelled, although it does require considering the properties of weighted MAPF.
-Task waypoints can model servicing/maintenance work that has to be done.
-
-	 Something totally different: consider restrictions rather than relaxations to limit the search for solutions.
-
-	 Lastly: there is more to TUSS and therefore relaxations than feasibility: cost in terms of personnel and so on is also relevant and should ideally be minimized.
-Practically, this could be done by minimizing simultaneous actions in solutions.
-At this point there simply isn't much 'choice' in picking solutions however: you just have to hope that what the heuristic search outputs is good.
+	\[\mathcal{O}(k_{t_{max}}!)\]
+	\[t_{max}\]
+	\[k_{t_{max}}\]
 	\printbibliography

### 2021-05-21 src/bench.py

@@ -129,7 +129,7 @@ def test_queue(solver,map_parser, timeout, queue: BenchmarkQueue, output):
 
 
 if __name__ == "__main__":
-    map_root = "../maps"
+    map_root = "maps"
     map_parser = MapParser(map_root)
     os.system("cp /dev/null results.txt; cp full_queue.txt queue.txt")
     test_queue(solve,map_parser,30000, BenchmarkQueue("queue.txt"), "results.txt")

### 2021-05-21 src/mapfm/astar.py

@@ -9,10 +9,6 @@ from mapfm.node import Node
 def astar(
     maze: Maze, start: CompactLocation, goal: CompactLocation
 ) -> List[Tuple[int, int]]:
-    """
-
-    :rtype: object
-    """
     ls: List[Node] = [Node(None, start, 0, manhattan_norm(start, goal))]
     heapq.heapify(ls)
     seen: Set[CompactLocation] = set()

### 2021-05-21 src/mapfm/flow.py

@@ -1,26 +1,0 @@
-class FlowEdge:
-    __slots__ = ["u", "v", "c", "rev"]
-
-    def __init__(self, u, v, c, rev):
-        self.u = u
-        self.v = v
-        self.c = c
-        self.rev = rev
-
-
-class FlowNode:
-    def __init__(self, id):
-        self.id = id
-        self.edges = []
-
-    def add_edge(self, other_id, capacity):
-        self.edges.append(FlowEdge(self.id, other_id, capacity, False))
-        self.edges.append(FlowEdge(other_id, self.id, capacity, True))
-
-
-def edmonds_karp(graph, s, t):
-    return graph
-
-
-if __name__ == "__main__":
-    print("Hello")

### 2021-05-21 src/mapfm/mdd_search.py

@@ -103,15 +103,6 @@ def seek_solution_in_joint_mdd(
         return found_path
 
 
-def sample_context_node(context: IDContext, depth: int):
-    return list(
-        map(
-            lambda agent: index_path(context.paths[agent], depth, context.lens[agent]),
-            context.other_agents,
-        )
-    )
-
-
 def joint_mdd_dfs(
     mdds: List[MDD],
     curr: Tuple[Any, int],
@@ -130,8 +121,8 @@ def joint_mdd_dfs(
         return True, visited
     children = get_valid_children(mdds, curr_nodes, curr_depth, unfold, accumulator)
     if context:
-        curr_context = sample_context_node(context, curr_depth)
-        next_context = sample_context_node(context, curr_depth + 1)
+        curr_context = context.sample_context_node(curr_depth)
+        next_context = context.sample_context_node(curr_depth + 1)
         children.sort(
             key=lambda child: count_conflicts(
                 curr_context + list(curr_nodes), next_context + list(child)
@@ -167,8 +158,8 @@ def joint_mdd_dfs_constructive(
         return [curr], visited
     children = get_valid_children(mdds, curr_nodes, curr_depth)
     if context:
-        curr_context = sample_context_node(context, curr_depth)
-        next_context = sample_context_node(context, curr_depth + 1)
+        curr_context = context.sample_context_node(curr_depth)
+        next_context = context.sample_context_node(curr_depth + 1)
         children.sort(
             key=lambda child: count_conflicts(
                 curr_context + list(curr_nodes), next_context + list(child)

### 2021-05-21 src/mapfm/solve.py

@@ -20,11 +20,11 @@ def solve_api_enum(problem: Problem) -> Solution:
     return solve_enum_sorted(problem)[0]
 
 def solve(problem: Problem) -> Solution:
-    solver = Solver(problem, 3, prune = True, enhanced = True, id = False, conflict_avoidance = True, enumerative = False)
+    solver = Solver(problem, 3, prune = True, enhanced = True, id = True, conflict_avoidance = True, enumerative = False)
     return solver.solve()
 
 def solve_enum_sorted(problem: Problem) -> Solution:
-    solver = Solver(problem, 3, prune = True, enhanced = True, id = False, conflict_avoidance = True, enumerative = True, sorted = True)
+    solver = Solver(problem, 3, prune = True, enhanced = True, id = True, conflict_avoidance = True, enumerative = True, sorted = True)
     return solver.solve()
 
 def solve_enum(problem: Problem) -> Solution:

### 2021-05-21 src/bench.py
Fixed some unused imports and other small things

@@ -1,36 +1,30 @@
 import os
-from collections import defaultdict
-from math import floor
-
 from mapfmclient import Problem, MarkedLocation
 import random
 import numpy as np
-import pickle
-
-from map.map_parser import MapParser
-from mapfm.solve import solve, solve_enum, solve_enum_sorted
-from slim_testbench import TestBench, TimeoutSolver
+from parsing.map_parser import MapParser
+from mapfm.solve import solve
+from slim_testbench import TestBench
 
 
 class BenchmarkQueue:
-
     def __init__(self, name):
         self.name = name
-        with open(name, 'a'):
+        with open(name, "a"):
             pass
 
     def get_next(self):
-        with open(self.name, 'r') as f:
+        with open(self.name, "r") as f:
             return f.readline().strip()
 
     def completed(self):
-        with open(self.name, 'r') as fin:
+        with open(self.name, "r") as fin:
             data = fin.read().splitlines(True)
-        with open(self.name, 'w') as fout:
+        with open(self.name, "w") as fout:
             fout.writelines(data[1:])
 
     def add(self, data):
-        with open(self.name, 'a') as f:
+        with open(self.name, "a") as f:
             f.write(data + "\n")
 
 
@@ -55,8 +49,7 @@ def gen_legal_point(taken, grid, width, height):
     return point
 
 
-
-def gen_agent_goals(grid, width, height, t,k_team):
+def gen_agent_goals(grid, width, height, t, k_team):
     starts = []
     goals = []
     taken_starts = set()
@@ -88,35 +81,42 @@ def show_problem(grid, width, height, starts, goals):
         print(s)
     return starts, goals
 
-def gen_problem(width,height,density,t,k_team):
+
+def gen_problem(width, height, density, t, k_team):
     grid = gen_rand_grid(width, height, density)
-    starts, goals = gen_agent_goals(grid, width, height, t,k_team)
+    starts, goals = gen_agent_goals(grid, width, height, t, k_team)
     return Problem(grid, width, height, starts, goals)
 
-def gen_problem_random(width,height,density,t,k_team):
+
+def gen_problem_random(width, height, density, t, k_team):
     grid = gen_rand_grid(width, height, density)
-    starts, goals = gen_agent_goals(grid, width, height, t,k_team)
+    starts, goals = gen_agent_goals(grid, width, height, t, k_team)
[…]

### 2021-05-21 src/main.py

@@ -6,9 +6,7 @@ import requests
 from mapfmclient import (
     MapfBenchmarker,
     Problem,
-    MarkedLocation,
-    BenchmarkDescriptor,
-    ProgressiveDescriptor,
+    MarkedLocation
 )
 
 from mapfm.solve import solve, solve_api, solve_api_enum

### 2021-05-21 src/mapfm/ict_search.py

@@ -1,4 +1,4 @@
-from collections import deque, defaultdict
+from collections import deque
 from itertools import combinations
 from typing import List, Tuple, Optional
 
@@ -24,7 +24,19 @@ class ICTSolution:
 
 
 class ICTSearcher(object):
-    __slots__ = ["maze", "combs", "team_combs","prune", "enhanced", "open_spaces", "budget","max_delta","lower_sic_bound","debug"]
+    __slots__ = [
+        "maze",
+        "combs",
+        "team_combs",
+        "prune",
+        "enhanced",
+        "open_spaces",
+        "budget",
+        "max_delta",
+        "lower_sic_bound",
+        "debug",
+    ]
+
     def __init__(
         self,
         maze: Maze,
@@ -77,7 +89,7 @@ class ICTSearcher(object):
         context: Optional[IDContext] = None,
     ):
         n_teams = len(team_agent_indices)
-        for combs in range(2,min(4,n_teams)):
+        for combs in range(2, min(4, n_teams)):
             for c in combinations(range(n_teams), combs):
                 indices = []
                 skip = False
@@ -92,7 +104,11 @@ class ICTSearcher(object):
                 if skip:
                     continue
                 if not seek_solution_in_joint_mdd(
-                    [mdds[i] for i in indices], False, self.enhanced, accumulator, context
+                    [mdds[i] for i in indices],
+                    False,
+                    self.enhanced,
+                    accumulator,
+                    context,
                 ):
                     return indices
         return None
@@ -103,11 +119,11 @@ class ICTSearcher(object):
         k: int,
         accumulator: List = [],
         context: Optional[IDContext] = None,
-        agents = None,
+        agents=None,
     ):
         if agents:
             if k > 2:
-                for combs in [2,3]:
+                for combs in [2, 3]:
                     for c in combinations(range(k), combs):
                         team = agents[c[0]][1]
                         skip = True
@@ -117,19 +133,23 @@ class ICTSearcher(object):
                                 break
 
                         if not skip and not seek_solution_in_joint_mdd(
-                            [mdds[i] for i in c], False, self.enhanced, accumulator, context
+                            [mdds[i] for i in c],
+                            False,
+                            self.enhanced,
+                            accumulator,
+                            context,
                         ):
                             return c
         else:
             if k > self.combs:
-                for c in combinations(range(k),self.combs):
+                for c in combinations(range(k), self.combs):
                     if not seek_solution_in_joint_mdd(
-                            [mdds[i] for i in c], False, self.enhanced, accumulator, context
[…]

### 2021-05-21 src/mapfm/id_context.py

@@ -2,7 +2,7 @@ from mapfm.util import index_path
 
 
 class IDContext:
-    def __init__(self, other_sum,other_agents, paths, lens):
+    def __init__(self, other_sum, other_agents, paths, lens):
         self.other_sum = other_sum
         self.other_agents = other_agents
         self.paths = paths

### 2021-05-21 src/mapfm/mdd_search.py

@@ -10,7 +10,6 @@ from mapfm.conflicts import (
 )
 from mapfm.id_context import IDContext
 from mapfm.mdd import MDD
-from mapfm.util import index_path
 
 JointSolution = List[Tuple[CompactLocation, ...]]
 JointTimedSolution = List[Tuple[Tuple[CompactLocation, ...], int]]

### 2021-05-21 src/mapfm/solve.py

@@ -12,24 +12,54 @@ from mapfm.maze import Maze
 from mapfm.util import index_path
 
 
-
 def solve_api(problem: Problem) -> Solution:
     return solve(problem)[0]
+
 
 def solve_api_enum(problem: Problem) -> Solution:
     return solve_enum_sorted(problem)[0]
 
+
 def solve(problem: Problem) -> Solution:
-    solver = Solver(problem, 3, prune = True, enhanced = True, id = True, conflict_avoidance = True, enumerative = False)
+    solver = Solver(
+        problem,
+        3,
+        prune=True,
+        enhanced=True,
+        id=True,
+        conflict_avoidance=True,
+        enumerative=False,
+    )
     return solver.solve()
+
 
 def solve_enum_sorted(problem: Problem) -> Solution:
-    solver = Solver(problem, 3, prune = True, enhanced = True, id = True, conflict_avoidance = True, enumerative = True, sorted = True)
+    solver = Solver(
+        problem,
+        3,
+        prune=True,
+        enhanced=True,
+        id=True,
+        conflict_avoidance=True,
+        enumerative=True,
+        sorted=True,
+    )
     return solver.solve()
 
+
 def solve_enum(problem: Problem) -> Solution:
-    solver = Solver(problem, 3, prune = True, enhanced = True, id = True, conflict_avoidance = True, enumerative = True, sorted = False)
+    solver = Solver(
+        problem,
+        3,
+        prune=True,
+        enhanced=True,
+        id=True,
+        conflict_avoidance=True,
+        enumerative=True,
+        sorted=False,
+    )
     return solver.solve()
+
 
 def enumerate_matchings(agents, tasks):
     if agents:
@@ -77,7 +107,7 @@ class Solver:
         "enumerative",
         "ict_searcher",
         "path_cache",
-        "sorted"
+        "sorted",
     ]
 
     def __init__(
@@ -89,7 +119,7 @@ class Solver:
         id: bool,
         conflict_avoidance: bool,
         enumerative: bool,
-        sorted: bool = True
+        sorted: bool = True,
     ):
         self.problem = problem
         self.k = len(problem.starts)
@@ -100,7 +130,7 @@ class Solver:
         self.conflict_avoidance = conflict_avoidance
         self.id = id
         self.enumerative = enumerative
-        self.ict_searcher = ICTSearcher(self.maze, combs, prune, enhanced,self.k)
[…]

### 2021-05-21 src/parsing/map_parser.py

@@ -4,7 +4,6 @@ from mapfmclient import MarkedLocation, Problem
 
 
 class MapParser:
-
     def __init__(self, map_root):
         self.map_root = map_root
 

### 2021-05-21 src/slim_testbench.py

@@ -12,7 +12,9 @@ class TimeoutSolver:
 
     def __call__(self, current_problem):
         try:
-            sol = func_timeout(self.timeout / 1000, self.solver, args=(current_problem,))
+            sol = func_timeout(
+                self.timeout / 1000, self.solver, args=(current_problem,)
+            )
 
         except FunctionTimedOut:
             sol = None
@@ -24,6 +26,7 @@ class TimeoutSolver:
 
 # https://stackoverflow.com/questions/62186218/python-multiprocessing-attributeerror-cant-pickle-local-object
 # I wonder why this approach (like rust closures) is not default...
+
 
 class TimingFunction:
     def __init__(self, solve_func):
@@ -46,20 +49,17 @@ class TestBench:
             solve_func = self.solver
         time_func = TimingFunction(solve_func)
         if self.cores == 1:
-            solutions = list(tqdm(
-                map(time_func, problem_list),
-                total=len(problem_list)
-            ))
+            solutions = list(
+                tqdm(map(time_func, problem_list), total=len(problem_list))
+            )
         elif self.cores == -1:
             with Pool() as p:
-                solutions = list(tqdm(
-                    p.imap(time_func, problem_list),
-                    total=len(problem_list)
-                ))
+                solutions = list(
+                    tqdm(p.imap(time_func, problem_list), total=len(problem_list))
+                )
         else:
             with Pool(self.cores) as p:
-                solutions = list(tqdm(
-                    p.imap(time_func, problem_list),
-                    total=len(problem_list)
-                ))
+                solutions = list(
+                    tqdm(p.imap(time_func, problem_list), total=len(problem_list))
+                )
         return solutions

### 2021-05-21 src/test/test_conflicts.py

@@ -1,7 +1,6 @@
 import unittest
-from typing import List, Tuple
 
-from mapfm.compact_location import CompactLocation, compact_location
+from mapfm.compact_location import compact_location
 from mapfm.conflicts import *
 
 

### 2021-05-21 src/bench.py
Made Solver callable, worked on typing

@@ -3,7 +3,7 @@ from mapfmclient import Problem, MarkedLocation
 import random
 import numpy as np
 from parsing.map_parser import MapParser
-from mapfm.solve import solve
+from mapfm.solve import solve, solve_enum
 from slim_testbench import TestBench
 
 
@@ -122,7 +122,7 @@ def test_queue(solver, map_parser, timeout, queue: BenchmarkQueue, output):
             enum_sols = bench.solve_problems(solver, problems)
             res, mean, std = process_results(enum_sols)
             f.write(f"{task}, {res}, {mean}, {std}\n")
-            print(f"{task}: {res} with average {mean}s and deviaton: {std}\n")
+            print(f"{task}: {res} with average {mean}s and deviation: {std}\n")
             queue.completed()
             task = queue.get_next()
 
@@ -131,4 +131,6 @@ if __name__ == "__main__":
     map_root = "maps"
     map_parser = MapParser(map_root)
     os.system("cp /dev/null results.txt; cp full_queue.txt queue.txt")
-    test_queue(solve, map_parser, 30000, BenchmarkQueue("queue.txt"), "results.txt")
+    test_queue(
+        solve_enum, map_parser, 30000, BenchmarkQueue("queue.txt"), "results.txt"
+    )

### 2021-05-21 src/main.py

@@ -3,11 +3,7 @@ import sys
 from pprint import pprint
 
 import requests
-from mapfmclient import (
-    MapfBenchmarker,
-    Problem,
-    MarkedLocation
-)
+from mapfmclient import MapfBenchmarker, Problem, MarkedLocation
 
 from mapfm.solve import solve, solve_api, solve_api_enum
 

### 2021-05-21 src/mapfm/compact_location.py

@@ -1,6 +1,9 @@
+from typing import Tuple
+
 ROW_FACTOR = 4096
 
 CompactLocation = int
+CompactLocationDepth = Tuple[CompactLocation, int]
 
 
 def compact_location(x, y):

### 2021-05-21 src/mapfm/conflicts.py

@@ -1,5 +1,5 @@
 from collections import defaultdict
-from typing import List, Optional, Tuple
+from typing import List, Optional, Tuple, Iterable, TypeVar, Sized, DefaultDict, Set
 
 from mapfm.compact_location import CompactLocation
 
@@ -10,8 +10,11 @@ from mapfm.compact_location import CompactLocation
 #     seen = set()
 #     return not any(i in seen or seen.add(i) for i in xs)
 
+Conflict = Tuple[int, int]
+a = TypeVar("a")
 
-def all_different(xs):
+
+def all_different(xs: List[a]):
     return len(set(xs)) == len(xs)
 
 
@@ -19,8 +22,8 @@ def is_invalid_move(curr_locs, next_locs):
     return not all_different(curr_locs) or has_edge_collisions(curr_locs, next_locs)
 
 
-def all_different_constructive(xs) -> Optional[Tuple[int, int]]:
-    loc_agent = defaultdict(set)
+def all_different_constructive(xs: Iterable[CompactLocation]) -> Optional[Conflict]:
+    loc_agent: DefaultDict[CompactLocation, Set[int]] = defaultdict(set)
     for (i, curr_loc) in enumerate(xs):
         if len(loc_agent[curr_loc]) > 0:
             return list(loc_agent[curr_loc])[0], i
@@ -29,9 +32,9 @@ def all_different_constructive(xs) -> Optional[Tuple[int, int]]:
     return None
 
 
-def count_all_different(xs) -> int:
+def count_all_different(xs: Iterable[CompactLocation]) -> int:
     count = 0
-    loc_agent = defaultdict(set)
+    loc_agent: DefaultDict[CompactLocation, Set[int]] = defaultdict(set)
     for (i, curr_loc) in enumerate(xs):
         if len(loc_agent[curr_loc]) > 0:
             count += 1
@@ -57,7 +60,7 @@ def count_conflicts(curr_locs, next_locs) -> int:
     return count_all_different(curr_locs) + count_edge_collsions(curr_locs, next_locs)
 
 
-def edge_collisions_constructive(curr_locs, next_locs) -> Optional[Tuple[int, int]]:
+def edge_collisions_constructive(curr_locs, next_locs) -> Optional[Conflict]:
     for (i, ei) in filter(
         lambda p: p[1][0] != p[1][1], enumerate(zip(curr_locs, next_locs))
     ):
[…]

### 2021-05-21 src/mapfm/ict_search.py

@@ -1,6 +1,6 @@
 from collections import deque
 from itertools import combinations
-from typing import List, Tuple, Optional
+from typing import List, Tuple, Optional, Dict
 
 from mapfm.compact_location import CompactLocation
 from mapfm.id_context import IDContext
@@ -47,7 +47,7 @@ class ICTSearcher(object):
         budget: Optional[int] = None,
     ):
         self.maze = maze
-        self.max_delta = [0] * (max_k + 1)
+        self.max_delta: List[int] = [0] * (max_k + 1)
         self.combs = combs
         self.team_combs = combs
         self.prune = prune
@@ -168,7 +168,7 @@ class ICTSearcher(object):
         frontier = deque()
         frontier.append(root)
         visited = set()
-        mdd_cache = dict()
+        mdd_cache: Dict[Tuple[int, int], MDD] = dict()
         team_lens = dict()
         for team in team_goals:
             team_lens[team] = len(team_goals[team])

### 2021-05-21 src/mapfm/mdd.py

@@ -4,12 +4,15 @@ from typing import Optional, DefaultDict, Tuple, Set, Iterable, Deque
 from graphviz import Digraph
 from matplotlib import pyplot as plt
 
-from mapfm.compact_location import CompactLocation, expand_location
+from mapfm.compact_location import (
+    CompactLocation,
+    expand_location,
+    CompactLocationDepth,
+)
 from mapfm.maze import Maze
 
-MDDGraph = Optional[
-    DefaultDict[Tuple[CompactLocation, int], Set[Tuple[CompactLocation, int]]]
-]
+TimeExpandedGraph = DefaultDict[CompactLocationDepth, Set[CompactLocationDepth]]
+MDDGraph = Optional[TimeExpandedGraph]
 
 
 class MDD(object):
@@ -28,7 +31,7 @@ class MDD(object):
         self.start: CompactLocation = start
         self.goals: Set[CompactLocation] = goals
         self.depth: int = depth
-        self.bfs_tree = {}
+        self.bfs_tree: dict = {}
         self.mdd: MDDGraph = None
         self.level: DefaultDict[int, Set[CompactLocation]] = defaultdict(set)
         if last_mdd and last_mdd.depth < depth and last_mdd.agent == agent:
@@ -47,10 +50,10 @@ class MDD(object):
         if mdd:
             self.populate_levels(self.mdd)
 
-    def populate_levels(self, mdd: MDDGraph):
+    def populate_levels(self, graph: TimeExpandedGraph):
         # all nodes except the start are children of other nodes at a level given by the depth
         self.level[0] = {self.start}
-        for children_sets in mdd.values():
+        for children_sets in graph.values():
             for child in children_sets:
                 self.level[child[1]].add(child[0])
 
@@ -98,7 +101,7 @@ TLDR: turns a child-parents structure into a parent-children structure with some
 
 
 def mdd_from_tree(
-    tree: DefaultDict[Tuple[CompactLocation, int], Set[Tuple[CompactLocation, int]]],
+    tree: DefaultDict[CompactLocationDepth, Set[CompactLocationDepth]],
     goals: Set[CompactLocation],
     depth: int,
 ) -> MDDGraph:
@@ -111,7 +114,7 @@ def mdd_from_tree(
         return None
     visited = set()
     mdd = defaultdict(set)
-    trace_list = deque()
[…]

### 2021-05-21 src/mapfm/solve.py

@@ -20,9 +20,8 @@ def solve_api_enum(problem: Problem) -> Solution:
     return solve_enum_sorted(problem)[0]
 
 
-def solve(problem: Problem) -> Solution:
+def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
     solver = Solver(
-        problem,
         3,
         prune=True,
         enhanced=True,
@@ -30,35 +29,33 @@ def solve(problem: Problem) -> Solution:
         conflict_avoidance=True,
         enumerative=False,
     )
-    return solver.solve()
+    return solver(problem)
 
 
-def solve_enum_sorted(problem: Problem) -> Solution:
+def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
     solver = Solver(
-        problem,
         3,
         prune=True,
         enhanced=True,
         id=True,
         conflict_avoidance=True,
         enumerative=True,
-        sorted=True,
+        sort_matchings=True,
     )
-    return solver.solve()
+    return solver(problem)
 
 
-def solve_enum(problem: Problem) -> Solution:
+def solve_enum(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
     solver = Solver(
-        problem,
-        3,
+        combs=3,
         prune=True,
         enhanced=True,
         id=True,
         conflict_avoidance=True,
         enumerative=True,
-        sorted=False,
+        sort_matchings=False,
     )
-    return solver.solve()
+    return solver(problem)
 
 
 def enumerate_matchings(agents, tasks):
@@ -107,34 +104,41 @@ class Solver:
         "enumerative",
         "ict_searcher",
         "path_cache",
-        "sorted",
+        "sort_matchings",
     ]
 
     def __init__(
         self,
-        problem: Problem,
         combs: int,
         prune: bool,
         enhanced: bool,
         id: bool,
         conflict_avoidance: bool,
         enumerative: bool,
-        sorted: bool = True,
+        sort_matchings: bool = True,
     ):
-        self.problem = problem
-        self.k = len(problem.starts)
-        self.maze: Maze = Maze(problem.grid, problem.width, problem.height)
         self.max_k_solved = 0
         self.combs = combs
         self.prune = prune
         self.conflict_avoidance = conflict_avoidance
         self.id = id
         self.enumerative = enumerative
-        self.ict_searcher = ICTSearcher(self.maze, combs, prune, enhanced, self.k)
         self.path_cache = dict()
-        self.sorted = sorted
[…]

### 2021-05-21 src/mapfm/ict_search.py
Cleaned up solve module using SolverConfig

@@ -62,7 +62,7 @@ class ICTSearcher(object):
 
     def check_within_teams(
         self,
-        team_agent_indices: List[List[int]],
+        team_agent_indices: Dict[int, List[int]],
         mdds: List[MDD],
         accumulator: List = [],
         context: Optional[IDContext] = None,

### 2021-05-21 src/mapfm/mdd.py

@@ -1,5 +1,5 @@
 from collections import defaultdict, deque
-from typing import Optional, DefaultDict, Tuple, Set, Iterable, Deque
+from typing import Optional, DefaultDict, Tuple, Set, Iterable, Deque, Dict
 
 from graphviz import Digraph
 from matplotlib import pyplot as plt
@@ -130,7 +130,7 @@ def mdd_from_tree(
 
 
 def construct_bfs_tree(maze: Maze, start: CompactLocation, depth: int):
-    fringe = deque()
+    fringe: Deque[CompactLocationDepth] = deque()
     fringe.append((start, 0))
     # DAG represented by child-parents map. This formulation makes it easier to construct the path(s) from the parents
     # to the child later, similar to the get_directions function in the A* Node class
@@ -139,7 +139,7 @@ def construct_bfs_tree(maze: Maze, start: CompactLocation, depth: int):
     return main_bfs_loop(maze, depth, fringe, prev_dict, visited)
 
 
-def bootstrap_depth_d_bfs_tree(maze: Maze, depth: int, old_tree):
+def bootstrap_depth_d_bfs_tree(maze: Maze, depth: int, old_tree: Dict):
     fringe = deque()
     old_fringe = list(old_tree["fringe"])
     old_fringe.sort()

### 2021-05-21 src/mapfm/solve.py

@@ -21,20 +21,20 @@ def solve_api_enum(problem: Problem) -> Solution:
 
 
 def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
-    solver = Solver(
-        3,
+    config = SolverConfig(
+        combs=3,
         prune=True,
         enhanced=True,
         id=True,
         conflict_avoidance=True,
         enumerative=False,
     )
-    return solver(problem)
+    return Solver(config, problem)()
 
 
 def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
-    solver = Solver(
-        3,
+    config = SolverConfig(
+        combs=3,
         prune=True,
         enhanced=True,
         id=True,
@@ -42,11 +42,11 @@ def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], 
         enumerative=True,
         sort_matchings=True,
     )
-    return solver(problem)
+    return Solver(config, problem)()
 
 
 def solve_enum(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
-    solver = Solver(
+    config = SolverConfig(
         combs=3,
         prune=True,
         enhanced=True,
@@ -55,7 +55,7 @@ def solve_enum(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
         enumerative=True,
         sort_matchings=False,
     )
-    return solver(problem)
+    return Solver(config, problem)()
 
 
 def enumerate_matchings(agents, tasks):
@@ -90,20 +90,14 @@ def merge_groups(agent_groups, group_i, group_j):
     return new_agent_groups
 
 
-class Solver:
+class SolverConfig:
     __slots__ = [
-        "problem",
-        "k",
-        "max_k_solved",
-        "maze",
         "combs",
         "prune",
         "enhanced",
         "id",
         "conflict_avoidance",
         "enumerative",
-        "ict_searcher",
-        "path_cache",
         "sort_matchings",
     ]
 
@@ -117,28 +111,42 @@ class Solver:
         enumerative: bool,
         sort_matchings: bool = True,
     ):
-        self.max_k_solved = 0
         self.combs = combs
         self.prune = prune
-        self.conflict_avoidance = conflict_avoidance
-        self.id = id
-        self.enumerative = enumerative
-        self.path_cache = dict()
         self.enhanced = enhanced
+        self.id = id
+        self.conflict_avoidance = conflict_avoidance
[…]

### 2021-05-21 src/mapfm/id_context.py
Recast MAPF as TAPF instance

@@ -9,6 +9,7 @@ class IDContext:
         self.lens = lens
         self.len = 0
         self.path = []
+        self.cache = dict()
 
     def sample_context_node(self, depth: int):
         while depth >= self.len:

### 2021-05-21 src/mapfm/solve.py

@@ -172,14 +172,15 @@ class Solver:
             min_sic = None
             min_sol = None
             for (matching, _) in rooted_matchings:
-                sol = self.solve_matching(matching)
+                team_agent_indices = dict(map(lambda x: (x,{x}),agents))
+                team_goals = dict(map(lambda x: (x[0],{x[1][1]}),enumerate(matching)))
+                sol = self.solve_tapf_instance(agents, team_agent_indices, team_goals)
                 if sol:
                     sic = sol.sic
                     if not min_sic or min_sic > sic:
                         min_sic = sic
                         min_sol = sol.solution
                         self.update_budget(min_sic)
-            # print("Enumerative SIC: " + str(min_sic))
             subsols = list(zip(*min_sol))
             for subsol in subsols:
                 paths.append(list(map(lambda loc: expand_location(loc), subsol)))
@@ -194,11 +195,9 @@ class Solver:
                     for team in teams
                 ]
             )
-            # print(agents, teams, team_goals, team_agent_indices)
             min_sol = self.solve_tapf_instance(agents, team_agent_indices, team_goals)
             if min_sol:
                 subsols = list(zip(*min_sol.solution))
-                # print("Native SIC: " + str(min_sol.sic))
                 for subsol in subsols:
                     paths.append(list(map(lambda loc: expand_location(loc), subsol)))
             else:
@@ -234,23 +233,28 @@ class Solver:
         team_goals,
         context: Optional[IDContext] = None,
     ):
-        subproblems = []
-        root_list = []
-        for agent in agents:
-            min_len = None
-            for goal in team_goals[agent[1]]:
-                subproblems.append((agent[0], goal))
-                shortest_path = astar(self.maze, agent[0], goal)
-                if not shortest_path:
-                    return None
-                assert len(shortest_path) > 0
-                if not min_len or min_len >= len(shortest_path):
-                    min_len = len(shortest_path)
-            root_list.append(min_len - 1)
-        root = tuple(root_list)
+        root = self.compute_root_m(agents,team_goals)
         return self.ict_searcher.search_tapf(
             agents, team_agent_indices, team_goals, root, context
         )
+
+    def compute_root_m(self,agents,team_goals):
+        root_list = []
+        for agent in agents:
+            min_c = None
+            start = agent[0]
+            for goal in team_goals[agent[1]]:
+                if not (start, goal) in self.path_cache:
+                    shortest_path = astar(self.maze, start, goal)
[…]

### 2021-05-21 src/mapfm/ict_search.py
Removed duplicate MAPF code

@@ -2,7 +2,6 @@ from collections import deque
 from itertools import combinations
 from typing import List, Tuple, Optional, Dict
 
-from mapfm.compact_location import CompactLocation
 from mapfm.id_context import IDContext
 from mapfm.maze import Maze
 from mapfm.mdd import MDD
@@ -259,83 +258,6 @@ class ICTSearcher(object):
                         node_list[i] += 1
                         if not tuple(node_list) in visited:
                             frontier.append(tuple(node_list))
-                for (i, p, c) in accumulator:
-                    mdds[i].mdd[p].add(c)
-        return None
-
-    def search(
-        self,
-        subproblems: List[Tuple[CompactLocation, CompactLocation]],
-        root: Tuple[int, ...],
-        context: Optional[IDContext] = None,
-    ) -> Optional[ICTSolution]:
-        k = len(subproblems)
-        budget = self.get_budget(k)
-        if self.budget and context:
-            budget -= context.other_sum
-        frontier = deque()
-        frontier.append(root)
-        visited = set()
-        mdd_cache = dict()
-        root_cost = sum(root)
-        cost = root_cost
-        if self.debug:
-            print(k, budget, root)
-        while frontier:
-            node = frontier.popleft()
-            if (self.lower_sic_bound - k) <= sum(
-                node
-            ) <= budget and not node in visited:
-                if self.debug:
-                    if sum(node) > cost:
-                        cost = sum(node)
-                        print(cost)
-                self.max_delta[k] = max(self.max_delta[k], sum(node) - root_cost)
-                accumulator = []
-                visited.add(node)
-                mdds = []
-                for (i, c) in enumerate(node):
-                    if not (i, c) in mdd_cache:
-                        if (i, c - 1) in mdd_cache:
-                            mdd_cache[(i, c)] = MDD(
-                                self.maze,
-                                i,
-                                subproblems[i][0],
-                                {subproblems[i][1]},
-                                c,
-                                mdd_cache[(i, c - 1)],
-                            )
-                        else:
-                            mdd_cache[(i, c)] = MDD(
-                                self.maze, i, subproblems[i][0], {subproblems[i][1]}, c
-                            )
-                    mdds.append(mdd_cache[(i, c)])
-                conflict_combination = None
-                if self.prune and k > self.combs:
-                    conflict_combination = self.check_combinations(
-                        mdds, k, accumulator, context
-                    )
-
-                if not conflict_combination:
[…]

### 2021-05-21 src/mapfm/solve.py

@@ -172,8 +172,8 @@ class Solver:
             min_sic = None
             min_sol = None
             for (matching, _) in rooted_matchings:
-                team_agent_indices = dict(map(lambda x: (x,{x}),agents))
-                team_goals = dict(map(lambda x: (x[0],{x[1][1]}),enumerate(matching)))
+                team_agent_indices = dict(map(lambda x: (x, {x}), agents))
+                team_goals = dict(map(lambda x: (x[0], {x[1][1]}), enumerate(matching)))
                 sol = self.solve_tapf_instance(agents, team_agent_indices, team_goals)
                 if sol:
                     sic = sol.sic
@@ -214,12 +214,6 @@ class Solver:
     def update_lower_sic(self, lower_sic):
         self.ict_searcher.lower_sic_bound = lower_sic
 
-    def solve_matching(self, matching: List[Tuple[CompactLocation, CompactLocation]]):
-        if self.config.id:
-            return self.solve_mapf_with_id(matching)
-        else:
-            return self.solve_mapf(matching)
-
     def solve_tapf_instance(self, agents, team_agent_indices, team_goals):
         if self.config.id:
             return self.solve_tapf_with_id(agents, team_agent_indices, team_goals)
@@ -233,12 +227,12 @@ class Solver:
         team_goals,
         context: Optional[IDContext] = None,
     ):
-        root = self.compute_root_m(agents,team_goals)
+        root = self.compute_root_m(agents, team_goals)
         return self.ict_searcher.search_tapf(
             agents, team_agent_indices, team_goals, root, context
         )
 
-    def compute_root_m(self,agents,team_goals):
+    def compute_root_m(self, agents, team_goals):
         root_list = []
         for agent in agents:
             min_c = None
@@ -273,14 +267,6 @@ class Solver:
                 self.path_cache[(start, goal)] = c
                 root_list.append(c)
         return tuple(root_list)
-
-    def solve_mapf(
-        self,
-        matching: List[Tuple[CompactLocation, CompactLocation]],
-        context: Optional[IDContext] = None,
-    ) -> Optional[ICTSolution]:
-        root = self.compute_root(matching)
-        return self.ict_searcher.search(matching, root, context)
 
     def solve_tapf_group(
         self,
@@ -386,91 +372,6 @@ class Solver:
 
                 for (i, agent_index) in enumerate(group_agent_indices):
                     agent_paths[agent_index] = group_agent_paths[i]
[…]

### 2021-05-21 src/mapfm/ict_search.py
Added debug to SolverConfig

@@ -43,6 +43,7 @@ class ICTSearcher(object):
         prune: bool,
         enhanced: bool,
         max_k: int,
+        debug: bool,
         budget: Optional[int] = None,
     ):
         self.maze = maze
@@ -53,8 +54,8 @@ class ICTSearcher(object):
         self.enhanced = enhanced
         self.open_spaces = find_number_of_open_spaces(maze)
         self.lower_sic_bound = 0
+        self.debug = debug
         self.budget = budget
-        self.debug = False
 
     def calculate_upper_bound_cost(self, k: int):
         return (k ** 2) * self.open_spaces

### 2021-05-21 src/mapfm/solve.py

@@ -28,6 +28,7 @@ def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
         id=True,
         conflict_avoidance=True,
         enumerative=False,
+        debug=False,
     )
     return Solver(config, problem)()
 
@@ -41,6 +42,7 @@ def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], 
         conflict_avoidance=True,
         enumerative=True,
         sort_matchings=True,
+        debug=False,
     )
     return Solver(config, problem)()
 
@@ -54,6 +56,7 @@ def solve_enum(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
         conflict_avoidance=True,
         enumerative=True,
         sort_matchings=False,
+        debug = False,
     )
     return Solver(config, problem)()
 
@@ -98,6 +101,7 @@ class SolverConfig:
         "id",
         "conflict_avoidance",
         "enumerative",
+        "debug",
         "sort_matchings",
     ]
 
@@ -109,6 +113,7 @@ class SolverConfig:
         id: bool,
         conflict_avoidance: bool,
         enumerative: bool,
+        debug: bool,
         sort_matchings: bool = True,
     ):
         self.combs = combs
@@ -118,6 +123,7 @@ class SolverConfig:
         self.conflict_avoidance = conflict_avoidance
         self.enumerative = enumerative
         self.sort_matchings = sort_matchings
+        self.debug = debug
 
 
 class Solver:
@@ -144,6 +150,7 @@ class Solver:
             self.config.prune,
             self.config.enhanced,
             self.k,
+            self.config.debug
         )
 
     def __call__(self) -> Tuple[Optional[Solution], List[int], int]:

### 2021-05-21 src/mapfm/ict_search.py
Extracted function for getting node MDDs from cache, more type hints

@@ -1,6 +1,6 @@
 from collections import deque
 from itertools import combinations
-from typing import List, Tuple, Optional, Dict
+from typing import List, Tuple, Optional, Dict, Deque
 
 from mapfm.id_context import IDContext
 from mapfm.maze import Maze
@@ -34,6 +34,7 @@ class ICTSearcher(object):
         "max_delta",
         "lower_sic_bound",
         "debug",
+        "mdd_cache",
     ]
 
     def __init__(
@@ -56,6 +57,7 @@ class ICTSearcher(object):
         self.lower_sic_bound = 0
         self.debug = debug
         self.budget = budget
+        self.mdd_cache: Dict[Tuple[int, int], MDD] = dict()
 
     def calculate_upper_bound_cost(self, k: int):
         return (k ** 2) * self.open_spaces
@@ -149,11 +151,31 @@ class ICTSearcher(object):
                         return c
         return None
 
-    def get_budget(self, k):
+    def get_budget(self, k: int):
         if self.budget:
             return self.budget
         else:
             return self.calculate_upper_bound_cost(k)
+
+    def get_node_mdds(self, node, agents, team_goals):
+        mdds = []
+        for (i, c) in enumerate(node):
+            if not (i, c) in self.mdd_cache:
+                if (i, c - 1) in self.mdd_cache:
+                    self.mdd_cache[(i, c)] = MDD(
+                        self.maze,
+                        i,
+                        agents[i][0],
+                        team_goals[agents[i][1]],
+                        c,
+                        self.mdd_cache[(i, c - 1)],
+                    )
+                else:
+                    self.mdd_cache[(i, c)] = MDD(
+                        self.maze, i, agents[i][0], team_goals[agents[i][1]], c
+                    )
+            mdds.append(self.mdd_cache[(i, c)])
+        return mdds
 
     def search_tapf(
         self,
@@ -163,16 +185,16 @@ class ICTSearcher(object):
         root,
         context: Optional[IDContext] = None,
     ) -> Optional[ICTSolution]:
+        self.mdd_cache = dict()
         k = len(agents)
         budget = self.get_budget(k)
-        frontier = deque()
+        frontier: Deque[Tuple[int, ...]] = deque()
         frontier.append(root)
         visited = set()
-        mdd_cache: Dict[Tuple[int, int], MDD] = dict()
         team_lens = dict()
         for team in team_goals:
             team_lens[team] = len(team_goals[team])
[…]

### 2021-05-21 src/mapfm/mdd.py

@@ -134,13 +134,13 @@ def construct_bfs_tree(maze: Maze, start: CompactLocation, depth: int):
     fringe.append((start, 0))
     # DAG represented by child-parents map. This formulation makes it easier to construct the path(s) from the parents
     # to the child later, similar to the get_directions function in the A* Node class
-    prev_dict = defaultdict(set)
-    visited = set()
+    prev_dict: Dict[CompactLocationDepth, Set[CompactLocationDepth]] = defaultdict(set)
+    visited: Set[CompactLocationDepth] = set()
     return main_bfs_loop(maze, depth, fringe, prev_dict, visited)
 
 
 def bootstrap_depth_d_bfs_tree(maze: Maze, depth: int, old_tree: Dict):
-    fringe = deque()
+    fringe: Deque[CompactLocationDepth] = deque()
     old_fringe = list(old_tree["fringe"])
     old_fringe.sort()
     fringe.extend(old_fringe)
@@ -158,14 +158,14 @@ def main_bfs_loop(
     depth: int,
     fringe: Deque[CompactLocationDepth],
     prev_dict,
-    visited,
+    visited: Set[CompactLocationDepth],
 ):
     depth_d_plus_one_fringe = set()
     fringe_prevs = defaultdict(set)
     while fringe:
         curr = fringe.popleft()
         loc, d = curr
-        children: Iterable[Tuple[CompactLocation, int]] = map(
+        children: Iterable[CompactLocationDepth] = map(
             lambda c: (c, d + 1), maze.get_valid_children(loc)
         )
         for c in children:

### 2021-05-21 src/mapfm/mdd_search.py

@@ -89,7 +89,7 @@ def seek_solution_in_joint_mdd(
                 return False
     roots: Tuple[Any] = tuple(map(lambda mdd: mdd.start, mdds))
     depths: Iterable[int] = map(lambda mdd: mdd.depth, mdds)
-    visited = set()
+    visited: Set[Tuple[List[CompactLocation], int]] = set()
     if constructive:
         solution, _ = joint_mdd_dfs_constructive(
             mdds, None, (roots, 0), max(depths), visited, context

### 2021-05-21 src/mapfm/solve.py

@@ -56,7 +56,7 @@ def solve_enum(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
         conflict_avoidance=True,
         enumerative=True,
         sort_matchings=False,
-        debug = False,
+        debug=False,
     )
     return Solver(config, problem)()
 
@@ -150,7 +150,7 @@ class Solver:
             self.config.prune,
             self.config.enhanced,
             self.k,
-            self.config.debug
+            self.config.debug,
         )
 
     def __call__(self) -> Tuple[Optional[Solution], List[int], int]:

### 2021-05-25 docs/plan.tex
Added advanced pruning, speeded up hashing
Added handling of unsolvable matchings, worked on paper introduction
Made pruned child generation an option

@@
 \usepackage{babel}
+\usepackage[normalem]{ulem}
 
@@
 	\end{enumerate}
-	\paragraph{Week 3} \textbf{This week: first ACS session (7-5 8:45-10:45)}
+	\paragraph{Week 3} \textbf{This week: first ACS session (7-5 8:45-10:45), deadline for 300 word section for paper, the introduction (6-5 23:59)}
 	\begin{enumerate}
@@
 		\item[24-5 ] (Whit monday)
-		\item[25-5 ] Aim to finish up evaluation of algorithms, in particular comparison with algorithms derived within peer group.
+		\item[25-5 ] \sout{Aim to finish up evaluation of algorithms, in particular comparison with algorithms derived within peer group.} Evaluate pruning extension, adapt code to be fully configurable in terms of both pruning mechanisms and corresponding child-generation rules.
 		\item[26-5 ] Start processing of experimental data and analysis of results
@@
 	\end{enumerate}
+
+\newpage
 	\printbibliography
-
 \end{document}

### 2021-05-25 src/bench.py

@@ -3,7 +3,7 @@ from mapfmclient import Problem, MarkedLocation
 import random
 import numpy as np
 from parsing.map_parser import MapParser
-from mapfm.solve import solve, solve_enum
+from mapfm.solve import solve, solve_enum, solve_enum_sorted
 from slim_testbench import TestBench
 
 
@@ -132,5 +132,5 @@ if __name__ == "__main__":
     map_parser = MapParser(map_root)
     os.system("cp /dev/null results.txt; cp full_queue.txt queue.txt")
     test_queue(
-        solve_enum, map_parser, 1000, BenchmarkQueue("queue.txt"), "results.txt"
+        solve, map_parser, 30000, BenchmarkQueue("queue.txt"), "results.txt"
     )

### 2021-05-25 src/mapfm/ict_search.py

@@ -24,6 +24,8 @@ class ICTSolution:
         self.sic = sic
 
 
+
+
 class ICTSearcher(object):
     __slots__ = [
         "maze",
@@ -31,6 +33,7 @@ class ICTSearcher(object):
         "team_combs",
         "prune",
         "enhanced",
+        "pruned_child_gen",
         "open_spaces",
         "budget",
         "max_delta",
@@ -45,6 +48,7 @@ class ICTSearcher(object):
         combs: int,
         prune: bool,
         enhanced: bool,
+        pruned_child_gen: bool,
         max_k: int,
         debug: bool,
         budget: Optional[int] = None,
@@ -55,6 +59,7 @@ class ICTSearcher(object):
         self.team_combs = combs
         self.prune = prune
         self.enhanced = enhanced
+        self.pruned_child_gen = pruned_child_gen
         self.open_spaces = find_number_of_open_spaces(maze)
         self.lower_sic_bound = 0
         self.debug = debug
@@ -209,57 +214,95 @@ class ICTSearcher(object):
                 visited.add(node)
                 mdds = self.get_node_mdds(node, problem)
 
-                conflict_team_combination = None
-                if len(problem.team_agent_indices) > 1:
-                    conflict_team_combination = self.check_within_teams(
-                        problem,
-                        mdds,
-                        accumulator,
-                        context,
-                    )
-
-                if not conflict_team_combination:
-                    conflict_combination = None
-                    if self.prune and k > self.combs:
-                        conflict_combination = self.check_combinations(
-                            mdds, k, accumulator, context, problem.agents
+                if self.pruned_child_gen:
+                    conflict_team_combination = None
+                    if len(problem.team_agent_indices) > 1:
+                        conflict_team_combination = self.check_within_teams(
+                            problem,
+                            mdds,
+                            accumulator,
+                            context,
                         )
 
-                    if not conflict_combination:
-                        conflict_team_comb = None
-                        if len(problem.team_agent_indices) > self.team_combs:
-                            conflict_team_comb = self.check_team_combinations(
-                                problem, mdds, accumulator, context
+                    if not conflict_team_combination:
+                        conflict_combination = None
+                        if self.prune and k > self.combs:
+                            conflict_combination = self.check_combinations(
+                                mdds, k, accumulator, context, problem.agents
                             )
-                        if not conflict_team_comb:
-                            if self.lower_sic_bound <= node_sum:
-                                solution: JointTimedSolution = seek_solution_in_joint_mdd(
[…]

### 2021-05-25 src/mapfm/solve.py

@@ -19,19 +19,21 @@ def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
         combs=2,
         prune=True,
         enhanced=True,
+        pruned_child_gen=False,
         id=True,
         conflict_avoidance=True,
         enumerative=False,
-        debug=True,
+        debug=False,
     )
     return Solver(config, problem)()
 
 
 def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
     config = SolverConfig(
-        combs=2,
+        combs=3,
         prune=True,
         enhanced=True,
+        pruned_child_gen=False,
         id=True,
         conflict_avoidance=True,
         enumerative=True,
@@ -46,6 +48,7 @@ def solve_enum(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
         combs=2,
         prune=True,
         enhanced=True,
+        pruned_child_gen=False,
         id=True,
         conflict_avoidance=True,
         enumerative=True,

### 2021-05-25 src/mapfm/solver.py

@@ -70,6 +70,7 @@ class Solver:
             self.config.combs,
             self.config.prune,
             self.config.enhanced,
+            self.config.pruned_child_gen,
             self.k,
             self.config.debug,
         )
@@ -90,7 +91,7 @@ class Solver:
         )
         if self.config.enumerative:
             matchings: List[List[Tuple[CompactLocation,CompactLocation]]] = enumerate_matchings(agents, goals)
-            print(matchings)
+            # print(matchings)
             if self.config.sort_matchings:
                 rooted_matchings = list(
                     map(lambda m: (m, sum(self.compute_root(map(lambda x: x[1],m)))), matchings)
@@ -100,7 +101,7 @@ class Solver:
                 rooted_matchings = list(map(lambda m: (m, 0), matchings))
             min_sic = None
             min_sol = None
-            print(len(rooted_matchings))
+            # print(len(rooted_matchings))
             for (matching, _) in rooted_matchings:
                 team_agent_indices = dict(map(lambda x: (x[1][1], {x[0]}), enumerate(agents)))
                 team_goals = dict(map(lambda x: (x[0], {x[1][1]}), matching))

### 2021-05-25 src/mapfm/solver_config.py

@@ -8,6 +8,7 @@ class SolverConfig:
         "enumerative",
         "debug",
         "sort_matchings",
+        "pruned_child_gen",
     ]
 
     def __init__(
@@ -15,6 +16,7 @@ class SolverConfig:
         combs: int,
         prune: bool,
         enhanced: bool,
+        pruned_child_gen: bool,
         id: bool,
         conflict_avoidance: bool,
         enumerative: bool,
@@ -28,4 +30,5 @@ class SolverConfig:
         self.conflict_avoidance = conflict_avoidance
         self.enumerative = enumerative
         self.sort_matchings = sort_matchings
+        self.pruned_child_gen = pruned_child_gen
         self.debug = debug

### 2021-05-25 src/bench.py
Fixed root generation bug

@@ -132,5 +132,5 @@ if __name__ == "__main__":
     map_parser = MapParser(map_root)
     os.system("cp /dev/null results.txt; cp full_queue.txt queue.txt")
     test_queue(
-        solve, map_parser, 30000, BenchmarkQueue("queue.txt"), "results.txt"
+        solve_enum_sorted, map_parser, 30000, BenchmarkQueue("queue.txt"), "results.txt"
     )

### 2021-05-25 src/mapfm/solve.py

@@ -19,7 +19,7 @@ def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
         combs=2,
         prune=True,
         enhanced=True,
-        pruned_child_gen=False,
+        pruned_child_gen=True,
         id=True,
         conflict_avoidance=True,
         enumerative=False,
@@ -32,7 +32,7 @@ def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], 
     config = SolverConfig(
         combs=3,
         prune=True,
-        enhanced=True,
+        enhanced=False,
         pruned_child_gen=False,
         id=True,
         conflict_avoidance=True,
@@ -47,7 +47,7 @@ def solve_enum(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
     config = SolverConfig(
         combs=2,
         prune=True,
-        enhanced=True,
+        enhanced=False,
         pruned_child_gen=False,
         id=True,
         conflict_avoidance=True,

### 2021-05-25 src/mapfm/solver.py

@@ -112,9 +112,12 @@ class Solver:
                         min_sic = sic
                         min_sol = sol.solution
                         self.update_budget(min_sic)
-            subsols = list(zip(*min_sol))
-            for subsol in subsols:
-                paths.append(list(map(lambda loc: expand_location(loc), subsol)))
+            if min_sol:
+                subsols = list(zip(*min_sol))
+                for subsol in subsols:
+                    paths.append(list(map(lambda loc: expand_location(loc), subsol)))
+            else:
+                return None, self.ict_searcher.max_delta, self.max_k_solved
         else:
             teams = set(map(lambda a: a.color, self.problem.starts))
             team_goals = dict(
@@ -174,12 +177,11 @@ class Solver:
                     shortest_path = astar(self.maze, start, goal)
                     if not shortest_path:
                         return None
-                    self.path_cache[(start, goal)] = len(shortest_path)
+                    self.path_cache[(start, goal)] = len(shortest_path) - 1
                 c = self.path_cache[(start, goal)]
-                assert c > 0
                 if not min_c or min_c >= c:
                     min_c = c
-            root_list.append(min_c - 1)
+            root_list.append(min_c)
         return tuple(root_list)
 
     def compute_root(
@@ -194,7 +196,6 @@ class Solver:
                 shortest = astar(self.maze, start, goal)
                 if not shortest:
                     return None
-                assert len(shortest) > 0
                 c = len(shortest) - 1
                 self.path_cache[(start, goal)] = c
                 root_list.append(c)

### 2021-05-31 docs/paper-template.tex
Worked on logic for testing different solver configs systematically, worked on paper

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{verbose,tmargin=3.5cm,bmargin=4cm,lmargin=3.8cm,rmargin=3.8cm}

\makeatletter
\usepackage{url}

\makeatother

\usepackage{babel}
\begin{document}

\title{Research Paper Template}

\author{Mathijs de Weerdt}
\date{}

\maketitle

\begin{abstract}
The abstract should be short and give the overall idea:
what is the background, the research questions, what is contribution, and what are the main conclusions.
It should be readable as a stand-alone text (preferably no references to the paper or outside literature).
\end{abstract}

\section{Introduction}
\begin{itemize}
\item Introduce the topic and explain why it is important (motivation!). %\emph{How should a scientific paper look like?}

\item Relate to the most relevant existing work from the literature (use BibTeX), explain their contributions, and (critically) indicate what is still unanswered. 
%\emph{The existing state of the art describes the setup of general scientific papers, e.g.\ see~\cite{hengl2002rules}, but this may be different for computer science papers.}

\item Explain what the research questions for this work are. 
This usually is a subset of the unanswered questions. %\emph{The aim of this work is therefore to provide a good template specifically for papers in the field of computer science.}

\item Summarize the main contributions/conclusions of this research.
NB: Make sure the title of the paper is a good match to the main research question / contribution / conclusion.

\item Briefly indicate how the rest of the paper fits together to answer the research question.
\end{itemize}

For a longer research paper, a section with more elaborate discussion of the literature may follow, but for short (conference) submissions, this is often included in the introduction.

\section{Methodology or Problem Description}
Choose one that fits your research best:
\subsection{Methodology}
Typically in general research articles, the second section contains a description of the research methodology, explaining what you, the researcher, is doing to answer the research question(s), and why you have chosen this method.
For purely analytical work this is a description of the data collection or experimental setup on how to test the hypothesis, with a motivation.
In any case this section includes references to necessary background information.

\subsection{Formal Problem Description}
For some types of work in computer science the methodology is standard: analyze the problem (e.g., make assumptions and derive properties), present a new algorithm and its theoretical background, proving its correctness, and evaluate unproven aspects in simulation.
Then an explanation of the methodology is often omitted, and the setup of the evaluation is part of a later section on the evaluation of the ideas.\footnote{This already shows that there is no single outline to be given for all papers.}
In this case, explain relevant concepts, theory and models in this section (with references) and relate them to your research question.
Also this section then typically contains a more precise, formal description of the problem.

Do not forget to give this section another name, for example after the problem you are solving.

\section{Your contribution}
In computer science typically the third section contains an exposition of the main ideas, for example the development of a theory, the analysis of the problem (some proofs), a new algorithm, and potentially some theoretical analysis of the properties of the algorithm.

Do not forget to give this section another name, for example after the method or idea you are presenting.

Some more detailed suggestions for typical types of contributions in computer science are described in the following subsections.

\subsection*{Experimental work}
In this case, this section will mostly contain a description of the methods/algorithms you will be comparing. Although not all methods need to be described in detail (providing appropriate references are available), make sure that you reveal sufficient details to a reader not familiar with these methods to: a) obtain a high-level understanding of the method and differences between them, and b) understand your explanation of the results.

\subsection*{Improvement of an idea}
In this case, you would need to explain in detail how the improvement works. If it is based on some observation that can be proven, this is a good place to provide that proof (e.g., of the correctness of your approach).

%\subsection*{Literature survey}
%If your contribution is a literature survey, then the organization of these ``middle'' sections very much depends on the way you want to present/organize the literature you are discussing.
%First try to cluster papers that are similar in some aspect. Then think of how these clusters are related, from that you can think of a good order to discuss these clusters;this is sometimes called a bottom-up approach to writing a paper.
%
%In addition, you may try to think about the organization of the literature from a top-down perspective: try to ``take a step back'' and think about the field and what important questions/variants are and build a hierarchical categorization of the field.

\section{Experimental Setup and Results}
As discussed earlier, in many sciences the methodology is explained in section 2 and this section only discusses the results. 
However, in computer science, most often the details of the evaluation setup are described here first (simulation environment, etc.).
Very important here is that any skilled reader would be able to reproduce this setup and then obtain the same results.

Then, results are reported in an accessible manner through figures (preferably with captions that allow them to be understood without going through the whole text), observations are made that clearly follow from the presented results.
Conclusions are drawn that follow logically from the previous material.
Sometimes the conclusions are in fact hypotheses, which in turn may give rise to new experiments to be validated.

You may want to give this section another name.

\section{Responsible Research}
Reflect on the ethical aspects of your research and discuss the reproducibility of your methods.

\section{Discussion}
Results can be compared to known results and placed in a broader context.
Provide a reflection on what has been concluded and how this was done.
Then give a further possible explanation of results.

You may give this section another name, or merge it with the one before or the one hereafter.

\section{Conclusions and Future Work}
Summarize the research question(s) and the answers to the research question(s).
Make statements.
Highlight interesting elements.

Discuss open issues, possible improvements, and new questions that arise from this work; formulate recommendations for further research.

ideally, this section can stand on its own: it should be readable without having read the earlier sections.

\appendix
\section{The obvious}
\subsection{Reference use}
\begin{itemize}
\item use a system for generating the bibliographic information automatically from your database, e.g., use BibTex and/or Mendeley, EndNote, Papers, or \ldots
\item all ideas, fragments, figures and data that have been quoted from other work have correct references
\item literal quotations have quotation marks and page numbers
\item paraphrases are not too close to the original
\item the references and bibliography meet the requirements
\item every reference in the text corresponds to an item in the bibliography and vice versa
\end{itemize}

\subsection{Structure}
Paragraphs
\begin{itemize}
\item are well-constructed
\item are not too long: each paragraph discusses one topic
\item start with clear topic sentences
\item are divided into a clear paragraph structure
\item there is a clear line of argumentation from research question to conclusions
\item scientific literature is reviewed critically
\end{itemize}

\subsection{Style}
\begin{itemize}
\item correct use of English: understandable, no spelling errors, acceptable grammar, no lexical mistakes 
\item the style used is objective
\item clarity: sentences are not too complicated (not too long), there is no ambiguity
\item attractiveness: sentence length is varied, active voice and passive voice are mixed
\end{itemize}

\subsection{Tables and figures}
\begin{itemize}
\item all have a number and a caption
\item all are referred to at least once in the text
\item if copied, they contain a reference
\item can be interpreted on their own (e.g. by means of a legend)
\end{itemize}

\bibliographystyle{plain}
\bibliography{template}

\end{document}

### 2021-05-31 docs/paper.tex
Worked on logic for testing different solver configs systematically, worked on paper

@@
 
-\title{Multi-Agent Path Finding with matching using Increasing Cost Tree Search}
+	\title{Multi-Agent Path Finding with Matching using Increasing Cost Tree Search}
 
-\author{Thom van der Woude}
-\date{\today}
+	\author{Thom van der Woude\and Jesse Mulderij\and Mathijs de Weerdt}
+	\date{}
 
@@
 
-\section{Introduction}The Dutch Railways (NS) company\footnote{\url{https://www.ns.nl/}} needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day.
+	\begin{abstract}
+		Both the assignment problem and the multi-agent pathfinding problem are common problems in fields from robotics to transportation.
+The joint problem of finding matchings inducing an optimal non-conflicting routing of agents to their goals is something that has not been studied much.
+Few methods exist today that solve it although the problems do appear together in real-world problems, such as in the Train Unit Shunting and Servicing problem.
+In this work, a novel method based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding is presented that can optimally solve this joint problem.
+	\end{abstract}
+
+	\section{Introduction}
+	The Dutch Railways (NS) company\footnote{\url{https://www.ns.nl/}} needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day.
 The problem of scheduling the trains to achieve this is called the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}.
 It is an NP-hard problem with many different subproblems in addition to the basic routing, such as the scheduling of personnel and coupling and decoupling of train units entering and leaving the yard.
-The company is interested in learning tighter upper-bounds for the capacity of their shunting yards but a problem is that in practical scenarios, only heuristics can solve TUSS instances (as was shown by Geiger et al.
-\cite{geiger2018}), which gives little information about what optimal solutions would look like and what could still be achieved using existing shunting infrastructure.
+% introduce heuristics here.
+
+	The company is interested in learning tighter upper-bounds for the capacity of their shunting yards, but in practical scenarios, only heuristics can solve TUSS instances (as was shown by Geiger et al.
+\cite{geiger2018}).
+Heuristic solutions are often sub-optimal and give little information about what optimal solutions would look like and what could still be achieved using existing shunting infrastructure.
 To gain more insight into the capacity of shunting yards and the feasibility of problem instances, Mulderij et al.
@@
 Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
-This begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?
+It begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?
 
 	This work is the outcome of a search for an efficient algorithm for optimally solving MAPFM derived from ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}.
-ICTS, in short, is a two-level approach to MAPF with a top-level breadth-first traversal of an Increasing Cost Tree (ICT) representing combinations of per-agent path-lengths, and a bottom-level evaluation of ICT nodes using multi-value decision diagrams (MDDS) that represent per agent all possible paths to the goal of a set length.
-In the context of a research project in which multiple such MAPF algorithms were taken as starting points for MAPFM algorithms within a peer group, the novel ICTS-based algorithm is compared to these algorithms on a set of standard benchmarks described in \cite{stern2019}, in addition to being analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.
-Lastly, completeness of the algorithm is considered as this is an important property in the context of MAPFM as a TUSS relaxation.
+ICTS, in short, is a two-level approach to MAPF with a top-level breadth-first traversal of an Increasing Cost Tree (ICT) representing combinations of per-agent path costs and a bottom-level evaluation of ICT nodes using multi-valued decision diagrams (MDDS).
+These MDDS represent per agent all possible paths to the goal of a set length.
+In the context of a research project in which multiple such MAPF algorithms were taken as starting points for MAPFM algorithms within a group, the novel ICTS-based algorithm is compared to these algorithms on a set of benchmarks similar to those described in \cite{stern2019}.
+In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.
+Lastly, completeness of the algorithm is considered as this is a key property in the context of MAPFM as a TUSS relaxation.
 Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.
+
+	\section{Multi-agent pathfinding with matching} % Problem description
+	MAPFM is the problem of finding agent-goal matchings that induce a non-conflicting routing of agents to their goals.
+Each matching corresponds to a MAPF instance, so each feasible matching has an optimal solution, i.e.
+a solution with a minimal Sum of Individual Costs (SIC).
+In approaching MAPFM as a TUSS relaxation to find upper-bounds for instances, optimal MAPFM solutions are the most interesting as they can characterise such upper-bounds.
+Furthermore, defining optimality as minimal SIC corresponds more closely to TUSS objective functions such as personnel cost than the other common MAPF objective, minimal makespan.
+Optimally solving MAPFM is equivalent to finding a feasible matching such that there is no other matching for which the corresponding MAPF instance has a lower optimal SIC.
+This motivates the joint nature of MAPFM: some matchings might be infeasible and others may have sub-optimal SIC costs, so especially in larger instances where there may be thousands of matchings, it is preferable to integrate the generation of matchings with the search for non-conflicting path-combinations to avoid having to exhaustively process all matchings.
+In this work, both integrated approaches and exhaustive methods using ICTS are considered.
+
+	\subsection{Formulation}
+	Formally, a MAPFM instance can be described as follows.
+Let $G = (V,E)$ be an undirected connected graph, with each $v\in V$ representing an obstacle-free tile on a 4-grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles.
+Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$.
+
+	Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution \cite{ma2016}.
+In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts (and thus no edge conflicts) and no swapping conflicts.
+Practically, this means that no two agents may be at $v\in V$ at the same timestep and that if agents $i,j$ are at locations $u,v$ respectively at timestep $t$, they may not be at locations $v,u$ at timestep $t+1$.
+
+	\section{Extending ICTS with matching} % Your contribution
+	Increasing Cost Tree Search with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances.
+Few changes to ICTS were necessary to accomodate for matching in this increasing cost tree scheme.
+Specifically, the ICT root generation and the MDD generation had to be changed.
+In regular ICTS, given a MAPF instance with agents $a_1,\ldots,a_k$ with goals $g_1,\ldots,g_k$ starting at locations $s_1,\ldots,s_k$, the root is given by the cost $c_i$ for each agent $a_i$ of the shortest path from $s_i$ to $g_i$, i.e.
+without taking conflicts into account.
+Any optimal pathfinding algorithm can be used for this.
+The root of the ICT then is the vector $(c_1,c_2,\ldots,c_k)$ with $k$ children $(c_1 + 1, c_2,\ldots,c_k), (c_1, c_2 + 1,\ldots,c_k),\ldots,(c_1, c_2,\ldots,c_k + 1)$ so that each component of the parent is incremented by 1 in exactly one child.
+This child-generation rule holds for all ICT nodes.
+
+	As described in \cite{sharon2011}, given $a_i$, generating all paths $(s_i,g_i)$ of a certain target cost $c_i$ can be accomplished by a breadth-first search on the $c_i$-steps time-expanded graph.
+Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and also facilitates the efficient search of the $k$-agent space of path combinations.
+	\subsection{Root generation for matching}
+	Given a team $t_i$ of size $k_i$, for any agent $a_j^i$ there are $k_i$ costs $c_j(1),c_j(2),\ldots,c_j(k_i)$ for shortest paths from $s_j^i$ to each goal $g_k^i$.
+Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with cost $c_j(m)$ such that $c_j(m) = \min_{n\in\{0,\ldots,k_i\}} c_j(n)$.
+Therefore, to guarantee optimality, this minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root.
+The resulting root is equivalent in the case that all teams are singleton.
+Intuitively, the sum of individual costs of this root is highly optimistic.
+Often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts.
+
+	\subsection{MDD generation for matching}
+	In MDD generation, each agent also has to consider not one goal but all matching goals.
+By following a BFS-based approach, with all team goals being goals in the search and in turn endpoints from which, using the time-expanded graph, the MDD was generated that is used in the low-level search, agent MDDs can be made to represent all possible paths of a set length to any matching goal.
+Once again, if all teams are singleton, the MDDs generated using this goal-set approach are the same as in regular ICTS.
+
+	\subsection{Properties of ICTS-m}
+	<insert proof>
 	\printbibliography

### 2021-05-31 src/bench.py

@@ -1,10 +1,18 @@
 import os
+import pickle
+from typing import List
+
 from mapfmclient import Problem, MarkedLocation
 import random
 import numpy as np
+import shutil
+
+from mapfm.solver import Solver
+from mapfm.solver_config import SolverConfig
 from parsing.map_parser import MapParser
-from mapfm.solve import solve, solve_enum, solve_enum_sorted
-from slim_testbench import TestBench
+from mapfm.solve import solve, solve_enum, solve_enum_sorted, solve_enum_sorted_prune_child, solve_pc, \
+    solver_from_config
+from mapfmclient.test_bench import TestBench
 
 
 class BenchmarkQueue:
@@ -107,30 +115,75 @@ def solve_setting(solver, t, k_team, timeout, samples):
     print("t = {} (k = {})".format(t, t * k_team))
     problems = [gen_problem(20, 20, 0.0, t, k_team) for i in range(samples)]
     bench = TestBench(-1, timeout)
-    enum_sols = bench.solve_problems(solver, problems)
+    enum_sols = bench.run(solver, problems)
     return enum_sols
 
 
-def test_queue(solver, map_parser, timeout, queue: BenchmarkQueue, output):
+def test_queue(solver, map_parser, timeout, queue: BenchmarkQueue):
+    output = solver.name
     task = queue.get_next()
     with open(output, "a") as f:
         f.write(f"task_id,completed,avg,std\n")
+    raw_dir = "raw/{}".format(output)
+    if os.path.exists(raw_dir):
+        shutil.rmtree(raw_dir)
+    os.mkdir(raw_dir)
     while task is not None and task != "":
         with open(output, "a") as f:
             problems = map_parser.parse_batch(task)
-            bench = TestBench(-1, timeout)
-            enum_sols = bench.solve_problems(solver, problems)
+            bench = TestBench(1, timeout)
+            enum_sols = bench.run(solver, problems)
+            with open("{}/{}".format(raw_dir,task),"wb+") as raw:
+                pickle.dump(enum_sols, raw)
             res, mean, std = process_results(enum_sols)
             f.write(f"{task}, {res}, {mean}, {std}\n")
             print(f"{task}: {res} with average {mean}s and deviation: {std}\n")
             queue.completed()
             task = queue.get_next()
 
-
-if __name__ == "__main__":
+def compare_configs(configs: List[SolverConfig]):
     map_root = "maps"
     map_parser = MapParser(map_root)
[…]

### 2021-05-31 src/mapfm/ict_search.py

@@ -271,6 +271,11 @@ class ICTSearcher(object):
                             if not tuple(node_list) in visited:
                                 frontier.append(tuple(node_list))
                 else:
+                    for (i, c) in enumerate(node):
+                        node_list = list(node)
+                        node_list[i] += 1
+                        if not tuple(node_list) in visited:
+                            frontier.append(tuple(node_list))
                     conflict_team_combination = None
                     if len(problem.team_agent_indices) > 1:
                         conflict_team_combination = self.check_within_teams(
@@ -302,11 +307,6 @@ class ICTSearcher(object):
                                         return ICTSolution(
                                             list(map(lambda x: x[0], solution)), sum(node)
                                         )
-                    for (i, c) in enumerate(node):
-                        node_list = list(node)
-                        node_list[i] += 1
-                        if not tuple(node_list) in visited:
-                            frontier.append(tuple(node_list))
                 for (i, p, c) in accumulator:
                     mdds[i].mdd[p].add(c)
         return None

### 2021-05-31 src/mapfm/solve.py

@@ -14,11 +14,29 @@ def solve_api_enum(problem: Problem) -> Solution:
     return solve_enum_sorted(problem)[0]
 
 
-def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
+def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int,Optional[int]]:
     config = SolverConfig(
         combs=2,
         prune=True,
-        enhanced=True,
+        enhanced=False,
+        pruned_child_gen=False,
+        id=True,
+        conflict_avoidance=True,
+        enumerative=False,
+        debug=False,
+    )
+    return Solver(config, problem)()
+
+
+def solver_from_config(config: SolverConfig):
+    return lambda problem: Solver(config, problem)()
+
+
+def solve_pc(problem: Problem) -> Tuple[Optional[Solution], List[int], int,Optional[int]]:
+    config = SolverConfig(
+        combs=2,
+        prune=True,
+        enhanced=False,
         pruned_child_gen=True,
         id=True,
         conflict_avoidance=True,
@@ -28,11 +46,11 @@ def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
     return Solver(config, problem)()
 
 
-def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
+def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], int,Optional[int]]:
     config = SolverConfig(
-        combs=3,
+        combs=2,
         prune=True,
-        enhanced=False,
+        enhanced=True,
         pruned_child_gen=False,
         id=True,
         conflict_avoidance=True,
@@ -43,7 +61,22 @@ def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], 
     return Solver(config, problem)()
 
 
-def solve_enum(problem: Problem) -> Tuple[Optional[Solution], List[int], int]:
+def solve_enum_sorted_prune_child(problem: Problem) -> Tuple[Optional[Solution], List[int], int,Optional[int]]:
+    config = SolverConfig(
+        combs=2,
+        prune=True,
+        enhanced=True,
+        pruned_child_gen=True,
+        id=True,
+        conflict_avoidance=True,
+        enumerative=True,
+        sort_matchings=True,
+        debug=False,
+    )
+    return Solver(config, problem)()
+
+
[…]

### 2021-05-31 src/mapfm/solver.py

@@ -75,7 +75,7 @@ class Solver:
             self.config.debug,
         )
 
-    def __call__(self) -> Tuple[Optional[Solution], List[int], int]:
+    def __call__(self) -> Tuple[Optional[Solution], List[int], int,Optional[int]]:
         paths: List[List[Tuple[int, int]]] = []
         agents: List[MarkedCompactLocation] = list(
             map(
@@ -99,7 +99,6 @@ class Solver:
                 rooted_matchings.sort(key=lambda a: a[1])
             else:
                 rooted_matchings = list(map(lambda m: (m, 0), matchings))
-            min_sic = None
             min_sol = None
             # print(len(rooted_matchings))
             for (matching, _) in rooted_matchings:
@@ -107,17 +106,15 @@ class Solver:
                 team_goals = dict(map(lambda x: (x[0], {x[1][1]}), matching))
                 sol = self.solve_tapf_instance(agents, team_agent_indices, team_goals)
                 if sol:
-                    sic = sol.sic
-                    if not min_sic or min_sic > sic:
-                        min_sic = sic
-                        min_sol = sol.solution
-                        self.update_budget(min_sic)
+                    if not min_sol or min_sol.sic > sol.sic:
+                        min_sol = sol
+                        self.update_budget(min_sol.sic)
             if min_sol:
-                subsols = list(zip(*min_sol))
+                subsols = list(zip(*min_sol.solution))
                 for subsol in subsols:
                     paths.append(list(map(lambda loc: expand_location(loc), subsol)))
             else:
-                return None, self.ict_searcher.max_delta, self.max_k_solved
+                return None, self.ict_searcher.max_delta, self.max_k_solved,None
         else:
             teams = set(map(lambda a: a.color, self.problem.starts))
             team_goals = dict(
@@ -135,11 +132,12 @@ class Solver:
                 for subsol in subsols:
                     paths.append(list(map(lambda loc: expand_location(loc), subsol)))
             else:
-                return None, self.ict_searcher.max_delta, self.max_k_solved
+                return None, self.ict_searcher.max_delta, self.max_k_solved, None
         return (
             Solution.from_paths(paths),
             self.ict_searcher.max_delta,
             self.max_k_solved,
+            min_sol.sic
         )
 
     def update_budget(self, budget):
@@ -179,7 +177,7 @@ class Solver:
                         return None
                     self.path_cache[(start, goal)] = len(shortest_path) - 1
                 c = self.path_cache[(start, goal)]
[…]

### 2021-05-31 src/mapfm/solver_config.py

@@ -1,5 +1,6 @@
 class SolverConfig:
     __slots__ = [
+        "name",
         "combs",
         "prune",
         "enhanced",
@@ -22,7 +23,9 @@ class SolverConfig:
         enumerative: bool,
         debug: bool,
         sort_matchings: bool = True,
+        name: str = "unnamed",
     ):
+        self.name = name
         self.combs = combs
         self.prune = prune
         self.enhanced = enhanced

### 2021-05-31 src/parsing/map_parser.py

@@ -1,4 +1,5 @@
 import os.path
+from typing import List
 
 from mapfmclient import MarkedLocation, Problem
 
@@ -7,7 +8,7 @@ class MapParser:
     def __init__(self, map_root):
         self.map_root = map_root
 
-    def parse_map(self, location: str):
+    def parse_map(self, location: str) -> Problem:
         if location.endswith(".map"):
             path = os.path.join(self.map_root, location)
         else:
@@ -41,6 +42,6 @@ class MapParser:
             goals.append(MarkedLocation(color, x, y))
         return Problem(grid, width, height, starts, goals)
 
-    def parse_batch(self, folder):
+    def parse_batch(self, folder) -> List[Problem]:
         paths = os.listdir(os.path.join(self.map_root, folder))
         return [self.parse_map(str(os.path.join(folder, path))) for path in paths]

### 2021-05-31 src/slim_testbench.py

@@ -1,65 +1,0 @@
-from multiprocessing import Pool
-
-from func_timeout import func_timeout, FunctionTimedOut
-from mapfmclient.functime import time_fun
-from tqdm import tqdm
-
-
-class TimeoutSolver:
-    def __init__(self, solver, timeout):
-        self.solver = solver
-        self.timeout = timeout
-
-    def __call__(self, current_problem):
-        try:
-            sol = func_timeout(
-                self.timeout / 1000, self.solver, args=(current_problem,)
-            )
-
-        except FunctionTimedOut:
-            sol = None
-        # except Exception as e:
-        #     print(f"An error occurred while running: {e}")
-        #     return None
-        return sol
-
-
-# https://stackoverflow.com/questions/62186218/python-multiprocessing-attributeerror-cant-pickle-local-object
-# I wonder why this approach (like rust closures) is not default...
-
-
-class TimingFunction:
-    def __init__(self, solve_func):
-        self.solve_func = solve_func
-
-    def __call__(self, current_problem):
-        return current_problem, *time_fun(current_problem, self.solve_func)
-
-
-class TestBench:
-    def __init__(self, cores=-1, timeout=4000):
-        self.cores = cores
-        self.timeout = timeout
-
-    def solve_problems(self, solver, problem_list):
-        self.solver = solver
-        if self.timeout:
-            solve_func = TimeoutSolver(solver, self.timeout)
-        else:
-            solve_func = self.solver
-        time_func = TimingFunction(solve_func)
-        if self.cores == 1:
-            solutions = list(
-                tqdm(map(time_func, problem_list), total=len(problem_list))
-            )
-        elif self.cores == -1:
-            with Pool() as p:
-                solutions = list(
-                    tqdm(p.imap(time_func, problem_list), total=len(problem_list))
-                )
-        else:
-            with Pool(self.cores) as p:
-                solutions = list(
-                    tqdm(p.imap(time_func, problem_list), total=len(problem_list))
-                )
-        return solutions

### 2021-05-31 docs/paper.tex
Added discussion of heuristics and heuristic solution properties prior to relaxation discussion

@@
 	\begin{abstract}
-		Both the assignment problem and the multi-agent pathfinding problem are common problems in fields from robotics to transportation.
+		Both the assignment problem and the multi-agent pathfinding problem are common problems in fields such as robotics and transportation.
 The joint problem of finding matchings inducing an optimal non-conflicting routing of agents to their goals is something that has not been studied much.
@@
 	The Dutch Railways (NS) company\footnote{\url{https://www.ns.nl/}} needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day.
-The problem of scheduling the trains to achieve this is called the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}.
-It is an NP-hard problem with many different subproblems in addition to the basic routing, such as the scheduling of personnel and coupling and decoupling of train units entering and leaving the yard.
+	The problem of scheduling the trains and personnel to achieve this is called the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}. 
+	It is an NP-hard problem with many different subproblems in addition to the basic train unit routing, such as the timetabling of personnel and coupling and decoupling of train units entering and leaving the yard.
 % introduce heuristics here.
 
-	The company is interested in learning tighter upper-bounds for the capacity of their shunting yards, but in practical scenarios, only heuristics can solve TUSS instances (as was shown by Geiger et al.
-\cite{geiger2018}).
-Heuristic solutions are often sub-optimal and give little information about what optimal solutions would look like and what could still be achieved using existing shunting infrastructure.
-To gain more insight into the capacity of shunting yards and the feasibility of problem instances, Mulderij et al.
-\cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation that can be used to compute upper-bounds for TUSS instances by solving the corresponding MAPFM instances optimally.
+	As was shown by Geiger et al. \cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
+	Such methods are in general suboptimal so solutions to instances defined for a set shunting yard can be thought of as crudely characterising a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost.
+	The company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about infrastructure expansion. 
+	Mulderij et al.
+\cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation for finding such upper-bounds using an approach analogous to that outlined above.
+	For this to succeed, a way to optimally solve MAPFM instances is needed.
 
-	Comparatively, little research has been done on MAPFM, and the Conflict-Based Min-Cost-Flow algorithm by Ma and Koenig \cite{ma2016} is one of the few existing approaches to optimally solve this more general problem along with the somewhat similar one described in \cite{henkel2019}.
+	Comparatively, little research has been done on MAPFM and solving MAPFM optimally.
+	The Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} is one of the few existing approaches to optimally solve this more general problem along with the somewhat similar one described in \cite{henkel2019}.
+It should be noted that this method minimizes the makespan and not the sum of individual costs which is the objective used in the TUSS relaxation, meaning that CBM would have to be modified in order to minimize SIC.
 	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
-It begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?
-
+	It begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for an optimal MAPFM solver?
+	\subsection{Increasing Cost Tree Search}
 	This work is the outcome of a search for an efficient algorithm for optimally solving MAPFM derived from ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}.

### 2021-06-01 docs/paper.tex
Renamed mapfm -> ictsm, removed redundant MapParser and added requirements.txt

@@
 	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
-	It begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for an optimal MAPFM solver?
-	\subsection{Increasing Cost Tree Search}
+	It begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?
+
 	This work is the outcome of a search for an efficient algorithm for optimally solving MAPFM derived from ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}.

### 2021-06-01 src/bench.py

@@ -7,10 +7,10 @@ import random
 import numpy as np
 import shutil
 
-from mapfm.solver import Solver
-from mapfm.solver_config import SolverConfig
-from parsing.map_parser import MapParser
-from mapfm.solve import solve, solve_enum, solve_enum_sorted, solve_enum_sorted_prune_child, solve_pc, \
+from ictsm.solver import Solver
+from ictsm.solver_config import SolverConfig
+from mapfmclient.parser import MapParser
+from ictsm.solve import solve, solve_enum, solve_enum_sorted, solve_enum_sorted_prune_child, solve_pc, \
     solver_from_config
 from mapfmclient.test_bench import TestBench
 

### 2021-06-01 src/ictsm/astar.py

@@ -1,9 +1,9 @@
 import heapq
 from typing import List, Set, Tuple
 
-from mapfm.compact_location import CompactLocation, manhattan_norm, expand_location
-from mapfm.maze import Maze
-from mapfm.node import Node
+from ictsm.compact_location import CompactLocation, manhattan_norm, expand_location
+from ictsm.maze import Maze
+from ictsm.node import Node
 
 
 def astar(

### 2021-06-01 src/ictsm/compact_location.py

@@ -1,5 +1,6 @@
 from typing import Tuple
 
+# Set to max grid width of problem instances
 ROW_FACTOR = 4096
 
 CompactLocation = int

### 2021-06-01 src/ictsm/conflicts.py

@@ -1,7 +1,7 @@
 from collections import defaultdict
 from typing import List, Optional, Tuple, Iterable, TypeVar, Sized, DefaultDict, Set
 
-from mapfm.compact_location import CompactLocation
+from ictsm.compact_location import CompactLocation
 
 # early-exit variant of the version below. Intuitively, it should be faster
 # https://stackoverflow.com/questions/5278122/checking-if-all-elements-in-a-list-are-unique

### 2021-06-01 src/ictsm/ict_search.py

@@ -2,12 +2,12 @@ from collections import deque
 from itertools import combinations
 from typing import List, Tuple, Optional, Dict, Deque
 
-from mapfm.compact_location import MarkedCompactLocation
-from mapfm.id_context import IDContext
-from mapfm.mapfm_problem import MAPFMProblem
-from mapfm.maze import Maze
-from mapfm.mdd import MDD
-from mapfm.mdd_search import (
+from ictsm.compact_location import MarkedCompactLocation
+from ictsm.id_context import IDContext
+from ictsm.mapfm_problem import MAPFMProblem
+from ictsm.maze import Maze
+from ictsm.mdd import MDD
+from ictsm.mdd_search import (
     JointSolution,
     seek_solution_in_joint_mdd,
     JointTimedSolution,

### 2021-06-01 src/ictsm/id_context.py

@@ -1,4 +1,4 @@
-from mapfm.util import index_path
+from ictsm.util import index_path
 
 
 class IDContext:

### 2021-06-01 src/ictsm/mapfm_problem.py

@@ -1,6 +1,6 @@
 from typing import Dict, List
 
-from mapfm.compact_location import MarkedCompactLocation
+from ictsm.compact_location import MarkedCompactLocation
 
 
 class MAPFMProblem:

### 2021-06-01 src/ictsm/maze.py

@@ -1,6 +1,6 @@
 from typing import List, Tuple
 
-from mapfm.compact_location import CompactLocation, expand_location, compact_location
+from ictsm.compact_location import CompactLocation, expand_location, compact_location
 
 
 class Maze(object):

### 2021-06-01 src/ictsm/mdd.py

@@ -1,15 +1,15 @@
 from collections import defaultdict, deque
 from typing import Optional, DefaultDict, Tuple, Set, Iterable, Deque, Dict
 
-# from graphviz import Digraph
-# from matplotlib import pyplot as plt
+from graphviz import Digraph
+from matplotlib import pyplot as plt
 
-from mapfm.compact_location import (
+from ictsm.compact_location import (
     CompactLocation,
     expand_location,
     CompactLocationDepth,
 )
-from mapfm.maze import Maze
+from ictsm.maze import Maze
 
 TimeExpandedGraph = DefaultDict[CompactLocationDepth, Set[CompactLocationDepth]]
 MDDGraph = Optional[TimeExpandedGraph]

### 2021-06-01 src/ictsm/mdd_search.py

@@ -1,15 +1,15 @@
 import itertools
 from typing import List, Tuple, Iterable, Any, Union, Set, Optional
 
-from mapfm.compact_location import CompactLocation
-from mapfm.conflicts import (
+from ictsm.compact_location import CompactLocation
+from ictsm.conflicts import (
     is_invalid_move,
     has_edge_collisions,
     all_different,
     count_conflicts,
 )
-from mapfm.id_context import IDContext
-from mapfm.mdd import MDD
+from ictsm.id_context import IDContext
+from ictsm.mdd import MDD
 
 JointSolution = List[Tuple[CompactLocation, ...]]
 JointTimedSolution = List[Tuple[Tuple[CompactLocation, ...], int]]

### 2021-06-01 src/ictsm/node.py

@@ -1,6 +1,6 @@
 from typing import Optional
 
-from mapfm.compact_location import CompactLocation
+from ictsm.compact_location import CompactLocation
 
 
 class Node(object):

### 2021-06-01 src/ictsm/solve.py

@@ -2,8 +2,8 @@ from typing import List, Tuple, Optional
 
 from mapfmclient import Problem, Solution
 
-from mapfm.solver import Solver
-from mapfm.solver_config import SolverConfig
+from ictsm.solver import Solver
+from ictsm.solver_config import SolverConfig
 
 
 def solve_api(problem: Problem) -> Solution:

### 2021-06-01 src/ictsm/solver.py

@@ -3,15 +3,15 @@ from typing import List, Tuple, Optional, Dict, Iterator
 
 from mapfmclient import Problem, Solution
 
-from mapfm.astar import astar
-from mapfm.compact_location import compact_location, expand_location, CompactLocation, MarkedCompactLocation
-from mapfm.conflicts import find_conflict
-from mapfm.ict_search import ICTSearcher, ICTSolution
-from mapfm.id_context import IDContext
-from mapfm.mapfm_problem import MAPFMProblem
-from mapfm.maze import Maze
-from mapfm.solver_config import SolverConfig
-from mapfm.util import index_path
+from ictsm.astar import astar
+from ictsm.compact_location import compact_location, expand_location, CompactLocation, MarkedCompactLocation
+from ictsm.conflicts import find_conflict
+from ictsm.ict_search import ICTSearcher, ICTSolution
+from ictsm.id_context import IDContext
+from ictsm.mapfm_problem import MAPFMProblem
+from ictsm.maze import Maze
+from ictsm.solver_config import SolverConfig
+from ictsm.util import index_path
 
 
 def enumerate_matchings(agents, tasks):

### 2021-06-01 src/main.py

@@ -5,7 +5,7 @@ from pprint import pprint
 import requests
 from mapfmclient import MapfBenchmarker, Problem, MarkedLocation
 
-from mapfm.solve import solve, solve_api, solve_api_enum
+from ictsm.solve import solve, solve_api, solve_api_enum
 
 
 def run_custom(token, p_id):

### 2021-06-01 src/parsing/map_parser.py

@@ -1,47 +1,0 @@
-import os.path
-from typing import List
-
-from mapfmclient import MarkedLocation, Problem
-
-
-class MapParser:
-    def __init__(self, map_root):
-        self.map_root = map_root
-
-    def parse_map(self, location: str) -> Problem:
-        if location.endswith(".map"):
-            path = os.path.join(self.map_root, location)
-        else:
-            path = os.path.join(self.map_root, location + ".map")
-        with open(path) as f:
-            lines = f.readlines()
-        width_line = list(lines[0].split(" "))
-        height_line = list(lines[1].split(" "))
-        width = int(width_line[1])
-        height = int(height_line[1])
-        grid = []
-        for i in range(height):
-            grid.append([int(c == "@") for c in lines[2 + i]])
-        agents = int(lines[2 + height])
-        starts = []
-        starting_line = 3 + height
-        for i in range(agents):
-            start_line = list(lines[starting_line + i].split(" "))
-            x = int(start_line[0])
-            y = int(start_line[1])
-            color = int(start_line[2])
-            starts.append(MarkedLocation(color, x, y))
-
-        goals = []
-        starting_line = 4 + height + agents
-        for i in range(agents):
-            start_line = list(lines[starting_line + i].split(" "))
-            x = int(start_line[0])
-            y = int(start_line[1])
-            color = int(start_line[2])
-            goals.append(MarkedLocation(color, x, y))
-        return Problem(grid, width, height, starts, goals)
-
-    def parse_batch(self, folder) -> List[Problem]:
-        paths = os.listdir(os.path.join(self.map_root, folder))
-        return [self.parse_map(str(os.path.join(folder, path))) for path in paths]

### 2021-06-01 src/test/test_astar.py

@@ -1,9 +1,9 @@
 import unittest
 from typing import List
 
-from mapfm.astar import astar
-from mapfm.compact_location import CompactLocation, compact_location
-from mapfm.maze import Maze
+from ictsm.astar import astar
+from ictsm.compact_location import CompactLocation, compact_location
+from ictsm.maze import Maze
 
 
 class AStarTest(unittest.TestCase):

### 2021-06-01 src/test/test_compact_location.py

@@ -1,6 +1,6 @@
 from unittest import TestCase
 
-from mapfm.compact_location import compact_location, expand_location, ROW_FACTOR
+from ictsm.compact_location import compact_location, expand_location, ROW_FACTOR
 
 param_list = [(0, 0), (0, 1), (1, 0), (1, 1), (ROW_FACTOR - 1, 0)]
 

### 2021-06-01 src/test/test_conflicts.py

@@ -1,7 +1,7 @@
 import unittest
 
-from mapfm.compact_location import compact_location
-from mapfm.conflicts import *
+from ictsm.compact_location import compact_location
+from ictsm.conflicts import *
 
 
 def construct_node(ns: List[Tuple[int, int]]) -> List[CompactLocation]:

### 2021-06-01 src/test/test_solve.py

@@ -1,7 +1,7 @@
 import unittest
 
 from mapfmclient import MarkedLocation, Problem
-from mapfm.solver import solve
+from ictsm.solver import solve
 
 """
 Basic single-agent pathfinding tests using top-level 'solve' interface

### 2021-06-01 src/bench.py
Made benchmark persistence more robust

@@ -6,6 +6,7 @@ from mapfmclient import Problem, MarkedLocation
 import random
 import numpy as np
 import shutil
+import pathlib
 
 from ictsm.solver import Solver
 from ictsm.solver_config import SolverConfig
@@ -120,20 +121,25 @@ def solve_setting(solver, t, k_team, timeout, samples):
 
 
 def test_queue(solver, map_parser, timeout, queue: BenchmarkQueue):
-    output = solver.name
+    output = pathlib.Path(solver.name)
     task = queue.get_next()
-    with open(output, "a") as f:
+    if output.exists():
+        output.unlink()
+    with output.open("a") as f:
         f.write(f"task_id,completed,avg,std\n")
-    raw_dir = "raw/{}".format(output)
+    raw_dir = pathlib.Path("raw/{}".format(output))
+    if raw_dir.exists():
+        shutil.rmtree(raw_dir)
+    raw_dir.mkdir(parents=True)
     if os.path.exists(raw_dir):
         shutil.rmtree(raw_dir)
     os.mkdir(raw_dir)
     while task is not None and task != "":
         with open(output, "a") as f:
             problems = map_parser.parse_batch(task)
-            bench = TestBench(1, timeout)
+            bench = TestBench(-1, timeout)
             enum_sols = bench.run(solver, problems)
-            with open("{}/{}".format(raw_dir,task),"wb+") as raw:
+            with (raw_dir / task).open("wb+") as raw:
                 pickle.dump(enum_sols, raw)
             res, mean, std = process_results(enum_sols)
             f.write(f"{task}, {res}, {mean}, {std}\n")
@@ -145,7 +151,7 @@ def compare_configs(configs: List[SolverConfig]):
     map_root = "maps"
     map_parser = MapParser(map_root)
     for (i,config) in enumerate(configs):
-        os.system("cp /dev/null results_{}.txt; cp full_queue.txt queue.txt".format(i))
+        os.system("cp full_queue.txt queue.txt")
         test_queue(ConfiguredSolver(config), map_parser, 100, BenchmarkQueue("queue.txt"))
 
 class ConfiguredSolver:

### 2021-06-01 src/bench.py
Replaced maps with larger set

@@ -2,8 +2,6 @@ import os
 import pickle
 from typing import List
 
-from mapfmclient import Problem, MarkedLocation
-import random
 import numpy as np
 import shutil
 import pathlib
@@ -36,49 +34,6 @@ class BenchmarkQueue:
         with open(self.name, "a") as f:
             f.write(data + "\n")
 
-
-def p_bool(p):
-    return random.random() < p
-
-
-def gen_rand_grid(width, height, p):
-    rows = []
-    for y in range(height):
-        rows.append([int(p_bool(p)) for x in range(width)])
-    return rows
-
-
-def gen_legal_point(taken, grid, width, height):
-    point = None
-    while not point:
-        start_x = random.randrange(width)
-        start_y = random.randrange(height)
-        if not grid[start_y][start_x] and not (start_x, start_y) in taken:
-            point = start_x, start_y
-    return point
-
-
-def gen_agent_goals(grid, width, height, t, k_team):
-    starts = []
-    goals = []
-    taken_starts = set()
-    taken_goals = set()
-    taken = set()
-    for team in range(t):
-        for agent in range(k_team):
-            start_x, start_y = gen_legal_point(taken, grid, width, height)
-            taken_starts.add((start_x, start_y))
-            taken.add((start_x, start_y))
-            goal_x, goal_y = gen_legal_point(taken, grid, width, height)
-            taken_goals.add((goal_x, goal_y))
-            taken.add((goal_x, goal_y))
-            start = MarkedLocation(team, start_x, start_y)
-            goal = MarkedLocation(team, goal_x, goal_y)
-            starts.append(start)
-            goals.append(goal)
-    return starts, goals
-
-
 def show_problem(grid, width, height, starts, goals):
     for y in range(height):
         s = ""
@@ -90,19 +45,6 @@ def show_problem(grid, width, height, starts, goals):
         print(s)
     return starts, goals
 
-
-def gen_problem(width, height, density, t, k_team):
-    grid = gen_rand_grid(width, height, density)
-    starts, goals = gen_agent_goals(grid, width, height, t, k_team)
-    return Problem(grid, width, height, starts, goals)
-
-
-def gen_problem_random(width, height, density, t, k_team):
-    grid = gen_rand_grid(width, height, density)
-    starts, goals = gen_agent_goals(grid, width, height, t, k_team)
-    return Problem(grid, width, height, starts, goals)
-
-
[…]

### 2021-06-01 src/gen/map_generator.py

@@ -1,0 +1,244 @@
+class Coord:
+    __slots__ = ("x", "y")
+
+    def __init__(self, x: int, y: int):
+        """
+        Create a coordinate.
+        :param x: The x position
+        :param y: The y position
+        """
+        self.x = x
+        self.y = y
+
+    def move(self, dx, dy):
+        """
+        Create a new coordinate moved in the given direction.
+        :param dx: The x direction to move
+        :param dy: The y direction to move
+        :return: A new moved coordinate
+        """
+        return Coord(self.x + dx, self.y + dy)
+
+    def __hash__(self) -> int:
+        return tuple.__hash__((self.x, self.y))
+
+    def __eq__(self, other):
+        return (self.x, self.y) == (other.x, other.y)
+
+    def __iter__(self):
+        yield self.x
+        yield self.y
+
+import os
+import random
+from numbers import Number
+from queue import Queue
+from random import randint, uniform
+from typing import List, Tuple
+
+from mapfmclient import Problem, MarkedLocation
+
+
+class MapGenerator:
+
+    def __init__(self, map_root):
+        self.map_root = map_root
+
+    def generate_map(self, width: int,
+                     height: int,
+                     num_agents: List[int],
+                     open_factor: float = 0.75,
+                     max_neighbors: int = 1,
+                     min_goal_distance: float = 0.5,
+                     max_goal_distance: float = 1
+
+                     ) -> Problem:
+        while True:
+            grid = self.__generate_maze(width, height, open_factor=open_factor, max_neighbors=max_neighbors)
+            count_traversable = 0
+            for y in range(height):
+                count_traversable += width - sum(grid[y])
+            if count_traversable < (open_factor * width * height * 0.25 * max_neighbors) or self.__num_3neighbors(grid) < sum(
+                    num_agents) - 1:
+                print("Not enough traversable cells or not solvable, running again!")
+            else:
+                result = None
+                while result is None:
+                    try:
+                        # connect
+                        result = self.__generate_agent_positions(grid, width, height, num_agents, min_goal_distance, max_goal_distance)
+                    except:
+                        pass
+                starts, goals = result
+                start_locations: List[MarkedLocation] = []
+                goal_locations: List[MarkedLocation] = []
+
+                i = 0
+                for color, team_size in enumerate(num_agents):
+                    for _ in range(team_size):
[…]

### 2021-06-01 src/gen_maps.py

@@ -1,0 +1,14 @@
+import pathlib
+import shutil
+
+from gen.map_generator import MapGenerator
+
+if __name__ == '__main__':
+    raw_dir = pathlib.Path("../new-maps")
+    if raw_dir.exists():
+        shutil.rmtree(raw_dir)
+    raw_dir.mkdir()
+    map_generator = MapGenerator("../new-maps")
+    for i in range(1, 16):
+        map_generator.generate_even_batch(200, 20, 20, i, 1, prefix="Open", min_goal_distance=0, open_factor=1.0, max_neighbors=3)
+        map_generator.generate_even_batch(200, 20, 20, i, 3, prefix="Open", min_goal_distance=0, open_factor=1.0,max_neighbors=3)

### 2021-06-01 src/ictsm/conflicts.py
Worked on benchmarks, changed import format to leave out package name

@@ -1,7 +1,7 @@
 from collections import defaultdict
 from typing import List, Optional, Tuple, Iterable, TypeVar, Sized, DefaultDict, Set
 
-from ictsm.compact_location import CompactLocation
+from .compact_location import CompactLocation
 
 # early-exit variant of the version below. Intuitively, it should be faster
 # https://stackoverflow.com/questions/5278122/checking-if-all-elements-in-a-list-are-unique

### 2021-06-01 src/ictsm/ict_search.py

@@ -2,16 +2,12 @@ from collections import deque
 from itertools import combinations
 from typing import List, Tuple, Optional, Dict, Deque
 
-from ictsm.compact_location import MarkedCompactLocation
-from ictsm.id_context import IDContext
-from ictsm.mapfm_problem import MAPFMProblem
-from ictsm.maze import Maze
-from ictsm.mdd import MDD
-from ictsm.mdd_search import (
-    JointSolution,
-    seek_solution_in_joint_mdd,
-    JointTimedSolution,
-)
+from .compact_location import MarkedCompactLocation
+from .id_context import IDContext
+from .mapfm_problem import MAPFMProblem
+from .maze import Maze
+from .mdd import MDD
+from .mdd_search import (JointSolution,seek_solution_in_joint_mdd,JointTimedSolution)
 
 
 def find_number_of_open_spaces(maze: Maze):

### 2021-06-01 src/ictsm/maze.py

@@ -1,6 +1,6 @@
 from typing import List, Tuple
 
-from ictsm.compact_location import CompactLocation, expand_location, compact_location
+from .compact_location import CompactLocation, expand_location, compact_location
 
 
 class Maze(object):

### 2021-06-01 src/ictsm/solve.py

@@ -2,8 +2,8 @@ from typing import List, Tuple, Optional
 
 from mapfmclient import Problem, Solution
 
-from ictsm.solver import Solver
-from ictsm.solver_config import SolverConfig
+from .solver import Solver
+from .solver_config import SolverConfig
 
 
 def solve_api(problem: Problem) -> Solution:

### 2021-06-01 src/ictsm/solver.py

@@ -3,15 +3,15 @@ from typing import List, Tuple, Optional, Dict, Iterator
 
 from mapfmclient import Problem, Solution
 
-from ictsm.astar import astar
-from ictsm.compact_location import compact_location, expand_location, CompactLocation, MarkedCompactLocation
-from ictsm.conflicts import find_conflict
-from ictsm.ict_search import ICTSearcher, ICTSolution
-from ictsm.id_context import IDContext
-from ictsm.mapfm_problem import MAPFMProblem
-from ictsm.maze import Maze
-from ictsm.solver_config import SolverConfig
-from ictsm.util import index_path
+from .astar import astar
+from .compact_location import compact_location, expand_location, CompactLocation, MarkedCompactLocation
+from .conflicts import find_conflict
+from .ict_search import ICTSearcher, ICTSolution
+from .id_context import IDContext
+from .mapfm_problem import MAPFMProblem
+from .maze import Maze
+from .solver_config import SolverConfig
+from .util import index_path
 
 
 def enumerate_matchings(agents, tasks):

### 2021-06-06 docs/paper.tex
Worked on plotting of experiments, set out outline for paper

@@
 \usepackage{geometry}
+\usepackage{hyperref}
 \usepackage{inputenc}
@@
 
-	As was shown by Geiger et al. \cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
-	Such methods are in general suboptimal so solutions to instances defined for a set shunting yard can be thought of as crudely characterising a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost.
+	As was shown by Geiger et al.\cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
+	Such methods are suboptimal so solutions to instances defined for a set shunting yard can be
+ said to characterise a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost. 
 	The company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about infrastructure expansion. 
@@
 Practically, this means that no two agents may be at $v\in V$ at the same timestep and that if agents $i,j$ are at locations $u,v$ respectively at timestep $t$, they may not be at locations $v,u$ at timestep $t+1$.
+	\section{Matching in ICTS} % Your contribution
+	Two classes of algorithms were found to solve MAPFM using ICTS-based methods: exhaustively enumerating MAPF instances corresponding to matchings solving these using a variant of regular ICTS, and modifying the increasing cost tree search itself to accomodate for the matching extension.
+In the following, both
 
-	\section{Extending ICTS with matching} % Your contribution
 	Increasing Cost Tree Search with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances.
@@
 	<insert proof>
+	\section{Experimental results}
+	\section{Responsible Research}
+	In experiments used to compare the different MAPFM algorithms within the peer group, care was taken to make the comparison fair: all algorithms are implemented in Python 3 and run on the same system: a server with a 12-core Intel Xeon E5-2683 with 8Gb of RAM dedicated to running experiments for this project.
+Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
+
+	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository \footnote{\url{https://github.com/tbvanderwoude/icts-m}}.
+Included is also code used to benchmark different configurations of the ICTS solver.
+
+	\section{Discussion}
+	\section{Conclusions}
+	\section{Future work}
 	\printbibliography

### 2021-06-06 src/bench.py

@@ -51,7 +51,7 @@ def test_queue(solver, map_parser, timeout,queue: BenchmarkQueue, num: int = 200
     while task is not None and task != "":
         with open(output_file_path, "a") as f:
             problems = map_parser.parse_batch(task)[:num]
-            bench = TestBench(4, timeout)
+            bench = TestBench(-1, timeout)
             enum_sols = bench.run(solver, problems)
             with (raw_dir / task).open("wb+") as raw:
                 pickle.dump(enum_sols, raw)
@@ -66,7 +66,7 @@ def compare_configs(configs: List[SolverConfig]):
     map_parser = MapParser(map_root)
     for (i,config) in enumerate(configs):
         os.system("cp full_queue.txt queue.txt")
-        test_queue(ConfiguredSolver(config), map_parser, 120000, BenchmarkQueue("queue.txt"),200)
+        test_queue(ConfiguredSolver(config), map_parser, 30000, BenchmarkQueue("queue.txt"),50)
 
 class ConfiguredSolver:
     def __init__(self,config: SolverConfig):
@@ -81,36 +81,48 @@ class ConfiguredSolver:
 
 if __name__ == "__main__":
     configs = [
-        SolverConfig(
-            name="(exh)-(enhanced)-(no-id)",
-            combs=3,
-            prune=True,
-            enhanced=False,
-            pruned_child_gen=True,
-            id=False,
-            conflict_avoidance=True,
-            enumerative=True,
-            debug=False,
-            sort_matchings=False,
-        ),
-        SolverConfig(
-            name="(exh)-(enhanced)-(id)",
-            combs=3,
-            prune=True,
-            enhanced=True,
-            pruned_child_gen=False,
-            id=True,
-            conflict_avoidance=True,
-            enumerative=True,
-            debug=False,
-            sort_matchings=False,
-        ),
+        # SolverConfig(
+        #     name="(exh-sort)-(enhanced)-(no-id)",
+        #     combs=3,
+        #     prune=True,
+        #     enhanced=True,
+        #     pruned_child_gen=False,
+        #     id=False,
+        #     conflict_avoidance=True,
+        #     enumerative=True,
+        #     debug=False,
+        #     sort_matchings=True,
+        # ),
+        # SolverConfig(
+        #     name="(exh)-(enhanced)-(no-id)",
+        #     combs=3,
+        #     prune=True,
+        #     enhanced=True,
+        #     pruned_child_gen=False,
+        #     id=False,
[…]

### 2021-06-07 docs/paper.tex
Worked on paper (background mostly)

@@
 \usepackage{url}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{wrapfig}
+\usepackage{subcaption}
 \makeatother
@@
 	As was shown by Geiger et al.\cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
-	Such methods are suboptimal so solutions to instances defined for a set shunting yard can be
- said to characterise a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost. 
-	The company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about infrastructure expansion. 
+	Such methods are suboptimal and heuristic solutions to instances defined for a set shunting yard can be said to characterise a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost.
+	The railway company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about matters like infrastructure expansion. 
 	Mulderij et al.
@@
 	The Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} is one of the few existing approaches to optimally solve this more general problem along with the somewhat similar one described in \cite{henkel2019}.
-It should be noted that this method minimizes the makespan and not the sum of individual costs which is the objective used in the TUSS relaxation, meaning that CBM would have to be modified in order to minimize SIC.
 	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
-	It begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?
+It should be noted that this method minimizes the makespan and not the sum of individual costs which is the objective used in the TUSS relaxation, meaning that non-trivial modifications to CMB are needed in order to minimize SIC.
+	The successful application of CBS to solving MAPFM begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?
 
+	\begin{wrapfigure}{R}{.25\textwidth}
+		\begin{minipage}{\linewidth}
+			\centering\captionsetup[subfigure]{justification=centering}
+			\includegraphics[width=\linewidth]{img/vertex-conflict}
+			\subcaption{Vertex conflict}
+			\label{fig:conflictsa}\par\vfill
+			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
+			\subcaption{Swapping conflict}
+			\label{fig:conflictsb}
+		\end{minipage}
+		\caption{The two types of conflict (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
+	\end{wrapfigure}
 	This work is the outcome of a search for an efficient algorithm for optimally solving MAPFM derived from ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}.
@@
 These MDDS represent per agent all possible paths to the goal of a set length.
-In the context of a research project in which multiple such MAPF algorithms were taken as starting points for MAPFM algorithms within a group, the novel ICTS-based algorithm is compared to these algorithms on a set of benchmarks similar to those described in \cite{stern2019}.
+In the context of a research project in which multiple such
+	MAPF algorithms were taken as starting points for MAPFM algorithms within a group, the novel ICTS-based algorithm is compared to these algorithms on a set of benchmarks similar to those described in \cite{stern2019}.
 In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.
@@
 	\section{Multi-agent pathfinding with matching} % Problem description
+	The MAPFM problem is an extension of MAPF, a well-studied problem.
+Formally, a MAPF instance can be described as follows.
+Let $G = (V,E)$ be an undirected connected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles.
+Let there be $k$ agents $a_1,\ldots,a_k$ with respective starting locations $s_1,\ldots,s_k$ and goals $g_1,\ldots,g_k$.
+For each agent $a_i$, a path $\pi_i$ from $s_i$ to $g_i$ is to be found such that all agents paths $\pi_i$ taken together are non-conflicting and therefore are a solution.
+In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts (and thus no edge conflicts) and no swapping conflicts, as shown in Figure \ref{fig:conflicts}.
+Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$.
+Given a solution $(\pi_1,\ldots,\pi_k)$, a vector of per-agent costs $(c_1,\ldots,c_k)$ can be found.
+For $\pi_i$, $c_i$ is defined as the time at which $a_i$ reaches $g_i$ for the last time and remains there, meaning that for $t \geq c_i$, $\pi_i^{t} = g_i$.
+One property of $c_i$ is that $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of $\pi^*_i$, the shortest path from $s_i$ to $g_i$.
+There are two common objectives in MAPF:
+	\begin{itemize}
+		\item The makespan: $\max_{i} c_i$
+		\item The sum of individual costs (SIC): $\sum_i c_i$
+	\end{itemize}
+	In this work, following the definition of the TUSS relaxation in \cite{mulderij2020}, an optimal solution is defined as having minimal SIC. Note that $\sum_i c_i \geq \sum_i c^*_i$
+	\subsection{Increasing Cost Tree Search}
+	In the above, given a combination of paths $(\pi_1,\ldots,\pi_k)$, a vector of costs is found from which the SIC is derived.
+This is a surjective mapping: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
+On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical solutions\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods like Jump Point Search\cite{harabor2011} are used to speed up search.
+In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.4\linewidth]{img/symmetries}
+		\caption{Symmetric paths on a 4-connected grid\cite{harabor2010}}
+		\label{fig:symmetries}
+	\end{figure}
+
+	In Increasing Cost Tree Search\cite{sharon2011}, the above two-step mapping from path combination to cost vector and from cost vector to SIC is reversed in order to search for a solution with minimal SIC.
+This is done by searching for cost vectors corresponding to increasing SIC on the top level and searching for non-conflicting path combinations (solutions) for each cost vector on the bottom level.
+
+	\subsubsection{Top-level search}
+	 In the top-level search, all possible cost vectors for a given SIC are evaluated by searching an Increasing Cost Tree as depicted in \ref{fig:ict}, starting from $C_{root} = \sum_i c^*_i$ corresponding to a single root cost vector $(c^*_1,c^*_2,\ldots,c^*_k)$.
+This root has $k$ children $(c^*_1 + 1,c^*_2,\ldots,c^*_k),(c^*_1,c^*_2 + 1,\ldots,c^*_k),\ldots,(c^*_1,c^*_2,\ldots,c^*_k + 1)$ all of cost $C = C_{root} + 1$.
+Searching this ICT breadth-first corresponds to evaluating all possible cost vectors corresponding to increasing cost $C$ starting with $C_{root}$.
+The number of cost vectors evaluated when searching up to a depth of $\Delta$ with vectors cost of $C_{root} + \Delta$ is $\mathcal{O}(k^\Delta)$.
+Node evaluation is done by a low-level search that searches for a solution $(\pi_1,\ldots,\pi_k)$ corresponding to the node costs $(c_1,\ldots,c_k)$.
+
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.7\linewidth]{img/ict}
+		\caption{Increasing Cost Tree for three agents (Fig 4. in \cite{sharon2011})}
+		\label{fig:ict}
+	\end{figure}
+	\subsubsection{Bottom-level search}
+	Explicitly generating all paths of a set cost to the goal for each agent is expensive: the number of paths is exponential in the target cost.
+As the space of all path combinations for $k$ agents have to be searched, a more efficient method is required.
+This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDS) are used to compactly represent all paths per agent and facilitate efficient search of the $k$-agent space of path combinations.
+
+	Figure \ref{fig:symmetries} only shows a few possible paths of the same cost to the goal
+	Evaluating a node in the above means performing a low-level search that searches the space of all combinations of paths $(\pi_1,\ldots,\pi_k)$ that correspond to the node costs $(c_1,\ldots,c_k)$.
+
+	 the mapping from SIC to possible cost vectors, and from cost vectors to possible path combinations is reversed.
+
+	, w y might map to the same vector of costs and still more might yield the same SIC.
+
+	In an abstract sense, Increasing Cost Tree Search algorithm for MAPF \cite{sharon2011} can be thought of as exhaustively reversing this mapping.
+
+	Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$.
+
+	Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution \cite{ma2016}.
+In this work, non-conflicting means, in the conflict-terminology of
+	\paragraph{Old}
 	MAPFM is the problem of finding agent-goal matchings that induce a non-conflicting routing of agents to their goals.
@@
 	\section{Matching in ICTS} % Your contribution
-	Two classes of algorithms were found to solve MAPFM using ICTS-based methods: exhaustively enumerating MAPF instances corresponding to matchings solving these using a variant of regular ICTS, and modifying the increasing cost tree search itself to accomodate for the matching extension.
+	Two classes of algorithms were found for solving MAPFM optimally using ICTS-based methods.
+exhaustively enumerating MAPF instances corresponding to matchings solving these using a variant of regular ICTS, and modifying the increasing cost tree search itself to accomodate for the matching extension.
 In the following, both

### 2021-06-07 docs/dump.tex
Finished draft of Problem Description (background), rewrote part about icts-m

--- 2021-06-01 docs/paper.tex
@@
 
-	\title{Multi-Agent Path Finding with Matching using Increasing Cost Tree Search}
+	\title{Dump}
 
-	\author{Thom van der Woude\and Jesse Mulderij\and Mathijs de Weerdt}
+	\author{Thom van der Woude}
 	\date{}
@@
 
-	\begin{abstract}
-		Both the assignment problem and the multi-agent pathfinding problem are common problems in fields such as robotics and transportation.
-The joint problem of finding matchings inducing an optimal non-conflicting routing of agents to their goals is something that has not been studied much.
-Few methods exist today that solve it although the problems do appear together in real-world problems, such as in the Train Unit Shunting and Servicing problem.
-In this work, a novel method based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding is presented that can optimally solve this joint problem.
-	\end{abstract}
+	\section{Introduction}
 
-	\section{Introduction}
-	The Dutch Railways (NS) company\footnote{\url{https://www.ns.nl/}} needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day.
-	The problem of scheduling the trains and personnel to achieve this is called the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}. 
-	It is an NP-hard problem with many different subproblems in addition to the basic train unit routing, such as the timetabling of personnel and coupling and decoupling of train units entering and leaving the yard.
-% introduce heuristics here.
-
-	As was shown by Geiger et al. \cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
-	Such methods are in general suboptimal so solutions to instances defined for a set shunting yard can be thought of as crudely characterising a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost.
-	The company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about infrastructure expansion. 
-	Mulderij et al.
-\cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation for finding such upper-bounds using an approach analogous to that outlined above.
-	For this to succeed, a way to optimally solve MAPFM instances is needed.
-
-	Comparatively, little research has been done on MAPFM and solving MAPFM optimally.
-	The Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} is one of the few existing approaches to optimally solve this more general problem along with the somewhat similar one described in \cite{henkel2019}.
-It should be noted that this method minimizes the makespan and not the sum of individual costs which is the objective used in the TUSS relaxation, meaning that CBM would have to be modified in order to minimize SIC.
-	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
-	It begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?
-
-	This work is the outcome of a search for an efficient algorithm for optimally solving MAPFM derived from ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}.
-ICTS, in short, is a two-level approach to MAPF with a top-level breadth-first traversal of an Increasing Cost Tree (ICT) representing combinations of per-agent path costs and a bottom-level evaluation of ICT nodes using multi-valued decision diagrams (MDDS).
-These MDDS represent per agent all possible paths to the goal of a set length.
-In the context of a research project in which multiple such MAPF algorithms were taken as starting points for MAPFM algorithms within a group, the novel ICTS-based algorithm is compared to these algorithms on a set of benchmarks similar to those described in \cite{stern2019}.
-In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.
-Lastly, completeness of the algorithm is considered as this is a key property in the context of MAPFM as a TUSS relaxation.
-Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.
-
-	\section{Multi-agent pathfinding with matching} % Problem description
+	\paragraph{Old}
 	MAPFM is the problem of finding agent-goal matchings that induce a non-conflicting routing of agents to their goals.
@@
 Practically, this means that no two agents may be at $v\in V$ at the same timestep and that if agents $i,j$ are at locations $u,v$ respectively at timestep $t$, they may not be at locations $v,u$ at timestep $t+1$.
-
-	\section{Extending ICTS with matching} % Your contribution
-	Increasing Cost Tree Search with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances.
-Few changes to ICTS were necessary to accomodate for matching in this increasing cost tree scheme.
-Specifically, the ICT root generation and the MDD generation had to be changed.
-In regular ICTS, given a MAPF instance with agents $a_1,\ldots,a_k$ with goals $g_1,\ldots,g_k$ starting at locations $s_1,\ldots,s_k$, the root is given by the cost $c_i$ for each agent $a_i$ of the shortest path from $s_i$ to $g_i$, i.e.
-without taking conflicts into account.
-Any optimal pathfinding algorithm can be used for this.
-The root of the ICT then is the vector $(c_1,c_2,\ldots,c_k)$ with $k$ children $(c_1 + 1, c_2,\ldots,c_k), (c_1, c_2 + 1,\ldots,c_k),\ldots,(c_1, c_2,\ldots,c_k + 1)$ so that each component of the parent is incremented by 1 in exactly one child.
-This child-generation rule holds for all ICT nodes.
-
-	As described in \cite{sharon2011}, given $a_i$, generating all paths $(s_i,g_i)$ of a certain target cost $c_i$ can be accomplished by a breadth-first search on the $c_i$-steps time-expanded graph.
-Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and also facilitates the efficient search of the $k$-agent space of path combinations.
-	\subsection{Root generation for matching}
-	Given a team $t_i$ of size $k_i$, for any agent $a_j^i$ there are $k_i$ costs $c_j(1),c_j(2),\ldots,c_j(k_i)$ for shortest paths from $s_j^i$ to each goal $g_k^i$.
-Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with cost $c_j(m)$ such that $c_j(m) = \min_{n\in\{0,\ldots,k_i\}} c_j(n)$.
-Therefore, to guarantee optimality, this minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root.
-The resulting root is equivalent in the case that all teams are singleton.
-Intuitively, the sum of individual costs of this root is highly optimistic.
-Often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts.
-
-	\subsection{MDD generation for matching}
-	In MDD generation, each agent also has to consider not one goal but all matching goals.
-By following a BFS-based approach, with all team goals being goals in the search and in turn endpoints from which, using the time-expanded graph, the MDD was generated that is used in the low-level search, agent MDDs can be made to represent all possible paths of a set length to any matching goal.
-Once again, if all teams are singleton, the MDDs generated using this goal-set approach are the same as in regular ICTS.
-
-	\subsection{Properties of ICTS-m}
-	<insert proof>
 	\printbibliography

### 2021-06-07 docs/paper.tex
Finished draft of Problem Description (background), rewrote part about icts-m

@@
 	MAPF algorithms were taken as starting points for MAPFM algorithms within a group, the novel ICTS-based algorithm is compared to these algorithms on a set of benchmarks similar to those described in \cite{stern2019}.
-In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.
-Lastly, completeness of the algorithm is considered as this is a key property in the context of MAPFM as a TUSS relaxation.
-Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.
+In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.
 
+	% Lastly, completeness of the algorithm is considered as this is a key property in the context of MAPFM as a TUSS relaxation.
 	\section{Multi-agent pathfinding with matching} % Problem description
@@
 For $\pi_i$, $c_i$ is defined as the time at which $a_i$ reaches $g_i$ for the last time and remains there, meaning that for $t \geq c_i$, $\pi_i^{t} = g_i$.
-One property of $c_i$ is that $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of $\pi^*_i$, the shortest path from $s_i$ to $g_i$.
+One property of $c_i$ is that $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of $\pi^*_i$, the shortest path from $s_i$ to $g_i$ that can be computed using any optimal pathfinding algorithm.
 There are two common objectives in MAPF:
@@
 	\end{itemize}
-	In this work, following the definition of the TUSS relaxation in \cite{mulderij2020}, an optimal solution is defined as having minimal SIC. Note that $\sum_i c_i \geq \sum_i c^*_i$
+	In this work, following the definition of the TUSS relaxation in \cite{mulderij2020}, an optimal solution is defined as having minimal SIC. Note that $\sum_i c_i \geq \sum_i c^*_i$.
+
+	So given a combination of paths $(\pi_1,\ldots,\pi_k)$, a vector of costs is found from which the SIC is derived.
+This is a surjective mapping: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
+On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods like Jump Point Search\cite{harabor2011} are used to speed up search.
+In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
 	\subsection{Increasing Cost Tree Search}
-	In the above, given a combination of paths $(\pi_1,\ldots,\pi_k)$, a vector of costs is found from which the SIC is derived.
-This is a surjective mapping: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
-On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical solutions\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods like Jump Point Search\cite{harabor2011} are used to speed up search.
-In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
+	\label{icts}
 	\begin{figure}[t]
@@
 	\end{figure}
-
-	In Increasing Cost Tree Search\cite{sharon2011}, the above two-step mapping from path combination to cost vector and from cost vector to SIC is reversed in order to search for a solution with minimal SIC.
+	In Increasing Cost Tree Search\cite{sharon2011}, the above two-step mapping from path combination to SIC is reversed in order to search for a solution with minimal SIC.
 This is done by searching for cost vectors corresponding to increasing SIC on the top level and searching for non-conflicting path combinations (solutions) for each cost vector on the bottom level.
@@
 This root has $k$ children $(c^*_1 + 1,c^*_2,\ldots,c^*_k),(c^*_1,c^*_2 + 1,\ldots,c^*_k),\ldots,(c^*_1,c^*_2,\ldots,c^*_k + 1)$ all of cost $C = C_{root} + 1$.
-Searching this ICT breadth-first corresponds to evaluating all possible cost vectors corresponding to increasing cost $C$ starting with $C_{root}$.
-The number of cost vectors evaluated when searching up to a depth of $\Delta$ with vectors cost of $C_{root} + \Delta$ is $\mathcal{O}(k^\Delta)$.
+Searching this ICT breadth-first corresponds to evaluating all possible cost vectors corresponding to increasing cost $C$ starting with $C_{root}$, guaranteeing optimality of a found solution.
+The number of cost vectors evaluated when searching up to nodes of cost $C_{root} + \Delta$ is $\mathcal{O}(k^\Delta)$.
 Node evaluation is done by a low-level search that searches for a solution $(\pi_1,\ldots,\pi_k)$ corresponding to the node costs $(c_1,\ldots,c_k)$.
@@
 		\includegraphics[width=0.7\linewidth]{img/ict}
-		\caption{Increasing Cost Tree for three agents (Fig 4. in \cite{sharon2011})}
+		\caption{Increasing Cost Tree for three agents \cite{sharon2011}}
 		\label{fig:ict}
 	\end{figure}
+\begin{figure}
+
+\end{figure}
+
+\begin{figure}[b]
+	\centering
+	\begin{subfigure}{0.2\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/mdds1}
+		\caption{An example problem}
+		\label{fig:problem}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/ict2}
+		\caption{The corresponding ICT with solution node $(3,2)$}
+		\label{fig:ict2}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.4\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/mdds}
+		\caption{MDDs for the agents are found and combined}
+		\label{fig:mdds}
+	\end{subfigure}
+
+	\caption{Example of using ICTS to solve MAPF from \cite{sharon2011}}
+	\label{fig:bottom}
+\end{figure}
 	\subsubsection{Bottom-level search}
-	Explicitly generating all paths of a set cost to the goal for each agent is expensive: the number of paths is exponential in the target cost.
-As the space of all path combinations for $k$ agents have to be searched, a more efficient method is required.
-This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDS) are used to compactly represent all paths per agent and facilitate efficient search of the $k$-agent space of path combinations.
+	Explicitly generating all paths to the goal for agent $a_i$ of cost $c_i$ is expensive: the number of paths is exponential in $c_i$.
+This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent.
+For $a_i$ with target cost $c_i$ (from cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents.
+Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations.
 
-	Figure \ref{fig:symmetries} only shows a few possible paths of the same cost to the goal
-	Evaluating a node in the above means performing a low-level search that searches the space of all combinations of paths $(\pi_1,\ldots,\pi_k)$ that correspond to the node costs $(c_1,\ldots,c_k)$.
+	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as low-level search of the (solution) node $(3,2)$ using MDDs.
+Note that the second agent staying at node D after completing the path is modelled in its MDD also to ensure that place remains blocked.
 
-	 the mapping from SIC to possible cost vectors, and from cost vectors to possible path combinations is reversed.
+	Subfigure \ref{fig:mdds} illustrates the way in which two or more MDDs can be combined: first, the root nodes are joined; next, the product of the children of both roots is taken and checked for conflicts.
+In \ref{fig:mdds}, a vertex conflict occurs and therefore this joint child can be removed from the MDD.
+If a $(B,A)$ node would be generated by the same root, $(A,B)$, this would similarly be a swapping conflict and hence $(B,A)$ would also be removed from the joint MDD $MDD_{1,2}^{c_1,c_2}$.
+In the next layer, the process repeats with multiple parent nodes.
 
-	, w y might map to the same vector of costs and still more might yield the same SIC.
-
-	In an abstract sense, Increasing Cost Tree Search algorithm for MAPF \cite{sharon2011} can be thought of as exhaustively reversing this mapping.
+	In practice, joint MDDs are not explicitly constructed but instead a depth-first search is used to search joint MDDs.
+This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
+	\subsubsection{Pruning in ICTS}
+	\label{pruning}
+	In \cite{sharon2011}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work.
+All work by taking $j < k$ and applying the described method to each possible combination of $j$ out of $k$ agents.
+If no solution exists for any such combination, the full $k$-agent low-level search is not triggered.
+The two basic pruning methods are as follows.
+	\begin{enumerate}
+		\item Simple pruning: the $j$-agent MDD is searched using DFS for a solution.
+		\item Enhanced pruning: the $j$-agent MDD is searched using BFS and when children are generated, for each agent, all children that do not appear in any unified node are removed from the MDD.
+In \ref{fig:mdds}, the $C$ node of $MDD_1$ would be removed as it cannot be unified with any node of $MDD_2$ at that level.
+	\end{enumerate}
+	In addition, repeated enhanced pairwise pruning is described in which the enhanced pruning procedure is repeated for all combinations until a fixpoint is reached, which is when no child node is removed from any of the agent MDDs in an iteration.
+This was not used in this work.
+	\subsection{Extending MAPF with matching}
+	With the multi-agent pathfinding problem as well as the ICTS method of solving it defined, the matching extension of MAPF (MAPFM) that is the subject of this paper can be described.
+Possible extensions of ICTS to match these changes will be discussed in Section \ref{section:icts-matching}.
 
 	Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$.
+Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution \cite{ma2016}, similarly defined as for MAPF.
 
-	Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution \cite{ma2016}.
-In this work, non-conflicting means, in the conflict-terminology of
-	\paragraph{Old}
-	MAPFM is the problem of finding agent-goal matchings that induce a non-conflicting routing of agents to their goals.
-Each matching corresponds to a MAPF instance, so each feasible matching has an optimal solution, i.e.
-a solution with a minimal Sum of Individual Costs (SIC).
-In approaching MAPFM as a TUSS relaxation to find upper-bounds for instances, optimal MAPFM solutions are the most interesting as they can characterise such upper-bounds.
-Furthermore, defining optimality as minimal SIC corresponds more closely to TUSS objective functions such as personnel cost than the other common MAPF objective, minimal makespan.
-Optimally solving MAPFM is equivalent to finding a feasible matching such that there is no other matching for which the corresponding MAPF instance has a lower optimal SIC.
-This motivates the joint nature of MAPFM: some matchings might be infeasible and others may have sub-optimal SIC costs, so especially in larger instances where there may be thousands of matchings, it is preferable to integrate the generation of matchings with the search for non-conflicting path-combinations to avoid having to exhaustively process all matchings.
-In this work, both integrated approaches and exhaustive methods using ICTS are considered.
+%
+	\section{Solving MAPF with Matching using ICTS} % Your contribution
+	\label{section:icts-matching}
+	Taking ICTS for MAPF as starting point, two methods to use ICTS for MAPFM were identified.
+The first method relies on the well-known reduction from MAPFM to repeated MAPF: any optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found.
+In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
+For each method, some properties and method-specific optimizations and variations will be discussed.
+Afterwards, some more general considerations will be discussed.
+	\subsection{Exhaustive ICTS}
+	For $K$ teams $t_1,\ldots,t_K$ of size $t_i$, there are in total $n = \prod_{i} k_i!$ ways to match team agents to team goals.
+	Exhaustive ICTS is $\mathcal{O}(\prod_{i} k_i!)$
 
-	\subsection{Formulation}
-	Formally, a MAPFM instance can be described as follows.
-Let $G = (V,E)$ be an undirected connected graph, with each $v\in V$ representing an obstacle-free tile on a 4-grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles.
-Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$.
-
-	Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution \cite{ma2016}.
-In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts (and thus no edge conflicts) and no swapping conflicts.
-Practically, this means that no two agents may be at $v\in V$ at the same timestep and that if agents $i,j$ are at locations $u,v$ respectively at timestep $t$, they may not be at locations $v,u$ at timestep $t+1$.
-	\section{Matching in ICTS} % Your contribution
-	Two classes of algorithms were found for solving MAPFM optimally using ICTS-based methods.
-exhaustively enumerating MAPF instances corresponding to matchings solving these using a variant of regular ICTS, and modifying the increasing cost tree search itself to accomodate for the matching extension.
-In the following, both
-
-	Increasing Cost Tree Search with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances.
+	\subsection{ICTS-m}
+	ICTS with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances.
 Few changes to ICTS were necessary to accomodate for matching in this increasing cost tree scheme.
 Specifically, the ICT root generation and the MDD generation had to be changed.
-In regular ICTS, given a MAPF instance with agents $a_1,\ldots,a_k$ with goals $g_1,\ldots,g_k$ starting at locations $s_1,\ldots,s_k$, the root is given by the cost $c_i$ for each agent $a_i$ of the shortest path from $s_i$ to $g_i$, i.e.
+As described in \ref{icts}, in ICTS the root cost for each agent $a_i$ is given by $c^*_i$, the cost of the shortest path from $s_i$ to $g_i$, i.e.
 without taking conflicts into account.
-Any optimal pathfinding algorithm can be used for this.
-The root of the ICT then is the vector $(c_1,c_2,\ldots,c_k)$ with $k$ children $(c_1 + 1, c_2,\ldots,c_k), (c_1, c_2 + 1,\ldots,c_k),\ldots,(c_1, c_2,\ldots,c_k + 1)$ so that each component of the parent is incremented by 1 in exactly one child.
-This child-generation rule holds for all ICT nodes.
-
-	As described in \cite{sharon2011}, given $a_i$, generating all paths $(s_i,g_i)$ of a certain target cost $c_i$ can be accomplished by a breadth-first search on the $c_i$-steps time-expanded graph.
-Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and also facilitates the efficient search of the $k$-agent space of path combinations.
-	\subsection{Root generation for matching}
+$MDD_i^{c_i}$ is generated using a breadth-first search from $s_i$ to $g_i$ followed by some additional processing.
+	\subsubsection{Root generation for matching}
 	Given a team $t_i$ of size $k_i$, for any agent $a_j^i$ there are $k_i$ costs $c_j(1),c_j(2),\ldots,c_j(k_i)$ for shortest paths from $s_j^i$ to each goal $g_k^i$.
@@
 
-	\subsection{MDD generation for matching}
+	\subsubsection{MDD generation for matching}
 	In MDD generation, each agent also has to consider not one goal but all matching goals.
@@
 
-	\subsection{Properties of ICTS-m}
+	\subsubsection{Properties of ICTS-m}
 	<insert proof>
@@
 	\section{Conclusions}
+
 	\section{Future work}

### 2021-06-07 docs/paper.tex
Worked on Contribution, added ICTS pseudocode

@@
 \usepackage{babel}
+\usepackage{amsmath}
+\usepackage{algorithm}
+\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
+\usepackage[noend]{algpseudocode}
+\makeatletter
+\def\BState{\State\hskip-\ALG@thistlm}
+\makeatother
 
@@
 This was not used in this work.
+
+	The full ICT-search algorithm including a pruning step is described by pseudocode listing \ref{icts-algo}. It is reproduced from \cite{sharon2011} for completeness.
+	\begin{algorithm}
+		\begin{algorithmic}[1]
+			\Procedure{ICT-search}{MAPF instance}
+			\State \text{Construct ICT root}
+			\ForAll{\text{ICT nodes }$(c_1,\ldots,c_k)$\text{ in breadth-first order }} 
+				\ForAll{\text{agents} $a_i$} 
+					\text{Construct} $MDD_i^{c_i}$
+				\EndFor
+				\ForAll{$j$-\text{agent combinations} $(i_1,\ldots,i_j)$} 
+				\State \text{Run node-pruning procedure with MDDs }$MDD_{i_1}^{c_{i_1}},\ldots,MDD_{i_j}^{c_{i_j}}$
+				\If{\text{no solution was found for a combination in pruning}}
+					\State \textbf{Break}\text{ and continue with next ICT node}
+				\EndIf
+				\EndFor
+				\State \text{Search }$k$\text{-agent MDD space}
+				\If{\text{solution was found}}
+				\State \textbf{return solution}
+				\EndIf
+			\EndFor
+
+			\EndProcedure
+		\end{algorithmic}
+		\caption{Increasing Cost Tree Search}
+		\label{icts-algo}
+	\end{algorithm}
 	\subsection{Extending MAPF with matching}
@@
 	\subsection{Exhaustive ICTS}
-	For $K$ teams $t_1,\ldots,t_K$ of size $t_i$, there are in total $n = \prod_{i} k_i!$ ways to match team agents to team goals.
-	Exhaustive ICTS is $\mathcal{O}(\prod_{i} k_i!)$
+	For $K$ teams $t_1,\ldots,t_K$ of size $t_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals.
+Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the instance, with $C_m = \infty$ for unfeasible $m$.
+Let $\Delta_m$ be similarly defined and represent the difference between $C_m$ and the root cost of $m$.
+
+	In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instance have to be solved.
+However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound for the SIC of nodes, effectively depth-limiting the ICT traversal.
 
@@
 	Given a team $t_i$ of size $k_i$, for any agent $a_j^i$ there are $k_i$ costs $c_j(1),c_j(2),\ldots,c_j(k_i)$ for shortest paths from $s_j^i$ to each goal $g_k^i$.
-Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with cost $c_j(m)$ such that $c_j(m) = \min_{n\in\{0,\ldots,k_i\}} c_j(n)$.
+Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with path cost $c^*_j = c_j(m)$ such that $c_j(m) = \min_{n\in\{0,\ldots,k_i\}} c_j(n)$.
 Therefore, to guarantee optimality, this minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root.
-The resulting root is equivalent in the case that all teams are singleton.
-Intuitively, the sum of individual costs of this root is highly optimistic.
-Often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts.
+The resulting root is equivalent to that generated in regular ICTS in the case that all teams are singleton, which is equivalent to a MAPF instance.
+Intuitively, the sum of individual costs of this root is highly optimistic, in particular if the teams are large.
+This is because often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts.
 
@@
 Once again, if all teams are singleton, the MDDs generated using this goal-set approach are the same as in regular ICTS.
+	\begin{wrapfigure}{R}{.35\textwidth}
+	\centering
+	\includegraphics[width=\linewidth]{img/path}
+	\caption{Pathelogical case for ICTS-m [Placeholder graphic]}
+	\label{fig:path}
+\end{wrapfigure}
+	\subsubsection{Properties of ICTS-m}
+	As a consequence of the $\min$ operation in the root definition, a pathelogical case can be derived.
+Consider a team of 4 agents $a_1^1$ through $a_4^1$.
+Let them be arranged in a configuration as depicted in Figure \ref{fig:path}.
+As indicated by the color, all four agents match the colour of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$.
+The optimal solution however is, numbering the agents clockwise, $(1,3,3,3)$ with SIC $10$, meaning that $\Delta = 6$.
+It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed.
+As ICTS-m being generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'arms' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
 
-	\subsubsection{Properties of ICTS-m}
-	<insert proof>
 	\section{Experimental results}
@@
 	\section{Future work}
+	The ICTS-m algorithm described in this work scales quite poorly for a number of reasons including the highly optimistic root SIC value.
+It might be possible to conceive of a different ICTS-m algorithm that is better able to take advantage of the agents being divided into teams, for instance by first solving all intra-team conflicts before proceeding to consider inter-team conflicts.
+Some early experiments with pruning techniques were in this vein but experimentally there was no observable improvement.
 	\printbibliography

### 2021-06-07 docs/paper.tex
Worked on describing experiments and exhaustive variant descr., added plots of results

@@
 
-	In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instance have to be solved.
-However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound for the SIC of nodes, effectively depth-limiting the ICT traversal.
+	In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
+However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound for the SIC of nodes.
+Formally, let $B = \infty$ represent the initial SIC bound of the ICT search.
+After solving $C_m$, let $B_{new} = \min(B,C_m)$.
+By successively contracting this upper-bound on solution SIC, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.
+
+	 the effort needed to solve the remaining matchings can greatly be reduced.
+
+	 and effectively depth-limiting the ICT traversal.
 
@@
 	\section{Experimental results}
+	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks appear to exist.
+For MAPF there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances.
+It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
+This observation informed the creation of a map generator within the peer group
+
+	\begin{figure*}
+		\centering
+		\begin{subfigure}{0.49\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/open-1}
+			\caption{Open, 1 team}
+			\label{fig:problem}
+		\end{subfigure}
+		\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/open-3}
+		\caption{Open, 3 teams}
+		\label{fig:problem}
+		\end{subfigure}
+		\begin{subfigure}{0.49\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/obstacle-1}
+			\caption{Obstacle, 1 team}
+			\label{fig:ict2}
+		\end{subfigure}
+		\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/obstacle-3}
+		\caption{Obstacle, 3 teams}
+		\label{fig:ict2}
+		\end{subfigure}
+		\begin{subfigure}{0.49\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/maze-1}
+			\caption{Maze, 1 team}
+			\label{fig:mdds}
+		\end{subfigure}
+		\begin{subfigure}{0.49\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/maze-3}
+			\caption{Maze, 3 teams}
+			\label{fig:mdds}
+		\end{subfigure}
+
+		\caption{Average solving time of algorithm variants on various types of 20x20 grids with a 30s timeout}
+		\label{fig:bottom}
+	\end{figure*}
 	\section{Responsible Research}

### 2021-06-07 docs/paper.tex
Added plots for fraction solved
Added description of ID framework

@@
 This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
+	\subsubsection{ICTS with Independence Detection}
+	Like many other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced in \cite{standley2010}.
+ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups.
+If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case ICTS, until no conflicts between groups occur.
+The goal of ID is to minimize $k'$, the size of the largest group that has to be planned.
+Optionally, a conflict avoidance table (CAT) can be maintained for use during planning of groups.
+This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from listing \ref{id-algo} for brevity but was implemented and used in experiments.
+	\begin{algorithm}
+	\begin{algorithmic}[1]
+		\State \text{Assign each agent to a singleton group}
+		\State \text{plan a path for each group}
+		\Repeat
+			\State \text{simulate execution of all paths until a conflict occurs}
+			\State \text{merge two conflicting groups into a single group}
+			\State \text{cooperatively plan new group}
+		\Until{\text{no conflicts occur}}
+		\State $solution\gets\text{paths of all groups combined}$
+		\State \textbf{return solution}
+	\end{algorithmic}
+	\caption{Simple Independence Detection by Standley} 
+	\label{id-algo}
+	\end{algorithm}
+
 	\subsubsection{Pruning in ICTS}
@@
 	\section{Experimental results}
-	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks appear to exist.
+	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks exist\footnote{That is, to the knowledge of the author.}.
 For MAPF there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances.
 It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
-This observation informed the creation of a map generator within the peer group
+This observation informed the creation of a map generator within the peer group with various parameters.
+Using this map generator, three types of 20x20 grids were generated:
+	\begin{enumerate}
+		\item Open: An obstacle-free grid
+		\item Obstacle: A grid with some obstacles
+		\item Maze: A grid with many obstructed tiles
+	\end{enumerate}
 
@@
 			\caption{Open, 1 team}
-			\label{fig:problem}
+			\label{fig:open1}
 		\end{subfigure}
@@
 		\caption{Open, 3 teams}
-		\label{fig:problem}
+		\label{fig:open3}
 		\end{subfigure}
@@
 			\caption{Obstacle, 1 team}
-			\label{fig:ict2}
+			\label{fig:obstacle1}
 		\end{subfigure}
@@
 		\caption{Obstacle, 3 teams}
-		\label{fig:ict2}
+		\label{fig:obstacle3}
 		\end{subfigure}
@@
 			\caption{Maze, 1 team}
-			\label{fig:mdds}
+			\label{fig:m1}
 		\end{subfigure}
@@
 			\caption{Maze, 3 teams}
-			\label{fig:mdds}
+			\label{fig:m3}
 		\end{subfigure}
+		\caption{Average solving time of algorithm variants on various types of 20x20 grids with a 30s timeout}
+		\label{fig:bottom}
+	\end{figure*}
 
-		\caption{Average solving time of algorithm variants on various types of 20x20 grids with a 30s timeout}
+	\begin{figure*}
+	\centering
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/open-1-p}
+		\caption{Open, 1 team}
+		\label{fig:open1}
+	\end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/open-3-p}
+		\caption{Open, 3 teams}
+		\label{fig:open3}
+	\end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/obstacle-1-p}
+		\caption{Obstacle, 1 team}
+		\label{fig:obstacle1}
+	\end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/obstacle-3-p}
+		\caption{Obstacle, 3 teams}
+		\label{fig:obstacle3}
+	\end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/maze-1-p}
+		\caption{Maze, 1 team}
+		\label{fig:m1}
+	\end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/maze-3-p}
+		\caption{Maze, 3 teams}
+		\label{fig:m3}
+	\end{subfigure}
+	\caption{Fraction solved out of 50 maps of algorithm variants on various types of 20x20 grids with a 30s timeout}
 	\label{fig:bottom}

### 2021-06-07 docs/paper.tex
Added claim about exhaustive method with sorting

@@
 	\subsubsection{ICTS with Independence Detection}
-	Like many other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced in \cite{standley2010}.
+	Like many other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}.
 ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups.
@@
 Optionally, a conflict avoidance table (CAT) can be maintained for use during planning of groups.
-This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from listing \ref{id-algo} for brevity but was implemented and used in experiments.
+This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from Algorithm \ref{id-algo} for brevity but was implemented and used in experiments.
 	\begin{algorithm}
@@
 
-	The full ICT-search algorithm including a pruning step is described by pseudocode listing \ref{icts-algo}. It is reproduced from \cite{sharon2011} for completeness.
+	The full ICT-search algorithm including a pruning step is described by Algorithm \ref{icts-algo}.
+It is reproduced from \cite{sharon2011} for completeness.
+As noted before, this procedure could be used for planning groups in Algorithm \ref{id-algo}.
 	\begin{algorithm}
@@
 Let $\Delta_m$ be similarly defined and represent the difference between $C_m$ and the root cost of $m$.
+In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
 
-	In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
-However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound for the SIC of nodes.
+	However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes.
 Formally, let $B = \infty$ represent the initial SIC bound of the ICT search.
-After solving $C_m$, let $B_{new} = \min(B,C_m)$.
-By successively contracting this upper-bound on solution SIC, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.
+After solving each $C_m$, let $B_{m+1} = \min(B_m,C_m)$.
+By successively updating this $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.
 
-	 the effort needed to solve the remaining matchings can greatly be reduced.
-
-	 and effectively depth-limiting the ICT traversal.
+	As a further improvement of this method, the order in which matchings are enumerated and solved could be changed.
+In particular, by sorting the matchings in increasing order of root SIC, it can be seen that $\Delta'_{m + 1}$, the distance from $B_{m+1}$ or the solution to matching $m + 1$ (whichever was reached first) and the root SIC, will always be less or equal to the $\Delta'_m$ [TODO: proof].
+Although this is itself a promising property, in order to make use of it, all roots have to be computed and all $M$ corresponding SIC values have to be sorted which is a $\mathcal{O}(M\log M)$ procedure.
 

### 2021-06-07 docs/paper.tex
Finished pre-spelling-check version

@@
 It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed.
-As ICTS-m being generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'arms' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
+As ICTS-m being generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
+	\subsection{General optimization: child pruning}
+An optimization of ICTS that hitherto appears to not have been described in the literature was found in the process of optimizing ICTS-m.
+The idea is simple: when pruning, in the original ICTS formulation all $k$-children are generated in every case because pruning only controls skipping the low-level search, assumed to be the most expensive operation.
+However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented in any solution node.
+This reduces the number of children generated to the number of conflicting agents, which quite drastically can improve the branching factor of the ICT search if say $k = 12$ but a conflicting pair is found.
 
-	\section{Experimental results}
-	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks exist\footnote{That is, to the knowledge of the author.}.
-For MAPF there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances.
-It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
-This observation informed the creation of a map generator within the peer group with various parameters.
-Using this map generator, three types of 20x20 grids were generated:
-	\begin{enumerate}
-		\item Open: An obstacle-free grid
-		\item Obstacle: A grid with some obstacles
-		\item Maze: A grid with many obstructed tiles
-	\end{enumerate}
-
+It is conjectured that child pruning combined with enhanced pruning does not in general guarantee optimality, but despite extensive search no counter-example has been found.
+[TODO: find counter-example/proof optimality]
 	\begin{figure*}
@@
 	\caption{Average solving time of algorithm variants on various types of 20x20 grids with a 30s timeout}
-		\label{fig:bottom}
+	\label{fig:times}
 \end{figure*}
@@
 		\caption{Open, 1 team}
-		\label{fig:open1}
+		\label{fig:open1p}
 	\end{subfigure}
@@
 		\caption{Open, 3 teams}
-		\label{fig:open3}
+		\label{fig:open3p}
 	\end{subfigure}
@@
 		\caption{Obstacle, 1 team}
-		\label{fig:obstacle1}
+		\label{fig:obstacle1p}
 	\end{subfigure}
@@
 		\caption{Obstacle, 3 teams}
-		\label{fig:obstacle3}
+		\label{fig:obstacle3p}
 	\end{subfigure}
@@
 		\caption{Maze, 1 team}
-		\label{fig:m1}
+		\label{fig:maze1p}
 	\end{subfigure}
@@
 		\caption{Maze, 3 teams}
-		\label{fig:m3}
+		\label{fig:maze3p}
 	\end{subfigure}
 	\caption{Fraction solved out of 50 maps of algorithm variants on various types of 20x20 grids with a 30s timeout}
-	\label{fig:bottom}
+	\label{fig:probs}
 \end{figure*}
+
+	\section{Experiments}
+	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks exist\footnote{That is, to the knowledge of the author.}.
+For MAPF there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances.
+It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
+This observation informed the creation of a map generator within the peer group with various parameters.
+Using this map generator, three types of 20x20 grids were generated:
+	\begin{enumerate}
+		\item Open: An obstacle-free grid
+		\item Obstacle: A grid with some obstacles
+		\item Maze: A grid with many obstructed tiles
+	\end{enumerate}
+	For each of these types, two sets of maps were generated with between $1$ and $10$ agents and 50 instances generated for each such agent-setting: one set where all agents belong to one team, another in which the agents were divided into three teams (or $1,2$ teams respectively for the datapoints with $1,2$ agents).
+The results are shown in Figure \ref{fig:times} and \ref{fig:probs}, that respectively show the average time to solution and the fraction of problems solved out of 50 instances.
+The algorithms and interpretation of results are discussed below.
+	\subsection{Algorithms}
+	Various improvements and variations of algorithms were tried out, as shown in the legend.
+S and E denote simple and enhanced pruning respectively; ID means that Independence Detection was used; C means that child pruning was used.
+	\subsection{Results}
+	A first observation is that exhaustive methods, while dominant throughout all settings, fare much better when agents are divided into three teams as opposed to when there is just one team.
+This can be explained by exhaustive algorithms having to process $M = k!$ matchings, which grows quite large for say $k = 10$.
+Another is that simple pruning combined with child pruning appears to outperform enhanced in many cases, as in Subfigure \ref{fig:maze1p}.
+More analysis is necessary however before any conclusions can be drawn.
+
 	\section{Responsible Research}
@@
 	\section{Discussion}
+	Compared to the results achieved by \cite{ma2016}, the results recorded are somewhat disappointing.
 	\section{Conclusions}
-
+	The goal of this research was to seek alternative approaches to solving MAPFM based on ICTS.
+In this the research has succeeded, but the performance and in particular the scalability of the algorithms leaves something to be desired.
 	\section{Future work}

### 2021-06-07 docs/paper.tex
Fixed some issues using grammarly

@@
 	As was shown by Geiger et al.\cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
-	Such methods are suboptimal and heuristic solutions to instances defined for a set shunting yard can be said to characterise a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost.
+	Such methods are suboptimal and heuristic solutions to instances defined for a set shunting yard can be said to characterise a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper bound for the optimal solution cost.
 	The railway company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about matters like infrastructure expansion. 
@@
 	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
-It should be noted that this method minimizes the makespan and not the sum of individual costs which is the objective used in the TUSS relaxation, meaning that non-trivial modifications to CMB are needed in order to minimize SIC.
+It should be noted that this method minimizes the makespan and not the sum of individual costs which is the objective used in the TUSS relaxation, meaning that non-trivial modifications to CMB are needed to minimize SIC.
 	The successful application of CBS to solving MAPFM begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?
@@
 	MAPF algorithms were taken as starting points for MAPFM algorithms within a group, the novel ICTS-based algorithm is compared to these algorithms on a set of benchmarks similar to those described in \cite{stern2019}.
-In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.
+In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.
+Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.
 
@@
 This is a surjective mapping: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
-On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods like Jump Point Search\cite{harabor2011} are used to speed up search.
+On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods like Jump Point Search\cite{harabor2011} are used to speed up the search.
 In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
@@
 	\end{figure}
-	In Increasing Cost Tree Search\cite{sharon2011}, the above two-step mapping from path combination to SIC is reversed in order to search for a solution with minimal SIC.
+	In Increasing Cost Tree Search\cite{sharon2011}, the above two-step mapping from path combination to SIC is reversed to search for a solution with minimal SIC.
 This is done by searching for cost vectors corresponding to increasing SIC on the top level and searching for non-conflicting path combinations (solutions) for each cost vector on the bottom level.
@@
 This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent.
-For $a_i$ with target cost $c_i$ (from cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents.
+For $a_i$ with a target cost $c_i$ (from cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents.
 Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations.
 
-	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as low-level search of the (solution) node $(3,2)$ using MDDs.
-Note that the second agent staying at node D after completing the path is modelled in its MDD also to ensure that place remains blocked.
+	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs.
+Note that the second agent staying at node D after completing the path is modelled in its MDD also to ensure that the place remains blocked.
 
-	Subfigure \ref{fig:mdds} illustrates the way in which two or more MDDs can be combined: first, the root nodes are joined; next, the product of the children of both roots is taken and checked for conflicts.
+	Subfigure \ref{fig:mdds} illustrates how two or more MDDs can be combined: first, the root nodes are joined; next, the product of the children of both roots is taken and checked for conflicts.
 In \ref{fig:mdds}, a vertex conflict occurs and therefore this joint child can be removed from the MDD.
@@
 
-	In practice, joint MDDs are not explicitly constructed but instead a depth-first search is used to search joint MDDs.
+	In practice, joint MDDs are not explicitly constructed but instead, a depth-first search is used to search joint MDDs.
 This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
@@
 ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups.
-If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case ICTS, until no conflicts between groups occur.
+If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case, ICTS, until no conflicts between groups occur.
 The goal of ID is to minimize $k'$, the size of the largest group that has to be planned.
-Optionally, a conflict avoidance table (CAT) can be maintained for use during planning of groups.
+Optionally, a conflict avoidance table (CAT) can be maintained for use during the planning of groups.
 This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from Algorithm \ref{id-algo} for brevity but was implemented and used in experiments.
@@
 In particular, by sorting the matchings in increasing order of root SIC, it can be seen that $\Delta'_{m + 1}$, the distance from $B_{m+1}$ or the solution to matching $m + 1$ (whichever was reached first) and the root SIC, will always be less or equal to the $\Delta'_m$ [TODO: proof].
-Although this is itself a promising property, in order to make use of it, all roots have to be computed and all $M$ corresponding SIC values have to be sorted which is a $\mathcal{O}(M\log M)$ procedure.
+Although this is itself a promising property, to make use of it, all roots have to be computed and all $M$ corresponding SIC values have to be sorted which is a $\mathcal{O}(M\log M)$ procedure.
 
@@
 	ICTS with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances.
-Few changes to ICTS were necessary to accomodate for matching in this increasing cost tree scheme.
+Few changes to ICTS were necessary to accommodate for matching in this increasing cost tree scheme.
 Specifically, the ICT root generation and the MDD generation had to be changed.
@@
 The resulting root is equivalent to that generated in regular ICTS in the case that all teams are singleton, which is equivalent to a MAPF instance.
-Intuitively, the sum of individual costs of this root is highly optimistic, in particular if the teams are large.
+Intuitively, the sum of individual costs of this root is highly optimistic, in particular, if the teams are large.
 This is because often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts.
@@
 	\subsubsection{Properties of ICTS-m}
-As a consequence of the $\min$ operation in the root definition, a pathelogical case can be derived.
+	As a consequence of the $\min$ operation in the root definition, a pathological case can be derived.
 Consider a team of 4 agents $a_1^1$ through $a_4^1$.
@@
 It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed.
-As ICTS-m being generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
+As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
 	\subsection{General optimization: child pruning}

### 2021-06-09 docs/paper.tex
Worked on paper, changed benchmark setup

@@
 	Taking ICTS for MAPF as starting point, two methods to use ICTS for MAPFM were identified.
-The first method relies on the well-known reduction from MAPFM to repeated MAPF: any optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found.
+The first method relies on the well-known reduction from MAPFM to repeated MAPF: an optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found.
 In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
@@
 	\subsection{Exhaustive ICTS}
-	For $K$ teams $t_1,\ldots,t_K$ of size $t_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals.
+	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals.
 Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the instance, with $C_m = \infty$ for unfeasible $m$.
@@
 	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks exist\footnote{That is, to the knowledge of the author.}.
-For MAPF there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances.
+For MAPF, there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances.
 It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
@@
 	For each of these types, two sets of maps were generated with between $1$ and $10$ agents and 50 instances generated for each such agent-setting: one set where all agents belong to one team, another in which the agents were divided into three teams (or $1,2$ teams respectively for the datapoints with $1,2$ agents).
-The results are shown in Figure \ref{fig:times} and \ref{fig:probs}, that respectively show the average time to solution and the fraction of problems solved out of 50 instances.
+The results are shown in Figure \ref{fig:times} and \ref{fig:probs}, which respectively show the average time to solution and the fraction of problems solved out of 50 instances.
 The algorithms and interpretation of results are discussed below.
@@
 	The goal of this research was to seek alternative approaches to solving MAPFM based on ICTS.
-In this the research has succeeded, but the performance and in particular the scalability of the algorithms leaves something to be desired.
+In this, the research has succeeded, but the performance and in particular the scalability of the algorithms leaves something to be desired.
 	\section{Future work}
-	The ICTS-m algorithm described in this work scales quite poorly for a number of reasons including the highly optimistic root SIC value.
+	The ICTS-m algorithm described in this work scales quite poorly for several reasons including the highly optimistic root SIC value.
 It might be possible to conceive of a different ICTS-m algorithm that is better able to take advantage of the agents being divided into teams, for instance by first solving all intra-team conflicts before proceeding to consider inter-team conflicts.

### 2021-06-09 src/bench.py

@@ -117,32 +117,32 @@ if __name__ == "__main__":
         #     debug=False,
         #     sort_matchings=False,
         # ),
+        # SolverConfig(
+        #     name="(ictsm)-(enhanced)-(no-id)",
+        #     combs=3,
+        #     prune=True,
+        #     enhanced=True,
+        #     pruned_child_gen=False,
+        #     id=False,
+        #     conflict_avoidance=True,
+        #     enumerative=False,
+        #     debug=False,
+        #     sort_matchings=False,
+        # ),
+        # SolverConfig(
+        #     name="(ictsm)-(enhanced)-(id)",
+        #     combs=3,
+        #     prune=True,
+        #     enhanced=True,
+        #     pruned_child_gen=False,
+        #     id=True,
+        #     conflict_avoidance=True,
+        #     enumerative=False,
+        #     debug=False,
+        #     sort_matchings=False,
+        # ),
         SolverConfig(
-            name="(ictsm)-(enhanced)-(no-id)",
-            combs=3,
-            prune=True,
-            enhanced=True,
-            pruned_child_gen=False,
-            id=False,
-            conflict_avoidance=True,
-            enumerative=False,
-            debug=False,
-            sort_matchings=False,
-        ),
-        SolverConfig(
-            name="(ictsm)-(enhanced)-(id)",
-            combs=3,
-            prune=True,
-            enhanced=True,
-            pruned_child_gen=False,
-            id=True,
-            conflict_avoidance=True,
-            enumerative=False,
-            debug=False,
-            sort_matchings=False,
-        ),
-        SolverConfig(
-            name="(ictsm)-(simple-child)-(no-id)",
+            name="test",
             combs=3,
             prune=True,
             enhanced=False,

### 2021-06-12 src/ictsm/ict_search.py
Added Exh. with ID to comparison, generated new plots

@@ -299,30 +299,29 @@ class ICTSearcher(object):
                         node_list[i] += 1
                         if not tuple(node_list) in visited:
                             frontier.append(tuple(node_list))
-
-                    conflict_team_combination = None
-                    if False and len(problem.team_agent_indices) > 1:
-                        conflict_team_combination = self.check_within_teams(
-                            problem,
-                            mdds,
-                            accumulator,
-                            context,
-                        )
-                    if not conflict_team_combination:
-                        conflict_combination = None
-                        if self.prune and k > self.combs:
-                            conflict_combination = self.check_combinations(
-                                mdds, k, accumulator, context
+                    if self.lower_sic_bound <= node_sum:
+                        conflict_team_combination = None
+                        if False and len(problem.team_agent_indices) > 1:
+                            conflict_team_combination = self.check_within_teams(
+                                problem,
+                                mdds,
+                                accumulator,
+                                context,
                             )
-
-                        if not conflict_combination:
-                            conflict_team_comb = None
-                            if False and len(problem.team_agent_indices) > self.team_combs:
-                                conflict_team_comb = self.check_team_combinations(
-                                    problem, mdds, accumulator, context
+                        if not conflict_team_combination:
+                            conflict_combination = None
+                            if self.prune and k > self.combs:
+                                conflict_combination = self.check_combinations(
+                                    mdds, k, accumulator, context
                                 )
-                            if not conflict_team_comb:
-                                if self.lower_sic_bound <= node_sum:
+
+                            if not conflict_combination:
+                                conflict_team_comb = None
+                                if False and len(problem.team_agent_indices) > self.team_combs:
+                                    conflict_team_comb = self.check_team_combinations(
+                                        problem, mdds, accumulator, context
+                                    )
+                                if not conflict_team_comb:
                                     solution: JointTimedSolution = seek_solution_in_joint_mdd(
                                         mdds, True, False, [], context
                                     )

### 2021-06-12 docs/paper.tex

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{conjecture}{Conjecture}
+\newtheorem{property}{Property}
 \usepackage{algorithm}
@@
 	\subsubsection{Top-level search}
-	In the top-level search, all possible cost vectors for a given SIC are evaluated by searching an Increasing Cost Tree as depicted in \ref{fig:ict}, starting from $C_{root} = \sum_i c^*_i$ corresponding to a single root cost vector $(c^*_1,c^*_2,\ldots,c^*_k)$.
-This root has $k$ children $(c^*_1 + 1,c^*_2,\ldots,c^*_k),(c^*_1,c^*_2 + 1,\ldots,c^*_k),\ldots,(c^*_1,c^*_2,\ldots,c^*_k + 1)$ all of cost $C = C_{root} + 1$.
-Searching this ICT breadth-first corresponds to evaluating all possible cost vectors corresponding to increasing cost $C$ starting with $C_{root}$, guaranteeing optimality of a found solution.
-The number of cost vectors evaluated when searching up to nodes of cost $C_{root} + \Delta$ is $\mathcal{O}(k^\Delta)$.
+	In the top-level search, all possible cost vectors for a given SIC are evaluated by searching an Increasing Cost Tree as depicted in \ref{fig:ict}, starting from $C^* = \sum_i c^*_i$ corresponding to a single root cost vector $(c^*_1,c^*_2,\ldots,c^*_k)$.
+This root has $k$ children $(c^*_1 + 1,c^*_2,\ldots,c^*_k),(c^*_1,c^*_2 + 1,\ldots,c^*_k),\ldots,(c^*_1,c^*_2,\ldots,c^*_k + 1)$ all of cost $C = C^* + 1$.
+Searching this ICT breadth-first corresponds to evaluating all possible cost vectors corresponding to increasing cost $C$ starting with $C^*$, guaranteeing optimality of a found solution.
+The number of cost vectors evaluated when searching up to nodes of cost $C^* + \Delta$ is $\mathcal{O}(k^\Delta)$.
 Node evaluation is done by a low-level search that searches for a solution $(\pi_1,\ldots,\pi_k)$ corresponding to the node costs $(c_1,\ldots,c_k)$.
@@
 	\end{algorithm}
-
 	\subsubsection{Pruning in ICTS}
@@
 In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
+	\subsubsection{Bounded search}
+	Once the first solution is found with cost $C$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched.
+Formally, let $B_0 = \infty$ represent the initial SIC bound of the ICT search.
+After solving each $m$ with solution cost $C_m$, let $B_{m+1} = \min(B_m,C_m)$.
+By successively updating this $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.
+With $C_m$ denoting the optimal SIC for matching $m$, this effort can be expressed as
+	\[\Delta_{m,bounded} = C^*_m - \min(B_m,C_m) = C^*_m - B_{m+1}\]
+	\subsubsection{Ordering matchings}
+	As a further improvement of this method, the matchings $m$ could be enumerated and solved in increasing order of $C^*_m$.
+In this case, the effort per matching can be shown to be monotonically non-increasing.
+As will be shown in section \ref{experiments}, this monotonic reduction of effort appears to be a desirable property but pathelogical cases can be constructed where the $\Delta_{m,bounded}$ of $m$ with low SIC is much higher, thus dominating the performance.
+	\begin{property}[Monotonicity]
+		In bounded exhaustive search using ICTS, solving the matchings in increasing order of root SIC makes the effort $\Delta_{m,bounded}$ monotonically non-increasing as a function of $m$.
+	\end{property}
+	\begin{proof}
+		Due to the order of matchings for successive matchings $m,m+t$ for some $t\geq 1$, $C^*_{m} \leq C^*_{m+t}$.
+By definition, $B_{m+1} = \min(B_m,C_m)$ meaning that $B_{m+1} \leq C_m$ and $B_{m+1} \leq B_m$ so by induction $B_{m+t} \leq C_m$ and similarly $B_{m+t} \leq B_m$.
+Therefore
+		\[C^*_{m+t} - B_{m+t} \leq C^*_m - B_m \implies \Delta_{m+t,bounded} \leq \Delta_{m,bounded}\]
+	\end{proof}
+	In practice, it is quite difficult enumerate all matchings in increasing order of root SIC.
+Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time; however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking for equivalent matchings).
+This means that matchings have to be exhaustively enumerated and stored in memory to sort them, but this requires $\mathcal{O}(M)$ memory which was found to be more problematic in implementation than the corresponding time complexity of the sorting, $\mathcal{O}(M\log(M))$.
 
-	However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes.
-Formally, let $B = \infty$ represent the initial SIC bound of the ICT search.
-After solving each $C_m$, let $B_{m+1} = \min(B_m,C_m)$.
-By successively updating this $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.
-
-	As a further improvement of this method, the order in which matchings are enumerated and solved could be changed.
-In particular, by sorting the matchings in increasing order of root SIC, it can be seen that $\Delta'_{m + 1}$, the distance from $B_{m+1}$ or the solution to matching $m + 1$ (whichever was reached first) and the root SIC, will always be less or equal to the $\Delta'_m$ [TODO: proof].
-Although this is itself a promising property, to make use of it, all roots have to be computed and all $M$ corresponding SIC values have to be sorted which is a $\mathcal{O}(M\log M)$ procedure.
-
+	To still make use of a form of monotonicity, a
 	\subsection{ICTS-m}
@@
 As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
-	\subsection{General optimization: child pruning}
+	\subsection{General optimizations}
+	\subsubsection{Lower bound in ID}
+	\begin{property}[Lower bound]
+		When merging groups $g_i,g_j$ with solution costs $C_i,C_j$ to yield group $g_k$, for any solution for this group with cost $C_k$
+		\[C_k\geq C_i + C_j\]
+	\end{property}
+	\begin{proof}
+		Assume there would be a solution with $C_k < C_i + C_j$.
+Taking $C_k^i$ to denote the SIC of agents that used to make up $g_i$ in the solution to $g_k$, without loss of generality $C_k^i < C_i$, which contradicts the optimality of $C_i$ as solution for $g_i$ independent of $g_j$.
+	\end{proof}
+	In practice, this means that the above lower-bound can be used to skip the $k$-agent low-level search for any candidate ICT node with $C_{k,candidate}<C_i + C_j$.
+
+	\subsubsection{Child pruning}
 	An optimization of ICTS that hitherto appears to not have been described in the literature was found in the process of optimizing ICTS-m.
 The idea is simple: when pruning, in the original ICTS formulation all $k$-children are generated in every case because pruning only controls skipping the low-level search, assumed to be the most expensive operation.
-However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented in any solution node.
+However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented.
 This reduces the number of children generated to the number of conflicting agents, which quite drastically can improve the branching factor of the ICT search if say $k = 12$ but a conflicting pair is found.
 
+	Child pruning cannot be combined with enhanced pruning whilst retaining optimality due to the \textit{cascading effect} that Sharon et al.
+describe in the original ICTS paper\cite{sharon2011}.
+Consider Figure \ref{fig:counter-example-ep}.
+It can be seen that $(3,8,5)$ with SIC $16$ is the optimal solution here, which corresponds to $red$ moving aside, allowing $green$ to pass.
+Say enhanced pruning with pairs is applied to these three agents at node $(c_{red},c_{green},c_{gray}) = (0,8,5)$.
+	Let the enhanced pruning order be $(red,green)$, $(red,gray)$, $(green,gray)$.
+$(red,green)$ is solvable but will leave for $green$ out of the two paths of length $8$ only the clock-wise path.
+$(red,gray)$ will not change either MDD.
+When $(green,gray)$ is evaluated, it is found that the remaining clockwise path for $green$ and $gray$'s path are incompatible (would require swapping) so $(0,9,5)$ and $(0,8,6)$ are generated.
+Proceeding similarly for these two nodes, for neither a solution is found so from $(0,9,5)$, $(0,10,5),(0,9,6)$ and from $(0,8,6)$, $(0,9,6),(0,8,7)$.
+In the end, with this pruning scheme, nodes
+
+	\begin{figure*}
+	\centering
+	\begin{subfigure}{0.40\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/counter-example-ep-2}
+		\caption{Instance}
+		\label{fig:open1}
+	\end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/counter-example-tree}
+		\caption{Pruned ICT that is traversed}
+		\label{fig:open3}
+	\end{subfigure}
+		\caption{Counter-example for enhanced pruning with child pruning}
+	\end{figure*}
+	In enhanced pruning, it is less clear if in every case it is safe to only generate nodes corresponding to conflicting agents.
+This is due to the \textit{cascading effect} that Sharon et al.
+describe in the original ICTS paper\cite{sharon2011}.
+Consider ICT node $(c_1,c_2,c_3)$ with MDDs $MDD_1^{c_1},MDD_2^{c_2},MDD_3^{c_3}$
+
+	 in enhanced pruning with pairs, even if $MDD_i,MDD_j$ have a solution, as part of the search routine the MDDs could have become sparser due to totally incompatible children being pruned in the process.
+If now $MDD_i$ and some $MDD_k$ are searched and no solution is found, in child pruning only children for these two nodes would be generated while in the optimal solution, $MDD_i$ might need its $c_i$ increased.
+
+	\begin{conjecture}
+		Enhanced pruning combined with child pruning is suboptimal.
+	\end{conjecture}
 	It is conjectured that child pruning combined with enhanced pruning does not in general guarantee optimality, but despite extensive search no counter-example has been found.
@@
 	\section{Experiments}
+	\label{experiments}
 	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks exist\footnote{That is, to the knowledge of the author.}.
@@
 	\subsection{Algorithms}
-	Various improvements and variations of algorithms were tried out, as shown in the legend.
-S and E denote simple and enhanced pruning respectively; ID means that Independence Detection was used; C means that child pruning was used.
+	Various improvements and variations of algorithms were tried out, as shown in the legend. The meanings of the various modifiers are as follows.
+	\begin{enumerate}
+		\item S: Simple pruning
+		\item E: Enhanced pruning
+		\item C: Child pruning. Notice that enhanced pruning and child pruning were not combined because for this optimality is not guaranteed in the general case.
+		\item ID: Independence detection, so the algorithm was run as ID subroutine
+		\item O: Evaluate matchings in increasing order of root SIC (with some practical limitations)
+		\item D: Limit 
+	\end{enumerate}
 	\subsection{Results}

### 2021-06-12 docs/paper.tex
Finished counter-example demonstration, corrected monotonicity proof and added exhaustive icts pseudocode

@@
 Few methods exist today that solve it although the problems do appear together in real-world problems, such as in the Train Unit Shunting and Servicing problem.
-In this work, a novel method based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding is presented that can optimally solve this joint problem.
+In this work, two families of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem.
 	\end{abstract}
@@
 Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.
+	[TODO: update to reflect focus on optimizations of exhaustive approach]
 
@@
 
-	So given a combination of paths $(\pi_1,\ldots,\pi_k)$, a vector of costs is found from which the SIC is derived.
-This is a surjective mapping: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
+	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
 On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods like Jump Point Search\cite{harabor2011} are used to speed up the search.
@@
 For each method, some properties and method-specific optimizations and variations will be discussed.
-Afterwards, some more general considerations will be discussed.
+Afterwards, some more general optimizations and variants will be discussed.
 	\subsection{Exhaustive ICTS}
@@
 With $C_m$ denoting the optimal SIC for matching $m$, this effort can be expressed as
-	\[\Delta_{m,bounded} = C^*_m - \min(B_m,C_m) = C^*_m - B_{m+1}\]
-	\subsubsection{Ordering matchings}
+	\[\Delta_{m,bounded} = \min(B_m,C_m) - C^*_m = B_{m+1} - C^*_m\]
+	\subsubsection{Ordered enumeration}
 	As a further improvement of this method, the matchings $m$ could be enumerated and solved in increasing order of $C^*_m$.
 In this case, the effort per matching can be shown to be monotonically non-increasing.
-As will be shown in section \ref{experiments}, this monotonic reduction of effort appears to be a desirable property but pathelogical cases can be constructed where the $\Delta_{m,bounded}$ of $m$ with low SIC is much higher, thus dominating the performance.
+As will be shown in section \ref{experiments}, this monotonic reduction of effort appears to be a desirable property in practice but pathelogical cases could be constructed where the $\Delta_{m,bounded}$ of $m$ with low SIC is much higher, thus dominating the performance.
 	\begin{property}[Monotonicity]
@@
 		Due to the order of matchings for successive matchings $m,m+t$ for some $t\geq 1$, $C^*_{m} \leq C^*_{m+t}$.
-By definition, $B_{m+1} = \min(B_m,C_m)$ meaning that $B_{m+1} \leq C_m$ and $B_{m+1} \leq B_m$ so by induction $B_{m+t} \leq C_m$ and similarly $B_{m+t} \leq B_m$.
-Therefore
-		\[C^*_{m+t} - B_{m+t} \leq C^*_m - B_m \implies \Delta_{m+t,bounded} \leq \Delta_{m,bounded}\]
+By definition, $B_{m+1} = \min(B_m,C_m)$ meaning that $B_{m+1} \leq C_m$ and $B_{m+1} \leq B_m$ so transitively $B_{m+t} \leq B_m$.
+Therefore as $B_{m+t} \leq B_m$ and $C^*_{m+t} \geq C^*_{m}$,
+		\[\min(B_{m+t},C_{m+t}) - C^*_{m+t}\leq \min(B_m,C_m) - C^*_m\implies \Delta_{m+t,bounded} \leq \Delta_{m,bounded}\]
 	\end{proof}
 	In practice, it is quite difficult enumerate all matchings in increasing order of root SIC.
-Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time; however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking for equivalent matchings).
+Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time; however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking).
 This means that matchings have to be exhaustively enumerated and stored in memory to sort them, but this requires $\mathcal{O}(M)$ memory which was found to be more problematic in implementation than the corresponding time complexity of the sorting, $\mathcal{O}(M\log(M))$.
 
-	To still make use of a form of monotonicity, a
+		\begin{algorithm}
+		\begin{algorithmic}[1]
+			\State \text{Fill PQ with }$\min(M,M_{pq})$\text{ matchings}
+			\State $B \gets \infty$
+			\State $solution \gets none$
+			\Repeat
+			\State $m\gets\text{Take matching with lowest SIC from PQ}$
+			\State $solution_m$ \text{with cost} $C_m\gets$\text{Solve $m$ with upper-bound }$B$ 
+			\If{\text{$C_m < B$}}
+			\State $B\gets C_m$
+			\State $solution \gets solution_m$
+			\EndIf
+			\State $B\gets\min(B,C_m)$
+			\If{\text{there is an unsolved matching }$m_{new}$\text{ not in }$PQ$}
+			\State \text{Compute root SIC and insert }$m_{new}$\text{into PQ}
+			\EndIf
+			\Until{\text{PQ is empty}}
+			\Return $solution$
+		\end{algorithmic}
+		\caption{Approximate ordered exhaustive ICTS} 
+		\label{pq-algo}
+	\end{algorithm}
+
+	In implementation, the above behaviour is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$ ($M_{pq} = 10000$ was used but this could be much increased at the cost of memory).
+Algorithm \ref{pq-algo} outlines the procedure.
+This way of getting around memory limitations originates in [TODO: cite Jaap's paper].
+
+	 As long as matchings still remain, the priority queue is refilled after each processed matching until running out of matchings, after which. .
+
 	\subsection{ICTS-m}
@@
 		Assume there would be a solution with $C_k < C_i + C_j$.
-Taking $C_k^i$ to denote the SIC of agents that used to make up $g_i$ in the solution to $g_k$, without loss of generality $C_k^i < C_i$, which contradicts the optimality of $C_i$ as solution for $g_i$ independent of $g_j$.
+Taking $C_k^i$ to denote the SIC of agents that used to make up $g_i$ in the solution to $g_k$, without loss of generality $C_k^i < C_i$, which contradicts the optimality of the solution with cost $C_i$ for $g_i$ independent of $g_j$.
 	\end{proof}
@@
 	\subsubsection{Child pruning}
-	An optimization of ICTS that hitherto appears to not have been described in the literature was found in the process of optimizing ICTS-m.
-The idea is simple: when pruning, in the original ICTS formulation all $k$-children are generated in every case because pruning only controls skipping the low-level search, assumed to be the most expensive operation.
+	In the original ICTS formulation all $k$-children are generated in every case because pruning only controls skipping the low-level search, assumed to be the most expensive operation.
 However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented.
-This reduces the number of children generated to the number of conflicting agents, which quite drastically can improve the branching factor of the ICT search if say $k = 12$ but a conflicting pair is found.
-
-	Child pruning cannot be combined with enhanced pruning whilst retaining optimality due to the \textit{cascading effect} that Sharon et al.
-describe in the original ICTS paper\cite{sharon2011}.
-Consider Figure \ref{fig:counter-example-ep}.
-It can be seen that $(3,8,5)$ with SIC $16$ is the optimal solution here, which corresponds to $red$ moving aside, allowing $green$ to pass.
-Say enhanced pruning with pairs is applied to these three agents at node $(c_{red},c_{green},c_{gray}) = (0,8,5)$.
-	Let the enhanced pruning order be $(red,green)$, $(red,gray)$, $(green,gray)$.
-$(red,green)$ is solvable but will leave for $green$ out of the two paths of length $8$ only the clock-wise path.
-$(red,gray)$ will not change either MDD.
-When $(green,gray)$ is evaluated, it is found that the remaining clockwise path for $green$ and $gray$'s path are incompatible (would require swapping) so $(0,9,5)$ and $(0,8,6)$ are generated.
-Proceeding similarly for these two nodes, for neither a solution is found so from $(0,9,5)$, $(0,10,5),(0,9,6)$ and from $(0,8,6)$, $(0,9,6),(0,8,7)$.
-In the end, with this pruning scheme, nodes
+This reduces the number of children generated to the number of conflicting agents, often just 2 or 3, which quite drastically can improve the (average) branching factor.
+	\begin{property}[Incompatibility with enhanced pruning]
+		Child pruning combined with enhanced pruning is suboptimal due to the \textit{cascading effect} that Sharon et al. describe in the original ICTS paper\cite{sharon2011}.
+	\end{property}
+	\begin{proof}
+		Assume this combination is optimal.
+Consider Figure \ref{fig:counter-example:a} with a red agent $r$, green agent $g$ and black agent $b$.
+It can be seen that $(3,8,5)$ with SIC $16$ is an optimal solution for this instance, which corresponds to $r$ moving aside, allowing $g$ to pass.
+Say enhanced pruning with pairs is applied to these three agents at $(c^*_r,c^*_g,c^*_b) = (0,8,5)$.
+Let the enhanced pruning order be $(r,g)$, $(r,b)$, $(g,b)$ without loss of generality.
+$(r,g)$ is solvable but will leave for $g$ out of the two paths of length $8$ only the clock-wise path.
+$(r,b)$ will not change either MDD in this node.
+When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (swapping conflict) so $(0,9,5)$ and $(0,8,6)$ are generated.
+By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed.
+Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that \ref{fig:counter-example:a} contradicts the optimality of enhanced pruning combined with child pruning and that therefore this combination must be suboptimal.
+	\end{proof}
 
@@
 		\caption{Instance}
-		\label{fig:open1}
+		\label{fig:counter-example:a}
 	\end{subfigure}
@@
 		\caption{Pruned ICT that is traversed}
-		\label{fig:open3}
+		\label{fig:counter-example:b}
 	\end{subfigure}
 		\caption{Counter-example for enhanced pruning with child pruning}
+		\label{fig:counter-example}
 	\end{figure*}
-	In enhanced pruning, it is less clear if in every case it is safe to only generate nodes corresponding to conflicting agents.
-This is due to the \textit{cascading effect} that Sharon et al.
-describe in the original ICTS paper\cite{sharon2011}.
-Consider ICT node $(c_1,c_2,c_3)$ with MDDs $MDD_1^{c_1},MDD_2^{c_2},MDD_3^{c_3}$
-
-	 in enhanced pruning with pairs, even if $MDD_i,MDD_j$ have a solution, as part of the search routine the MDDs could have become sparser due to totally incompatible children being pruned in the process.
-If now $MDD_i$ and some $MDD_k$ are searched and no solution is found, in child pruning only children for these two nodes would be generated while in the optimal solution, $MDD_i$ might need its $c_i$ increased.
-
-	\begin{conjecture}
-		Enhanced pruning combined with child pruning is suboptimal.
-	\end{conjecture}
-	It is conjectured that child pruning combined with enhanced pruning does not in general guarantee optimality, but despite extensive search no counter-example has been found.
-[TODO: find counter-example/proof optimality]
 	\begin{figure*}

### 2021-06-14 docs/paper.tex
Worked on paper

@@
 \newtheorem{property}{Property}
+\newtheorem{corollary}{Corollary}[property] % Use theorem counter as `parent`
 \usepackage{algorithm}
@@
 	\begin{abstract}
-		Both the assignment problem and the multi-agent pathfinding problem are common problems in fields such as robotics and transportation.
-The joint problem of finding matchings inducing an optimal non-conflicting routing of agents to their goals is something that has not been studied much.
-Few methods exist today that solve it although the problems do appear together in real-world problems, such as in the Train Unit Shunting and Servicing problem.
-In this work, two families of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem.
+		Both the assignment problem and the multi-agent pathfinding problem are common problems in the fields of robotics and transportation.
+The joint problem of multi-agent pathfinding extended with matching between agents and goals is something that has not been studied much.
+Few methods exist today that solve it although the problems do appear together in practice, such as in the Train Unit Shunting and Servicing problem.
+In this work, two classes of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem.
+Algorithms within the families are compared to each other experimentally.
+An algorithm from the first family, one based on exhaustive matching enumeration, is compared to alternative algorithms.
 	\end{abstract}
@@
 	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
-It should be noted that this method minimizes the makespan and not the sum of individual costs which is the objective used in the TUSS relaxation, meaning that non-trivial modifications to CMB are needed to minimize SIC.
-	The successful application of CBS to solving MAPFM begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?
+It should be noted that this method minimizes the makespan and not the sum of individual costs (SIC) which is the objective used in the TUSS relaxation, meaning that non-trivial modifications to CBM are needed to minimize SIC.
+	The successful application of CBS to solving MAPFM begs the question: \textit{can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM algorithm?}
 
@@
 	\end{wrapfigure}
-	This work is the outcome of a search for an efficient algorithm for optimally solving MAPFM derived from ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}.
-ICTS, in short, is a two-level approach to MAPF with a top-level breadth-first traversal of an Increasing Cost Tree (ICT) representing combinations of per-agent path costs and a bottom-level evaluation of ICT nodes using multi-valued decision diagrams (MDDS).
-These MDDS represent per agent all possible paths to the goal of a set length.
-In the context of a research project in which multiple such
-	MAPF algorithms were taken as starting points for MAPFM algorithms within a group, the novel ICTS-based algorithm is compared to these algorithms on a set of benchmarks similar to those described in \cite{stern2019}.
-In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.
-Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.
-	[TODO: update to reflect focus on optimizations of exhaustive approach]
+	This work is the outcome of a search for algorithms for optimally solving MAPFM based on ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}.
+Two classes of algorithms were found, one based on exhaustive enumeration of matchings using a variant of ICTS as subroutine, the other based on modifications to the ICT structure and its search.
+In the context of a research project in which multiple MAPF algorithms in addition to ICTS were taken as starting points for MAPFM algorithms, one exhaustive ICTS algorithm is compared to these alternatives on a set of benchmarks.
+In addition, properties of the various algorithm variants are discussed and their performance is compared experimentally.
 
-	% Lastly, completeness of the algorithm is considered as this is a key property in the context of MAPFM as a TUSS relaxation.
 	\section{Multi-agent pathfinding with matching} % Problem description
@@
 
+	If all teams are singleton, the MAPFM instance is equivalent to a MAPF instance; if there is just one team, this corresponds to an anonymous MAPF problem that can be solved in polynomial time.
+
 	%
@@
 Let $\Delta_m$ be similarly defined and represent the difference between $C_m$ and the root cost of $m$.
-In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
+In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
 	\subsubsection{Bounded search}
@@
 	\[\Delta_{m,bounded} = \min(B_m,C_m) - C^*_m = B_{m+1} - C^*_m\]
+	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,bounded}})$.
 	\subsubsection{Ordered enumeration}
 	As a further improvement of this method, the matchings $m$ could be enumerated and solved in increasing order of $C^*_m$.
-In this case, the effort per matching can be shown to be monotonically non-increasing.
-As will be shown in section \ref{experiments}, this monotonic reduction of effort appears to be a desirable property in practice but pathelogical cases could be constructed where the $\Delta_{m,bounded}$ of $m$ with low SIC is much higher, thus dominating the performance.
+In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}.
+As will be shown in section \ref{experiments}, this monotonic reduction of effort appears to be a desirable property in practice but pathelogical cases could be constructed where the $\Delta_{m,bounded}$ of $m$ with low $C^*_m$ is much higher, thus dominating the performance.
 	\begin{property}[Monotonicity]
+		\label{monotonicity}
 		In bounded exhaustive search using ICTS, solving the matchings in increasing order of root SIC makes the effort $\Delta_{m,bounded}$ monotonically non-increasing as a function of $m$.
@@
 		Due to the order of matchings for successive matchings $m,m+t$ for some $t\geq 1$, $C^*_{m} \leq C^*_{m+t}$.
-By definition, $B_{m+1} = \min(B_m,C_m)$ meaning that $B_{m+1} \leq C_m$ and $B_{m+1} \leq B_m$ so transitively $B_{m+t} \leq B_m$.
-Therefore as $B_{m+t} \leq B_m$ and $C^*_{m+t} \geq C^*_{m}$,
-		\[\min(B_{m+t},C_{m+t}) - C^*_{m+t}\leq \min(B_m,C_m) - C^*_m\implies \Delta_{m+t,bounded} \leq \Delta_{m,bounded}\]
+By definition, $B_{m+2} = \min(B_{m+1},C_{m+1})$ meaning that $B_{m+2} \leq B_{m + 1}$ so transitively $B_{m+t+1} \leq B_{m+1}$.
+Therefore
+		\[B_{m+t+1} - C^*_{m+t}\leq B_{m+1} - C^*_m\implies \Delta_{m+t,bounded} \leq \Delta_{m,bounded}\]
 	\end{proof}
+	\subsubsection{Approximate ordered enumeration}
 	In practice, it is quite difficult enumerate all matchings in increasing order of root SIC.
 Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time; however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking).
-This means that matchings have to be exhaustively enumerated and stored in memory to sort them, but this requires $\mathcal{O}(M)$ memory which was found to be more problematic in implementation than the corresponding time complexity of the sorting, $\mathcal{O}(M\log(M))$.
+This means that matchings have to be exhaustively enumerated and stored in memory to sort them, but this requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
 
@@
 
-	In implementation, the above behaviour is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$ ($M_{pq} = 10000$ was used but this could be much increased at the cost of memory).
+	In implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory}.
 Algorithm \ref{pq-algo} outlines the procedure.
 This way of getting around memory limitations originates in [TODO: cite Jaap's paper].
-
-	 As long as matchings still remain, the priority queue is refilled after each processed matching until running out of matchings, after which. .
 
@@
 	\end{wrapfigure}
-	\subsubsection{Properties of ICTS-m}
+	\subsubsection{Pathological case}
+	\label{pathology}
 	As a consequence of the $\min$ operation in the root definition, a pathological case can be derived.
@@
 	\subsection{General optimizations}
-	\subsubsection{Lower bound in ID}
+	To improve both types of algorithms, some general optimizations were found that can be used to speed up the search that are here motivated. 
+	\subsubsection{Bounds in ID}
 	\begin{property}[Lower bound]
@@
 	\end{proof}
-	In practice, this means that the above lower-bound can be used to skip the $k$-agent low-level search for any candidate ICT node with $C_{k,candidate}<C_i + C_j$.
-
+	\begin{corollary}[Reduced upper bound]
+		In bounded exhaustive search, the sum of costs of groups not being merged can be subtracted from bound $B$ without losing optimality.
+	\end{corollary}
 	\subsubsection{Child pruning}
@@
 However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented.
-This reduces the number of children generated to the number of conflicting agents, often just 2 or 3, which quite drastically can improve the (average) branching factor.
+This prunes the children generated that do not correspond to the conflicting agents, of which there are often just 2 or 3, which quite drastically can improve the (average) branching factor.
 	\begin{property}[Incompatibility with enhanced pruning]
-		Child pruning combined with enhanced pruning is suboptimal due to the \textit{cascading effect} that Sharon et al. describe in the original ICTS paper\cite{sharon2011}.
+		Enhanced pruning combined with child pruning (hereafter E+C pruning) is suboptimal due to the \textit{cascading effect} described in \cite{sharon2011}.
 	\end{property}
 	\begin{proof}
-		Assume this combination is optimal.
 		Consider Figure \ref{fig:counter-example:a} with a red agent $r$, green agent $g$ and black agent $b$.
@@
 By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed.
-Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that \ref{fig:counter-example:a} contradicts the optimality of enhanced pruning combined with child pruning and that therefore this combination must be suboptimal.
+Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that E+C pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making it suboptimal.
 	\end{proof}
@@
 	\end{subfigure}
-		\caption{Counter-example for enhanced pruning with child pruning}
+		\caption{Counter-example for E+C pruning}
 		\label{fig:counter-example}
@@
 
-	\section{Experiments}
+	\section{Results}
 	\label{experiments}
 	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks exist\footnote{That is, to the knowledge of the author.}.
-For MAPF, there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances.
+For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances.
 It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
 This observation informed the creation of a map generator within the peer group with various parameters.
-Using this map generator, three types of 20x20 grids were generated:
+Using this map generator, two types of 20x20 grids were generated:
 	\begin{enumerate}
-		\item Open: An obstacle-free grid
-		\item Obstacle: A grid with some obstacles
-		\item Maze: A grid with many obstructed tiles
+		\item 25: a grid with 25\% of tiles being obstacles.
+		\item 75: a grid with 75\% of tiles being obstacles. 
 	\end{enumerate}
-	For each of these types, two sets of maps were generated with between $1$ and $10$ agents and 50 instances generated for each such agent-setting: one set where all agents belong to one team, another in which the agents were divided into three teams (or $1,2$ teams respectively for the datapoints with $1,2$ agents).
+	For each of these types, two sets of maps were generated with between $1$ to $16$ agents and 200 instances generated for each such agent-setting: one set where all agents belong to one team, another in which the agents were divided into three teams (or $1,2$ teams respectively for the datapoints with $1,2$ agents).
+
+	Two different experiments were run: one comparing ICTS-based algorithms discussed in this work, and one comparing one of these, the approximate ordered enumeration variant (Exh+E+B+O in the relative comparisons), to other algorithms for MAPFM developed within the peer group\footnote{I want to thank Jonathan Dönszelmann, who worked on M*-based algorithms, for setting up this comparison[TODO: move to thanks note at end]}.
+
+	In experiments used to compare the different MAPFM algorithms within the peer group, care was taken to make the comparison fair: all algorithms are implemented in Python 3 and run on the same system: a server with a 12-core Intel Xeon E5-2683 with 8Gb of RAM dedicated to running experiments for this project.
+
 	The results are shown in Figure \ref{fig:times} and \ref{fig:probs}, which respectively show the average time to solution and the fraction of problems solved out of 50 instances.
@@
 		\item E: Enhanced pruning
-		\item C: Child pruning. Notice that enhanced pruning and child pruning were not combined because for this optimality is not guaranteed in the general case.
-		\item ID: Independence detection, so the algorithm was run as ID subroutine
-		\item O: Evaluate matchings in increasing order of root SIC (with some practical limitations)
-		\item D: Limit 
+		\item C: Child pruning
+		\item ID: Independence detection
+		\item B: Bounded search
+		\item O: Approximate ordered enumeration
 	\end{enumerate}
@@
 	\section{Responsible Research}
-	In experiments used to compare the different MAPFM algorithms within the peer group, care was taken to make the comparison fair: all algorithms are implemented in Python 3 and run on the same system: a server with a 12-core Intel Xeon E5-2683 with 8Gb of RAM dedicated to running experiments for this project.
 	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
@@
 	\section{Future work}
+	TODO: discuss following unexplored ideas (mention that some are more engineering-related)
+	\begin{enumerate}
+		\item Team cost lower-bounds (low-level search pruning) using hungarian algorithm.
+		\item Hybridized approaches between exhaustive and native methods.
+		\item More aggressive pruning (in particular for ICTS-m): different (simple child) pruning stages 2,3,4 agents. Prioritizing pruning within teams.
+	\end{enumerate}
+	As discussed in \ref{pathology}, the root of the ICT searched in ICTS-m is highly optimistic and often 
 	The ICTS-m algorithm described in this work scales quite poorly for several reasons including the highly optimistic root SIC value.

### 2021-06-14 docs/paper.tex
Updated plots in paper

@@
 		\centering
-			\includegraphics[width=\linewidth]{img/results/open-1}
-			\caption{Open, 1 team}
-			\label{fig:open1}
+		\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
+		\caption{25, 1 team}
+		\label{fig:open1p}
 	\end{subfigure}
@@
 		\centering
-			\includegraphics[width=\linewidth]{img/results/open-3}
-			\caption{Open, 3 teams}
-			\label{fig:open3}
+		\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
+		\caption{25, 3 teams}
+		\label{fig:open3p}
 	\end{subfigure}
@@
 		\centering
-			\includegraphics[width=\linewidth]{img/results/obstacle-1}
-			\caption{Obstacle, 1 team}
-			\label{fig:obstacle1}
+		\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
+		\caption{75, 1 team}
+		\label{fig:obstacle1p}
 	\end{subfigure}
@@
 		\centering
-			\includegraphics[width=\linewidth]{img/results/obstacle-3}
-			\caption{Obstacle, 3 teams}
-			\label{fig:obstacle3}
+		\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
+		\caption{75, 3 teams}
+		\label{fig:obstacle3p}
 	\end{subfigure}
-		\begin{subfigure}{0.49\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{img/results/maze-1}
-			\caption{Maze, 1 team}
-			\label{fig:m1}
-		\end{subfigure}
-		\begin{subfigure}{0.49\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{img/results/maze-3}
-			\caption{Maze, 3 teams}
-			\label{fig:m3}
-		\end{subfigure}
-		\caption{Average solving time of algorithm variants on various types of 20x20 grids with a 30s timeout}
-		\label{fig:times}
+	\caption{Fraction solved out of 50 maps of algorithm variants on two types of 20x20 grids with a 120s timeout}
+	\label{fig:probs}
 	\end{figure*}
-
 	\begin{figure*}
@@
 			\centering
-			\includegraphics[width=\linewidth]{img/results/open-1-p}
-			\caption{Open, 1 team}
-			\label{fig:open1p}
+			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
+			\caption{25, 1 team}
+			\label{fig:25-1}
 		\end{subfigure}
@@
 			\centering
-			\includegraphics[width=\linewidth]{img/results/open-3-p}
-			\caption{Open, 3 teams}
-			\label{fig:open3p}
+			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
+			\caption{25, 3 teams}
+			\label{fig:25-3}
 		\end{subfigure}
@@
 			\centering
-			\includegraphics[width=\linewidth]{img/results/obstacle-1-p}
-			\caption{Obstacle, 1 team}
-			\label{fig:obstacle1p}
+			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
+			\caption{75, 1 team}
+			\label{fig:75-1}
 		\end{subfigure}
@@
 			\centering
-			\includegraphics[width=\linewidth]{img/results/obstacle-3-p}
-			\caption{Obstacle, 3 teams}
-			\label{fig:obstacle3p}
+			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
+			\caption{75, 3 teams}
+			\label{fig:75-3}
 		\end{subfigure}
-		\begin{subfigure}{0.49\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{img/results/maze-1-p}
-			\caption{Maze, 1 team}
-			\label{fig:maze1p}
-		\end{subfigure}
-		\begin{subfigure}{0.49\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{img/results/maze-3-p}
-			\caption{Maze, 3 teams}
-			\label{fig:maze3p}
-		\end{subfigure}
-		\caption{Fraction solved out of 50 maps of algorithm variants on various types of 20x20 grids with a 30s timeout}
-		\label{fig:probs}
+		\caption{Average solving time of algorithm variants on two types of 20x20 grids with a 120s timeout}
+		\label{fig:times}
 	\end{figure*}

### 2021-06-14 docs/paper.tex
Worked on paper, removed duplicate legends from plots

@@
 In this work, two classes of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem.
-Algorithms within the families are compared to each other experimentally.
-An algorithm from the first family, one based on exhaustive matching enumeration, is compared to alternative algorithms.
+These are compared to each other experimentally on a set of grid maps.
+An algorithm from the first family, one based on exhaustive matching enumeration, is compared to alternative algorithms based on other MAPF algorithms.
 	\end{abstract}
@@
 
-	\begin{wrapfigure}{R}{.25\textwidth}
+	\begin{wrapfigure}[19]{R}{.25\textwidth}
 		\begin{minipage}{\linewidth}
@@
 		\end{minipage}
+		\vspace{-10pt}
 		\caption{The two types of conflict (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
@@
 Let $G = (V,E)$ be an undirected connected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles.
-Let there be $k$ agents $a_1,\ldots,a_k$ with respective starting locations $s_1,\ldots,s_k$ and goals $g_1,\ldots,g_k$.
+Let there be $k$ agents $a_1,\ldots,a_k$ with starting locations $s_1,\ldots,s_k$ and goals $g_1,\ldots,g_k$.
 For each agent $a_i$, a path $\pi_i$ from $s_i$ to $g_i$ is to be found such that all agents paths $\pi_i$ taken together are non-conflicting and therefore are a solution.
@@
 	In this work, following the definition of the TUSS relaxation in \cite{mulderij2020}, an optimal solution is defined as having minimal SIC. Note that $\sum_i c_i \geq \sum_i c^*_i$.
-
+	\begin{wrapfigure}[10]{R}{.35\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/symmetries}
+		\caption{Symmetric paths on a 4-connected grid\cite{harabor2010}}
+		\label{fig:symmetries}
+		\vspace{-10pt}
+	\end{wrapfigure}
 	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
@@
 	\label{icts}
-	\begin{figure}[t]
-		\centering
-		\includegraphics[width=0.4\linewidth]{img/symmetries}
-		\caption{Symmetric paths on a 4-connected grid\cite{harabor2010}}
-		\label{fig:symmetries}
-	\end{figure}
 	In Increasing Cost Tree Search\cite{sharon2011}, the above two-step mapping from path combination to SIC is reversed to search for a solution with minimal SIC.
@@
 For $a_i$ with a target cost $c_i$ (from cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents.
-Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations.
+Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations \cite{sharon2011}.
 
@@
 As noted before, this procedure could be used for planning groups in Algorithm \ref{id-algo}.
+In this work, triple-pruning was used and enhanced triple-pruning was taken as a base-line, as the conclusion in \cite{sharon2011} is that this generally outperforms other variants.
 	\begin{algorithm}
@@
 	Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$.
-Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution \cite{ma2016}, similarly defined as for MAPF.
+Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution, similarly defined as for MAPF.
 
-	If all teams are singleton, the MAPFM instance is equivalent to a MAPF instance; if there is just one team, this corresponds to an anonymous MAPF problem that can be solved in polynomial time.
-
+	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem which can be solved in polynomial time.
 	%
@@
 In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
-For each method, some properties and method-specific optimizations and variations will be discussed.
-Afterwards, some more general optimizations and variants will be discussed.
+In this section, the MAPFM algorithms are introduced properties of the algorithms and some variants are discussed.
+In Section \ref{experiments}, these will be compared experimentally.
 	\subsection{Exhaustive ICTS}
@@
 Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the instance, with $C_m = \infty$ for unfeasible $m$.
-Let $\Delta_m$ be similarly defined and represent the difference between $C_m$ and the root cost of $m$.
 In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
@@
 	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,bounded}})$.
+	If $B_m < C^*_m$, there is no need to consider $m$ and $\Delta_{m,bounded} = 0$.
+	Using this, the number of ICT nodes searched in total becomes $\mathcal{O}(\sum_m k^{\Delta_{m,bounded}})$.
 	\subsubsection{Ordered enumeration}
-	As a further improvement of this method, the matchings $m$ could be enumerated and solved in increasing order of $C^*_m$.
+	\label{ordered-enum}
+	In an effort to reduce the total effort as much as possible, the matchings $m$ could be enumerated and solved in increasing order of $C^*_m$.
 In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}.
-As will be shown in section \ref{experiments}, this monotonic reduction of effort appears to be a desirable property in practice but pathelogical cases could be constructed where the $\Delta_{m,bounded}$ of $m$ with low $C^*_m$ is much higher, thus dominating the performance.
+This induces a case in which this enumeration minimizes the number of nodes searched in total, $\Delta_m$ (Property \ref{cond-monoton-optim}).
+However, cases in which $\Delta_m$ of the first $m$'s searched is much higher could also be constructed, in which case this approach might cause more nodes to be processed in total than alternative methods.
+
 	\begin{property}[Monotonicity]
@@
 	\end{proof}
+	\begin{property}[Conditional optimality]
+	\label{cond-monoton-optim}
+	Assuming that $\Delta_m$, the unbounded effort, is monotonically non-decreasing as a function of $m$ (with $m$ in increasing order of $C^*_m$), ordered enumeration minimizes the total number of nodes searched across matchings.
+	\end{property}
 	\subsubsection{Approximate ordered enumeration}
@@
 Few changes to ICTS were necessary to accommodate for matching in this increasing cost tree scheme.
-Specifically, the ICT root generation and the MDD generation had to be changed.
-As described in \ref{icts}, in ICTS the root cost for each agent $a_i$ is given by $c^*_i$, the cost of the shortest path from $s_i$ to $g_i$, i.e.
-without taking conflicts into account.
-$MDD_i^{c_i}$ is generated using a breadth-first search from $s_i$ to $g_i$ followed by some additional processing.
+Specifically, the ICT root generation and the MDD generation as described in \ref{icts} had to be changed.
 	\subsubsection{Root generation for matching}
@@
 Therefore, to guarantee optimality, this minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root.
-The resulting root is equivalent to that generated in regular ICTS in the case that all teams are singleton, which is equivalent to a MAPF instance.
-Intuitively, the sum of individual costs of this root is highly optimistic, in particular, if the teams are large.
-This is because often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts.
+Intuitively, the sum of individual costs of this root is highly optimistic, particularly if the teams are large.
+This is because often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts (see \ref{pathology}).
 
 	\subsubsection{MDD generation for matching}
-	In MDD generation, each agent also has to consider not one goal but all matching goals.
+	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals.
 By following a BFS-based approach, with all team goals being goals in the search and in turn endpoints from which, using the time-expanded graph, the MDD was generated that is used in the low-level search, agent MDDs can be made to represent all possible paths of a set length to any matching goal.
-Once again, if all teams are singleton, the MDDs generated using this goal-set approach are the same as in regular ICTS.
 	\begin{wrapfigure}{R}{.35\textwidth}
@@
 		\includegraphics[width=\linewidth]{img/path}
-		\caption{Pathelogical case for ICTS-m [Placeholder graphic]}
+		\caption{Pathelogical case for ICTS-m}
 		\label{fig:path}
@@
 As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
+[TODO: reduce case to just 2 agents?]
+	\subsubsection{Inverted MDD search}
+	When searching MDDs for a solution in regular MAPF, it is guaranteed that there exists a goal node in the joint MDD without vertex conflicts.
+This follows from the fact that goals are assumed to be unique per agent.
+In MAPFM, for a large number of nodes that are searched, this is not the case.
+As a result, analogously to how pathfinding algorithms will more-or-less floodfill a graph if there exists no path to the goal, the entire joint MDD space will have to be searched which becomes very expensive as the number of agents increases.
+
+	Two strategies could be used to avoid this: firstly, the MDD search could be changed to start at the maximal depth and search for a way towards the start (which is still guaranteed to be a nonconflicting node); secondly, a bipartite matching algorithm could be employed to see if any matching exists between agents and goals they can reach.
+An advantage of the former strategy is that it will, in particular with larger team sizes, reduce the number of maximal depth nodes drastically, so that the subsequent search is from few nodes to one goal.
+By only running a matching algorithm to skip regular MDD search, there is no such reduction so from one starting position paths will be searched to potentially many goal nodes, of which many will end up being illegal.
+
+	[TODO: either describe inverted MDD search or the use of some bipartite matching algorithm that shortcuts the regular MDD search]
 	\subsection{General optimizations}
+
 	To improve both types of algorithms, some general optimizations were found that can be used to speed up the search that are here motivated. 
@@
 	\end{proof}
-	\begin{corollary}[Reduced upper bound]
+	\begin{property}[Reduced upper bound]
 		In bounded exhaustive search, the sum of costs of groups not being merged can be subtracted from bound $B$ without losing optimality.
-	\end{corollary}
+	\end{property}
 	\subsubsection{Child pruning}
@@
 		\caption{25, 1 team}
-		\label{fig:open1p}
+		\label{fig:25-1-p}
 	\end{subfigure}
@@
 		\caption{25, 3 teams}
-		\label{fig:open3p}
+		\label{fig:25-3-p}
 	\end{subfigure}
@@
 		\caption{75, 1 team}
-		\label{fig:obstacle1p}
+		\label{fig:75-1-p}
 	\end{subfigure}
@@
 		\caption{75, 3 teams}
-		\label{fig:obstacle3p}
+		\label{fig:75-3-p}
 	\end{subfigure}
@@
 	\label{experiments}
+	To compare the algorithms and variants described above and put them into the context of alternative MAPFM algorithms, two types of experiments are here reported.
+In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant (Exh+E+B+O) is compared to other algorithms for MAPFM developed within the peer group\footnote{I want to thank Jonathan Dönszelmann, who worked on M*-based algorithms, for setting up this comparison[TODO: move to thanks note at end]}.
+The values compared are the fraction of instances solved, and the average runtime per sentence.
+It should be noticed that the in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are reported for completeness, only the fraction of instances solved is considered in analysis.
+	\subsection{Experimental setup}
 	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks exist\footnote{That is, to the knowledge of the author.}.
-For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances.
-It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
+For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
 This observation informed the creation of a map generator within the peer group with various parameters.
@@
 	\end{enumerate}
-	For each of these types, two sets of maps were generated with between $1$ to $16$ agents and 200 instances generated for each such agent-setting: one set where all agents belong to one team, another in which the agents were divided into three teams (or $1,2$ teams respectively for the datapoints with $1,2$ agents).
+	For each of these types, two sets of maps were generated with between $1$ to $16$ agents and 200 instances generated for each such agent-setting: one set where all agents belong to one team, another in which the agents were divided into three teams (or $1,2$ teams strictly speaking for the datapoints with respectively $1,2$ agents).
 
-	Two different experiments were run: one comparing ICTS-based algorithms discussed in this work, and one comparing one of these, the approximate ordered enumeration variant (Exh+E+B+O in the relative comparisons), to other algorithms for MAPFM developed within the peer group\footnote{I want to thank Jonathan Dönszelmann, who worked on M*-based algorithms, for setting up this comparison[TODO: move to thanks note at end]}.
+	The first experiments were performed on a laptop an Intel i7-8750H hexacore operating at 2.2GHz with 16GiB of memory. Here, for each setting, a fixed subset of 50 out of 200 maps were used.
 
-	In experiments used to compare the different MAPFM algorithms within the peer group, care was taken to make the comparison fair: all algorithms are implemented in Python 3 and run on the same system: a server with a 12-core Intel Xeon E5-2683 with 8Gb of RAM dedicated to running experiments for this project.
+	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a Intel Xeon E5-2683 dodecacore operating at 2.0Ghz with 8GiB of RAM.
+All 200 maps were used for each setting.
+Although these algorithms have different authors, all are implemented in Python 3 (with one using an ILP solver implemented in C++ as a subroutine) to avoid performance differences as often seen between interpreted versus compiled languages.
 
-	The results are shown in Figure \ref{fig:times} and \ref{fig:probs}, which respectively show the average time to solution and the fraction of problems solved out of 50 instances.
-The algorithms and interpretation of results are discussed below.
-	\subsection{Algorithms}
-	Various improvements and variations of algorithms were tried out, as shown in the legend. The meanings of the various modifiers are as follows.
+	\subsection{Experiment 1: ICTS-based MAPFM algorithms}
+	Figure \ref{fig:probs} reports the fraction of instances that each algorithm variant solved within the timeout of 120s in different settings.
+The meaning of the abbreviations used in the legend are as follows:
 	\begin{enumerate}
@@
 	\end{enumerate}
+	\subsubsection{Analysis}
+	Across exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, as best illustrated by \ref{fig:25-3-p}.
+Almost without exception, Exh+E is outperformed by Exh+E+B which similarly is outperformed by Exh+E+B+O which is again outperformed by Exh+S+C+B+O.
+Exh+E being outperformed by Exh+E+B was to be expected, given that Exh+E+B does at most as much work as Exh+E while in practice often being able to search ICT's much less deep as more instances are solved.
+Exh+E+B+O outperforming Exh+E+B is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}.
+Although no bound-value data was recorded, one hypothetical explanation might be that often, early on in the search, single matchings with low $\Delta_m$ are found, causing the rest of the searches to be significantly curtailed.
+
+	Exh+S+C+B+O outperforming Exh+E+B+O shows the potential of the child pruning method described relative to the enhanced pruning method.
+In particular as $k$ grows larger and in scenarios with more obstacle (\ref{fig:75-1-p},\ref{fig:75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
+
+	Simple pruning with child pruning outperforming the enhanced pruning variant.
+
+	With some exceptions, the ICTS-m 
+	In almost every instance the ICTS-m variants are outperformed by exhaustive variants. 
+	\subsection{Experiment 2: Algorithms for MAPFM}
 	\subsection{Results}
@@
 More analysis is necessary however before any conclusions can be drawn.
+	\section{Discussion}
 
-	\section{Responsible Research}
 	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
 
-	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository \footnote{\url{https://github.com/tbvanderwoude/icts-m}}.
-Included is also code used to benchmark different configurations of the ICTS solver.
-
-	\section{Discussion}
 	Compared to the results achieved by \cite{ma2016}, the results recorded are somewhat disappointing.
@@
 Some early experiments with pruning techniques were in this vein but experimentally there was no observable improvement.
+	\section{Responsible Research}
+	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository \footnote{\url{https://github.com/tbvanderwoude/icts-m}}.
+Included is also code for benchmarking different configurations of the ICTS solver and the maps that were used in the benchmarks reported above.
+
 	\printbibliography

### 2021-06-14 src/ictsm/conflicts.py

@@ -71,7 +71,6 @@ def edge_collisions_constructive(curr_locs, next_locs) -> Optional[Conflict]:
                 return i, j
     return None
 
-
 def find_conflict(curr_locs, next_locs) -> Optional[Conflict]:
     all_diff = all_different_constructive(curr_locs)
     if all_diff:

### 2021-06-14 src/ictsm/solve.py

@@ -15,13 +15,13 @@ def solve_api_enum(problem: Problem) -> Solution:
 
 def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int,Optional[int]]:
     config = SolverConfig(
-        combs=2,
+        combs=3,
         prune=True,
-        enhanced=True,
+        enhanced=False,
         pruned_child_gen=True,
         id=True,
         conflict_avoidance=True,
-        enumerative=True,
+        enumerative=False,
         debug=True,
     )
     return Solver(config, problem)()
@@ -30,8 +30,8 @@ def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], 
     config = SolverConfig(
         combs=3,
         prune=True,
-        enhanced=True,
-        pruned_child_gen=False,
+        enhanced=False,
+        pruned_child_gen=True,
         id=True,
         conflict_avoidance=True,
         enumerative=True,

### 2021-06-14 docs/paper.tex
Compacted figures to fit two sets of 4 on 1 page

@@
 	\end{proof}
-
 	\begin{figure*}
@@
 	\end{figure*}
-	\begin{figure*}
+	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
+	\begin{figure*}[t]
 	\centering
-	\begin{subfigure}{0.49\textwidth}
+	\begin{subfigure}{0.44\textwidth}
 		\centering
@@
 	\end{subfigure}
-	\begin{subfigure}{0.49\textwidth}
+	\begin{subfigure}{0.44\textwidth}
 		\centering
@@
 	\end{subfigure}
-	\caption{Fraction solved out of 50 maps of algorithm variants on two types of 20x20 grids with a 120s timeout}
+	\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
 	\label{fig:probs}
 	\end{figure*}
-	\begin{figure*}
+	\begin{figure*}[b]
 	\centering
-		\begin{subfigure}{0.49\textwidth}
+	\begin{subfigure}{0.44\textwidth}
 		\centering
@@
 	\end{subfigure}
-		\begin{subfigure}{0.49\textwidth}
+	\begin{subfigure}{0.44\textwidth}
 		\centering
@@
 	\end{subfigure}
-		\caption{Average solving time of algorithm variants on two types of 20x20 grids with a 120s timeout}
+	\caption{Average solving time on two types of 20x20 grids with a 120s timeout}
 	\label{fig:times}
 \end{figure*}
+\restoregeometry
 
@@
 	\label{experiments}
-	To compare the algorithms and variants described above and put them into the context of alternative MAPFM algorithms, two types of experiments are here reported.
+	To compare the algorithms and variants described above and put them into the context of alternative MAPFM algorithms, two types of experiments were performed.
 In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant (Exh+E+B+O) is compared to other algorithms for MAPFM developed within the peer group\footnote{I want to thank Jonathan Dönszelmann, who worked on M*-based algorithms, for setting up this comparison[TODO: move to thanks note at end]}.
-The values compared are the fraction of instances solved, and the average runtime per sentence.
-It should be noticed that the in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are reported for completeness, only the fraction of instances solved is considered in analysis.
+The values compared are the fraction of instances solved, and the average runtime per instance.
+It should be noticed that in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are reported for completeness, only the fraction of instances solved is guiding in the analysis of results.
 	\subsection{Experimental setup}
-	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks exist\footnote{That is, to the knowledge of the author.}.
+	Because MAPFM lies on the fringe of pathfinding research, no standard benchmark exists\footnote{That is, to the knowledge of the author.}.
 For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
@@
 
-	The first experiments were performed on a laptop an Intel i7-8750H hexacore operating at 2.2GHz with 16GiB of memory. Here, for each setting, a fixed subset of 50 out of 200 maps were used.
+	The first experiments were performed on an Intel i7-8750H hexacore operating at 2.2GHz with 16GiB of memory. Here, for each setting, a fixed subset of 50 out of 200 maps were used.
 
@@
 Although these algorithms have different authors, all are implemented in Python 3 (with one using an ILP solver implemented in C++ as a subroutine) to avoid performance differences as often seen between interpreted versus compiled languages.
+Nonetheless, conclusions are here a bit more limited, as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.
 
@@
 The meaning of the abbreviations used in the legend are as follows:
-	\begin{enumerate}
+	\begin{itemize}
+		\begin{minipage}{0.45\linewidth}
 			\item S: Simple pruning
@@
 			\item C: Child pruning
+		\end{minipage}
+		\begin{minipage}{0.45\linewidth}
 			\item ID: Independence detection
@@
 			\item O: Approximate ordered enumeration
-	\end{enumerate}
+		\end{minipage}
+	\end{itemize}
 	\subsubsection{Analysis}
@@
 Almost without exception, Exh+E is outperformed by Exh+E+B which similarly is outperformed by Exh+E+B+O which is again outperformed by Exh+S+C+B+O.
-Exh+E being outperformed by Exh+E+B was to be expected, given that Exh+E+B does at most as much work as Exh+E while in practice often being able to search ICT's much less deep as more instances are solved.
-Exh+E+B+O outperforming Exh+E+B is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}.
+Bounded search outperforming unbounded search was to be expected, given that the former does at most as much work as the latter and often less.
+Approximate ordering outperforming unordered enumeration is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}.
 Although no bound-value data was recorded, one hypothetical explanation might be that often, early on in the search, single matchings with low $\Delta_m$ are found, causing the rest of the searches to be significantly curtailed.
 
-	Exh+S+C+B+O outperforming Exh+E+B+O shows the potential of the child pruning method described relative to the enhanced pruning method.
+	Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this novel method.
 In particular as $k$ grows larger and in scenarios with more obstacle (\ref{fig:75-1-p},\ref{fig:75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.

### 2021-06-15 docs/paper.tex
Worked on analysis of results

@@
-\documentclass[english]{article}
+\documentclass[english,10pt]{article}
 \usepackage{geometry}
@@
 	\author{Thom van der Woude\and Jesse Mulderij\and Mathijs de Weerdt}
-	\date{}
+	\date{\today}
 
@@
 		\centering
-		\includegraphics[width=0.7\linewidth]{img/ict}
+		\includegraphics[width=0.5\linewidth]{img/ict}
 		\caption{Increasing Cost Tree for three agents \cite{sharon2011}}
 		\label{fig:ict}
+		\vspace{-30pt}
 	\end{figure}
@@
 	\subsection{Exhaustive ICTS}
+	\label{exhaustive}
 	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals.
@@
 		\includegraphics[width=\linewidth]{img/path}
-		\caption{Pathelogical case for ICTS-m}
+		\caption{Pathological case for ICTS-m}
 		\label{fig:path}
@@
 Let them be arranged in a configuration as depicted in Figure \ref{fig:path}.
-As indicated by the color, all four agents match the colour of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$.
+All four agents match the colour of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$.
 The optimal solution however is, numbering the agents clockwise, $(1,3,3,3)$ with SIC $10$, meaning that $\Delta = 6$.
@@
 [TODO: reduce case to just 2 agents?]
-	\subsubsection{Inverted MDD search}
-	When searching MDDs for a solution in regular MAPF, it is guaranteed that there exists a goal node in the joint MDD without vertex conflicts.
-This follows from the fact that goals are assumed to be unique per agent.
-In MAPFM, for a large number of nodes that are searched, this is not the case.
-As a result, analogously to how pathfinding algorithms will more-or-less floodfill a graph if there exists no path to the goal, the entire joint MDD space will have to be searched which becomes very expensive as the number of agents increases.
+	%\subsubsection{Inverted MDD search}
+	%The uniqueness of goals guarantees the existence of a goal node without vertex conflicts in searching MDDs in MAPF.
+In MAPFM, this is not the case and causes joint MDDs to be searched fully without finding a result.
+In addition, even if there exists a goal node, many of the paths represented by the joint MDD lead to conflicting maximal-depth nodes.
 
-	Two strategies could be used to avoid this: firstly, the MDD search could be changed to start at the maximal depth and search for a way towards the start (which is still guaranteed to be a nonconflicting node); secondly, a bipartite matching algorithm could be employed to see if any matching exists between agents and goals they can reach.
+	%To avoid this, the MDD search could be changed to start at the maximal depth and search for a way towards the start node, which by start uniqueness remains without vertex conflicts.
+	%Two strategies could be used to avoid this: firstly, the MDD search could be changed to start at the maximal depth and search for a way towards the start (which by start uniqueness is always non-conflicting); secondly, a bipartite matching algorithm could be employed to see if any matching exists between agents and goals they can reach.
 An advantage of the former strategy is that it will, in particular with larger team sizes, reduce the number of maximal depth nodes drastically, so that the subsequent search is from few nodes to one goal.
-By only running a matching algorithm to skip regular MDD search, there is no such reduction so from one starting position paths will be searched to potentially many goal nodes, of which many will end up being illegal.
-
-	[TODO: either describe inverted MDD search or the use of some bipartite matching algorithm that shortcuts the regular MDD search]
+By only running a matching algorithm to skip regular MDD search, there is no such reduction so from one starting position paths will be searched to potentially an exponential number of goal nodes, of which many will end up being illegal.
+	%[TODO: just focus on explaining why inverted MDD search was/could be used to solve this? Or just toss this out for lack of time/space. Why didn't I come up with this idea earlier...]
 	\subsection{General optimizations}
@@
 However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented.
-This prunes the children generated that do not correspond to the conflicting agents, of which there are often just 2 or 3, which quite drastically can improve the (average) branching factor.
+This can be explioted by pruning the node's children that do not correspond to the conflicting agents, of which there are often just 2 or 3, which can drastically improve the (average) branching factor as $k$ increases.
 	\begin{property}[Incompatibility with enhanced pruning]
@@
 	\end{property}
-	\begin{proof}
-		Consider Figure \ref{fig:counter-example:a} with a red agent $r$, green agent $g$ and black agent $b$.
-It can be seen that $(3,8,5)$ with SIC $16$ is an optimal solution for this instance, which corresponds to $r$ moving aside, allowing $g$ to pass.
-Say enhanced pruning with pairs is applied to these three agents at $(c^*_r,c^*_g,c^*_b) = (0,8,5)$.
-Let the enhanced pruning order be $(r,g)$, $(r,b)$, $(g,b)$ without loss of generality.
-$(r,g)$ is solvable but will leave for $g$ out of the two paths of length $8$ only the clock-wise path.
-$(r,b)$ will not change either MDD in this node.
-When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (swapping conflict) so $(0,9,5)$ and $(0,8,6)$ are generated.
-By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed.
-Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that E+C pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making it suboptimal.
-	\end{proof}
-	\begin{figure*}
+	\begin{figure}[H]
 	\centering
@@
 	\label{fig:counter-example}
-	\end{figure*}
+\end{figure}
+	\begin{proof}
+		Consider Figure \ref{fig:counter-example:a} with a red agent $r$, green agent $g$ and black agent $b$.
+It can be seen that $(3,8,5)$ with SIC $16$ is an optimal solution for this instance, which corresponds to $r$ moving aside, allowing $g$ to pass.
+Say enhanced pruning with pairs is applied to these three agents at $(c^*_r,c^*_g,c^*_b) = (0,8,5)$.
+Let the enhanced pruning order be $(r,g)$, $(r,b)$, $(g,b)$ without loss of generality.
+$(r,g)$ is solvable but will leave for $g$ out of the two paths of length $8$ only the clock-wise path.
+$(r,b)$ will not change either MDD in this node.
+When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (swapping conflict) so $(0,9,5)$ and $(0,8,6)$ are generated.
+By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed.
+Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that E+C pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making it suboptimal.
+	\end{proof}
 	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
@@
 The values compared are the fraction of instances solved, and the average runtime per instance.
-It should be noticed that in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are reported for completeness, only the fraction of instances solved is guiding in the analysis of results.
+It should be noticed that in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work, the fraction of instances solved is guiding in the analysis of results.
 	\subsection{Experimental setup}
-	Because MAPFM lies on the fringe of pathfinding research, no standard benchmark exists\footnote{That is, to the knowledge of the author.}.
+	Because MAPFM lies on the fringe of pathfinding research, no standard benchmark exists.
 For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
@@
 	\subsubsection{Analysis}
-	Across exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, as best illustrated by \ref{fig:25-3-p}.
-Almost without exception, Exh+E is outperformed by Exh+E+B which similarly is outperformed by Exh+E+B+O which is again outperformed by Exh+S+C+B+O.
-Bounded search outperforming unbounded search was to be expected, given that the former does at most as much work as the latter and often less.
+	Across exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by \ref{fig:25-3-p}.
+Almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E.
+Bounded search outperforms unbounded search as expected, given that the former does at most as much work as the latter and often less.
 Approximate ordering outperforming unordered enumeration is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}.
-Although no bound-value data was recorded, one hypothetical explanation might be that often, early on in the search, single matchings with low $\Delta_m$ are found, causing the rest of the searches to be significantly curtailed.
+Although no bound-value data was recorded, one explanation might be that often, early on in the search, single matchings with low $\Delta_m$ are found, causing the rest of the searches to be significantly curtailed.
 
 	Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this novel method.
-In particular as $k$ grows larger and in scenarios with more obstacle (\ref{fig:75-1-p},\ref{fig:75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
+In particular as $k$ grows larger and in scenarios with more obstacles (\ref{fig:75-1-p},\ref{fig:75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
 
-	Simple pruning with child pruning outperforming the enhanced pruning variant.
+	Ordered enumeration with ID performs much better in \ref{fig:75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:25-1-p}).
+The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:25-1-p},\ref{fig:75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
+This explains why no speedup is seen, as ICTS-m between and ICTS-m+ID, which is is more typical.
 
-	With some exceptions, the ICTS-m 
+	With some exceptions, ICTS-m variants are outperformed by the exhaustive variants.
 	In almost every instance the ICTS-m variants are outperformed by exhaustive variants. 
 	\subsection{Experiment 2: Algorithms for MAPFM}
-	\subsection{Results}
-	A first observation is that exhaustive methods, while dominant throughout all settings, fare much better when agents are divided into three teams as opposed to when there is just one team.
-This can be explained by exhaustive algorithms having to process $M = k!$ matchings, which grows quite large for say $k = 10$.
-Another is that simple pruning combined with child pruning appears to outperform enhanced in many cases, as in Subfigure \ref{fig:maze1p}.
-More analysis is necessary however before any conclusions can be drawn.
+	[TODO: add relative comparison]
+
 	\section{Discussion}
 
-	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
+%	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
 
@@
 	The goal of this research was to seek alternative approaches to solving MAPFM based on ICTS.
-In this, the research has succeeded, but the performance and in particular the scalability of the algorithms leaves something to be desired.
+In this, the research has succeeded, but the scalability of the algorithms leaves something to be desired.
+Exhaustive methods, like those discussed in detail in \ref{exhaustive}, will never scale well as teams grow larger, no matter what optimizations are put in place.
+Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive algorithms consistenly outperform the ICTS-m based algorithms.
+In this
 	\section{Future work}
-	TODO: discuss following unexplored ideas (mention that some are more engineering-related)
+	In this project there were many roads not taken, from algorithmic improvements to closer analysis and more elaborate experimentation.
+In particular for the ICTS-m variant, there are still many things that could be experimented with in order to improve performance, such as more extensive or multi-staged pruning procedures and exploiting the fact that agents are partitioned into teams.
+Although it might be somewhat early
 	\begin{enumerate}
@@
 	\end{enumerate}
+
+	TODO: discuss following unexplored ideas (mention that some are more engineering-related)
 	As discussed in \ref{pathology}, the root of the ICT searched in ICTS-m is highly optimistic and often 

### 2021-06-15 docs/paper.tex
Bundled problems and algorithms together in seperate sections

@@
 		Both the assignment problem and the multi-agent pathfinding problem are common problems in the fields of robotics and transportation.
-The joint problem of multi-agent pathfinding extended with matching between agents and goals is something that has not been studied much.
-Few methods exist today that solve it although the problems do appear together in practice, such as in the Train Unit Shunting and Servicing problem.
-In this work, two classes of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem.
-These are compared to each other experimentally on a set of grid maps.
-An algorithm from the first family, one based on exhaustive matching enumeration, is compared to alternative algorithms based on other MAPF algorithms.
+The joint problem of multi-agent pathfinding extended with matching between agents and goals is something that has not been studied much; few methods exist today that solve it.
+In this work, two types of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem: exhaustive algorithms that reduce the problem to solving many MAPF problems using regular ICTS, and algorithms that search a generalized increasing cost tree.
+These are compared to each other experimentally on a set of grid maps, and it is shown that exhaustive methods typically outperform the generalized ICT search.
+An algorithm of the first type is compared to alternative algorithms based on other MAPF algorithms to put its performance into the context.
 	\end{abstract}
@@
 	\section{Introduction}
-	The Dutch Railways (NS) company\footnote{\url{https://www.ns.nl/}} needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day.
+	The Dutch Railways company (NS) needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day. 
 	The problem of scheduling the trains and personnel to achieve this is called the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}. 
@@
 	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
-It should be noted that this method minimizes the makespan and not the sum of individual costs (SIC) which is the objective used in the TUSS relaxation, meaning that non-trivial modifications to CBM are needed to minimize SIC.
+It should be noted that this method minimizes the makespan and not the sum of individual costs (SIC) which is the objective used in this work, meaning that non-trivial modifications to CBM are needed to minimize SIC.
 	The successful application of CBS to solving MAPFM begs the question: \textit{can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM algorithm?}
@@
 			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
-			\subcaption{Swapping conflict}
+			\subcaption{Edge conflict}
 			\label{fig:conflictsb}
@@
 	\section{Multi-agent pathfinding with matching} % Problem description
+	\label{mapfm}
 	The MAPFM problem is an extension of MAPF, a well-studied problem.
@@
 For each agent $a_i$, a path $\pi_i$ from $s_i$ to $g_i$ is to be found such that all agents paths $\pi_i$ taken together are non-conflicting and therefore are a solution.
-In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts (and thus no edge conflicts) and no swapping conflicts, as shown in Figure \ref{fig:conflicts}.
+In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts (and thus no edge conflicts) and no edge conflicts, as shown in Figure \ref{fig:conflicts}.
 Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$.
@@
 	\begin{wrapfigure}[10]{R}{.35\textwidth}
+		\vspace{-10pt}
 		\centering
@@
 		\label{fig:symmetries}
-		\vspace{-10pt}
 	\end{wrapfigure}
@@
 In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
+
+	\subsection{Extending MAPF with matching}
+	With the multi-agent pathfinding problem defined, the matching extension of MAPF (MAPFM) that is the subject of this paper can be described.
+The ICTS algorithm for MAPF and possible matching extensions of ICTS will be discussed in Section \ref{section:icts-matching}.
+
+	Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$.
+Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution, similarly defined as for MAPF.
+
+	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem which can be solved in polynomial time.
+	\section{Solving MAPF with Matching using ICTS} % Your contribution
+	\label{section:icts-matching}
+	Taking ICTS for MAPF as starting point, two methods to use ICTS for MAPFM were identified.
+The first method relies on a reduction from MAPFM to repeated MAPF: an optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found.
+In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
+In this section, first ICTS for MAPF and some common variants will be described.
+Next, derived MAPFM algorithms are introduced and properties of these algorithms and some variants are discussed.
+In Section \ref{experiments}, these will be compared experimentally.
 	\subsection{Increasing Cost Tree Search}
 	\label{icts}
-	In Increasing Cost Tree Search\cite{sharon2011}, the above two-step mapping from path combination to SIC is reversed to search for a solution with minimal SIC.
+	In Increasing Cost Tree Search\cite{sharon2011}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC.
 This is done by searching for cost vectors corresponding to increasing SIC on the top level and searching for non-conflicting path combinations (solutions) for each cost vector on the bottom level.
@@
 In \ref{fig:mdds}, a vertex conflict occurs and therefore this joint child can be removed from the MDD.
-If a $(B,A)$ node would be generated by the same root, $(A,B)$, this would similarly be a swapping conflict and hence $(B,A)$ would also be removed from the joint MDD $MDD_{1,2}^{c_1,c_2}$.
+If a $(B,A)$ node would be generated by the same root, $(A,B)$, this would similarly be an edge conflict and hence $(B,A)$ would also be removed from the joint MDD $MDD_{1,2}^{c_1,c_2}$.
 In the next layer, the process repeats with multiple parent nodes.
@@
 	\subsubsection{ICTS with Independence Detection}
-	Like many other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}.
+	Like other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}.
 ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups.
@@
 	\end{algorithm}
-	\subsection{Extending MAPF with matching}
-	With the multi-agent pathfinding problem as well as the ICTS method of solving it defined, the matching extension of MAPF (MAPFM) that is the subject of this paper can be described.
-Possible extensions of ICTS to match these changes will be discussed in Section \ref{section:icts-matching}.
-
-	Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$.
-Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution, similarly defined as for MAPF.
-
-	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem which can be solved in polynomial time.
-	%
-	\section{Solving MAPF with Matching using ICTS} % Your contribution
-	\label{section:icts-matching}
-	Taking ICTS for MAPF as starting point, two methods to use ICTS for MAPFM were identified.
-The first method relies on the well-known reduction from MAPFM to repeated MAPF: an optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found.
-In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
-In this section, the MAPFM algorithms are introduced properties of the algorithms and some variants are discussed.
-In Section \ref{experiments}, these will be compared experimentally.
 	\subsection{Exhaustive ICTS}
@@
 	\subsubsection{Approximate ordered enumeration}
-	In practice, it is quite difficult enumerate all matchings in increasing order of root SIC.
+	In practice, it is difficult enumerate all matchings in increasing order of root SIC.
 Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time; however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking).
@@
 $(r,b)$ will not change either MDD in this node.
-When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (swapping conflict) so $(0,9,5)$ and $(0,8,6)$ are generated.
+When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (edge conflict) so $(0,9,5)$ and $(0,8,6)$ are generated.
 By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed.
@@
 	As discussed in \ref{pathology}, the root of the ICT searched in ICTS-m is highly optimistic and often 
-	The ICTS-m algorithm described in this work scales quite poorly for several reasons including the highly optimistic root SIC value.
+	The ICTS-m algorithm described in this work scales poorly for several reasons including the highly optimistic root SIC value.
 It might be possible to conceive of a different ICTS-m algorithm that is better able to take advantage of the agents being divided into teams, for instance by first solving all intra-team conflicts before proceeding to consider inter-team conflicts.

### 2021-06-15 docs/paper.tex
Processed relative comparison data, added plots to paper

@@
 		\centering
+		\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
+		\caption{25, 1 team}
+		\label{fig:25-1-p}
+	\end{subfigure}
+	\begin{subfigure}{0.44\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
+		\caption{25, 3 teams}
+		\label{fig:25-3-p}
+	\end{subfigure}
+	\begin{subfigure}{0.44\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
+		\caption{75, 1 team}
+		\label{fig:75-1-p}
+	\end{subfigure}
+	\begin{subfigure}{0.44\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
+		\caption{75, 3 teams}
+		\label{fig:75-3-p}
+	\end{subfigure}
+	\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
+	\label{fig:probs}
+	\end{figure*}
+	\begin{figure*}[t]
+	\centering
+	\begin{subfigure}{0.44\textwidth}
+		\centering
 		\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
@@
 	\end{figure*}
-	\begin{figure*}[b]
-	\centering
-	\begin{subfigure}{0.44\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
-		\caption{25, 1 team}
-		\label{fig:25-1}
-	\end{subfigure}
-	\begin{subfigure}{0.44\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
-		\caption{25, 3 teams}
-		\label{fig:25-3}
-	\end{subfigure}
-	\begin{subfigure}{0.44\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
-		\caption{75, 1 team}
-		\label{fig:75-1}
-	\end{subfigure}
-	\begin{subfigure}{0.44\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
-		\caption{75, 3 teams}
-		\label{fig:75-3}
-	\end{subfigure}
-	\caption{Average solving time on two types of 20x20 grids with a 120s timeout}
-	\label{fig:times}
-\end{figure*}
+
 \restoregeometry
@@
 In this, the research has succeeded, but the scalability of the algorithms leaves something to be desired.
-Exhaustive methods, like those discussed in detail in \ref{exhaustive}, will never scale well as teams grow larger, no matter what optimizations are put in place.
-Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive algorithms consistenly outperform the ICTS-m based algorithms.
-In this
+Exhaustive methods, like those discussed in detail in \ref{exhaustive}, cannot be expected to scale well as teams grow larger due to their complexity, no matter what optimizations are put in place.
+Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive ICTS algorithms consistently outperform the ICTS-m based algorithms.
+It was also seen that in turn a SIC-adaptation of the CBM method \cite{ma2016} greatly outperforms exhaustive alternatives in the settings that were tried out.
+Therefore, it can be concluded that the method that arguably has the most potential to scale well, ICTS-m, has a very long way to go before being usable in practical scenarios with significant problem sizes.
 	\section{Future work}
-	In this project there were many roads not taken, from algorithmic improvements to closer analysis and more elaborate experimentation.
-In particular for the ICTS-m variant, there are still many things that could be experimented with in order to improve performance, such as more extensive or multi-staged pruning procedures and exploiting the fact that agents are partitioned into teams.
-Although it might be somewhat early
-	\begin{enumerate}
-		\item Team cost lower-bounds (low-level search pruning) using hungarian algorithm.
-		\item Hybridized approaches between exhaustive and native methods.
-		\item More aggressive pruning (in particular for ICTS-m): different (simple child) pruning stages 2,3,4 agents. Prioritizing pruning within teams.
-	\end{enumerate}
+	In this project, there were many roads not taken.
+In particular for the ICTS-m variant, there are still many things that could be experimented with in order to improve performance, such as more extensive or multi-staged pruning procedures or ways to exploit the fact that agents are partitioned into teams.
+For instance, the hungarian algorithm could be used to find lower-bounds for per-team SICs, which allows skipping the low-level search in many cases and can trivially be combined with pruned child generation branching within teams.
 
-	TODO: discuss following unexplored ideas (mention that some are more engineering-related)
-	As discussed in \ref{pathology}, the root of the ICT searched in ICTS-m is highly optimistic and often 
-	The ICTS-m algorithm described in this work scales poorly for several reasons including the highly optimistic root SIC value.
-It might be possible to conceive of a different ICTS-m algorithm that is better able to take advantage of the agents being divided into teams, for instance by first solving all intra-team conflicts before proceeding to consider inter-team conflicts.
-Some early experiments with pruning techniques were in this vein but experimentally there was no observable improvement.
+	Hybridized approaches, where approximate ordered search is combined with the search of partially restricted MAPFM problems, could be promising to explore in the future; this is not restricted to ICTS: any MAPF algorithm generalized to solve MAPFM could be used in this scheme.
+
+	Another subject for future research might be a closer theoretical and experimental analysis of simple child pruning as alternative to enhanced pruning in the context of ICTS for MAPF, assuming this method has not been described before.
+Although experimentally it was shown to outperform enhanced pruning in exhaustive matching, ideally the two pruning strategies should be tested using the Moving AI benchmark \cite{sturtevant2012} to reach definite conclusions about how they compare.
+Using simple pruning to prune children and enhanced pruning for pruning low-level search could also be interesting to explore, as it could potentially combine the benefits of searching a smaller ICT and performing fewer $k$-agent low-level searches at the cost of spending more time pruning.
 	\section{Responsible Research}
@@
 	\printbibliography
+	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
+	\begin{figure*}[b]
+		\centering
+		\begin{subfigure}{0.44\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
+			\caption{25, 1 team}
+			\label{fig:25-1}
+		\end{subfigure}
+		\begin{subfigure}{0.44\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
+			\caption{25, 3 teams}
+			\label{fig:25-3}
+		\end{subfigure}
+		\begin{subfigure}{0.44\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
+			\caption{75, 1 team}
+			\label{fig:75-1}
+		\end{subfigure}
+		\begin{subfigure}{0.44\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
+			\caption{75, 3 teams}
+			\label{fig:75-3}
+		\end{subfigure}
+		\caption{Average solving time on two types of 20x20 grids with a 120s timeout}
+		\label{fig:times}
+	\end{figure*}
+	\begin{figure*}[t]
+		\centering
+		\begin{subfigure}{0.44\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
+			\caption{25, 1 team}
+			\label{fig:25-1-p}
+		\end{subfigure}
+		\begin{subfigure}{0.44\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
+			\caption{25, 3 teams}
+			\label{fig:25-3-p}
+		\end{subfigure}
+		\begin{subfigure}{0.44\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
+			\caption{75, 1 team}
+			\label{fig:75-1-p}
+		\end{subfigure}
+		\begin{subfigure}{0.44\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
+			\caption{75, 3 teams}
+			\label{fig:75-3-p}
+		\end{subfigure}
+		\caption{Average solving time on two types of 20x20 grids with a 120s timeout}
+		\label{fig:probs}
+	\end{figure*}
 
+	\restoregeometry
 \end{document}

### 2021-06-16 docs/paper.tex
Worked on describing comparison, added references to peer group papers

@@
 	%[TODO: just focus on explaining why inverted MDD search was/could be used to solve this? Or just toss this out for lack of time/space. Why didn't I come up with this idea earlier...]
-	\subsection{General optimizations}
-
-	To improve both types of algorithms, some general optimizations were found that can be used to speed up the search that are here motivated. 
+	\subsection{Optimizations}
+	To improve both types of algorithms, some optimizations were found that can be used to speed up the search. These are here motivated. 
 	\subsubsection{Bounds in ID}
+	Information gained about solution costs of independent groups can be used to establish a lower bound on solution SIC as per Property \ref{property:id-lower}, and in bounded search the upper bound can be further constrained (Property \ref{property:id-upper}).
 	\begin{property}[Lower bound]
@@
 		\[C_k\geq C_i + C_j\]
+		\label{property:id-lower}
 	\end{property}
@@
 		In bounded exhaustive search, the sum of costs of groups not being merged can be subtracted from bound $B$ without losing optimality.
+		\label{property:id-upper}
 	\end{property}
@@
 However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented.
-This can be explioted by pruning the node's children that do not correspond to the conflicting agents, of which there are often just 2 or 3, which can drastically improve the (average) branching factor as $k$ increases.
+This can be explioted by pruning the node's children that do not correspond to the conflicting agents, of which there are often just 2 or 3, drastically improving the (average) branching factor as $k$ increases.
+By Property \ref{property:ec-incompat}, child pruning is not compatible with enhanced pruning.
 	\begin{property}[Incompatibility with enhanced pruning]
 		Enhanced pruning combined with child pruning (hereafter E+C pruning) is suboptimal due to the \textit{cascading effect} described in \cite{sharon2011}.
+		\label{property:ec-incompat}
 	\end{property}
+
 	\begin{figure}[H]
@@
 	\end{proof}
+
+	\section{Results}
+	\label{experiments}
+	To compare the algorithms and variants described above and put them into the context of alternative MAPFM algorithms, two types of experiments were performed.
+In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM developed within the peer group\footnote{I want to thank Jonathan Dönszelmann, who worked on M*-based algorithms, for setting up this comparison[TODO: move to thanks note at end]}.
+The values compared are the fraction of instances solved, and the average runtime per instance.
+It should be noticed that in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work, the fraction of instances solved is guiding in the analysis of results.
 		\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
@@
 			\caption{25, 1 team}
-		\label{fig:25-1-p}
+			\label{fig:i-25-1-p}
 		\end{subfigure}
@@
 			\caption{25, 3 teams}
-		\label{fig:25-3-p}
+			\label{fig:i-25-3-p}
 		\end{subfigure}
@@
 			\caption{75, 1 team}
-		\label{fig:75-1-p}
+			\label{fig:i-75-1-p}
 		\end{subfigure}
@@
 			\caption{75, 3 teams}
-		\label{fig:75-3-p}
+			\label{fig:i-75-3-p}
 		\end{subfigure}
 		\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
-	\label{fig:probs}
+		\label{fig:i-probs}
 	\end{figure*}
-	\begin{figure*}[t]
+	\begin{figure*}[b]
 		\centering
@@
 			\caption{25, 1 team}
-		\label{fig:25-1-p}
+			\label{fig:r-25-1-p}
 		\end{subfigure}
@@
 			\caption{25, 3 teams}
-		\label{fig:25-3-p}
+			\label{fig:r-25-3-p}
 		\end{subfigure}
@@
 			\caption{75, 1 team}
-		\label{fig:75-1-p}
+			\label{fig:r-75-1-p}
 		\end{subfigure}
@@
 		\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
-	\label{fig:probs}
+		\label{fig:r-probs}
 	\end{figure*}
@@
 	\restoregeometry
-
-	\section{Results}
-	\label{experiments}
-	To compare the algorithms and variants described above and put them into the context of alternative MAPFM algorithms, two types of experiments were performed.
-In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant (Exh+E+B+O) is compared to other algorithms for MAPFM developed within the peer group\footnote{I want to thank Jonathan Dönszelmann, who worked on M*-based algorithms, for setting up this comparison[TODO: move to thanks note at end]}.
-The values compared are the fraction of instances solved, and the average runtime per instance.
-It should be noticed that in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work, the fraction of instances solved is guiding in the analysis of results.
 	\subsection{Experimental setup}
@@
 	\subsection{Experiment 1: ICTS-based MAPFM algorithms}
-	Figure \ref{fig:probs} reports the fraction of instances that each algorithm variant solved within the timeout of 120s in different settings.
+	Figure \ref{fig:i-probs} reports the fraction of instances that each algorithm variant solved within the timeout of 120s in different settings.
 The meaning of the abbreviations used in the legend are as follows:
@@
 	\subsubsection{Analysis}
-	Across exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by \ref{fig:25-3-p}.
-Almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E.
+	Across scenarios, it is seen that typically exhaustive methods outperform ICTS-m algorithms (\ref{fig:i-probs}), with performance being more similar in the 75 maps with more obstructions.
+In particular on 75 maps with 3 teams (\ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases, and some of these also manage to solve a small fraction of problems of 75 maps with 1 team that exhaustive methods cannot within the time-out (\ref{fig:i-75-1-p}).
+
+	Between exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by \ref{fig:i-25-3-p}; almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E.
 Bounded search outperforms unbounded search as expected, given that the former does at most as much work as the latter and often less.
 Approximate ordering outperforming unordered enumeration is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}.
+Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this novel method.
+In particular as $k$ grows larger and in scenarios with more obstacles (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
+In the
+
+	The benefit of using ID together with ordered enumeration is less clear.
+Ordered enumeration with ID performs much better in \ref{fig:i-75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:i-25-1-p}).
+The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
+This explains why no speedup is seen, as ICTS-m between and ICTS-m+ID.
+	\subsection{Experiment 2: Algorithms for MAPFM}
+	Figure \ref{fig:r-probs} reports the fraction of instances solved within 120s by various algorithms for MAPFM. The algorithms are as follows
+	\begin{itemize}
+		\begin{minipage}{0.49\linewidth}
+			\item A*+ID+OD with matching ID and sorted exhaustive matching\cite{bruin2021}
+			\item EPEA* with matching ID and sorted exhaustive matching\cite{jong2021}
+			\item M* with sorted exhaustive matching\cite{donszelmann2021}
+		\end{minipage}
+		\hspace{1cm}
+		\begin{minipage}{0.40\linewidth}
+			\item CBM adapted to use SIC, using the successive shortest path algorithm (SSP) \cite{goldberg1987} as subroutine for solving teams\cite{baauw2021}.
+			\item ICTS with approximate sorted exhaustive matching (Exh+E+B+O)
+
+		\end{minipage}
+	\end{itemize}
+	One of the first things that meets the eye is the staggering performance of CBM in all scenarios with one team (\ref{fig:r-25-1-p},\ref{fig:r-75-1-p}), which are equivalent to anonymous MAPF problems.
+This can adequately be explained by CBM solving single teams as anonymous MAPF instances in polynomial time, meaning that solving a single team reduces to a polynomial-time procedure (SSP to be specific).
+It is expected that conform the results reported in \cite{ma2016}, as the number of teams approaches $k$, CBM performance will deteriorate and thus become more similar to the results for exhaustive methods here reported.
+	\section{Discussion}
 	Although no bound-value data was recorded, one explanation might be that often, early on in the search, single matchings with low $\Delta_m$ are found, causing the rest of the searches to be significantly curtailed.
-
-	Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this novel method.
-In particular as $k$ grows larger and in scenarios with more obstacles (\ref{fig:75-1-p},\ref{fig:75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
-
-	Ordered enumeration with ID performs much better in \ref{fig:75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:25-1-p}).
-The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:25-1-p},\ref{fig:75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
-This explains why no speedup is seen, as ICTS-m between and ICTS-m+ID, which is is more typical.
-
-	With some exceptions, ICTS-m variants are outperformed by the exhaustive variants.
-	In almost every instance the ICTS-m variants are outperformed by exhaustive variants. 
-	\subsection{Experiment 2: Algorithms for MAPFM}
-	[TODO: add relative comparison]
-
-	\section{Discussion}
-
+Mo
+	However, closer analysis of performance differences between these pruning strategies and alternatives  (repeated enhanced pruning or pruning with pairs, quadruples, etc.) across different scenarios is something for further research.
 %	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
-
-	Compared to the results achieved by \cite{ma2016}, the results recorded are somewhat disappointing.
 	\section{Conclusions}
@@
 It was also seen that in turn a SIC-adaptation of the CBM method \cite{ma2016} greatly outperforms exhaustive alternatives in the settings that were tried out.
-Therefore, it can be concluded that the method that arguably has the most potential to scale well, ICTS-m, has a very long way to go before being usable in practical scenarios with significant problem sizes.
+Therefore, it can be concluded that the method that arguably has the most potential to scale well, ICTS-m, has a long way to go before being usable in practical scenarios with significant problem sizes.
 	\section{Future work}
@@
 	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
-	\begin{figure*}[b]
+	\begin{figure*}[t]
 		\centering
@@
 			\caption{25, 1 team}
-			\label{fig:25-1}
+			\label{fig:i-25-1}
 		\end{subfigure}
@@
 			\caption{25, 3 teams}
-			\label{fig:25-3}
+			\label{fig:i-25-3}
 		\end{subfigure}
@@
 			\caption{75, 1 team}
-			\label{fig:75-1}
+			\label{fig:i-75-1}
 		\end{subfigure}
@@
 			\caption{75, 3 teams}
-			\label{fig:75-3}
+			\label{fig:i-75-3}
 		\end{subfigure}
-		\caption{Average solving time on two types of 20x20 grids with a 120s timeout}
-		\label{fig:times}
+		\caption{Average solving time of different ICTS-based algorithms}
+		\label{fig:i-times}
 	\end{figure*}
-	\begin{figure*}[t]
+	\begin{figure*}[b]
 		\centering
@@
 			\caption{25, 1 team}
-			\label{fig:25-1-p}
+			\label{fig:r-25-1}
 		\end{subfigure}
@@
 			\caption{25, 3 teams}
-			\label{fig:25-3-p}
+			\label{fig:r-25-3}
 		\end{subfigure}
@@
 			\caption{75, 1 team}
-			\label{fig:75-1-p}
+			\label{fig:r-75-1}
 		\end{subfigure}
@@
 			\caption{75, 3 teams}
-			\label{fig:75-3-p}
+			\label{fig:r-75-3}
 		\end{subfigure}
-		\caption{Average solving time on two types of 20x20 grids with a 120s timeout}
-		\label{fig:probs}
+		\caption{Average solving time of MAPFM algorithms}
+		\label{fig:r-times}
 	\end{figure*}

### 2021-06-16 docs/paper.tex
Added references to other algorithms used as starting point

@@
 	\end{wrapfigure}
-	This work is the outcome of a search for algorithms for optimally solving MAPFM based on ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}.
-Two classes of algorithms were found, one based on exhaustive enumeration of matchings using a variant of ICTS as subroutine, the other based on modifications to the ICT structure and its search.
-In the context of a research project in which multiple MAPF algorithms in addition to ICTS were taken as starting points for MAPFM algorithms, one exhaustive ICTS algorithm is compared to these alternatives on a set of benchmarks.
-In addition, properties of the various algorithm variants are discussed and their performance is compared experimentally.
+	This work is the outcome of a search for algorithms for optimally solving MAPFM based on ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which took place as part of a project in which  other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
+Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as subroutine, the other based on modifications to the ICT structure and its search.
+One exhaustive ICTS algorithm is compared to algorithms based on M*\cite{wagner2011}, A*+OD+ID\cite{standley2010}, CBM\cite{ma2016} and EPEA*\cite{goldenberg2014} respectively to put ICTS methods for MAPFM into a broader context.
 
@@
 Algorithm \ref{pq-algo} outlines the procedure.
-This way of getting around memory limitations originates in [TODO: cite Jaap's paper].
 
@@
 For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
-This observation informed the creation of a map generator within the peer group with various parameters.
+This observation informed the creation of a map generator by the author of \cite{jong2021} with various parameters.
 Using this map generator, two types of 20x20 grids were generated:
@@
 	\end{enumerate}
-	For each of these types, two sets of maps were generated with between $1$ to $16$ agents and 200 instances generated for each such agent-setting: one set where all agents belong to one team, another in which the agents were divided into three teams (or $1,2$ teams strictly speaking for the datapoints with respectively $1,2$ agents).
+	For each of these types, two sets of maps were generated with between $1$ to $25$ agents and 200 instances generated for each such agent-setting: one set with one team, another with three teams of approximately the same size ($1,2$ teams strictly speaking for the datapoints with $1,2$ agents).
+For each scenario, the number of agents was increased until 0\% of instances was solved at which point no more data was recorded for greater numbers of agents.
 
-	The first experiments were performed on an Intel i7-8750H hexacore operating at 2.2GHz with 16GiB of memory. Here, for each setting, a fixed subset of 50 out of 200 maps were used.
+	The first experiments were performed on an Intel i7-8750H hexacore operating at 2.2GHz with 16GiB of memory. For each setting, a fixed subset of 50 out of 200 maps were used.
 
-	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a Intel Xeon E5-2683 dodecacore operating at 2.0Ghz with 8GiB of RAM.
+	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0Ghz with 8GiB of RAM.
 All 200 maps were used for each setting.
+
 	Although these algorithms have different authors, all are implemented in Python 3 (with one using an ILP solver implemented in C++ as a subroutine) to avoid performance differences as often seen between interpreted versus compiled languages.
@@
 	\end{itemize}
-	\subsubsection{Analysis}
 	Across scenarios, it is seen that typically exhaustive methods outperform ICTS-m algorithms (\ref{fig:i-probs}), with performance being more similar in the 75 maps with more obstructions.
@@
 In particular as $k$ grows larger and in scenarios with more obstacles (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
-In the
 
@@
 			\item ICTS with approximate sorted exhaustive matching (Exh+E+B+O)
-
 		\end{minipage}
 	\end{itemize}
+	With exception of CBM, all methods described use a variant of sorted exhaustive matching.
+This is due to the fact that from each family of algorithms, one of the best performing algorithms was chosen, which always was such an exhaustive method as opposed to a generalization of the base algorithm to MAPFM (ICTS-m in this work).
+A*+ID+OD and EPEA* also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver.
+
 	One of the first things that meets the eye is the staggering performance of CBM in all scenarios with one team (\ref{fig:r-25-1-p},\ref{fig:r-75-1-p}), which are equivalent to anonymous MAPF problems.
@@
 Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive ICTS algorithms consistently outperform the ICTS-m based algorithms.
+Compared to the SIC-adaptation of the CBM method \cite{baauw2021} (which is adapted from \cite{ma2016}, the state-of-the-art MAPFM with makespan algorithm), it was seen that exhaustive methods in general perform quite poorly if there are fewer teams and fewer obstacles, while being competitive once teams grow smaller and maps become more constrained.
+
 	It was also seen that in turn a SIC-adaptation of the CBM method \cite{ma2016} greatly outperforms exhaustive alternatives in the settings that were tried out.
@@
 	\section{Responsible Research}
-	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository \footnote{\url{https://github.com/tbvanderwoude/icts-m}}.
+	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository\footnote{\url{https://github.com/tbvanderwoude/icts-m}}.
 Included is also code for benchmarking different configurations of the ICTS solver and the maps that were used in the benchmarks reported above.
+The benchmarks and maps used in relative comparison of MAPFM algorithms is also available on Github\footnote{\url{https://github.com/jonay2000/research-project}}.
 

### 2021-06-16 docs/paper.tex
Finished (crude) version of complete paper

@@
 The joint problem of multi-agent pathfinding extended with matching between agents and goals is something that has not been studied much; few methods exist today that solve it.
-In this work, two types of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem: exhaustive algorithms that reduce the problem to solving many MAPF problems using regular ICTS, and algorithms that search a generalized increasing cost tree.
+In this work, two types of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem: exhaustive algorithms that reduce the problem to solving many MAPF problems using regular Increasing Cost Tree Search, and algorithms that search a generalized increasing cost tree.
 These are compared to each other experimentally on a set of grid maps, and it is shown that exhaustive methods typically outperform the generalized ICT search.
-An algorithm of the first type is compared to alternative algorithms based on other MAPF algorithms to put its performance into the context.
+Lastly, an exhaustive algorithm is compared to alternative algorithms based on other multi-agent pathfinding approaches to put its performance into the broader context of algorithms for multi-agent pathfinding with matching.
 	\end{abstract}
@@
 	\end{wrapfigure}
-	This work is the outcome of a search for algorithms for optimally solving MAPFM based on ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which took place as part of a project in which  other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
+	This work is the outcome of a search for algorithms for optimally solving MAPFM based on ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a project in which  other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
 Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as subroutine, the other based on modifications to the ICT structure and its search.
-One exhaustive ICTS algorithm is compared to algorithms based on M*\cite{wagner2011}, A*+OD+ID\cite{standley2010}, CBM\cite{ma2016} and EPEA*\cite{goldenberg2014} respectively to put ICTS methods for MAPFM into a broader context.
+One exhaustive ICTS algorithm is compared to algorithms based on CBM\cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} respectively to put ICTS methods for MAPFM into a broader context.
 
@@
 		\end{algorithmic}
-		\caption{Simple Independence Detection by Standley} 
+		\caption{Simple Independence Detection \cite{standley2010}} 
 		\label{id-algo}
@@
 It is reproduced from \cite{sharon2011} for completeness.
-As noted before, this procedure could be used for planning groups in Algorithm \ref{id-algo}.
-In this work, triple-pruning was used and enhanced triple-pruning was taken as a base-line, as the conclusion in \cite{sharon2011} is that this generally outperforms other variants.
+As noted before, this procedure can be used for planning groups in Algorithm \ref{id-algo}.
+In this work, triple-pruning was used and enhanced triple-pruning was taken as a base-line, as the conclusion in \cite{sharon2011} is that this often outperforms other variants.
 	\begin{algorithm}
@@
 	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,bounded}})$.
-	If $B_m < C^*_m$, there is no need to consider $m$ and $\Delta_{m,bounded} = 0$.
+	If $B_m < C^*_m$, only the root node will be generated to determine this so $\Delta_{m,bounded} = 0$.
 	Using this, the number of ICT nodes searched in total becomes $\mathcal{O}(\sum_m k^{\Delta_{m,bounded}})$.
@@
 	\label{ordered-enum}
-	In an effort to reduce the total effort as much as possible, the matchings $m$ could be enumerated and solved in increasing order of $C^*_m$.
+	In an effort to reduce the total effort as much as possible, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$.
 In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}.
-This induces a case in which this enumeration minimizes the number of nodes searched in total, $\Delta_m$ (Property \ref{cond-monoton-optim}).
+This induces a case in which this enumeration minimizes the number of nodes searched in total (Property \ref{cond-monoton-optim}).
 However, cases in which $\Delta_m$ of the first $m$'s searched is much higher could also be constructed, in which case this approach might cause more nodes to be processed in total than alternative methods.
+Therefore, this ordered enumeration remains a heuristic improvement that works well in practice, as shown in Section \ref{experiments}.
 
@@
 As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
-[TODO: reduce case to just 2 agents?]
 	%\subsubsection{Inverted MDD search}
@@
 	\subsubsection{Bounds in ID}
-	Information gained about solution costs of independent groups can be used to establish a lower bound on solution SIC as per Property \ref{property:id-lower}, and in bounded search the upper bound can be further constrained (Property \ref{property:id-upper}).
+	Information gained about solution costs of independent groups can be used to establish a lower bound on solution SIC as per Property \ref{property:id-lower}.
+In bounded search the upper bound can be further constrained by Property \ref{property:id-upper}.
 	\begin{property}[Lower bound]
@@
 	\begin{property}[Incompatibility with enhanced pruning]
-		Enhanced pruning combined with child pruning (hereafter E+C pruning) is suboptimal due to the \textit{cascading effect} described in \cite{sharon2011}.
+		Enhanced pruning combined with child pruning is suboptimal due to the \textit{cascading effect} described in \cite{sharon2011}.
 		\label{property:ec-incompat}
@@
 	\end{subfigure}
-	\caption{Counter-example for E+C pruning}
+	\caption{Counter-example for enhanced pruning combined with child pruning}
 	\label{fig:counter-example}
@@
 By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed.
-Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that E+C pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making it suboptimal.
+Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that enhanced pruning combined with child pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making this pruning strategy suboptimal.
 	\end{proof}
 
-	\section{Results}
+	\section{Experimental Results}
 	\label{experiments}
-	To compare the algorithms and variants described above and put them into the context of alternative MAPFM algorithms, two types of experiments were performed.
-In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM developed within the peer group\footnote{I want to thank Jonathan Dönszelmann, who worked on M*-based algorithms, for setting up this comparison[TODO: move to thanks note at end]}.
+	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed.
+In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM developed within the peer group.
+This comparison data originates in \cite{donszelmann2021}.
 The values compared are the fraction of instances solved, and the average runtime per instance.
-It should be noticed that in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work, the fraction of instances solved is guiding in the analysis of results.
+It should be noticed that in the latter, the recorded runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
 	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
-			\caption{25, 1 team}
+			\caption{25\% wall, 1 team}
 			\label{fig:i-25-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
-			\caption{25, 3 teams}
+			\caption{25\% wall, 3 teams}
 			\label{fig:i-25-3-p}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
-			\caption{75, 1 team}
+			\caption{75\% wall, 1 team}
 			\label{fig:i-75-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
-			\caption{75, 3 teams}
+			\caption{75\% wall, 3 teams}
 			\label{fig:i-75-3-p}
 		\end{subfigure}
-		\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
+		\caption{Fraction solved out of 50 maps by different ICTS-based algorithms}
 		\label{fig:i-probs}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
-			\caption{25, 1 team}
+			\caption{25\% wall, 1 team}
 			\label{fig:r-25-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
-			\caption{25, 3 teams}
+			\caption{25\% wall, 3 teams}
 			\label{fig:r-25-3-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
-			\caption{75, 1 team}
+			\caption{75\% wall, 1 team}
 			\label{fig:r-75-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
-			\caption{75, 3 teams}
-			\label{fig:75-3-p}
+			\caption{75\% wall, 3 teams}
+			\label{fig:r-75-3-p}
 		\end{subfigure}
-		\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
+		\caption{Fraction solved out of 200 maps by MAPFM algorithms}
 		\label{fig:r-probs}
@@
 	\begin{enumerate}
-		\item 25: a grid with 25\% of tiles being obstacles.
-		\item 75: a grid with 75\% of tiles being obstacles. 
+		\item 25\% wall: a grid with 25\% of tiles being obstacles.
+		\item 75\% wall: a grid with 75\% of tiles being obstacles. 
 	\end{enumerate}
-	For each of these types, two sets of maps were generated with between $1$ to $25$ agents and 200 instances generated for each such agent-setting: one set with one team, another with three teams of approximately the same size ($1,2$ teams strictly speaking for the datapoints with $1,2$ agents).
-For each scenario, the number of agents was increased until 0\% of instances was solved at which point no more data was recorded for greater numbers of agents.
+	For each of these types, maps were generated with between $1$ and $25$ agents either all in the same team or partitioned into $3$ teams as fairly as possible.
+When solving the instances, for each combination of map-type and number of teams, the number of agents was increased until 0\% of instances could be solved within a timeout of 120s, at which point no more data was recorded for greater numbers of agents.
 
@@
 
-	Although these algorithms have different authors, all are implemented in Python 3 (with one using an ILP solver implemented in C++ as a subroutine) to avoid performance differences as often seen between interpreted versus compiled languages.
-Nonetheless, conclusions are here a bit more limited, as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.
+	All algorithms are implemented in Python 3 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use a SSP solver implemented in C++ as a subroutine.
+Nonetheless, the comparison is here a bit more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.
 
 	\subsection{Experiment 1: ICTS-based MAPFM algorithms}
-	Figure \ref{fig:i-probs} reports the fraction of instances that each algorithm variant solved within the timeout of 120s in different settings.
+	To investigate the relative performance of various algorithms discussed in Section \ref{section:icts-matching}, a selection of both exhaustive and ICTS-m variants was made.
+Their performance in terms of fraction of problems solved within a timeout of 120s is shown in Figure \ref{fig:i-probs}.
 The meaning of the abbreviations used in the legend are as follows:
@@
 	\end{itemize}
-	Across scenarios, it is seen that typically exhaustive methods outperform ICTS-m algorithms (\ref{fig:i-probs}), with performance being more similar in the 75 maps with more obstructions.
-In particular on 75 maps with 3 teams (\ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases, and some of these also manage to solve a small fraction of problems of 75 maps with 1 team that exhaustive methods cannot within the time-out (\ref{fig:i-75-1-p}).
+	Across scenarios, it is seen that typically exhaustive methods outperform ICTS-m algorithms (\ref{fig:i-probs}), with performance being more similar in the maps with 75\% wall.
+In particular on 75\% wall maps with 3 teams (\ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases, and some of these also manage to solve a small fraction of 75\% maps with 1 team that exhaustive methods cannot within the time-out (\ref{fig:i-75-1-p}).
 
@@
 Bounded search outperforms unbounded search as expected, given that the former does at most as much work as the latter and often less.
-Approximate ordering outperforming unordered enumeration is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}.
-Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this novel method.
+Approximate ordering outperforming unordered enumeration is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}, and simply indicates that sorting works well in practice.
+Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this pruning method.
 In particular as $k$ grows larger and in scenarios with more obstacles (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
+As discussed in Section \ref{future}, more work is needed to determine if such an improvement is to be expected more generally.
 
@@
 This explains why no speedup is seen, as ICTS-m between and ICTS-m+ID.
+Another factor is that if all agents belong to the same team, it is somewhat unlikely that there will a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.
+
 	\subsection{Experiment 2: Algorithms for MAPFM}
-	Figure \ref{fig:r-probs} reports the fraction of instances solved within 120s by various algorithms for MAPFM. The algorithms are as follows
+	From the variants discussed and compared above, the Exh+E+B+O variant was selected for comparison with various other algorithms for MAPFM.
+This results in the following set of algorithms whose performance is shown in Figure \ref{fig:r-probs}.
 	\begin{itemize}
-		\begin{minipage}{0.49\linewidth}
+		\begin{minipage}{0.45\linewidth}
+			\item ICTS with approximate sorted exhaustive matching (Exh+E+B+O)
 			\item A*+ID+OD with matching ID and sorted exhaustive matching\cite{bruin2021}
 			\item EPEA* with matching ID and sorted exhaustive matching\cite{jong2021}
-			\item M* with sorted exhaustive matching\cite{donszelmann2021}
 		\end{minipage}
@@
 		\begin{minipage}{0.40\linewidth}
+			\item M* with sorted exhaustive matching\cite{donszelmann2021}
 			\item CBM adapted to use SIC, using the successive shortest path algorithm (SSP) \cite{goldberg1987} as subroutine for solving teams\cite{baauw2021}.
-			\item ICTS with approximate sorted exhaustive matching (Exh+E+B+O)
 		\end{minipage}
@@
 A*+ID+OD and EPEA* also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver.
+Hypothetically, this could explain why both outperform the methods using just sorted exhaustive matching in maps with 75\% wall and 3 teams (\ref{fig:r-75-3-p}); this difference is not quite as clear in the remaining scenarios shown in Figure \ref{fig:r-probs} however.
 
-	One of the first things that meets the eye is the staggering performance of CBM in all scenarios with one team (\ref{fig:r-25-1-p},\ref{fig:r-75-1-p}), which are equivalent to anonymous MAPF problems.
-This can adequately be explained by CBM solving single teams as anonymous MAPF instances in polynomial time, meaning that solving a single team reduces to a polynomial-time procedure (SSP to be specific).
+	CBM solving all problems with one team (Figure \ref{fig:r-25-1-p} and \ref{fig:r-75-1-p}), problems equivalent to anonymous MAPF instances, is at first surprising, but follows directly from the definition of the CBM method.
+CBM solves single teams as anonymous MAPF instances in polynomial time, meaning that solving a single team reduces to a polynomial-time procedure, namely SSP.
 It is expected that conform the results reported in \cite{ma2016}, as the number of teams approaches $k$, CBM performance will deteriorate and thus become more similar to the results for exhaustive methods here reported.
-	\section{Discussion}
-	Although no bound-value data was recorded, one explanation might be that often, early on in the search, single matchings with low $\Delta_m$ are found, causing the rest of the searches to be significantly curtailed.
-Mo
-	However, closer analysis of performance differences between these pruning strategies and alternatives  (repeated enhanced pruning or pruning with pairs, quadruples, etc.) across different scenarios is something for further research.
 %	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
-	\section{Conclusions}
+	\section{Conclusions and future work}
+	\label{conclusions}
+	\label{future}
 	The goal of this research was to seek alternative approaches to solving MAPFM based on ICTS.
@@
 Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive ICTS algorithms consistently outperform the ICTS-m based algorithms.
-Compared to the SIC-adaptation of the CBM method \cite{baauw2021} (which is adapted from \cite{ma2016}, the state-of-the-art MAPFM with makespan algorithm), it was seen that exhaustive methods in general perform quite poorly if there are fewer teams and fewer obstacles, while being competitive once teams grow smaller and maps become more constrained.
+Compared to the SIC-adaptation of the CBM method \cite{baauw2021}, it was seen that exhaustive methods in general perform quite poorly if there are fewer teams and fewer obstacles, while being competitive once teams grow smaller and maps become more constrained.
+Delineating under which conditions exhaustive methods outperform CBM and vice versa is something for further research.
 
-	It was also seen that in turn a SIC-adaptation of the CBM method \cite{ma2016} greatly outperforms exhaustive alternatives in the settings that were tried out.
-Therefore, it can be concluded that the method that arguably has the most potential to scale well, ICTS-m, has a long way to go before being usable in practical scenarios with significant problem sizes.
-	\section{Future work}
-	In this project, there were many roads not taken.
-In particular for the ICTS-m variant, there are still many things that could be experimented with in order to improve performance, such as more extensive or multi-staged pruning procedures or ways to exploit the fact that agents are partitioned into teams.
-For instance, the hungarian algorithm could be used to find lower-bounds for per-team SICs, which allows skipping the low-level search in many cases and can trivially be combined with pruned child generation branching within teams.
+	Future research could also look into improving the ICTS-m method described using for instance more extensive pruning or properties of the problem such as lower-bounds on per-team solution SIC that can be computed using the Hungarian Algorithm.
+Another approach to explore would be hybridized approaches that enumerate partially constrained MAPFM instances which can be solved using any MAPFM solver.
+In this way, the benefit of the successive bounding of the search could be exploited and by carefully picking which agents to constrain, these constrained MAPFM instances could potentially be made relatively easy.
 
-	Hybridized approaches, where approximate ordered search is combined with the search of partially restricted MAPFM problems, could be promising to explore in the future; this is not restricted to ICTS: any MAPF algorithm generalized to solve MAPFM could be used in this scheme.
+	Lastly, more experimentation is needed to reach definite conclusions about how simple child pruning compares to existing pruning techniques for ICTS, which could be done by reproducing the ICTS pruning technique experiments reported in \cite{sharon2011} extended with simple child pruning variants.
+%Given that simple pruning is somewhat cheap computationally, it might also be possible to prune the child generation using simple child pruning but still use enhanced pruning to decide whether to execute $k$-agent low-level search, combining the benefits of searching a smaller ICT and performing fewer $k$-agent searches.
 
-	Another subject for future research might be a closer theoretical and experimental analysis of simple child pruning as alternative to enhanced pruning in the context of ICTS for MAPF, assuming this method has not been described before.
-Although experimentally it was shown to outperform enhanced pruning in exhaustive matching, ideally the two pruning strategies should be tested using the Moving AI benchmark \cite{sturtevant2012} to reach definite conclusions about how they compare.
-Using simple pruning to prune children and enhanced pruning for pruning low-level search could also be interesting to explore, as it could potentially combine the benefits of searching a smaller ICT and performing fewer $k$-agent low-level searches at the cost of spending more time pruning.
 	\section{Responsible Research}
@@
 Included is also code for benchmarking different configurations of the ICTS solver and the maps that were used in the benchmarks reported above.
-The benchmarks and maps used in relative comparison of MAPFM algorithms is also available on Github\footnote{\url{https://github.com/jonay2000/research-project}}.
+The benchmarks and maps used in relative comparison of MAPFM algorithms are also available in the code and data repository of \cite{donszelmann2021}\footnote{\url{https://github.com/jonay2000/research-project}}.
 
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
-			\caption{25, 1 team}
+			\caption{25\% wall, 1 team}
 			\label{fig:i-25-1}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
-			\caption{25, 3 teams}
+			\caption{25\% wall, 3 teams}
 			\label{fig:i-25-3}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
-			\caption{75, 1 team}
+			\caption{75\% wall, 1 team}
 			\label{fig:i-75-1}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
-			\caption{75, 3 teams}
+			\caption{75\% wall, 3 teams}
 			\label{fig:i-75-3}
 		\end{subfigure}
-		\caption{Average solving time of different ICTS-based algorithms}
+		\caption{Average solving time of different ICTS-based algorithms with a timeout of 120s}
 		\label{fig:i-times}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
-			\caption{25, 1 team}
+			\caption{25\% wall, 1 team}
 			\label{fig:r-25-1}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
-			\caption{25, 3 teams}
+			\caption{25\% wall, 3 teams}
 			\label{fig:r-25-3}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
-			\caption{75, 1 team}
+			\caption{75\% wall, 1 team}
 			\label{fig:r-75-1}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
-			\caption{75, 3 teams}
+			\caption{75\% wall, 3 teams}
 			\label{fig:r-75-3}
 		\end{subfigure}
-		\caption{Average solving time of MAPFM algorithms}
+		\caption{Average solving time of MAPFM algorithms timeout of 120s}
 		\label{fig:r-times}

### 2021-06-17 docs/paper.tex
Fixed grammar/spelling issues

@@
 	Mulderij et al.
-\cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation for finding such upper-bounds using an approach analogous to that outlined above.
+\cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding such upper-bounds using an approach analogous to that outlined above.
 	For this to succeed, a way to optimally solve MAPFM instances is needed.
@@
 	This work is the outcome of a search for algorithms for optimally solving MAPFM based on ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a project in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
-Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as subroutine, the other based on modifications to the ICT structure and its search.
+Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as a subroutine, the other based on modifications to the ICT structure and its search.
 One exhaustive ICTS algorithm is compared to algorithms based on CBM\cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} respectively to put ICTS methods for MAPFM into a broader context.
@@
 
-	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem which can be solved in polynomial time.
+	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem that can be solved in polynomial time.
 	\section{Solving MAPF with Matching using ICTS} % Your contribution
@@
 In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
-In this section, first ICTS for MAPF and some common variants will be described.
+First, ICTS for MAPF and some common variants will be described.
 Next, derived MAPFM algorithms are introduced and properties of these algorithms and some variants are discussed.
@@
 As noted before, this procedure can be used for planning groups in Algorithm \ref{id-algo}.
-In this work, triple-pruning was used and enhanced triple-pruning was taken as a base-line, as the conclusion in \cite{sharon2011} is that this often outperforms other variants.
+In this work, triple-pruning was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2011} is that this often outperforms other variants.
 	\begin{algorithm}
@@
 	\label{ordered-enum}
-	In an effort to reduce the total effort as much as possible, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$.
+	To reduce the total effort as much as possible, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$.
 In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}.
@@
 
-	In implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory}.
+	In the implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory}.
 Algorithm \ref{pq-algo} outlines the procedure.
@@
 	\subsubsection{Bounds in ID}
-	Information gained about solution costs of independent groups can be used to establish a lower bound on solution SIC as per Property \ref{property:id-lower}.
-In bounded search the upper bound can be further constrained by Property \ref{property:id-upper}.
+	The information gained about solution costs of independent groups can be used to establish a lower bound on solution SIC as per Property \ref{property:id-lower}.
+In bounded search, the upper bound can be further constrained by Property \ref{property:id-upper}.
 	\begin{property}[Lower bound]
@@
 However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented.
-This can be explioted by pruning the node's children that do not correspond to the conflicting agents, of which there are often just 2 or 3, drastically improving the (average) branching factor as $k$ increases.
+This can be exploited by pruning the node's children that do not correspond to the conflicting agents, of which there are often just 2 or 3, drastically improving the (average) branching factor as $k$ increases.
 By Property \ref{property:ec-incompat}, child pruning is not compatible with enhanced pruning.
@@
 
-	All algorithms are implemented in Python 3 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use a SSP solver implemented in C++ as a subroutine.
+	All algorithms are implemented in Python 3 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine.
 Nonetheless, the comparison is here a bit more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.
@@
 Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this pruning method.
-In particular as $k$ grows larger and in scenarios with more obstacles (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
+In particular, as $k$ grows larger and in scenarios with more obstacles (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
 As discussed in Section \ref{future}, more work is needed to determine if such an improvement is to be expected more generally.
@@
 	With exception of CBM, all methods described use a variant of sorted exhaustive matching.
-This is due to the fact that from each family of algorithms, one of the best performing algorithms was chosen, which always was such an exhaustive method as opposed to a generalization of the base algorithm to MAPFM (ICTS-m in this work).
+This is because from each family of algorithms one of the best performing algorithms was chosen, which always was such an exhaustive method as opposed to a generalization of the base algorithm to MAPFM (ICTS-m in this work).
 A*+ID+OD and EPEA* also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver.
@@
 
-	CBM solving all problems with one team (Figure \ref{fig:r-25-1-p} and \ref{fig:r-75-1-p}), problems equivalent to anonymous MAPF instances, is at first surprising, but follows directly from the definition of the CBM method.
+	CBM solving all problems with one team (Figure \ref{fig:r-25-1-p} and \ref{fig:r-75-1-p}), problems equivalent to anonymous MAPF instances, is at first surprising but follows directly from the definition of the CBM method.
 CBM solves single teams as anonymous MAPF instances in polynomial time, meaning that solving a single team reduces to a polynomial-time procedure, namely SSP.
-It is expected that conform the results reported in \cite{ma2016}, as the number of teams approaches $k$, CBM performance will deteriorate and thus become more similar to the results for exhaustive methods here reported.
+Following the results reported in \cite{ma2016}, it is expected that as the number of teams approaches $k$, CBM performance will deteriorate and thus become more similar to the results for exhaustive methods here reported.
 	%	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
-	\section{Conclusions and future work}
+	\section{Conclusions and Future work}
 	\label{conclusions}
@@
 Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive ICTS algorithms consistently outperform the ICTS-m based algorithms.
-Compared to the SIC-adaptation of the CBM method \cite{baauw2021}, it was seen that exhaustive methods in general perform quite poorly if there are fewer teams and fewer obstacles, while being competitive once teams grow smaller and maps become more constrained.
+Compared to the SIC-adaptation of the CBM method \cite{baauw2021}, it was seen that exhaustive methods generally perform quite poorly if there are fewer teams and fewer obstacles, while being competitive once teams grow smaller and maps become more constrained.
 Delineating under which conditions exhaustive methods outperform CBM and vice versa is something for further research.
@@
 Included is also code for benchmarking different configurations of the ICTS solver and the maps that were used in the benchmarks reported above.
-The benchmarks and maps used in relative comparison of MAPFM algorithms are also available in the code and data repository of \cite{donszelmann2021}\footnote{\url{https://github.com/jonay2000/research-project}}.
+The benchmarks and maps used in the relative comparison of MAPFM algorithms are also available in the code and data repository of \cite{donszelmann2021}\footnote{\url{https://github.com/jonay2000/research-project}}.
 
@@
 		\end{subfigure}
-		\caption{Average solving time of MAPFM algorithms timeout of 120s}
+		\caption{Average solving time of MAPFM algorithms with a timeout of 120s}
 		\label{fig:r-times}

### 2021-06-17 docs/paper.tex
Processed all Jonathan's feedback

@@
 		Both the assignment problem and the multi-agent pathfinding problem are common problems in the fields of robotics and transportation.
-The joint problem of multi-agent pathfinding extended with matching between agents and goals is something that has not been studied much; few methods exist today that solve it.
+The joint problem of multi-agent pathfinding extended with the assignment of goals to agents, matching, is something that has not been studied much; few methods exist today that solve it.
 In this work, two types of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem: exhaustive algorithms that reduce the problem to solving many MAPF problems using regular Increasing Cost Tree Search, and algorithms that search a generalized increasing cost tree.
@@
 	The railway company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about matters like infrastructure expansion.
-	Mulderij et al.
-\cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding such upper-bounds using an approach analogous to that outlined above.
-	For this to succeed, a way to optimally solve MAPFM instances is needed.
+\cite{mulderij2020} proposes the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding such upper-bounds using an approach analogous to that outlined above.
+	For this to succeed, a way to optimally solve MAPFM instances is needed, where optimal is defined as minimizing the Sum of Individual Costs (SIC) objective.
 
-	Comparatively, little research has been done on MAPFM and solving MAPFM optimally.
-	The Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} is one of the few existing approaches to optimally solve this more general problem along with the somewhat similar one described in \cite{henkel2019}.
-	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search.
-It should be noted that this method minimizes the makespan and not the sum of individual costs (SIC) which is the objective used in this work, meaning that non-trivial modifications to CBM are needed to minimize SIC.
-	The successful application of CBS to solving MAPFM begs the question: \textit{can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM algorithm?}
+	Little to no research has been done on MAPFM and solving it optimally.
+For MAPFM with a makespan objective instead of SIC, known as the combined  target-assignment  and  path-finding (TAPF) problem, there is the Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} and a similar approach described in \cite{henkel2019}.
+Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework; in the low-level search, the connection between anonymous MAPF problems and max-flow problems (as discussed in \cite{yu2013}) is exploited to plan single teams in polynomial time.
+
+	The experiments reported in \cite{ma2016} indicate that this method scales very well as the number of agents and the sizes of teams increase; however, because only 10\% of tiles is blocked in some of the grid maps they use and despite the fact that CBM performance on Kiva\cite{wurman2007} instances is also discussed, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios as included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.
+	Nonetheless, the successful application of CBS to solving TAPF begs the question: \textit{can MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} serve as the basis for a MAPFM algorithm?}
 
@@
 	\end{wrapfigure}
-	This work is the outcome of a search for algorithms for optimally solving MAPFM based on ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a project in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
+	This work is the outcome of a search for algorithms which optimally solve MAPFM based on ICTS \footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a study in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
 Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as a subroutine, the other based on modifications to the ICT structure and its search.
-One exhaustive ICTS algorithm is compared to algorithms based on CBM\cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} respectively to put ICTS methods for MAPFM into a broader context.
+One exhaustive ICTS algorithm is compared to algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} respectively to put ICTS methods for MAPFM into a broader context.
 
@@
 	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
-On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods like Jump Point Search\cite{harabor2011} are used to speed up the search.
+On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods such as Jump Point Search\cite{harabor2011} are used to speed up the search.
 In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
@@
 	Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$.
-Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution, similarly defined as for MAPF.
+Within each team $t_i$, agents $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution, similarly defined as for MAPF.
 
@@
 This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent.
-For $a_i$ with a target cost $c_i$ (from cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents.
+For $a_i$ with a target cost $c_i$ (from the cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents.
 Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations \cite{sharon2011}.
@@
 	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals.
-Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the instance, with $C_m = \infty$ for unfeasible $m$.
+Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the instance, with $C_m = \infty$ for infeasible $m$.
 In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
@@
 With $C_m$ denoting the optimal SIC for matching $m$, this effort can be expressed as
-	\[\Delta_{m,bounded} = \min(B_m,C_m) - C^*_m = B_{m+1} - C^*_m\]
-	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,bounded}})$.
-	If $B_m < C^*_m$, only the root node will be generated to determine this so $\Delta_{m,bounded} = 0$.
-	Using this, the number of ICT nodes searched in total becomes $\mathcal{O}(\sum_m k^{\Delta_{m,bounded}})$.
+	\[\Delta_{m,\text{bounded}} = \min(B_m,C_m) - C^*_m = B_{m+1} - C^*_m\]
+	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,\text{bounded}}})$.
+	If $B_m < C^*_m$, only the root node will be generated to determine this so $\Delta_{m,\text{bounded}} = 0$.
+	Using this, the number of ICT nodes searched in total becomes $\mathcal{O}(\sum_m k^{\Delta_{m,\text{bounded}}})$.
 	\subsubsection{Ordered enumeration}
@@
 		\label{monotonicity}
-		In bounded exhaustive search using ICTS, solving the matchings in increasing order of root SIC makes the effort $\Delta_{m,bounded}$ monotonically non-increasing as a function of $m$.
+		In bounded exhaustive search using ICTS, solving the matchings in increasing order of root SIC makes the effort $\Delta_{m,\text{bounded}}$ monotonically non-increasing as a function of $m$.
 	\end{property}
@@
 Therefore
-		\[B_{m+t+1} - C^*_{m+t}\leq B_{m+1} - C^*_m\implies \Delta_{m+t,bounded} \leq \Delta_{m,bounded}\]
+		\[B_{m+t+1} - C^*_{m+t}\leq B_{m+1} - C^*_m\implies \Delta_{m+t,\text{bounded}} \leq \Delta_{m,\text{bounded}}\]
 	\end{proof}
@@
 	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals.
-By following a BFS-based approach, with all team goals being goals in the search and in turn endpoints from which, using the time-expanded graph, the MDD was generated that is used in the low-level search, agent MDDs can be made to represent all possible paths of a set length to any matching goal.
+By following a BFS-based approach, with all team goals being goals in the search and in turn endpoints from which, using the time-expanded graph, the MDD is generated that is used in the low-level search, agent MDDs can be made to represent all possible paths of a set length to any matching goal.
 	\begin{wrapfigure}{R}{.35\textwidth}
@@
 	Because MAPFM lies on the fringe of pathfinding research, no standard benchmark exists.
-For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge.
+For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was already a challenge computationally.
 This observation informed the creation of a map generator by the author of \cite{jong2021} with various parameters.
@@
 
-	The first experiments were performed on an Intel i7-8750H hexacore operating at 2.2GHz with 16GiB of memory. For each setting, a fixed subset of 50 out of 200 maps were used.
+	The first experiments were performed on an Intel i7-8750H hexacore operating at 2.2GHz with 16GiB of memory.
+For each setting, a fixed subset of 50 out of 200 maps were used.
+Hyperthreading was used in experiments, but because agent-settings were solved in sequence as batches, it is expected that this has affected experimental outcomes equally.
 
@@
 
-	All algorithms are implemented in Python 3 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine.
-Nonetheless, the comparison is here a bit more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.
+	All algorithms are implemented in Python 3.9 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine.
+Nonetheless, the comparison in this experiment is more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.
 
@@
 Following the results reported in \cite{ma2016}, it is expected that as the number of teams approaches $k$, CBM performance will deteriorate and thus become more similar to the results for exhaustive methods here reported.
+As CBM is based on CBS, scenarios such as mazes with even more obstacles and potentially conflicts would also be interesting to consider in comparison of CBM to the exhaustive methods.
 	%	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.

### 2021-06-21 docs/paper.tex
Improved abstract and introduction, added emails

@@
 \usepackage{geometry}
+\usepackage{inputenc}
+\usepackage{csquotes}
 \usepackage{hyperref}
-\usepackage{inputenc}
 \geometry{verbose,tmargin=3.5cm,bmargin=4cm,lmargin=3.8cm,rmargin=3.8cm}
@@
 
-	\title{Multi-Agent Path Finding with Matching using Increasing Cost Tree Search}
-
-	\author{Thom van der Woude\and Jesse Mulderij\and Mathijs de Weerdt}
-	\date{\today}
+	\title{Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search}
+	\author{
+		Thom van der Woude$^1$\and
+		Jesse Mulderij$^1$\and
+		Mathijs de Weerdt$^1$\\
+	}
+	\date{%
+		$^1$TU Delft\\
+		t.b.vanderwoude@student.tudelft.nl\\\{j.mulderij, m.m.deweerdt\}@tudelft.nl\\[2ex]
+		\today
+	}
 
@@
 	\begin{abstract}
-		Both the assignment problem and the multi-agent pathfinding problem are common problems in the fields of robotics and transportation.
+		\noindent Both the assignment problem and the multi-agent pathfinding problem are common problems in the fields of robotics and transportation.
 The joint problem of multi-agent pathfinding extended with the assignment of goals to agents, matching, is something that has not been studied much; few methods exist today that solve it.
-In this work, two types of algorithms based on the Increasing Cost Tree Search algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem: exhaustive algorithms that reduce the problem to solving many MAPF problems using regular Increasing Cost Tree Search, and algorithms that search a generalized increasing cost tree.
-These are compared to each other experimentally on a set of grid maps, and it is shown that exhaustive methods typically outperform the generalized ICT search.
-Lastly, an exhaustive algorithm is compared to alternative algorithms based on other multi-agent pathfinding approaches to put its performance into the broader context of algorithms for multi-agent pathfinding with matching.
+In this work, two types of algorithms based on the Increasing Cost Tree Search (ICTS) algorithm for multi-agent pathfinding are presented that can optimally solve this joint problem: exhaustive algorithms that reduce the problem to solving many multi-agent pathfinding problems using regular ICTS, and algorithms that search a generalized increasing cost tree.
+These are compared to each other experimentally on a set of grid maps, and it is shown that exhaustive methods typically outperform the generalized ICTS.
+Lastly, an exhaustive ICTS algorithm is compared to alternative algorithms based on other multi-agent pathfinding approaches to put its performance into the broader context of algorithms for multi-agent pathfinding with matching.
 	\end{abstract}
@@
 	The railway company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about matters like infrastructure expansion.
-\cite{mulderij2020} proposes the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding such upper-bounds using an approach analogous to that outlined above.
+\cite{mulderij2020} proposes the multi-agent pathfinding (MAPF) problem, as described in \cite{stern2019}, extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding such upper-bounds using an approach analogous to that outlined above.
 	For this to succeed, a way to optimally solve MAPFM instances is needed, where optimal is defined as minimizing the Sum of Individual Costs (SIC) objective.
 
-	Little to no research has been done on MAPFM and solving it optimally.
-For MAPFM with a makespan objective instead of SIC, known as the combined  target-assignment  and  path-finding (TAPF) problem, there is the Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} and a similar approach described in \cite{henkel2019}.
+	To date, no research has been done on MAPFM.
+For MAPFM with a makespan objective instead of SIC, known as the combined target-assignment and pathfinding (TAPF) problem, there is the Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} and a similar approach described in \cite{henkel2019}.
 Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework; in the low-level search, the connection between anonymous MAPF problems and max-flow problems (as discussed in \cite{yu2013}) is exploited to plan single teams in polynomial time.
@@
 This is because from each family of algorithms one of the best performing algorithms was chosen, which always was such an exhaustive method as opposed to a generalization of the base algorithm to MAPFM (ICTS-m in this work).
-A*+ID+OD and EPEA* also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver.
+A*+ID+OD and EPEA * also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver.
 Hypothetically, this could explain why both outperform the methods using just sorted exhaustive matching in maps with 75\% wall and 3 teams (\ref{fig:r-75-3-p}); this difference is not quite as clear in the remaining scenarios shown in Figure \ref{fig:r-probs} however.

### 2021-06-22 docs/paper.tex
Processed Jaap's feedback, added experimental data for simple pruning variant

@@
 	\author{
-		Thom van der Woude$^1$\and
-		Jesse Mulderij$^1$\and
-		Mathijs de Weerdt$^1$\\
+		Thom van der Woude$^1$\\[2ex]
+		Supervisors: Jesse Mulderij$^1$ Mathijs de Weerdt$^1$
 	}
@@
 	The experiments reported in \cite{ma2016} indicate that this method scales very well as the number of agents and the sizes of teams increase; however, because only 10\% of tiles is blocked in some of the grid maps they use and despite the fact that CBM performance on Kiva\cite{wurman2007} instances is also discussed, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios as included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.
-	Nonetheless, the successful application of CBS to solving TAPF begs the question: \textit{can MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} serve as the basis for a MAPFM algorithm?}
+	Nonetheless, the successful application of CBS to solving TAPF begs the question: \textit{can MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} serve as the basis for a MAPFM algorithm?}
 
@@
 	This work is the outcome of a search for algorithms which optimally solve MAPFM based on ICTS \footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a study in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
-Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as a subroutine, the other based on modifications to the ICT structure and its search.
-One exhaustive ICTS algorithm is compared to algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} respectively to put ICTS methods for MAPFM into a broader context.
+Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as a subroutine, the other based on modifications to the Increasing Cost Tree (ICT) structure and its search.
+One exhaustive ICTS algorithm is compared to algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} to put ICTS methods for MAPFM into a broader context.
 
@@
 Formally, a MAPF instance can be described as follows.
-Let $G = (V,E)$ be an undirected connected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles.
+Let $G = (V,E)$ be an undirected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles.
 Let there be $k$ agents $a_1,\ldots,a_k$ with starting locations $s_1,\ldots,s_k$ and goals $g_1,\ldots,g_k$.
-For each agent $a_i$, a path $\pi_i$ from $s_i$ to $g_i$ is to be found such that all agents paths $\pi_i$ taken together are non-conflicting and therefore are a solution.
-In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts (and thus no edge conflicts) and no edge conflicts, as shown in Figure \ref{fig:conflicts}.
+For each agent $a_i$, a path $\pi_i$ from $s_i$ to $g_i$ is to be found such that all agents' paths $\pi_i$ taken together are non-conflicting and therefore are a solution.
+In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts and no edge conflicts, as shown in Figure \ref{fig:conflicts}.
 Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$.
@@
 	With the multi-agent pathfinding problem defined, the matching extension of MAPF (MAPFM) that is the subject of this paper can be described.
-The ICTS algorithm for MAPF and possible matching extensions of ICTS will be discussed in Section \ref{section:icts-matching}.
 
 	Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$.
-Within each team $t_i$, agents $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution, similarly defined as for MAPF.
+Within each team $t_i$, agents $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched with goals, for each agent $a_j^i$ matched with $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents' paths taken together are non-conflicting and therefore make up a solution, similarly defined as for MAPF.
 
@@
 	\label{section:icts-matching}
-	Taking ICTS for MAPF as starting point, two methods to use ICTS for MAPFM were identified.
+	In this section, taking ICTS for MAPF as a starting point, two methods to use ICTS for MAPFM are described.
 The first method relies on a reduction from MAPFM to repeated MAPF: an optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found.
-In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
-First, ICTS for MAPF and some common variants will be described.
-Next, derived MAPFM algorithms are introduced and properties of these algorithms and some variants are discussed.
-In Section \ref{experiments}, these will be compared experimentally.
+In the second method, the ICT search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
 	\subsection{Increasing Cost Tree Search}
@@
 	\subsubsection{Top-level search}
-	In the top-level search, all possible cost vectors for a given SIC are evaluated by searching an Increasing Cost Tree as depicted in \ref{fig:ict}, starting from $C^* = \sum_i c^*_i$ corresponding to a single root cost vector $(c^*_1,c^*_2,\ldots,c^*_k)$.
+	In the top-level search, all possible cost vectors for a given SIC are evaluated by searching an Increasing Cost Tree as depicted in Figure \ref{fig:ict}, starting from $C^* = \sum_i c^*_i$ corresponding to a single root cost vector $(c^*_1,c^*_2,\ldots,c^*_k)$.
 This root has $k$ children $(c^*_1 + 1,c^*_2,\ldots,c^*_k),(c^*_1,c^*_2 + 1,\ldots,c^*_k),\ldots,(c^*_1,c^*_2,\ldots,c^*_k + 1)$ all of cost $C = C^* + 1$.
@@
 This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent.
-For $a_i$ with a target cost $c_i$ (from the cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents.
+For agent $a_i$ with a target cost $c_i$ (from the cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents.
 Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations \cite{sharon2011}.
@@
 	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs.
-Note that the second agent staying at node D after completing the path is modelled in its MDD also to ensure that the place remains blocked.
+Note that the second agent staying at node D after completing the path is also modelled in its MDD to ensure that the place remains blocked.
 
@@
 In \ref{fig:mdds}, a vertex conflict occurs and therefore this joint child can be removed from the MDD.
-If a $(B,A)$ node would be generated by the same root, $(A,B)$, this would similarly be an edge conflict and hence $(B,A)$ would also be removed from the joint MDD $MDD_{1,2}^{c_1,c_2}$.
+If a $(B,A)$ node would be generated by the same root, $(A,B)$, this would be an edge conflict and hence $(B,A)$ would also be removed from the joint MDD $MDD_{1,2}^{c_1,c_2}$.
 In the next layer, the process repeats with multiple parent nodes.
@@
 	In practice, joint MDDs are not explicitly constructed but instead, a depth-first search is used to search joint MDDs.
-This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
+This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD than is necessary for finding a solution, which can get rather large.
 	\subsubsection{ICTS with Independence Detection}
@@
 	In \cite{sharon2011}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work.
-All work by taking $j < k$ and applying the described method to each possible combination of $j$ out of $k$ agents.
-If no solution exists for any such combination, the full $k$-agent low-level search is not triggered.
-The two basic pruning methods are as follows.
+These methods rely on the fact that if no solution exists for any combination of $j$ out of $k$ agents with $j < k$, no solution exists for all $k$ agents.
+If any such combination is found for a node, there is no need to search the $k$-agent MDD so the next ICT node can be considered.
+The three pruning methods are as follows.
 	\begin{enumerate}
-		\item Simple pruning: the $j$-agent MDD is searched using DFS for a solution.
-		\item Enhanced pruning: the $j$-agent MDD is searched using BFS and when children are generated, for each agent, all children that do not appear in any unified node are removed from the MDD.
+		\item Simple pruning: for all combinations of $j$ out of $k$ agents, the $j$-agent MDD is searched using DFS for a solution.
+		\item Enhanced pruning: for all combinations of $j$ out of $k$ agents, the $j$-agent MDD is searched using BFS and when children are generated, for each agent, all children that do not appear in any unified node are removed from the MDD.
 In \ref{fig:mdds}, the $C$ node of $MDD_1$ would be removed as it cannot be unified with any node of $MDD_2$ at that level.
+		\item Repeated enhanced pruning: the enhanced pruning procedure is repeated until a fixpoint is reached, which is when no child node is removed from any of the agent MDDs in an iteration.
+This was not used in this work.
 	\end{enumerate}
-	In addition, repeated enhanced pairwise pruning is described in which the enhanced pruning procedure is repeated for all combinations until a fixpoint is reached, which is when no child node is removed from any of the agent MDDs in an iteration.
-This was not used in this work.
-
-	The full ICT-search algorithm including a pruning step is described by Algorithm \ref{icts-algo}.
+	The full ICTS algorithm including a pruning step is described by Algorithm \ref{icts-algo}.
 It is reproduced from \cite{sharon2011} for completeness.
 As noted before, this procedure can be used for planning groups in Algorithm \ref{id-algo}.
-In this work, triple-pruning was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2011} is that this often outperforms other variants.
+In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2011} is that this often outperforms other variants.
 	\begin{algorithm}
@@
 	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals.
-Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the instance, with $C_m = \infty$ for infeasible $m$.
+Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the MAPFM instance, with $C_m = \infty$ for infeasible $m$.
 In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
 	\subsubsection{Bounded search}
-	Once the first solution is found with cost $C$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched.
+	Once a solution is found for matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched.
 Formally, let $B_0 = \infty$ represent the initial SIC bound of the ICT search.
@@
 	\label{ordered-enum}
-	To reduce the total effort as much as possible, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$.
+	To reduce the total effort, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$.
 In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}.
@@
 	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals.
-By following a BFS-based approach, with all team goals being goals in the search and in turn endpoints from which, using the time-expanded graph, the MDD is generated that is used in the low-level search, agent MDDs can be made to represent all possible paths of a set length to any matching goal.
+To do this, the MDD construction following the breadth-first search has to be changed: each goal becomes an endpoint from which paths to the start node are traced, resulting in an MDD with one start node and one or more terminal nodes.
 	\begin{wrapfigure}{R}{.35\textwidth}
@@
 All four agents match the colour of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$.
-The optimal solution however is, numbering the agents clockwise, $(1,3,3,3)$ with SIC $10$, meaning that $\Delta = 6$.
+The optimal solution however is $(1,3,3,3)$ with SIC $10$ numbering the agents clockwise, meaning that $\Delta = 6$.
 It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed.
@@
 	\subsection{Optimizations}
-	To improve both types of algorithms, some optimizations were found that can be used to speed up the search. These are here motivated. 
+	To improve both types of algorithms, some optimizations were found that can be used to speed up the search.
 	\subsubsection{Bounds in ID}
@@
 	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed.
-In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM developed within the peer group.
+In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}.
 This comparison data originates in \cite{donszelmann2021}.
@@
 	\end{enumerate}
-	For each of these types, maps were generated with between $1$ and $25$ agents either all in the same team or partitioned into $3$ teams as fairly as possible.
+	For each of these types, maps were generated with between $1$ and $25$ agents either all in the same team or partitioned into $3$ teams as evenly as possible.
 When solving the instances, for each combination of map-type and number of teams, the number of agents was increased until 0\% of instances could be solved within a timeout of 120s, at which point no more data was recorded for greater numbers of agents.
 
-	The first experiments were performed on an Intel i7-8750H hexacore operating at 2.2GHz with 16GiB of memory.
+	The first experiments were performed on a 2.2GHz Intel i7-8750H hexacore with 16GiB of memory.
 For each setting, a fixed subset of 50 out of 200 maps were used.
@@
 	All algorithms are implemented in Python 3.9 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine.
-Nonetheless, the comparison in this experiment is more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.
+The comparison in this experiment is more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.
 
@@
 The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
-This explains why no speedup is seen, as ICTS-m between and ICTS-m+ID.
+This explains why no speedup is seen, as  between ICTS-m and ICTS-m+ID.
 Another factor is that if all agents belong to the same team, it is somewhat unlikely that there will a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.
@@
 This is because from each family of algorithms one of the best performing algorithms was chosen, which always was such an exhaustive method as opposed to a generalization of the base algorithm to MAPFM (ICTS-m in this work).
-A*+ID+OD and EPEA * also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver.
-Hypothetically, this could explain why both outperform the methods using just sorted exhaustive matching in maps with 75\% wall and 3 teams (\ref{fig:r-75-3-p}); this difference is not quite as clear in the remaining scenarios shown in Figure \ref{fig:r-probs} however.
+A*+ID+OD and EPEA* also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver.
+The initial groups are here the teams, which is why in single team scenarios (Subfigures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}) matching ID has no effect.
+Hypothetically, matching ID could could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and 3 teams (\ref{fig:r-75-3-p}).
 
@@
 Following the results reported in \cite{ma2016}, it is expected that as the number of teams approaches $k$, CBM performance will deteriorate and thus become more similar to the results for exhaustive methods here reported.
-As CBM is based on CBS, scenarios such as mazes with even more obstacles and potentially conflicts would also be interesting to consider in comparison of CBM to the exhaustive methods.
 	%	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
@@
 Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive ICTS algorithms consistently outperform the ICTS-m based algorithms.
-Compared to the SIC-adaptation of the CBM method \cite{baauw2021}, it was seen that exhaustive methods generally perform quite poorly if there are fewer teams and fewer obstacles, while being competitive once teams grow smaller and maps become more constrained.
+Compared to the SIC-adaptation of the CBM method \cite{baauw2021}, it was seen that exhaustive methods generally perform relatively poorly if there are fewer teams and fewer obstacles, while being competitive once teams grow smaller and maps become more constrained.
 Delineating under which conditions exhaustive methods outperform CBM and vice versa is something for further research.

### 2021-06-22 src/bench.py

@@ -206,11 +206,11 @@ if __name__ == "__main__":
         #     sort_matchings=False,
         # ),
         SolverConfig(
-            name="Exh+S+C+B+O",
+            name="Exh+S+B+O",
             combs=3,
             prune=True,
             enhanced=False,
-            pruned_child_gen=True,
+            pruned_child_gen=False,
             id=False,
             conflict_avoidance=False,
             enumerative=True,
@@ -218,18 +218,31 @@ if __name__ == "__main__":
             sort_matchings=True,
             budget_search=True,
         ),
-        SolverConfig(
-            name="ICTS-m+ID+S+C",
-            combs=3,
-            prune=True,
-            enhanced=False,
-            pruned_child_gen=True,
-            id=True,
-            conflict_avoidance=True,
-            enumerative=False,
-            debug=False,
-            sort_matchings=False,
-        ),
+        # SolverConfig(
+        #     name="Exh+S+C+B+O",
+        #     combs=3,
+        #     prune=True,
+        #     enhanced=False,
+        #     pruned_child_gen=True,
+        #     id=False,
+        #     conflict_avoidance=False,
+        #     enumerative=True,
+        #     debug=False,
+        #     sort_matchings=True,
+        #     budget_search=True,
+        # ),
+        # SolverConfig(
+        #     name="ICTS-m+ID+S+C",
+        #     combs=3,
+        #     prune=True,
+        #     enhanced=False,
+        #     pruned_child_gen=True,
+        #     id=True,
+        #     conflict_avoidance=True,
+        #     enumerative=False,
+        #     debug=False,
+        #     sort_matchings=False,
+        # ),
         # SolverConfig(
         #     name="ICTS-m+E",
         #     combs=3,

### 2021-06-22 src/ictsm/solve.py
Reduced size of result plots to fit within margins

@@ -15,11 +15,11 @@ def solve_api_enum(problem: Problem) -> Solution:
 
 def solve(problem: Problem) -> Tuple[Optional[Solution], List[int], int,Optional[int]]:
     config = SolverConfig(
-        combs=3,
+        combs=2,
         prune=True,
         enhanced=False,
         pruned_child_gen=True,
-        id=True,
+        id=False,
         conflict_avoidance=True,
         enumerative=False,
         debug=True,
@@ -36,7 +36,7 @@ def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], 
         conflict_avoidance=True,
         enumerative=True,
         sort_matchings=True,
-        debug=False,
+        debug=True,
         budget_search=True,
     )
     return Solver(config, problem)()

### 2021-06-22 docs/paper.tex
Reduced size of result plots to fit within margins
Optimized aspect ratio of plots

@@
-\documentclass[english,10pt]{article}
+\documentclass[english]{article}
 \usepackage{geometry}
@@
 \geometry{verbose,tmargin=3.5cm,bmargin=4cm,lmargin=3.8cm,rmargin=3.8cm}
+\newcommand\graphwidth{0.49\textwidth}
 \usepackage[backend=biber,style=ieee]{biblatex}
@@
 
-	To date, no research has been done on MAPFM.
+	Little to no research has been done on MAPFM and solving it optimally.
 For MAPFM with a makespan objective instead of SIC, known as the combined target-assignment and pathfinding (TAPF) problem, there is the Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} and a similar approach described in \cite{henkel2019}.
@@
 It should be noticed that in the latter, the recorded runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
-	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
+	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
 	\begin{figure*}[t]
 		\centering
-		\begin{subfigure}{0.44\textwidth}
+		\begin{subfigure}{\graphwidth}
 			\centering
@@
 		\end{subfigure}
-		\begin{subfigure}{0.44\textwidth}
+		\begin{subfigure}{\graphwidth}
 			\centering
@@
 		\centering
-		\begin{subfigure}{0.44\textwidth}
+		\begin{subfigure}{\graphwidth}
 			\centering
@@
 Another approach to explore would be hybridized approaches that enumerate partially constrained MAPFM instances which can be solved using any MAPFM solver.
-In this way, the benefit of the successive bounding of the search could be exploited and by carefully picking which agents to constrain, these constrained MAPFM instances could potentially be made relatively easy.
+In this way, the benefit of the successive bounding of the search could be exploited and by carefully selecting agents to constrain, these constrained MAPFM instances could potentially be made relatively easy.
 
@@
 	\printbibliography
-	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
+	\newpage
 	\begin{figure*}[t]
 		\centering
-		\begin{subfigure}{0.44\textwidth}
+		\begin{subfigure}{\graphwidth}
 			\centering

### 2021-06-22 docs/paper.tex
Vectorized counterexample ICT graphic

@@
 	\subsubsection{Bounded search}
-	Once a solution is found for matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched.
+	Once a solution is found for a 0-matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched.
 Formally, let $B_0 = \infty$ represent the initial SIC bound of the ICT search.

### 2021-06-22 docs/paper.tex
Corrected typo

--- 2021-06-22 docs/paper.tex
@@
 	\subsubsection{Bounded search}
-	Once a solution is found for matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched.
+	Once a solution is found for a matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched.
 Formally, let $B_0 = \infty$ represent the initial SIC bound of the ICT search.

### 2021-06-22 docs/paper.tex
Corrected some errors mentioned in feedback

@@
 
-	Little to no research has been done on MAPFM and solving it optimally.
+	Comparatively little research has been done on MAPFM and solving it optimally.
 For MAPFM with a makespan objective instead of SIC, known as the combined target-assignment and pathfinding (TAPF) problem, there is the Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} and a similar approach described in \cite{henkel2019}.
@@
 	In Increasing Cost Tree Search\cite{sharon2011}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC.
-This is done by searching for cost vectors corresponding to increasing SIC on the top level and searching for non-conflicting path combinations (solutions) for each cost vector on the bottom level.
+This is done by searching for cost vectors corresponding to increasing SIC at the top level and searching for non-conflicting path combinations (solutions) for each cost vector at the bottom level.
 
@@
 Searching this ICT breadth-first corresponds to evaluating all possible cost vectors corresponding to increasing cost $C$ starting with $C^*$, guaranteeing optimality of a found solution.
-The number of cost vectors evaluated when searching up to nodes of cost $C^* + \Delta$ is $\mathcal{O}(k^\Delta)$.
-Node evaluation is done by a low-level search that searches for a solution $(\pi_1,\ldots,\pi_k)$ corresponding to the node costs $(c_1,\ldots,c_k)$.
+When searching up to  cost $C^* + \Delta$, $\mathcal{O}(k^\Delta)$ cost vectors are evaluated.
+Node evaluation corresponds to performing a low-level search for a solution $(\pi_1,\ldots,\pi_k)$ corresponding to the node cost vector $(c_1,\ldots,c_k)$.
 
@@
 Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the MAPFM instance, with $C_m = \infty$ for infeasible $m$.
-In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
+In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be infeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
 	\subsubsection{Bounded search}
@@
 	\subsubsection{Approximate ordered enumeration}
-	In practice, it is difficult enumerate all matchings in increasing order of root SIC.
+	In practice, it is difficult to enumerate all matchings in increasing order of root SIC.
 Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time; however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking).
@@
 Few changes to ICTS were necessary to accommodate for matching in this increasing cost tree scheme.
-Specifically, the ICT root generation and the MDD generation as described in \ref{icts} had to be changed.
+Specifically, the ICT root generation and the MDD generation as described in Subsection \ref{icts} had to be changed.
 	\subsubsection{Root generation for matching}
@@
 By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed.
-Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that enhanced pruning combined with child pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making this pruning strategy suboptimal.
+Notice that none of the nodes with SIC 16 in this ICT is a solution, meaning that enhanced pruning combined with child pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making this pruning strategy suboptimal.
 	\end{proof}
@@
 In this, the research has succeeded, but the scalability of the algorithms leaves something to be desired.
-Exhaustive methods, like those discussed in detail in \ref{exhaustive}, cannot be expected to scale well as teams grow larger due to their complexity, no matter what optimizations are put in place.
+Exhaustive methods, like those discussed in detail in Subsection \ref{exhaustive}, cannot be expected to scale well as teams grow larger due to their complexity, no matter what optimizations are put in place.
 Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive ICTS algorithms consistently outperform the ICTS-m based algorithms.

### 2021-06-23 docs/dump.tex
Implemented personal feedback (except future work note)

@@
 
+		each give (loose) upper bounds on the optimal solution cost for each instance.
+
+		so if a solution is found its cost is an upper bound for the optimal solution cost; however, if no solution can be found,
+
+		; the optimal solution cost cannot generally be known, 
+		While solutions to instances found using heuristics are assumed to be suboptimal, it is not possible to estimate by how much
+
+		As a result, found solutions are assumed to be suboptimal, they currently cannot
+
+		Still, such methods will not find a solution to every instance in reasonable time,
+		Heuristic solutions to instances defined for a set shunting yard can be said to characterise a lower bound on the capacity of the shunting yard.
+
+		This is because heuristic methods are suboptimal and not guaranteed to be complete, meaning that no solution may be found for a feasible instance and if one is found its solution cost might far exceed the optimal cost.
+
+		---
+			this leaves railway companies in the dark about
+
+		when shunting infrastructure has to be exp whether shunting infrastructure has to be expanded to accomodate for increasing
+
+		As a result, because current upper-bounds for capacity are highly optimistic,
+
+		meaning that it is hard for railway companies to
+
+		As optimal solution costs cannot be known \cite{geiger2018}, 
+		The railway company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about matters like infrastructure expansion. 
 	\paragraph{Old}

### 2021-06-23 docs/paper.tex
Implemented personal feedback (except future work note)

@@
 	As was shown by Geiger et al.\cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances.
-	Such methods are suboptimal and heuristic solutions to instances defined for a set shunting yard can be said to characterise a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper bound for the optimal solution cost.
-	The railway company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about matters like infrastructure expansion.
-\cite{mulderij2020} proposes the multi-agent pathfinding (MAPF) problem, as described in \cite{stern2019}, extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding such upper-bounds using an approach analogous to that outlined above.
+	Such methods are suboptimal so given a TUSS instance, a found heuristic solution gives a (loose) upper bound for the optimal solution cost; solving an instance also shows its feasibility, although there might be feasible instances for which no heuristic solution is found.
+	By defining instances for a set shunting yard, heuristic methods can be used to characterise lower-bounds on the capacity of the yard in terms of both instance feasibility and solution cost.
+	Because the quality of found heuristic solutions cannot be estimated \cite{mulderij2020}, it cannot be known how close such lower-bounds for yard capacity are to the true capacity. 
+	Combined with the fact that current upper-bounds for capacity are highly optimistic, this makes it difficult for rail companies to decide when to expand their shunting infrastructure.
+
+	Mulderij et al.
+propose the multi-agent pathfinding (MAPF) problem, as described in \cite{stern2019}, extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding better upper-bounds using an approach analogous to that outlined above \cite{mulderij2020}.
 	For this to succeed, a way to optimally solve MAPFM instances is needed, where optimal is defined as minimizing the Sum of Individual Costs (SIC) objective.
@@
 For MAPFM with a makespan objective instead of SIC, known as the combined target-assignment and pathfinding (TAPF) problem, there is the Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} and a similar approach described in \cite{henkel2019}.
-Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework; in the low-level search, the connection between anonymous MAPF problems and max-flow problems (as discussed in \cite{yu2013}) is exploited to plan single teams in polynomial time.
+Ma and Koenig's method uses the Meta-Agent variant of CBS \cite{sharon2015} as a high-level search framework; in the low-level search, single teams are planned in polynomial time as constrained anonymous MAPF instances using a max-flow approach \cite{yu2013}.
 
-	The experiments reported in \cite{ma2016} indicate that this method scales very well as the number of agents and the sizes of teams increase; however, because only 10\% of tiles is blocked in some of the grid maps they use and despite the fact that CBM performance on Kiva\cite{wurman2007} instances is also discussed, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios as included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.
+	The experiments reported in \cite{ma2016} indicate that this method scales well as the number of agents and the sizes of teams increase; although in addition to grid instances with 10\% of tiles being blocked, Kiva \cite{wurman2007} instances are also solved, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios, such as those included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.
 	Nonetheless, the successful application of CBS to solving TAPF begs the question: \textit{can MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} serve as the basis for a MAPFM algorithm?}
@@
 	\end{wrapfigure}
-	This work is the outcome of a search for algorithms which optimally solve MAPFM based on ICTS \footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a study in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
+	This work is the outcome of a search for algorithms that optimally solve MAPFM based on ICTS \footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a study in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
 Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as a subroutine, the other based on modifications to the Increasing Cost Tree (ICT) structure and its search.
@@
 
-	\section{Multi-agent pathfinding with matching} % Problem description
+	\section{Multi-agent Pathfinding with Matching} % Problem description
 	\label{mapfm}
-	The MAPFM problem is an extension of MAPF, a well-studied problem.
+	Multi-agent pathfinding with matching is a generalization of multi-agent pathfinding, the problem of finding paths for multiple agents without any conflicts. 
+	\subsection{Multi-agent pathfinding}
 	Formally, a MAPF instance can be described as follows.
@@
 	\end{itemize}
-	In this work, following the definition of the TUSS relaxation in \cite{mulderij2020}, an optimal solution is defined as having minimal SIC. Note that $\sum_i c_i \geq \sum_i c^*_i$.
+	In this work, following the definition of the TUSS relaxation in \cite{mulderij2020}, an optimal solution is defined as having minimal SIC.
 	\begin{wrapfigure}[10]{R}{.35\textwidth}
@@
 	\end{wrapfigure}
+
 	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
@@
 	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs.
-Note that the second agent staying at node D after completing the path is also modelled in its MDD to ensure that the place remains blocked.
+The second agent staying at node D after completing the path is also modelled in its MDD to ensure that the place remains blocked.
 
@@
 	\end{enumerate}
-	The full ICTS algorithm including a pruning step is described by Algorithm \ref{icts-algo}.
+	The full ICTS algorithm including a pruning step as described above is given by Algorithm \ref{icts-algo}.
 It is reproduced from \cite{sharon2011} for completeness.
-As noted before, this procedure can be used for planning groups in Algorithm \ref{id-algo}.
 In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2011} is that this often outperforms other variants.
@@
 By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed.
-Notice that none of the nodes with SIC 16 in this ICT is a solution, meaning that enhanced pruning combined with child pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making this pruning strategy suboptimal.
+None of the nodes with SIC 16 in this ICT is a solution, meaning that enhanced pruning combined with child pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making this pruning strategy suboptimal.
 	\end{proof}
@@
 	The first experiments were performed on a 2.2GHz Intel i7-8750H hexacore with 16GiB of memory.
-For each setting, a fixed subset of 50 out of 200 maps were used.
-Hyperthreading was used in experiments, but because agent-settings were solved in sequence as batches, it is expected that this has affected experimental outcomes equally.
+For each setting, a fixed subset of 50 out of 200 maps was used.
+%Hyperthreading was used in experiments, but because agent-settings were solved in sequence as batches, it is expected that this has affected experimental outcomes equally.
 
@@
 The initial groups are here the teams, which is why in single team scenarios (Subfigures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}) matching ID has no effect.
-Hypothetically, matching ID could could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and 3 teams (\ref{fig:r-75-3-p}).
+Hypothetically, matching ID could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and 3 teams (\ref{fig:r-75-3-p}).
 

### 2021-06-23 src/ictsm/solve.py

@@ -30,7 +30,7 @@ def solve_enum_sorted(problem: Problem) -> Tuple[Optional[Solution], List[int], 
     config = SolverConfig(
         combs=3,
         prune=True,
-        enhanced=False,
+        enhanced=True,
         pruned_child_gen=True,
         id=True,
         conflict_avoidance=True,

### 2021-06-24 docs/paper.tex
Improved TUSS-based introduction

@@
 
-	As was shown by Geiger et al.\cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances.
-	Such methods are suboptimal so given a TUSS instance, a found heuristic solution gives a (loose) upper bound for the optimal solution cost; solving an instance also shows its feasibility, although there might be feasible instances for which no heuristic solution is found.
-	By defining instances for a set shunting yard, heuristic methods can be used to characterise lower-bounds on the capacity of the yard in terms of both instance feasibility and solution cost.
-	Because the quality of found heuristic solutions cannot be estimated \cite{mulderij2020}, it cannot be known how close such lower-bounds for yard capacity are to the true capacity. 
-	Combined with the fact that current upper-bounds for capacity are highly optimistic, this makes it difficult for rail companies to decide when to expand their shunting infrastructure.
-
+	In practical scenarios, only heuristic methods can solve TUSS instances \cite{geiger2018}.
+Such a heuristic is used at NS to determine the capacity of shunting yards, which is the number of units a yard can serve in a day.
+This is done by defining a set of instances for the yard and determining the number of units for which 95\% of instances can be solved by the heuristic within a set time-out \cite{ven2019}.
+A problem is that a subset of feasible TUSS instances is not solved by the heuristic, meaning that the found capacity can be lower than the true capacity.
+Combined with the fact that current upper-bounds for capacity are highly optimistic, this makes it difficult to decide when to expand shunting infrastructure.
 Mulderij et al.

### 2021-06-26 docs/paper.tex
Rewrote introduction

@@
 		Thom van der Woude$^1$\\[2ex]
-		Supervisors: Jesse Mulderij$^1$ Mathijs de Weerdt$^1$
+		\normalsize{Supervisors: Jesse Mulderij$^1$ Mathijs de Weerdt$^1$}
 	}
-	\date{%
+	\date{
 		$^1$TU Delft\\
@@
 	\section{Introduction}
-	The Dutch Railways company (NS) needs to clean and service their fleet of trains during the night in shunting yards so that they can properly bring passengers from A to B during the day. 
-	The problem of scheduling the trains and personnel to achieve this is called the Train Unit Shunting and Servicing (TUSS) problem \cite{mulderij2020}. 
-	It is an NP-hard problem with many different subproblems in addition to the basic train unit routing, such as the timetabling of personnel and coupling and decoupling of train units entering and leaving the yard.
-% introduce heuristics here.
+	Finding a shortest path between two vertices on a graph is a fundamental problem that appears in many contexts like GPS navigation \cite{sturtevant2010} and network routing \cite{broch1998}.
+In some applications like autonomous aircraft towing \cite{morris2016} and train unit routing in shunting yards \cite{mulderij2020}, planning agents separately can result in conflicts between agents as they follow their paths.
+To prevent such conflicts, agents have to be planned together to find a combination of non-conflicting paths.
+The problem of finding such a combination is the Multi-Agent Pathfinding (MAPF) problem \cite{stern2019}.
+In finding optimal solutions, one of two objectives is typically optimized: the makespan which is the cost of the longest path, or the Sum of Individual path Costs (SIC).
+Algorithms for optimally solving MAPF include Increasing Cost Tree Search \cite{sharon2011}, Conflict-based search \cite{sharon2015} and Branch-and-Cut-and-Price \cite{lam2019}.
 
-	In practical scenarios, only heuristic methods can solve TUSS instances \cite{geiger2018}.
-Such a heuristic is used at NS to determine the capacity of shunting yards, which is the number of units a yard can serve in a day.
-This is done by defining a set of instances for the yard and determining the number of units for which 95\% of instances can be solved by the heuristic within a set time-out \cite{ven2019}.
-A problem is that a subset of feasible TUSS instances is not solved by the heuristic, meaning that the found capacity can be lower than the true capacity.
-Combined with the fact that current upper-bounds for capacity are highly optimistic, this makes it difficult to decide when to expand shunting infrastructure.
-Mulderij et al.
-propose the multi-agent pathfinding (MAPF) problem, as described in \cite{stern2019}, extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding better upper-bounds using an approach analogous to that outlined above \cite{mulderij2020}.
-	For this to succeed, a way to optimally solve MAPFM instances is needed, where optimal is defined as minimizing the Sum of Individual Costs (SIC) objective.
+	As observed by \cite{ma2016b}, in real-world applications of MAPF such as warehouse robotics \cite{wurman2007} goals are often assigned to teams of agents instead of single agents as in standard MAPF.
+Using MAPF in such applications requires pre-assignment of goals to agents using the Hungarian Algorithm \cite{kuhn55} or similar methods, but such approaches are suboptimal as the true cost of a given matching can only be found by solving the corresponding MAPF instance.
+Ma and Koenig \cite{ma2016} formulate the joint problem of finding the optimal makespan solution across all possible matchings as the combined target-assignment and pathfinding (TAPF) problem.
+They also present the Conflict-Based Min-Cost-Flow (CBM) algorithm for solving TAPF.
 
-	Comparatively little research has been done on MAPFM and solving it optimally.
-For MAPFM with a makespan objective instead of SIC, known as the combined target-assignment and pathfinding (TAPF) problem, there is the Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} and a similar approach described in \cite{henkel2019}.
-Ma and Koenig's method uses the Meta-Agent variant of CBS \cite{sharon2015} as a high-level search framework; in the low-level search, single teams are planned in polynomial time as constrained anonymous MAPF instances using a max-flow approach \cite{yu2013}.
+	In CBM, the Meta-Agent variant of CBS \cite{sharon2015} is used as a high-level search framework; in the low-level search, single teams are planned in polynomial time as constrained anonymous MAPF instances using a max-flow approach \cite{yu2013}.
+The experimental results reported in \cite{ma2016} indicate that CBM scales well as the number of agents and the sizes of teams increase; although in addition to grid instances with 10\% of tiles being blocked, Kiva \cite{wurman2007} instances are also solved, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios, such as those included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.
 
-	The experiments reported in \cite{ma2016} indicate that this method scales well as the number of agents and the sizes of teams increase; although in addition to grid instances with 10\% of tiles being blocked, Kiva \cite{wurman2007} instances are also solved, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios, such as those included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.
-	Nonetheless, the successful application of CBS to solving TAPF begs the question: \textit{can MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} serve as the basis for a MAPFM algorithm?}
+	Nonetheless, CBS successfully being used to solve TAPF raises two questions: Can MAPF algorithms other than CBS be used to solve TAPF?
+Can CBS or other MAPF algorithms be used to solve TAPF minimizing the SIC instead of the makespan?
+For this latter problem that will be referred to as Multi-agent Pathfinding with Matching (MAPFM), no methods are described in the literature.
 
-	\begin{wrapfigure}[19]{R}{.25\textwidth}
+	This work presents two types of algorithms based on ICTS \cite{sharon2011} that optimally solve MAPFM, and is part of a study in which other algorithms in addition to ICTS were taken as starting points for MAPFM algorithms.
+Those of the first type exhaustively enumerate matchings and use a variant of ICTS as a subroutine; those of the second type are based on an extension of ICTS itself to support matching, ICTS-m.
+The properties of both classes of algorithms as well as ICTS more generally are discussed, followed by experiments in which a selection of algorithm variants is compared.
+Additionally, one exhaustive ICTS algorithm is compared to MAPFM algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014}.
+
+	%To date, methods solving TAPF and similar problems \cite{henkel2019} use CBS.
+
+	%Can other MAPF algorithms be used to solve TAPF?
+
+	%The successful application of CBS to solving TAPF begs the question: \textit{can other MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} serve as the basis for a TAPF algorithm?}
+
+	% remains the question of how multi-agent pathfinding with matching (MAPFM) minimizing the SIC
+
+	%To date, no method is described in the literature for solving a related problem: multi-agent pathfinding with matching minimizing SIC.
+
+	%the multi-agent pathfinding with matching problem minimizing SIC
+
+	%Multi-agent pathfinding with matching (MAPFM) minimizing SIC. 
+	%describe a related problem in a factory setting where agents have to first move from their start location to the start position of a task.
+
+	%In this work, a problem related to TAPF will be discussed, namely multi-agent pathfinding with matching minimizing SIC (MAPFM). This is related to the problem described by
+
+	%To date, the Task Conflict-Based Search algorithm \cite{henkel2019} based on CBS is the on
+
+	%, as well as optimal ICTS-based a
+
+	%For an analogous problem, multi-agent pathfinding with matching using the SIC objective (hereafter MAPFM)
+
+	%Henkel et al. \cite{henkel2019} describe the Task Conflict-Based Search algorithm for the
+
+	%This work is the outcome of a search for algorithms that optimally solve MAPFM based on ICTS \footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a study in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
+Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as a subroutine, the other based on modifications to the Increasing Cost Tree (ICT) structure and its search.
+One exhaustive ICTS algorithm is compared to algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} to put ICTS methods for MAPFM into a broader context.
+
+	\section{Multi-agent Pathfinding with Matching} % Problem description
+	\label{mapfm}
+	\begin{wrapfigure}[19]{r}{.25\textwidth}
 		\begin{minipage}{\linewidth}
@@
 	\end{wrapfigure}
-	This work is the outcome of a search for algorithms that optimally solve MAPFM based on ICTS \footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a study in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms.
-Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as a subroutine, the other based on modifications to the Increasing Cost Tree (ICT) structure and its search.
-One exhaustive ICTS algorithm is compared to algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} to put ICTS methods for MAPFM into a broader context.
 
-	\section{Multi-agent Pathfinding with Matching} % Problem description
-	\label{mapfm}
 	Multi-agent pathfinding with matching is a generalization of multi-agent pathfinding, the problem of finding paths for multiple agents without any conflicts. 
 	\subsection{Multi-agent pathfinding}
+
 	Formally, a MAPF instance can be described as follows.
@@
 One property of $c_i$ is that $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of $\pi^*_i$, the shortest path from $s_i$ to $g_i$ that can be computed using any optimal pathfinding algorithm.
-There are two common objectives in MAPF:
+Using this terminology, the two common objectives for MAPF can be restated as follows:
 	\begin{itemize}
-		\item The makespan: $\max_{i} c_i$
-		\item The sum of individual costs (SIC): $\sum_i c_i$
+		\item Makespan: $\max_{i} c_i$
+		\item Sum of individual costs (SIC): $\sum_i c_i$
 	\end{itemize}
-	In this work, following the definition of the TUSS relaxation in \cite{mulderij2020}, an optimal solution is defined as having minimal SIC.
+	In this work, an optimal solution is defined as having minimal SIC.
+
 	\begin{wrapfigure}[10]{R}{.35\textwidth}
@@
 		\includegraphics[width=\linewidth]{img/symmetries}
-		\caption{Symmetric paths on a 4-connected grid\cite{harabor2010}}
+		\caption{Symmetric paths on a 4-connected grid \cite{harabor2010}}
 		\label{fig:symmetries}
@@
 	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
-On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods such as Jump Point Search\cite{harabor2011} are used to speed up the search.
+On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths \cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods such as Jump Point Search \cite{harabor2011} are used to speed up the search.
 In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
@@
 
-	\section{Responsible Research}
+	\section{Reproducibility}
 	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository\footnote{\url{https://github.com/tbvanderwoude/icts-m}}.

### 2021-06-26 docs/paper.tex
Extended future work section

@@
 	In practice, it is difficult to enumerate all matchings in increasing order of root SIC.
-Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time; however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking).
+
+	Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time;
+
+	however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking).
 This means that matchings have to be exhaustively enumerated and stored in memory to sort them, but this requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
@@
 
-	Future research could also look into improving the ICTS-m method described using for instance more extensive pruning or properties of the problem such as lower-bounds on per-team solution SIC that can be computed using the Hungarian Algorithm.
-Another approach to explore would be hybridized approaches that enumerate partially constrained MAPFM instances which can be solved using any MAPFM solver.
-In this way, the benefit of the successive bounding of the search could be exploited and by carefully selecting agents to constrain, these constrained MAPFM instances could potentially be made relatively easy.
+	%\section{Future work}
+	A key idea for future research to look into is how to exploit the lower-bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55}.
+This lower-bound could be used in a branch-and-bound \cite{land1960} search of matchings.
+The most straightforward way would be to use an algorithm for MAPF at leaf nodes but algorithms for MAPFM could be used to solve (small) branches.
+Another possibility would be to use this bound to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound.
+Lower-bounding in ICTS-m could be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using a similar approach as \cite{baauw2021}.
+As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.
+
+	A related observation is that the algorithms introduced in this work do not rely on the property of agents and goals having one color.
+Both exhaustive ICTS and ICTS-m could easily be adapted to support one or more colors (teams) for each agent and goal while still guaranteeing optimality, in contrast to CBM \cite{ma2016} and its SIC adaptation \cite{baauw2021} which specifically use this property to plan single teams in polynomial time.
+Future research could study the multi-color MAPFM variant and the application of methods described in this work to this problem.
 

### 2021-06-26 docs/paper.tex
Described matching generation strategy

@@
 	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals.
-Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the MAPFM instance, with $C_m = \infty$ for infeasible $m$.
-In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be infeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
+These matchings can be enumerated by indexing the $k_i!$ permutations of goals for each team $t_i$ as $1,\ldots,k_i!$.
+Using such indexing, each $e \in \{1,\ldots,k_1!\} \times \cdots \times \{1,\ldots,k_K!\}$ corresponds to a unique combination of permutations and can be mapped to a matching $m$ assuming some fixed ordering of agents within each team.
+Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the MAPFM instance, with $C_m = \infty$ for infeasible matching $m$.
+In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ matchings to be solved or found to be infeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
 	\subsubsection{Bounded search}
@@
 	\label{ordered-enum}
-	To reduce the total effort, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$.
+	To reduce the total effort, the matchings $m$ can instead be enumerated and solved in increasing order of $C^*_m$.
 In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}.
@@
 	\subsubsection{Approximate ordered enumeration}
-	In practice, it is difficult to enumerate all matchings in increasing order of root SIC.
+	In implementation matchings were enumerated using a product of goal permutation indices as described above so they are not enumerated in increasing order of root SIC.
+As a result, to achieve this ordering, matchings have to be exhaustively enumerated and stored in memory in order to be sorted.
+This requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
 
+	%Using the 
+	%To generate matchings 
+	%In the implementation of exhaustive matching, the algorithm used to generate matchings
+	%The algorithm for generating 
+	%In the implementation of ordered enumeration as described above, matchings are not generated in increasing order of root SIC.
+As a result, to achieve this ordering, matchings have to be exhaustively enumerated and stored in memory in order to be sorted.
+This requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
+
+	%In practice, it is difficult to enumerate all matchings in increasing order of root SIC.
 Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time;
+	%[TODO]
 
-	however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking).
+	%however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking).
 This means that matchings have to be exhaustively enumerated and stored in memory to sort them, but this requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
@@
 
-	In the implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory}.
+	This is why in implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory}.
 Algorithm \ref{pq-algo} outlines the procedure.
@@
 	\label{future}
-	The goal of this research was to seek alternative approaches to solving MAPFM based on ICTS.
+	The goal of this research was to seek methods for solving MAPFM based on ICTS.
 In this, the research has succeeded, but the scalability of the algorithms leaves something to be desired.
@@
 Another possibility would be to use this bound to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound.
-Lower-bounding in ICTS-m could be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using a similar approach as \cite{baauw2021}.
+Lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using a similar approach as \cite{baauw2021}.
 As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.
@@
 Both exhaustive ICTS and ICTS-m could easily be adapted to support one or more colors (teams) for each agent and goal while still guaranteeing optimality, in contrast to CBM \cite{ma2016} and its SIC adaptation \cite{baauw2021} which specifically use this property to plan single teams in polynomial time.
-Future research could study the multi-color MAPFM variant and the application of methods described in this work to this problem.
+Future research could study the multi-color MAPFM generalization and the application of methods described in this work to that problem.
 

### 2021-06-26 docs/paper.tex
Finished rework of exhaustive ICTS

@@
 	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,\text{bounded}}})$.
-	If $B_m < C^*_m$, only the root node will be generated to determine this so $\Delta_{m,\text{bounded}} = 0$.
+	If $B_m \leq C^*_m$, only the root node will be generated to determine this so $\Delta_{m,\text{bounded}} = 0$.
 	Using this, the number of ICT nodes searched in total becomes $\mathcal{O}(\sum_m k^{\Delta_{m,\text{bounded}}})$.
@@
 	\subsubsection{Approximate ordered enumeration}
-	In implementation matchings were enumerated using a product of goal permutation indices as described above so they are not enumerated in increasing order of root SIC.
-As a result, to achieve this ordering, matchings have to be exhaustively enumerated and stored in memory in order to be sorted.
-This requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
+	In the implementation of exhaustive ICTS, matchings are enumerated by taking the product of goal permutation indices as described above so they are not enumerated in increasing order of root SIC.
+To achieve this ordering, matchings would have to be exhaustively enumerated and stored in memory before being sorted.
+Storing all matchings requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
+This is why in implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory}.
+Algorithm \ref{pq-algo} outlines the procedure.
 
@@
 	%In the implementation of ordered enumeration as described above, matchings are not generated in increasing order of root SIC.
-As a result, to achieve this ordering, matchings have to be exhaustively enumerated and stored in memory in order to be sorted.
+As a result, to achieve this ordering, matchings have to be exhaustively enumerated and stored in memory to be sorted.
 This requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
@@
 	\end{algorithm}
-
-	This is why in implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory}.
-Algorithm \ref{pq-algo} outlines the procedure.
 

### 2021-06-26 docs/paper.tex
Updated future work to reflect new ideas

@@
 Let them be arranged in a configuration as depicted in Figure \ref{fig:path}.
-All four agents match the colour of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$.
+All four agents match the color of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$.
 The optimal solution however is $(1,3,3,3)$ with SIC $10$ numbering the agents clockwise, meaning that $\Delta = 6$.
@@
 	%\section{Future work}
-	A key idea for future research to look into is how to exploit the lower-bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55}.
+	A key idea for future research to look into is how to exploit the (inclusive) lower-bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55} or similar methods like the JVC algorithm \cite{jonker1987}.
 This lower-bound could be used in a branch-and-bound \cite{land1960} search of matchings.
-The most straightforward way would be to use an algorithm for MAPF at leaf nodes but algorithms for MAPFM could be used to solve (small) branches.
-Another possibility would be to use this bound to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound.
-Lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using a similar approach as \cite{baauw2021}.
+An algorithm for MAPF could be used at leaf nodes as in exhaustive ICTS; however, solving (small) branches as MAPFM instances using approaches other than branch-and-bound is also a direction to explore.
+To retain the benefits of ordered enumeration and to potentially allow for a higher degree of bounding, an optimized version \cite{miller1997} of Murty's algorithm \cite{murty1968} for ranking all matchings in increasing order of cost could be taken as a starting point for such a branch-and-bound approach.
+
+	%in which matchings are enumerated in increasing order of SIC
+
+	%for MAPFM could be used to solve (small) branches.
+
+	%The most straightforward way would be to use an algorithm for MAPF at leaf nodes but algorithms for MAPFM could be used to solve (small) branches.
+
+	%Specifically,
+
+	%By using the Hungarian Algorithm to determine
+
+	%The most straightforward way would be to use an algorithm for MAPF at leaf nodes but algorithms for MAPFM could be used to solve (small) branches.
+
+	Another possibility would be to use the lower-bound on solution SIC to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound.
+Lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using an approach similar to those described in \cite{baauw2021}.
 As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.
@@
 
-	Lastly, more experimentation is needed to reach definite conclusions about how simple child pruning compares to existing pruning techniques for ICTS, which could be done by reproducing the ICTS pruning technique experiments reported in \cite{sharon2011} extended with simple child pruning variants.
+	Lastly, more experimentation is needed to reach definite conclusions about how simple child pruning compares to existing pruning techniques for ICTS, which could be done by reproducing the ICTS pruning experiments reported in \cite{sharon2011} extended with simple child pruning variants.
+
 	%Given that simple pruning is somewhat cheap computationally, it might also be possible to prune the child generation using simple child pruning but still use enhanced pruning to decide whether to execute $k$-agent low-level search, combining the benefits of searching a smaller ICT and performing fewer $k$-agent searches.

### 2021-06-26 docs/paper.tex
Made spelling consistent with en_US

@@
 	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs.
-The second agent staying at node D after completing the path is also modelled in its MDD to ensure that the place remains blocked.
+The second agent staying at node D after completing the path is also modeled in its MDD to ensure that the place remains blocked.
 
@@
 In \ref{fig:mdds}, the $C$ node of $MDD_1$ would be removed as it cannot be unified with any node of $MDD_2$ at that level.
-		\item Repeated enhanced pruning: the enhanced pruning procedure is repeated until a fixpoint is reached, which is when no child node is removed from any of the agent MDDs in an iteration.
+		\item Repeated enhanced pruning: the enhanced pruning procedure is repeated until a fixed point is reached, which is when no child node is removed from any of the agent MDDs in an iteration.
 This was not used in this work.
@@
 Let them be arranged in a configuration as depicted in Figure \ref{fig:path}.
-All four agents match the color of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$.
+All four agents match the color of the center goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$.
 The optimal solution however is $(1,3,3,3)$ with SIC $10$ numbering the agents clockwise, meaning that $\Delta = 6$.
@@
 This comparison data originates in \cite{donszelmann2021}.
-The values compared are the fraction of instances solved, and the average runtime per instance.
-It should be noticed that in the latter, the recorded runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
+The values compared are the fraction of instances solved, and the average run time per instance.
+It should be noticed that in the latter, the recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
 	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
@@
 
-	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0Ghz with 8GiB of RAM.
+	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0GHz with 8GiB of RAM.
 All 200 maps were used for each setting.

### 2021-06-26 docs/paper.tex
Added spacing before all references

@@
 The properties of both classes of algorithms as well as ICTS more generally are discussed, followed by experiments in which a selection of algorithm variants is compared.
-Additionally, one exhaustive ICTS algorithm is compared to MAPFM algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014}.
+Additionally, one exhaustive ICTS algorithm is compared to MAPFM algorithms based on CBM \cite{ma2016}, M* \cite{wagner2011}, A*+OD+ID \cite{standley2010} and EPEA* \cite{goldenberg2014}.
 
@@
 	\label{icts}
-	In Increasing Cost Tree Search\cite{sharon2011}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC.
+	In Increasing Cost Tree Search \cite{sharon2011}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC.
 This is done by searching for cost vectors corresponding to increasing SIC at the top level and searching for non-conflicting path combinations (solutions) for each cost vector at the bottom level.
@@
 
-	All algorithms are implemented in Python 3.9 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine.
+	All algorithms are implemented in Python 3.9 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM \cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine.
 The comparison in this experiment is more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.
@@
 			\item ICTS with approximate sorted exhaustive matching (Exh+E+B+O)
-			\item A*+ID+OD with matching ID and sorted exhaustive matching\cite{bruin2021}
-			\item EPEA* with matching ID and sorted exhaustive matching\cite{jong2021}
+			\item A*+ID+OD with matching ID and sorted exhaustive matching \cite{bruin2021}
+			\item EPEA* with matching ID and sorted exhaustive matching \cite{jong2021}
 		\end{minipage}
@@
 		\begin{minipage}{0.40\linewidth}
-			\item M* with sorted exhaustive matching\cite{donszelmann2021}
-			\item CBM adapted to use SIC, using the successive shortest path algorithm (SSP) \cite{goldberg1987} as subroutine for solving teams\cite{baauw2021}.
+			\item M* with sorted exhaustive matching \cite{donszelmann2021}
+			\item CBM adapted to use SIC, using the successive shortest path algorithm (SSP) \cite{goldberg1987} as subroutine for solving teams \cite{baauw2021}.
 		\end{minipage}

### 2021-06-26 docs/paper.tex
Corrected some references, reordered bib file

@@
 In finding optimal solutions, one of two objectives is typically optimized: the makespan which is the cost of the longest path, or the Sum of Individual path Costs (SIC).
-Algorithms for optimally solving MAPF include Increasing Cost Tree Search \cite{sharon2011}, Conflict-based search \cite{sharon2015} and Branch-and-Cut-and-Price \cite{lam2019}.
+Algorithms for optimally solving MAPF include Increasing Cost Tree Search \cite{sharon2013}, Conflict-based search \cite{sharon2015} and Branch-and-Cut-and-Price \cite{lam2019}.
 
@@
 
-	This work presents two types of algorithms based on ICTS \cite{sharon2011} that optimally solve MAPFM, and is part of a study in which other algorithms in addition to ICTS were taken as starting points for MAPFM algorithms.
+	This work presents two types of algorithms based on ICTS \cite{sharon2013} that optimally solve MAPFM, and is part of a study in which other algorithms in addition to ICTS were taken as starting points for MAPFM algorithms.
 Those of the first type exhaustively enumerate matchings and use a variant of ICTS as a subroutine; those of the second type are based on an extension of ICTS itself to support matching, ICTS-m.
@@
 
-	%The successful application of CBS to solving TAPF begs the question: \textit{can other MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} serve as the basis for a TAPF algorithm?}
+	%The successful application of CBS to solving TAPF begs the question: \textit{can other MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2013} serve as the basis for a TAPF algorithm?}
 
@@
 	\label{icts}
-	In Increasing Cost Tree Search \cite{sharon2011}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC.
+	In Increasing Cost Tree Search \cite{sharon2013}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC.
 This is done by searching for cost vectors corresponding to increasing SIC at the top level and searching for non-conflicting path combinations (solutions) for each cost vector at the bottom level.
@@
 		\includegraphics[width=0.5\linewidth]{img/ict}
-		\caption{Increasing Cost Tree for three agents \cite{sharon2011}}
+		\caption{Increasing Cost Tree for three agents \cite{sharon2013}}
 		\label{fig:ict}
@@
 
-		\caption{Example of using ICTS to solve MAPF from \cite{sharon2011}}
+		\caption{Example of using ICTS to solve MAPF from \cite{sharon2013}}
 		\label{fig:bottom}
@@
 For agent $a_i$ with a target cost $c_i$ (from the cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents.
-Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations \cite{sharon2011}.
+Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations \cite{sharon2013}.
 
@@
 	\label{pruning}
-	In \cite{sharon2011}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work.
+	In \cite{sharon2013}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work.
 These methods rely on the fact that if no solution exists for any combination of $j$ out of $k$ agents with $j < k$, no solution exists for all $k$ agents.
@@
 	The full ICTS algorithm including a pruning step as described above is given by Algorithm \ref{icts-algo}.
-It is reproduced from \cite{sharon2011} for completeness.
-In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2011} is that this often outperforms other variants.
+It is reproduced from \cite{sharon2013} for completeness.
+In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2013} is that this often outperforms other variants.
 	\begin{algorithm}
@@
 	\begin{property}[Incompatibility with enhanced pruning]
-		Enhanced pruning combined with child pruning is suboptimal due to the \textit{cascading effect} described in \cite{sharon2011}.
+		Enhanced pruning combined with child pruning is suboptimal due to the \textit{cascading effect} described in \cite{sharon2013}.
 		\label{property:ec-incompat}
@@
 
-	Lastly, more experimentation is needed to reach definite conclusions about how simple child pruning compares to existing pruning techniques for ICTS, which could be done by reproducing the ICTS pruning experiments reported in \cite{sharon2011} extended with simple child pruning variants.
+	Lastly, more experimentation is needed to reach definite conclusions about how simple child pruning compares to existing pruning techniques for ICTS, which could be done by reproducing the ICTS pruning experiments reported in \cite{sharon2013} extended with simple child pruning variants.
 

### 2021-06-26 docs/paper.tex
Slightly modified use of references

@@
 	\subsubsection{ICTS with Independence Detection}
-	Like other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}.
+	Like other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley \cite{standley2010}.
 ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups.
@@
 	\label{pruning}
-	In \cite{sharon2013}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work.
+	In addition to ID, three pruning methods can be used to speed up ICTS \cite{sharon2013}, two of which are used in this work.
 These methods rely on the fact that if no solution exists for any combination of $j$ out of $k$ agents with $j < k$, no solution exists for all $k$ agents.
@@
 It is reproduced from \cite{sharon2013} for completeness.
-In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2013} is that this often outperforms other variants.
+In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as this often outperforms other variants \cite{sharon2013}.
 	\begin{algorithm}
@@
 	Another possibility would be to use the lower-bound on solution SIC to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound.
-Lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using an approach similar to those described in \cite{baauw2021}.
+The lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using an approach similar to those described in \cite{baauw2021}.
 As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.

### 2021-06-26 docs/paper.tex
Moved footnotes after '.'

@@
 Storing all matchings requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
-This is why in implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory}.
-Algorithm \ref{pq-algo} outlines the procedure.
+This is why in implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$.\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory} Algorithm \ref{pq-algo} outlines the procedure.
 
@@
 	\section{Reproducibility}
-	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository\footnote{\url{https://github.com/tbvanderwoude/icts-m}}.
-Included is also code for benchmarking different configurations of the ICTS solver and the maps that were used in the benchmarks reported above.
-The benchmarks and maps used in the relative comparison of MAPFM algorithms are also available in the code and data repository of \cite{donszelmann2021}\footnote{\url{https://github.com/jonay2000/research-project}}.
+	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository.\footnote{\url{https://github.com/tbvanderwoude/icts-m}} Included is also code for benchmarking different configurations of the ICTS solver and the maps that were used in the benchmarks reported above.
+The benchmarks and maps used in the relative comparison of MAPFM algorithms are also available in the code and data repository of \cite{donszelmann2021}.\footnote{\url{https://github.com/jonay2000/research-project}}
 

### 2021-06-26 docs/paper.tex
Wrote out small numbers

@@
 	In practice, joint MDDs are not explicitly constructed but instead, a depth-first search is used to search joint MDDs.
-This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD than is necessary for finding a solution, which can get rather large.
+This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD than is necessary for finding a solution, which can get large.
 	\subsubsection{ICTS with Independence Detection}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
-			\caption{25\% wall, 1 team}
+			\caption{25\% wall, one team}
 			\label{fig:i-25-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
-			\caption{25\% wall, 3 teams}
+			\caption{25\% wall, three teams}
 			\label{fig:i-25-3-p}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
-			\caption{75\% wall, 1 team}
+			\caption{75\% wall, one team}
 			\label{fig:i-75-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
-			\caption{75\% wall, 3 teams}
+			\caption{75\% wall, three teams}
 			\label{fig:i-75-3-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
-			\caption{25\% wall, 1 team}
+			\caption{25\% wall, one team}
 			\label{fig:r-25-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
-			\caption{25\% wall, 3 teams}
+			\caption{25\% wall, three teams}
 			\label{fig:r-25-3-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
-			\caption{75\% wall, 1 team}
+			\caption{75\% wall, one team}
 			\label{fig:r-75-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
-			\caption{75\% wall, 3 teams}
+			\caption{75\% wall, three teams}
 			\label{fig:r-75-3-p}
@@
 	\end{enumerate}
-	For each of these types, maps were generated with between $1$ and $25$ agents either all in the same team or partitioned into $3$ teams as evenly as possible.
+	For each of these types, maps were generated with between $1$ and $25$ agents either all in the same team or partitioned into three teams as evenly as possible.
 When solving the instances, for each combination of map-type and number of teams, the number of agents was increased until 0\% of instances could be solved within a timeout of 120s, at which point no more data was recorded for greater numbers of agents.
@@
 	Across scenarios, it is seen that typically exhaustive methods outperform ICTS-m algorithms (\ref{fig:i-probs}), with performance being more similar in the maps with 75\% wall.
-In particular on 75\% wall maps with 3 teams (\ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases, and some of these also manage to solve a small fraction of 75\% maps with 1 team that exhaustive methods cannot within the time-out (\ref{fig:i-75-1-p}).
+In particular on 75\% wall maps with three teams (\ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases, and some of these also manage to solve a small fraction of 75\% maps with one team that exhaustive methods cannot within the time-out (\ref{fig:i-75-1-p}).
 
@@
 This explains why no speedup is seen, as between ICTS-m and ICTS-m+ID.
-Another factor is that if all agents belong to the same team, it is somewhat unlikely that there will a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.
+Another factor is that if all agents belong to the same team, it is unlikely that there will a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.
 
@@
 The initial groups are here the teams, which is why in single team scenarios (Subfigures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}) matching ID has no effect.
-Hypothetically, matching ID could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and 3 teams (\ref{fig:r-75-3-p}).
+Hypothetically, matching ID could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and three teams (\ref{fig:r-75-3-p}).
 
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
-			\caption{25\% wall, 1 team}
+			\caption{25\% wall, one team}
 			\label{fig:i-25-1}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
-			\caption{25\% wall, 3 teams}
+			\caption{25\% wall, three teams}
 			\label{fig:i-25-3}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
-			\caption{75\% wall, 1 team}
+			\caption{75\% wall, one team}
 			\label{fig:i-75-1}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
-			\caption{75\% wall, 3 teams}
+			\caption{75\% wall, three teams}
 			\label{fig:i-75-3}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
-			\caption{25\% wall, 1 team}
+			\caption{25\% wall, one team}
 			\label{fig:r-25-1}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
-			\caption{25\% wall, 3 teams}
+			\caption{25\% wall, three teams}
 			\label{fig:r-25-3}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
-			\caption{75\% wall, 1 team}
+			\caption{75\% wall, one team}
 			\label{fig:r-75-1}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
-			\caption{75\% wall, 3 teams}
+			\caption{75\% wall, three teams}
 			\label{fig:r-75-3}

### 2021-06-27 docs/paper.tex
Worked on motivation of experiments

@@
 In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}.
-This comparison data originates in \cite{donszelmann2021}.
-The values compared are the fraction of instances solved, and the average run time per instance.
-It should be noticed that in the latter, the recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
+The data for the second experiment originates in \cite{donszelmann2021}.
+In both experiments, there are three variables: the number of agents, the fraction of blocked grid tiles and the number of teams.
+The values measured are the fraction of instances solved and the average run time per instance.
+In the latter, the recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), only the fraction of instances solved is used in the analysis of results.
 	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
@@
 This observation informed the creation of a map generator by the author of \cite{jong2021} with various parameters.
-Using this map generator, two types of 20x20 grids were generated:
+
+	%Using this generator, MAPFM instances situated on 20x20 grids with obstacles were generated by varying three variables: the number of agents; the fraction of blocked grid tiles; the number of teams.
+
+	Using this map generator, two types of 20x20 grids similar to the random maps in \cite{sturtevant2012} were generated:
+
 	\begin{enumerate}
@@
 When solving the instances, for each combination of map-type and number of teams, the number of agents was increased until 0\% of instances could be solved within a timeout of 120s, at which point no more data was recorded for greater numbers of agents.
+This approach is similar to the method described in \cite{stern2019}.
+
+	%In varying the number of obstacles and the number of agents, this setup is similar to those used in the MAPF literature \cite{stern2019}.
+
+	% In varying the number of obstacles and the number of agents, the comparison is similar to those used in the MAPF literature \cite{stern2019}.
+
+	%The purpose of
+
+	%Although the maps with one team are equivalent to anonymous MAPF instances
+
+	%While progressively increasing the number of agents is common in MAPF benchmarks
 

### 2021-06-27 docs/paper.tex
Removed 1 and 2 agents from three team plot, qualified statement about child pruning

@@
 In finding optimal solutions, one of two objectives is typically optimized: the makespan which is the cost of the longest path, or the Sum of Individual path Costs (SIC).
-Algorithms for optimally solving MAPF include Increasing Cost Tree Search \cite{sharon2013}, Conflict-based search \cite{sharon2015} and Branch-and-Cut-and-Price \cite{lam2019}.
+Algorithms for optimally solving MAPF include Increasing Cost Tree Search \cite{sharon2013}, Conflict-Based Search \cite{sharon2015} and Branch-and-Cut-and-Price \cite{lam2019}.
 
@@
 		\vspace{-10pt}
-		\caption{The two types of conflict (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
+		\caption{Two types of conflict between agents (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
 	\end{wrapfigure}
@@
 It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed.
-As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
+As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the limbs of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
 	%\subsubsection{Inverted MDD search}
@@
 For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was already a challenge computationally.
-This observation informed the creation of a map generator by the author of \cite{jong2021} with various parameters.
+This observation informed the creation of a map generator by the author of \cite{bruin2021} with various parameters.
 
@@
 	\end{enumerate}
-	For each of these types, maps were generated with between $1$ and $25$ agents either all in the same team or partitioned into three teams as evenly as possible.
+	For each of these types, instances were generated with between $1$ and $25$ agents either all in the same team or evenly partitioned into three teams.
+For each combination of map-type, number of teams and number of agents, 200 instances were generated.
+In scenarios with three teams, instances with $k < 3$ were not used.
 When solving the instances, for each combination of map-type and number of teams, the number of agents was increased until 0\% of instances could be solved within a timeout of 120s, at which point no more data was recorded for greater numbers of agents.
+This approach is similar to the method described in \cite{stern2019}.
+
+	% For each of these types, maps were generated with $K = 1$ and $K = 3$ and $k$ from $K$ to $25$.
+When solving the instances, for each combination of map-type and $K$, $k$ was increased until 0\% of instances could be solved within a timeout of 120s, at which point no more data was recorded for larger values of $k$.
 This approach is similar to the method described in \cite{stern2019}.
@@
 	Across scenarios, it is seen that typically exhaustive methods outperform ICTS-m algorithms (\ref{fig:i-probs}), with performance being more similar in the maps with 75\% wall.
-In particular on 75\% wall maps with three teams (\ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases, and some of these also manage to solve a small fraction of 75\% maps with one team that exhaustive methods cannot within the time-out (\ref{fig:i-75-1-p}).
+In particular on 75\% wall maps with three teams (\ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases, and some of these also manage to solve a small fraction of 75\% maps with one team that exhaustive methods can not within the time-out (\ref{fig:i-75-1-p}).
 
 	Between exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by \ref{fig:i-25-3-p}; almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E.
-Bounded search outperforms unbounded search as expected, given that the former does at most as much work as the latter and often less.
-Approximate ordering outperforming unordered enumeration is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}, and simply indicates that sorting works well in practice.
-Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this pruning method.
-In particular, as $k$ grows larger and in scenarios with more obstacles (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.
+Bounded search outperforms unbounded search as expected, given that the former does as much work as the latter and often less.
+Approximate ordering outperforming unordered enumeration is not as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}, and simply indicates that ordered enumeration works well in practice.
+Simple pruning with child pruning outperforms exhaustive pruning but this needs to be qualified.
+Comparing Exh+S+B+O with Exh+E+B+O shows that part of the difference can be explained by the use of simple pruning instead of enhanced pruning.
+Nonetheless, in instances with 75\% wall (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}) there appears to be a real benefit to searching a smaller ICT.
+Across ICTS-m variants, similar trends can be observed but the differences across pruning strategies are too slight to draw any conclusions from.
 As discussed in Section \ref{future}, more work is needed to determine if such an improvement is to be expected more generally.
@@
 This explains why no speedup is seen, as between ICTS-m and ICTS-m+ID.
-Another factor is that if all agents belong to the same team, it is unlikely that there will a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.
+Another factor is that if all agents belong to the same team, it is unlikely that there will be a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.
 
@@
 	CBM solving all problems with one team (Figure \ref{fig:r-25-1-p} and \ref{fig:r-75-1-p}), problems equivalent to anonymous MAPF instances, is at first surprising but follows directly from the definition of the CBM method.
-CBM solves single teams as anonymous MAPF instances in polynomial time, meaning that solving a single team reduces to a polynomial-time procedure, namely SSP.
+CBM solves single teams as anonymous MAPF instances in polynomial time, meaning that solving scenarios with a single team reduces to a polynomial-time procedure, namely SSP.
 Following the results reported in \cite{ma2016}, it is expected that as the number of teams approaches $k$, CBM performance will deteriorate and thus become more similar to the results for exhaustive methods here reported.
@@
 	%\section{Future work}
-	A key idea for future research to look into is how to exploit the (inclusive) lower-bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55} or similar methods like the JVC algorithm \cite{jonker1987}.
+	A key idea for future research to look into is how to exploit the lower-bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55} or similar methods like the JVC algorithm \cite{jonker1987}.
 This lower-bound could be used in a branch-and-bound \cite{land1960} search of matchings.

### 2021-06-27 docs/paper.tex
Fixed a few more typos

@@
 Approximate ordering outperforming unordered enumeration is not as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}, and simply indicates that ordered enumeration works well in practice.
-Simple pruning with child pruning outperforms exhaustive pruning but this needs to be qualified.
+Simple pruning with child pruning outperforms enhanced pruning but this needs to be qualified.
 Comparing Exh+S+B+O with Exh+E+B+O shows that part of the difference can be explained by the use of simple pruning instead of enhanced pruning.
@@
 Across ICTS-m variants, similar trends can be observed but the differences across pruning strategies are too slight to draw any conclusions from.
-As discussed in Section \ref{future}, more work is needed to determine if such an improvement is to be expected more generally.
+As discussed in Section \ref{future}, more work is needed to compare simple child pruning with other pruning methods for ICTS.
 

### 2021-06-27 docs/paper.tex
Improved captions, added missing particle

@@
 Those of the first type exhaustively enumerate matchings and use a variant of ICTS as a subroutine; those of the second type are based on an extension of ICTS itself to support matching, ICTS-m.
-The properties of both classes of algorithms as well as ICTS more generally are discussed, followed by experiments in which a selection of algorithm variants is compared.
+The properties of both classes of algorithms as well as ICTS more generally are discussed, followed by an experiment in which a selection of algorithm variants is compared.
 Additionally, one exhaustive ICTS algorithm is compared to MAPFM algorithms based on CBM \cite{ma2016}, M* \cite{wagner2011}, A*+OD+ID \cite{standley2010} and EPEA* \cite{goldenberg2014}.
@@
 		\vspace{-10pt}
-		\caption{Two types of conflict between agents (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
+		\caption{Two types of conflict between agents (from Fig. 1 in \cite{stern2019}).}\label{fig:conflicts}
 	\end{wrapfigure}
@@
 		\includegraphics[width=\linewidth]{img/symmetries}
-		\caption{Symmetric paths on a 4-connected grid \cite{harabor2010}}
+		\caption{Symmetric paths on a 4-connected grid \cite{harabor2010}.}
 		\label{fig:symmetries}
@@
 		\includegraphics[width=0.5\linewidth]{img/ict}
-		\caption{Increasing Cost Tree for three agents \cite{sharon2013}}
+		\caption{Increasing Cost Tree for three agents \cite{sharon2013}.}
 		\label{fig:ict}
@@
 			\includegraphics[width=\linewidth]{img/mdds1}
-			\caption{An example problem}
+			\caption{An example problem.}
 			\label{fig:problem}
@@
 			\includegraphics[width=\linewidth]{img/ict2}
-			\caption{The corresponding ICT with solution node $(3,2)$}
+			\caption{The corresponding ICT with solution node $(3,2)$.}
 			\label{fig:ict2}
@@
 			\includegraphics[width=\linewidth]{img/mdds}
-			\caption{MDDs for the agents are found and combined}
+			\caption{MDDs for the agents are found and combined.}
 			\label{fig:mdds}
@@
 
-		\caption{Example of using ICTS to solve MAPF from \cite{sharon2013}}
+		\caption{Example of using ICTS to solve MAPF from \cite{sharon2013}.}
 		\label{fig:bottom}
@@
 	\begin{wrapfigure}{R}{.35\textwidth}
+		\vspace{-10pt}
 		\centering
 		\includegraphics[width=\linewidth]{img/path}
-		\caption{Pathological case for ICTS-m}
+		\caption{Pathological case for ICTS-m. The squares represent agents and the flags represent goals.}
 		\label{fig:path}
+		\vspace{-10pt}
 	\end{wrapfigure}
@@
 			\includegraphics[width=\linewidth]{img/counter-example-ep-2}
-			\caption{Instance}
+			\caption{Counter-example instance.}
 			\label{fig:counter-example:a}
@@
 			\includegraphics[width=\linewidth]{img/counter-example-tree}
-			\caption{Pruned ICT that is traversed}
+			\caption{Pruned ICT that is traversed.}
 			\label{fig:counter-example:b}
 		\end{subfigure}
-		\caption{Counter-example for enhanced pruning combined with child pruning}
+		\caption{Counter-example for enhanced pruning combined with child pruning.
+If the black and green agent pair is considered last, an ICT is traversed while solving the instance that does not contain an optimal solution.}
 		\label{fig:counter-example}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
-			\caption{25\% wall, one team}
+			\caption{25\% wall, one team.}
 			\label{fig:i-25-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
-			\caption{25\% wall, three teams}
+			\caption{25\% wall, three teams.}
 			\label{fig:i-25-3-p}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
-			\caption{75\% wall, one team}
+			\caption{75\% wall, one team.}
 			\label{fig:i-75-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
-			\caption{75\% wall, three teams}
+			\caption{75\% wall, three teams.}
 			\label{fig:i-75-3-p}
 		\end{subfigure}
-		\caption{Fraction solved out of 50 maps by different ICTS-based algorithms}
+		\caption{Fraction solved out of 50 instances by different ICTS-based algorithms.}
 		\label{fig:i-probs}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
-			\caption{25\% wall, one team}
+			\caption{25\% wall, one team.}
 			\label{fig:r-25-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
-			\caption{25\% wall, three teams}
+			\caption{25\% wall, three teams.}
 			\label{fig:r-25-3-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
-			\caption{75\% wall, one team}
+			\caption{75\% wall, one team.}
 			\label{fig:r-75-1-p}
@@
 			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
-			\caption{75\% wall, three teams}
+			\caption{75\% wall, three teams.}
 			\label{fig:r-75-3-p}
 		\end{subfigure}
-		\caption{Fraction solved out of 200 maps by MAPFM algorithms}
+		\caption{Fraction solved out of 200 instances by MAPFM algorithms.}
 		\label{fig:r-probs}
@@
 	The first experiments were performed on a 2.2GHz Intel i7-8750H hexacore with 16GiB of memory.
-For each setting, a fixed subset of 50 out of 200 maps was used.
+For each setting, a fixed subset of 50 out of 200 instances was used.
 %Hyperthreading was used in experiments, but because agent-settings were solved in sequence as batches, it is expected that this has affected experimental outcomes equally.
@@
 	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0GHz with 8GiB of RAM.
-All 200 maps were used for each setting.
+All 200 instances were used for each setting.
 
@@
 
-	The benefit of using ID together with ordered enumeration is less clear.
+	The benefit of using ID together with ordered enumeration is not clear.
 Ordered enumeration with ID performs much better in \ref{fig:i-75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:i-25-1-p}).
-The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
+The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause of the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper-bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
 This explains why no speedup is seen, as between ICTS-m and ICTS-m+ID.
@@
 	\section{Reproducibility}
-	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository.\footnote{\url{https://github.com/tbvanderwoude/icts-m}} Included is also code for benchmarking different configurations of the ICTS solver and the maps that were used in the benchmarks reported above.
-The benchmarks and maps used in the relative comparison of MAPFM algorithms are also available in the code and data repository of \cite{donszelmann2021}.\footnote{\url{https://github.com/jonay2000/research-project}}
+	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository.\footnote{\url{https://github.com/tbvanderwoude/icts-m}} Included is also code for benchmarking different configurations of the ICTS solver and the instances that were used in the benchmarks reported above.
+The benchmarks and instances used in the relative comparison of MAPFM algorithms are also available in the code and data repository of \cite{donszelmann2021}.\footnote{\url{https://github.com/jonay2000/research-project}}
 
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
-			\caption{25\% wall, one team}
+			\caption{25\% wall, one team.}
 			\label{fig:i-25-1}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
-			\caption{25\% wall, three teams}
+			\caption{25\% wall, three teams.}
 			\label{fig:i-25-3}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
-			\caption{75\% wall, one team}
+			\caption{75\% wall, one team.}
 			\label{fig:i-75-1}
@@
 			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
-			\caption{75\% wall, three teams}
+			\caption{75\% wall, three teams.}
 			\label{fig:i-75-3}
 		\end{subfigure}
-		\caption{Average solving time of different ICTS-based algorithms with a timeout of 120s}
+		\caption{Average solving time of different ICTS-based algorithms with a timeout of 120s.}
 		\label{fig:i-times}
@@
 		\end{subfigure}
-		\caption{Average solving time of MAPFM algorithms with a timeout of 120s}
+		\caption{Average solving time of MAPFM algorithms with a timeout of 120s.}
 		\label{fig:r-times}

### 2021-06-27 docs/paper.tex
Improved description of matching generation

@@
 	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals.
-These matchings can be enumerated by indexing the $k_i!$ permutations of goals for each team $t_i$ as $1,\ldots,k_i!$.
-Using such indexing, each $e \in \{1,\ldots,k_1!\} \times \cdots \times \{1,\ldots,k_K!\}$ corresponds to a unique combination of permutations and can be mapped to a matching $m$ assuming some fixed ordering of agents within each team.
+These matchings can be enumerated by representing each permutation $p_i$ of goals for each team $t_i$ as an integer $n \in \{1,\ldots,k_i!\}$.
+Using such numbering, each $e \in \{1,\ldots,k_1!\} \times \cdots \times \{1,\ldots,k_K!\}$ corresponds to a unique combination of permutations and can be mapped to a matching $m$ assuming some fixed ordering of agents within each team.
 Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the MAPFM instance, with $C_m = \infty$ for infeasible matching $m$.
@@
 After solving each $m$ with solution cost $C_m$, let $B_{m+1} = \min(B_m,C_m)$.
-By successively updating this $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.
+By successively updating $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.
 With $C_m$ denoting the optimal SIC for matching $m$, this effort can be expressed as
@@
 Storing all matchings requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.
-This is why in implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$.\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory} Algorithm \ref{pq-algo} outlines the procedure.
+This is why in implementation, ordered enumeration is approximated using a priority queue that maintains a subset of matchings of a fixed size $M_{pq}$.\footnote{$M_{pq} = 10000$ was used in implementation but this could be much increased at the cost of memory.} Algorithm \ref{pq-algo} outlines the procedure.
 

### 2021-06-27 docs/paper.tex
Broke up problem definition into three parts, condensed formal MAPF statement

@@
 	In CBM, the Meta-Agent variant of CBS \cite{sharon2015} is used as a high-level search framework; in the low-level search, single teams are planned in polynomial time as constrained anonymous MAPF instances using a max-flow approach \cite{yu2013}.
-The experimental results reported in \cite{ma2016} indicate that CBM scales well as the number of agents and the sizes of teams increase; although in addition to grid instances with 10\% of tiles being blocked, Kiva \cite{wurman2007} instances are also solved, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios, such as those included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.
+The experimental results reported in \cite{ma2016} indicate that CBM scales well as the number of agents and the sizes of teams increase; although in addition to grid instances with 10\% of tiles being blocked, Kiva \cite{wurman2007} instances are also solved, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios such as the Moving AI maps \cite{sturtevant2012}.
 
@@
 
-	Multi-agent pathfinding with matching is a generalization of multi-agent pathfinding, the problem of finding paths for multiple agents without any conflicts. 
-	\subsection{Multi-agent pathfinding}
-
-	Formally, a MAPF instance can be described as follows.
+	A MAPF instance can be defined as follows.
 Let $G = (V,E)$ be an undirected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles.
@@
 Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$.
+To achieve this, agent $a_i$ may also wait ($\pi_i^t = \pi_i^{t+1}$) instead of moving to a grid neighbor.
 Given a solution $(\pi_1,\ldots,\pi_k)$, a vector of per-agent costs $(c_1,\ldots,c_k)$ can be found.
-For $\pi_i$, $c_i$ is defined as the time at which $a_i$ reaches $g_i$ for the last time and remains there, meaning that for $t \geq c_i$, $\pi_i^{t} = g_i$.
-One property of $c_i$ is that $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of $\pi^*_i$, the shortest path from $s_i$ to $g_i$ that can be computed using any optimal pathfinding algorithm.
-Using this terminology, the two common objectives for MAPF can be restated as follows:
+For $\pi_i$, $c_i$ is defined as the time at which $a_i$ reaches $g_i$ for the last time, meaning that for $t \geq c_i$, $\pi_i^{t} = g_i$.
+	For each $c_i$, $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of a shortest path from $s_i$ to $g_i$. 
+	\subsection{Objectives for MAPF}
+
+	Using the established terminology, the two common objectives for MAPF can be restated as follows:
 	\begin{itemize}
@@
 	\end{wrapfigure}
-
 	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.

### 2021-06-27 docs/paper.tex
Improved bit about waiting in paths

@@
 	A MAPF instance can be defined as follows.
-Let $G = (V,E)$ be an undirected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles.
+Let $G = (V,E)$ be an undirected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal move between two such tiles.
 Let there be $k$ agents $a_1,\ldots,a_k$ with starting locations $s_1,\ldots,s_k$ and goals $g_1,\ldots,g_k$.
@@
 Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$.
-To achieve this, agent $a_i$ may also wait ($\pi_i^t = \pi_i^{t+1}$) instead of moving to a grid neighbor.
+To achieve this, each agent $a_i$ may also wait ($\pi_i^t = \pi_i^{t+1}$) instead of moving to a grid neighbor.
 Given a solution $(\pi_1,\ldots,\pi_k)$, a vector of per-agent costs $(c_1,\ldots,c_k)$ can be found.

### 2021-06-27 docs/paper.tex
Subject of this paper -> Subject of this work

@@
 	\subsection{Extending MAPF with matching}
-	With the multi-agent pathfinding problem defined, the matching extension of MAPF (MAPFM) that is the subject of this paper can be described.
+	With the multi-agent pathfinding problem defined, the matching extension of MAPF (MAPFM) that is the subject of this work can be described.
 

### 2021-06-27 docs/paper.tex
Moved Figure 1 to top-right corner

@@
 	\date{
-		$^1$TU Delft\\
+		\normalsize{$^1$TU Delft\\
 		t.b.vanderwoude@student.tudelft.nl\\\{j.mulderij, m.m.deweerdt\}@tudelft.nl\\[2ex]
-		\today
+		}
 	}
@@
 Using MAPF in such applications requires pre-assignment of goals to agents using the Hungarian Algorithm \cite{kuhn55} or similar methods, but such approaches are suboptimal as the true cost of a given matching can only be found by solving the corresponding MAPF instance.
+	\begin{wrapfigure}[21]{r}{.25\textwidth}
+		\vspace{-10pt}
+		\begin{minipage}{\linewidth}
+			\centering\captionsetup[subfigure]{justification=centering}
+			\includegraphics[width=\linewidth]{img/vertex-conflict}
+			\subcaption{Vertex conflict}
+			\label{fig:conflictsa}\par\vfill
+			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
+			\subcaption{Edge conflict}
+			\label{fig:conflictsb}
+		\end{minipage}
+		\vspace{-10pt}
+		\caption{Two types of conflict between agents from \cite{stern2019}.}\label{fig:conflicts}
+	\end{wrapfigure}
 	Ma and Koenig \cite{ma2016} formulate the joint problem of finding the optimal makespan solution across all possible matchings as the combined target-assignment and pathfinding (TAPF) problem.
 They also present the Conflict-Based Min-Cost-Flow (CBM) algorithm for solving TAPF.
-
 	In CBM, the Meta-Agent variant of CBS \cite{sharon2015} is used as a high-level search framework; in the low-level search, single teams are planned in polynomial time as constrained anonymous MAPF instances using a max-flow approach \cite{yu2013}.
@@
 	\label{mapfm}
-	\begin{wrapfigure}[19]{r}{.25\textwidth}
-		\begin{minipage}{\linewidth}
-			\centering\captionsetup[subfigure]{justification=centering}
-			\includegraphics[width=\linewidth]{img/vertex-conflict}
-			\subcaption{Vertex conflict}
-			\label{fig:conflictsa}\par\vfill
-			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
-			\subcaption{Edge conflict}
-			\label{fig:conflictsb}
-		\end{minipage}
-		\vspace{-10pt}
-		\caption{Two types of conflict between agents (from Fig. 1 in \cite{stern2019}).}\label{fig:conflicts}
-	\end{wrapfigure}
 

### 2021-06-27 docs/paper.tex
Changed some last things in Section 1,2

@@
 		\vspace{-10pt}
-		\caption{Two types of conflict between agents from \cite{stern2019}.}\label{fig:conflicts}
+		\caption{Two types of conflicts between agents from \cite{stern2019}.}\label{fig:conflicts}
 	\end{wrapfigure}
@@
 Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$.
-To achieve this, each agent $a_i$ may also wait ($\pi_i^t = \pi_i^{t+1}$) instead of moving to a grid neighbor.
+To achieve this, each agent $a_i$ may wait during any time step $t$ so that $\pi_i^t = \pi_i^{t+1}$ instead of moving to a grid neighbor.
 Given a solution $(\pi_1,\ldots,\pi_k)$, a vector of per-agent costs $(c_1,\ldots,c_k)$ can be found.
@@
 	For each $c_i$, $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of a shortest path from $s_i$ to $g_i$.
+
+		 \begin{wrapfigure}[9]{r}{.35\textwidth}
+		\vspace{-10pt}
+		\centering
+		\includegraphics[width=\linewidth]{img/symmetries}
+		\caption{Symmetric paths on a 4-connected grid \cite{harabor2010}.}
+		\label{fig:symmetries}
+	\end{wrapfigure} 
 	\subsection{Objectives for MAPF}
@@
 	Using the established terminology, the two common objectives for MAPF can be restated as follows:
+
 	\begin{itemize}
@@
 
-	\begin{wrapfigure}[10]{R}{.35\textwidth}
-		\vspace{-10pt}
-		\centering
-		\includegraphics[width=\linewidth]{img/symmetries}
-		\caption{Symmetric paths on a 4-connected grid \cite{harabor2010}.}
-		\label{fig:symmetries}
-	\end{wrapfigure}
 	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$.
@@
 	\subsection{Extending MAPF with matching}
-	With the multi-agent pathfinding problem defined, the matching extension of MAPF (MAPFM) that is the subject of this work can be described.
+	With the multi-agent pathfinding problem defined, the MAPFM problem that is the subject of this work can be described as an extension of MAPF.
 
@@
 
-	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem that can be solved in polynomial time.
+	MAPFM, being TAPF with a SIC objective, generalizes both MAPF and anonymous MAPF \cite{ma2016}, which is MAPF allowing an agent to move to any goal, a problem that can be solved in polynomial time.
+
 	\section{Solving MAPF with Matching using ICTS} % Your contribution
 	\label{section:icts-matching}
-	In this section, taking ICTS for MAPF as a starting point, two methods to use ICTS for MAPFM are described.
+	In this section, taking ICTS for MAPF as a starting point, two methods to use ICTS to solve MAPFM are described.
 The first method relies on a reduction from MAPFM to repeated MAPF: an optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found.

### 2021-06-27 docs/paper.tex
Finished Section 3

@@
 	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs.
-The second agent staying at node D after completing the path is also modeled in its MDD to ensure that the place remains blocked.
+The second agent staying at node D after completing the path is also modeled in its MDD to ensure that the node remains blocked.
 
-	Subfigure \ref{fig:mdds} illustrates how two or more MDDs can be combined: first, the root nodes are joined; next, the product of the children of both roots is taken and checked for conflicts.
+	Figure \ref{fig:mdds} illustrates how two or more MDDs can be combined: first, the root nodes are joined; next, the product of the children of both roots is taken and checked for conflicts.
 In \ref{fig:mdds}, a vertex conflict occurs and therefore this joint child can be removed from the MDD.
@@
 ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups.
-If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case, ICTS, until no conflicts between groups occur.
+If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case ICTS, until no conflicts between groups occur.
 The goal of ID is to minimize $k'$, the size of the largest group that has to be planned.
@@
 	The full ICTS algorithm including a pruning step as described above is given by Algorithm \ref{icts-algo}.
-It is reproduced from \cite{sharon2013} for completeness.
 In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as this often outperforms other variants \cite{sharon2013}.
@@
 These matchings can be enumerated by representing each permutation $p_i$ of goals for each team $t_i$ as an integer $n \in \{1,\ldots,k_i!\}$.
-Using such numbering, each $e \in \{1,\ldots,k_1!\} \times \cdots \times \{1,\ldots,k_K!\}$ corresponds to a unique combination of permutations and can be mapped to a matching $m$ assuming some fixed ordering of agents within each team.
-Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the MAPFM instance, with $C_m = \infty$ for infeasible matching $m$.
+Using this representation, each $e \in \{1,\ldots,k_1!\} \times \cdots \times \{1,\ldots,k_K!\}$ corresponds to a unique combination of permutations and can be mapped to a matching represented as $m \in \{1,\ldots,M\}$.
+Assuming some fixed ordering of agents within each team, each matching $m$ can be translated to a MAPF instance with an optimal SIC cost $C_m$, with $C_m = \infty$ for $m$ corresponding to an unfeasible MAPF instance.
 In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ matchings to be solved or found to be infeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.
 	\subsubsection{Bounded search}
-	Once a solution is found for a matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched.
+	Once a solution is found for a matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper bound $B$ for the SIC of nodes that have to be searched.
 Formally, let $B_0 = \infty$ represent the initial SIC bound of the ICT search.
@@
 			\State $m\gets\text{Take matching with lowest SIC from PQ}$
-			\State $solution_m$ \text{with cost} $C_m\gets$\text{Solve $m$ with upper-bound }$B$ 
+			\State $solution_m$ \text{with cost} $C_m\gets$\text{Solve $m$ with upper bound }$B$ 
 			\If{\text{$C_m < B$}}
@@
 	Given a team $t_i$ of size $k_i$, for any agent $a_j^i$ there are $k_i$ costs $c_j(1),c_j(2),\ldots,c_j(k_i)$ for shortest paths from $s_j^i$ to each goal $g_k^i$.
-Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with path cost $c^*_j = c_j(m)$ such that $c_j(m) = \min_{n\in\{0,\ldots,k_i\}} c_j(n)$.
-Therefore, to guarantee optimality, this minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root.
+Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with path cost $c^*_j = c_j(m)$ such that $c_j(m) = \min_{n\in\{1,\ldots,k_i\}} c_j(n)$.
+Therefore, to guarantee optimality, the minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root.
 Intuitively, the sum of individual costs of this root is highly optimistic, particularly if the teams are large.
@@
 	\subsubsection{MDD generation for matching}
-	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals.
+	To generate MDDs for MAPFM, each agent has to consider not one goal but all matching goals.
 To do this, the MDD construction following the breadth-first search has to be changed: each goal becomes an endpoint from which paths to the start node are traced, resulting in an MDD with one start node and one or more terminal nodes.
@@
 	%[TODO: just focus on explaining why inverted MDD search was/could be used to solve this? Or just toss this out for lack of time/space. Why didn't I come up with this idea earlier...]
+	\newpage
 	\subsection{Optimizations}
@@
 	\begin{property}[Reduced upper bound]
-		In bounded exhaustive search, the sum of costs of groups not being merged can be subtracted from bound $B$ without losing optimality.
+		In bounded exhaustive search, the sum of costs of the groups not being merged can be subtracted from bound $B$ without losing optimality.
 		\label{property:id-upper}
@@
 	In the original ICTS formulation all $k$-children are generated in every case because pruning only controls skipping the low-level search, assumed to be the most expensive operation.
-However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented.
+However, in simple pruning, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented.
 This can be exploited by pruning the node's children that do not correspond to the conflicting agents, of which there are often just 2 or 3, drastically improving the (average) branching factor as $k$ increases.
@@
 When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (edge conflict) so $(0,9,5)$ and $(0,8,6)$ are generated.
-By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed.
-None of the nodes with SIC 16 in this ICT is a solution, meaning that enhanced pruning combined with child pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making this pruning strategy suboptimal.
+By repeating this order of enhanced pruning with child pruning, the ICT shown in Figure \ref{fig:counter-example:b} is traversed.
+None of the nodes with SIC 16 in this ICT is a solution, meaning that enhanced pruning combined with child pruning will return a suboptimal solution to the instance depicted in Figure \ref{fig:counter-example:a}, making this pruning strategy suboptimal.
 	\end{proof}
@@
 The values measured are the fraction of instances solved and the average run time per instance.
-In the latter, the recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), only the fraction of instances solved is used in the analysis of results.
+The recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), only the fraction of instances solved is used in the analysis of results.
 	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
@@
 Ordered enumeration with ID performs much better in \ref{fig:i-75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:i-25-1-p}).
-The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause of the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper-bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
+The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause of the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
 This explains why no speedup is seen, as between ICTS-m and ICTS-m+ID.
@@
 A*+ID+OD and EPEA* also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver.
-The initial groups are here the teams, which is why in single team scenarios (Subfigures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}) matching ID has no effect.
+The initial groups are here the teams, which is why in single team scenarios (Figures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}) matching ID has no effect.
 Hypothetically, matching ID could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and three teams (\ref{fig:r-75-3-p}).
@@
 	%\section{Future work}
-	A key idea for future research to look into is how to exploit the lower-bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55} or similar methods like the JVC algorithm \cite{jonker1987}.
-This lower-bound could be used in a branch-and-bound \cite{land1960} search of matchings.
+	A key idea for future research to look into is how to exploit the lower bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55} or similar methods like the JVC algorithm \cite{jonker1987}.
+This lower bound could be used in a branch-and-bound \cite{land1960} search of matchings.
 An algorithm for MAPF could be used at leaf nodes as in exhaustive ICTS; however, solving (small) branches as MAPFM instances using approaches other than branch-and-bound is also a direction to explore.
@@
 
-	Another possibility would be to use the lower-bound on solution SIC to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound.
-The lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using an approach similar to those described in \cite{baauw2021}.
+	Another possibility would be to use the lower bound on solution SIC to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound.
+The lower bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using an approach similar to those described in \cite{baauw2021}.
 As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.

### 2021-06-27 docs/paper.tex
Finished Section 4

@@
 	Because MAPFM lies on the fringe of pathfinding research, no standard benchmark exists.
-For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was already a challenge computationally.
+For MAPF, the Moving AI maps \cite{sturtevant2012} are often used and potentially a new standard benchmark for MAPFM could be defined based on these maps, similar to an existing standard benchmark for MAPF \cite{stern2019}; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was already a challenge computationally.
 This observation informed the creation of a map generator by the author of \cite{bruin2021} with various parameters.
@@
 
-	The first experiments were performed on a 2.2GHz Intel i7-8750H hexacore with 16GiB of memory.
+	The first experiment was performed on a 2.2GHz Intel i7-8750H hexacore with 16GiB of memory.
 For each setting, a fixed subset of 50 out of 200 instances was used.
@@
 
-	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0GHz with 8GiB of RAM.
+	The second experiment comparing different MAPFM algorithms was run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0GHz with 8GiB of RAM.
 All 200 instances were used for each setting.
@@
 	\subsection{Experiment 1: ICTS-based MAPFM algorithms}
-	To investigate the relative performance of various algorithms discussed in Section \ref{section:icts-matching}, a selection of both exhaustive and ICTS-m variants was made.
+	To investigate the relative performance of various algorithms discussed in Section \ref{section:icts-matching}, a selection of both exhaustive ICTS and ICTS-m variants was made.
 Their performance in terms of fraction of problems solved within a timeout of 120s is shown in Figure \ref{fig:i-probs}.
@@
 	\end{itemize}
-	Across scenarios, it is seen that typically exhaustive methods outperform ICTS-m algorithms (\ref{fig:i-probs}), with performance being more similar in the maps with 75\% wall.
-In particular on 75\% wall maps with three teams (\ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases, and some of these also manage to solve a small fraction of 75\% maps with one team that exhaustive methods can not within the time-out (\ref{fig:i-75-1-p}).
+	Across scenarios, it is seen that typically exhaustive methods outperform ICTS-m algorithms (Figure \ref{fig:i-probs}), with performance being more similar in the maps with 75\% wall.
+In particular on 75\% wall maps with three teams (Figure \ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases; additionally, some ICTS-m variants manage to solve a small fraction of 75\% maps with one team that exhaustive methods can not within the time-out (Figure \ref{fig:i-75-1-p}).
+This can be explained by the complexity of ICTS-m not being directly related to the number of matchings in contrast to the complexity of exhaustive ICTS.
 
-	Between exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by \ref{fig:i-25-3-p}; almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E.
+	Between exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by Figure \ref{fig:i-25-3-p}; almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E.
 Bounded search outperforms unbounded search as expected, given that the former does as much work as the latter and often less.
@@
 Comparing Exh+S+B+O with Exh+E+B+O shows that part of the difference can be explained by the use of simple pruning instead of enhanced pruning.
-Nonetheless, in instances with 75\% wall (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}) there appears to be a real benefit to searching a smaller ICT.
+Nonetheless, in instances with 75\% wall (Figures \ref{fig:i-75-1-p},\ref{fig:i-75-3-p}) there appears to be a real benefit to searching a smaller ICT.
 Across ICTS-m variants, similar trends can be observed but the differences across pruning strategies are too slight to draw any conclusions from.
-As discussed in Section \ref{future}, more work is needed to compare simple child pruning with other pruning methods for ICTS.
+As discussed in Section \ref{future}, more experiments are needed to adequately compare simple child pruning with other pruning methods for ICTS.
 
 	The benefit of using ID together with ordered enumeration is not clear.
-Ordered enumeration with ID performs much better in \ref{fig:i-75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:i-25-1-p}).
-The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause of the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
+Ordered enumeration with ID performs much better in a setting with more obstacles and more teams (Figure \ref{fig:i-75-3-p}), but ordered enumeration without ID on the other hand is superior in an open setting with a single team (Figure \ref{fig:i-25-1-p}).
+The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause of the slowdown observed once $M$ grows large (Figures \ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID.
 This explains why no speedup is seen, as between ICTS-m and ICTS-m+ID.
-Another factor is that if all agents belong to the same team, it is unlikely that there will be a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.
+Another factor is that if all agents belong to the same team, the benefit of using ID is reduced as agents from the same team planned independently often route to the same goal.
 
@@
 The initial groups are here the teams, which is why in single team scenarios (Figures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}) matching ID has no effect.
-Hypothetically, matching ID could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and three teams (\ref{fig:r-75-3-p}).
+Hypothetically, matching ID could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and three teams (Figure \ref{fig:r-75-3-p}).
 
-	CBM solving all problems with one team (Figure \ref{fig:r-25-1-p} and \ref{fig:r-75-1-p}), problems equivalent to anonymous MAPF instances, is at first surprising but follows directly from the definition of the CBM method.
+	CBM solving all problems with one team (Figures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}), problems equivalent to anonymous MAPF instances, is at first surprising but follows directly from the definition of the CBM method.
 CBM solves single teams as anonymous MAPF instances in polynomial time, meaning that solving scenarios with a single team reduces to a polynomial-time procedure, namely SSP.

### 2021-06-27 docs/paper.tex
Finished Section 5,6

@@
 		\centering
-		\begin{subfigure}{0.40\textwidth}
+		\begin{subfigure}{0.44\textwidth}
 			\centering
@@
 
-	CBM solving all problems with one team (Figures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}), problems equivalent to anonymous MAPF instances, is at first surprising but follows directly from the definition of the CBM method.
+	CBM solving all problems with one team (Figures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}) is at first surprising but follows directly from the definition of the CBM method.
 CBM solves single teams as anonymous MAPF instances in polynomial time, meaning that solving scenarios with a single team reduces to a polynomial-time procedure, namely SSP.
@@
 Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive ICTS algorithms consistently outperform the ICTS-m based algorithms.
-Compared to the SIC-adaptation of the CBM method \cite{baauw2021}, it was seen that exhaustive methods generally perform relatively poorly if there are fewer teams and fewer obstacles, while being competitive once teams grow smaller and maps become more constrained.
+Compared to the SIC-adaptation of the CBM method \cite{baauw2021}, it was seen that exhaustive methods perform relatively poorly if there are fewer teams and fewer obstacles, while being competitive once teams grow smaller and maps become more constrained.
 Delineating under which conditions exhaustive methods outperform CBM and vice versa is something for further research.
@@
 
-	A related observation is that the algorithms introduced in this work do not rely on the property of agents and goals having one color.
-Both exhaustive ICTS and ICTS-m could easily be adapted to support one or more colors (teams) for each agent and goal while still guaranteeing optimality, in contrast to CBM \cite{ma2016} and its SIC adaptation \cite{baauw2021} which specifically use this property to plan single teams in polynomial time.
+	A related observation is that the algorithms introduced in this work in their current form do not rely on the property of agents and goals having one color (team).
+Both exhaustive ICTS and ICTS-m could easily be adapted to support one or more colors for each agent and goal while still guaranteeing optimality, in contrast to CBM \cite{ma2016} and its SIC adaptation \cite{baauw2021} which specifically use this property to plan single teams in polynomial time.
 Future research could study the multi-color MAPFM generalization and the application of methods described in this work to that problem.

### 2021-06-27 docs/paper.tex
Clarified ICTS-m root definition

@@
 Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with path cost $c^*_j = c_j(m)$ such that $c_j(m) = \min_{n\in\{1,\ldots,k_i\}} c_j(n)$.
-Therefore, to guarantee optimality, the minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root.
+Therefore, to guarantee optimality, the minimal shortest path cost to any matching goal has to take the place of the shortest path cost from the original ICTS root.
 Intuitively, the sum of individual costs of this root is highly optimistic, particularly if the teams are large.

### 2021-06-27 docs/paper.tex
Corrected claim about multi-color MAPFM

@@
 
-	A related observation is that the algorithms introduced in this work in their current form do not rely on the property of agents and goals having one color (team).
-Both exhaustive ICTS and ICTS-m could easily be adapted to support one or more colors for each agent and goal while still guaranteeing optimality, in contrast to CBM \cite{ma2016} and its SIC adaptation \cite{baauw2021} which specifically use this property to plan single teams in polynomial time.
+	A related observation is that ICTS-m in its current form does not rely on the property of agents and goals having one color (team).
+It could easily be adapted to support one or more colors for each agent and goal while still guaranteeing optimality, in contrast to CBM \cite{ma2016} and its SIC adaptation \cite{baauw2021} which specifically use this property to plan single teams in polynomial time.
+A multi-color generalization of exhaustive ICTS would require a different matching enumeration method.
 Future research could study the multi-color MAPFM generalization and the application of methods described in this work to that problem.
